### 2017-02-09 doc/TetrahelixUntwist.tex
adding draft paper here

\documentclass[11pt]{article}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{gensymb}
\usepackage[affil-it]{authblk}
\usepackage[toc,page]{appendix}
\usepackage{pifont}
\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{float}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proofsketch}{Proof Sketech}
\usepackage{draftwatermark}

\SetWatermarkText{DRAFT}
\SetWatermarkScale{6}
\SetWatermarkLightness{0.95}

% \geometry{letter} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry

% See the ``Article customise'' template for come common customisations

\title{Untwisting the Tetrahelix (v0.4)}
\author{Robert L. Read
  \thanks{read.robert@gmail.com}
}
\affil{Founder, Public Invention, an educational non-profit.}

\date{\today}

%%% BEGIN DOCUMENT
\begin{document}

\maketitle

%% \tableofcontents

\begin{abstract}
  The Boerdijk--Coxeter helix (BC helix, or tetrahelix) is a face-to-face stack of regular tetrahedra whose outer vertices lie on helices.
  By allowing changes to edge lengths so that the tetrahedra are not regular, we can define a continuum of tetrahelices isomorphic to the
  BC helix of designable pitch or curvature, effectively ``untwisting'' the BC helix. We show that in the sense of minimal maximum
  difference in edge length, every tetrahelix has vertices equally spaced along the axis and at most three distinct edge lengths.
  In the case of a full untwisting to zero curvature, we describe a novel object, the
  \emph{equitetrabeam}.
  It has 3-fold symmetry about  axis, and chirality.  This tetrabeam and controllably twisted tetrahelices are
  interesting for structural engineering because they are inherently rigid space frames and trusses.
  A formula for the cartesian coordinates of the individual nodes of outer helices of the BC helix is given and
  unified with the formula for the equitetrabeam creating a class of edge-length optimal tetrahelices generated by single parameter.
  A further generalization is provided.
  Utility and use for truss/space frame design and robotics are discussed.
\end{abstract}

\section{Introduction}

The Boerdijk--Coxeter helix\cite{coxeter1985simplicial} (BC helix),
is a face-to-face stack of tetrahedra that winds about a straight axis.
The vertices of the tetrahedra
lie upon three
helices about the central axis.
The Tetrobot/Glussbot\cite{TetrobotBook} project
uses the regularity of this geometry to make a tentacle-like robot that can crawl like a slug or mollusc.
The Tetrobot concept
is to use mechanical members, called actuators, which can change their length, connected by special joints, called the Song-Kwon-Kim\cite{song2003spherical} or turret joint,
which allow many
members to come to a single point.
Such machines can follow purely regual mathematical models such as the Boerdijk–-Coxeter helix or the Octet Truss\cite{richard1961synergetic}.
Because architects, structural engineers, and robotocists are inspired by and follow such mathematical models but can build
structures and machines of differing or even dynamically changing length, it is useful to develop
the mathematics of structure formed from tetrahedra where we relax regularity. Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
a term now commonly used. In this paper we reserve BC helix to mean the purely regular structre and use \emph{tetrahelix} to refer
to any structure isomophic to a the BC helix, whether regular or not.

\begin{figure}[H] %float with two figures
  \centering
     \includegraphics[width=0.4\textwidth]{figures/Tetrahelix0.png}
     \caption{Regular Tetrahelix}
\end{figure}

BC helix does not rest on a plane in a simple way. It is convenient to be able to ``untwist'' it and form a tetrahelix space frame that
has a flat planar surface. By making length changes in a certain way, we can untwist a tetrahelix to form a \emph{tetrabeam} which
has planar faces and has, for example, an equilateral triangular profile.

\section{A User's Formulation of the BC Helix}

If you can choose member lengths, you can form a linear combination of the equitetrabream lengths and the completely regular
lengths of the tetrahelix, thereby choosing the torsion.  If you are designing a space frame, this is a static design choice,
in a robot, it is a dynamic choice that can be used to twist the robot and/or exert torsion on the environment.

Ideally we would have a simple formula for defining the nodes based on any torsion we choose.
Unfortunately, it is not obvious that a linear combination of lengths produces a simple formula.
It is a goal of this paper to relate these two approaches to generating a tetrahelix continuum.

Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and translation of the tetrahedra, showing the
rotation is:
\[
\theta = \arccos(-2/3) 
\]
and the translation:
\[
h_{bc} = 1/\sqrt{10}
\]

$\theta$ is approximately $131.8103149$ degrees.
The angle $\theta$ is the rotation of a \emph{each} tetrahedra.
That is, a yellow tetrahedron is rotated slightly more than a $1/3$ of a revolution to match the face of the red tetrahedra.
$3 \theta - 2\pi$ is the apparent rotation of $V_3$ relative to $V_0$.

From Robert Gray's site, repeating formula by H.S.M. Coxeter:
\[
V(n) =
\left [
  \begin{tabular}{c}
   $ r_{bc} \cos(n \theta $\\
   $ r_{bc} \sin(n \theta) $\\
   $ n h_{bc}  $
  \end{tabular}
  \right ],
\text{where:}
  \begin{tabular}{c}
 $ r_{bc} = \frac{3\sqrt{3}}{10} $\\
 $ h_{bc} = 1/\sqrt{10} $ \\
 $ \theta = \arccos(-2/3) $ \\
  \end{tabular}      
\]
where $n$ represents each integer numbered node in succession.

This formula defines a helix, but it is not any of the helices of the BC helix, but rather one that winds three times
as rapidly through all nodes. To a designer of tetrahelices, it is more natural to think of the three helices which
are visually apparent, that is, those three which are closely approximated by the by the outer edges or rails of the BC helix.

It is convenient to have a formula that gives us the nodes of just
each colored helix.
\[
H_{BCcolored}(n,c) = V(3n +c)
\]
where $c \in \{0,1,2\}$ specifies which of the rails is being computed.

Such a helix can be written:
\[
H_{BCcolored}(n,c) =
\left [
  \begin{tabular}{c}
   $ r_{bc}  \cos((3 \theta - 2 \pi)n + c  \theta $\\
   $ r_{bc} \sin((3 \theta - 2 \pi)n + c  \theta $\\
   $ (n + c/3) 3  h_{bc} $
  \end{tabular}
  \right ],
\text{where:}
  \begin{tabular}{c}
 $ r_{bc} = \frac{3\sqrt{3}}{10} $\\
 $ h_{bc} = 1/\sqrt{10} $ \\
 $ \theta = \arccos(-2/3) $ \\
  \end{tabular}      
  \]

In this formula, integral values of $n$ may be taken as a node number for one rail and used to compute its Cartesian
coordinates. Allowing $n$ to take non-integer values defines a continuous
helix in space which is close to the segmented polyline of the outer tetrahedra edges, and coincides with them at integer
values.
The parameter $c \in \{0,1,2\}$ specifies which of the rails is being computed.

The quantity $ (3 \theta - 2 \pi) \approx 35.43 \degree $, and is the angular shift between $V(n,color)$ and
$V(n+1,color)$. This quantity appears so often below that we call it the ``rail angle rho''. For the BC helix, $\rho_{bc} = (3 \theta - 2 \pi)$.

\begin{figure}[H]
  \label{railanglefig}
     \centering
     \includegraphics[width=0.7\textwidth]{figures/RailAngleGeometry.png}
     \caption{Rail Angle Geometry}
 \end{figure}

Since:
\[ \frac{2 \pi}{\rho_{bc}} \approx 10.16
\]
We can see that there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a single revolution.
The pitch of the Boerdijk--Coxeter helix of edge length $1$ is the length of three tetrahedra times this number:
\begin{align*}
  &= \frac{3 \cdot h_{bc} 2 \pi }{\rho_{bc}} \\
  &= \frac{3  \sqrt{\frac{2}{5}}  \pi}{\rho_{bc}} \\
  &\approx 9.6392 \\
\end{align*}
The pitch is less than the number of tetrahedra because the tetrahedra are not lined up perfectly.
It is a famous and interesting result that the pitch is irrational, a BC helix never has two tetrahedra
at precisely the same orientation around the $z$-axis. However, this is inconvenient to designers, who
might prefer a rational pitch. For example, a slight irregularity that led to a pitch of precisely 10 tetrahedra
in one revolution would allow an architect to design a column having a basis and a capital in the same relation to the tetrahedra
they touch.

A BC helix has the useful property that every member is precisely the same length. If we relax this, so that the tetrahedra it
comprises are not perfectly regular, then we can twist and curve the tetrahelix into a variety of shapes. This is useful to
the mechanical engineer or robotocist because the structure remains an inherently rigid, omni-triangulated space frame, which
may be expected to be at least somewhat mechanically strong.

 \begin{figure}[H]
     \centering
     \includegraphics[width=0.9\textwidth]{figures/TetrahelixColoringDiagram.png}
     \caption{Coloring of an (untwisted) Tetrabeam}
 \end{figure}

 \subsection{Recent Notes}

 Note that from the point of view of a single edge, we are on a slanted cylinder, when $\rho \neq 0$.
 This means for its point of view a cross section is an ellipse. So we have to be very careful in
 comparing lengths of edges relative to the tetrahedron, because a change in position along the edge
 changes the length of a line, but in a complicated way depending on where it is relative to the ellipse.

 \subsection{Very bad attempts to prove things}

  Note: This is a new, simpler proof attempt.
  \begin{theorem}
    Suppose that all edge vertices are on one of three helices of the same positive pitch and the same radius about the $z$ axis differing by $120\degree$ about $z$.
    However, we do not assume that the three helices are equidistant.
    Without loss of generality, consider $A$ and $B$ to be to be on the same axis, $C$ to be on a second axis, and $D$ to be on the final.
    Without loss of generality assume: $A.z \leq C.z \leq D.z \leq B.z$.
    Then the minimum maximum difference between any two nodes is acheived when
    $ \overline{\rm AD} =  \overline{\rm BC} $ and $ \overline{\rm AC} =  \overline{\rm CD}, \overline{\rm DB} $.
  \end{theorem}

  \begin{proof}
\begin{align*}
  O  &= C.z - A.z \\
  G &= D.z - C.z \\
  P &=  B.z - D.z
\end{align*}
First we show any configuration in which $O \neq P$ implies a solution at least as good in terms of minimax difference in which $O = P$.
Let 
\begin{align*}
  \frac{O' + P'}{2} &= \frac{1}{2} + \delta
\end{align*}
Then any configuration $O' - \delta/2, P' - \delta/2$ has a minimax at least as good as $O',P'$, because, if $\delta > 0$, then
$\overline{\rm A'C'}$ is the longest segment of the four $\overline{\rm A'C'}, \overline{\rm A'D'}, \overline{\rm B'C'} =  \overline{\rm B'D'} $.
$\overline{\rm B'D'}$ is the shortest of this set.
\begin{align*}
  \overline{\rm A'D'} &> \overline{\rm B'C'}  \\
   \overline{\rm B'D'} &< \overline{\rm A'C'}  \\  
   \overline{\rm AB} &=   \overline{\rm A'B'}   \\
   \overline{\rm CD} &=   \overline{\rm C'D'}   \\
  \\
   \overline{\rm AC} &=   \overline{\rm BD}   \\
   \overline{\rm AD} &=   \overline{\rm BC}   \\
  \\  
   \overline{\rm AC} &<  \overline{\rm A'C'} \\
   \overline{\rm AD} &< \overline{\rm A'D'}   \\
   \overline{\rm BC} &>  \overline{\rm B'C'} \\
   \overline{\rm BD} &> \overline{\rm B'D'}   \\
\end{align*}
So the maximum $\overline{\rm AD}$ is at most the old maximum. The minimum $\overline{\rm AC}$ is at least the old minimum of our set of four.
If the maximum or minimum of a subset is not worsened, the maximum or minimum of the total set cannot be worsened. Therefore $O' - \delta/2, P' - \delta/2$
is no worse than $O', P'$. So any mimimax solution is no better than one in which $(O + P)/2 = 1/2$, or $O = P$.

Suppose $\overline{\rm C'D'}$ is the shortest edge. Increasing $G$ thereby improves our mimimum, up until the next shortest edge length, $\overline{\rm AC}$.
This may increase $\overline{\rm BC}$ and $\overline{\rm AD}$, but more slowly than $\overline{\rm C'D'}$ is being increased, until  $\overline{\rm C'D'} =
\overline{\rm AC}$.

  Any tetrahelix $ABCD$ of edge lengths $AD = u, AB = BC = CD = v , AC = BD = w$, where $1 \leq u \leq v$ is mimimax optimal.
  Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ mid-length edges connected to the rail and $2$ long edges connected to the rail.
  The edge opposite of the rail edge is a mid-length edge.
    \end{proof}

\begin{theorem}
  Suppose that all edge vertices are on helices about the same axis and that $R,B,Y$ and are $120\degree$ from each other from that axis.
  Then a minimax positioning occurs when at least 3 non-rail edge classes are the longest length and equivalent.
 \end{theorem}
\begin{proof}
Note: It is not perfectly clear this proof is valid for extreme radii which are either very short or very large.

   Suppose that all edge vertices are on helices about the same axis and that $R,B,Y$ and are $120\degree$ from each other from that axis.

  If there is a unique longest distance, it touches two rails. Moving those rails closer together infinitesimally decreases the longest length and
  therefore the minimax.

  Suppose there are exactly two longest edges of equal length. By the pigeonhole principle, these edges must share one rail and touch the other two.
  If moving the shared rail in one direction decreases both edge lengths, doing so infinitesimally decreases the minimax.

  Therefore there must be at least three longest edges of equal length, each of which touches two rails.
  \end{proof}

\begin{theorem}
  Any minimax-optimal tetrahelix at most precisely three classes of edge lengths.
\end{theorem}

\begin{proof}
  Every vertex is connected to each rail by two edges. These two edges cannot be of the same length, unless all six edge classes are the same
  length. If all six are the same length, $Y_0$ and $B_0$ lie on the same $z$ value, but then $green_o$ is much longer than $purple_e = purple_o = orange_e = organge_o$,
  making it a unique longest length, a contradiciton. Therefore the odd and even lengths in each color class are different. Therfore there is a second,
  shorter length, which occurs once in each color class. Taken with the rail edge length of $1$, this makes precisely three classes of equivalent
  edge lengths for any minimax-optimal helix.
\end{proof}

\begin{theorem}
  \label{tetrahelixoptimality}
  Any one tetrahedron in a minimax-optimal tetrahelix $ABCD$ of edge lengths $AD = 1, AB = BC = CD = u , AC = BD = v$, where $1 \leq u \leq v$.
  Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ mid-length edges connected to the rail and $2$ long edges connected to the rail.
  The edge opposite of the rail edge is a mid-length edge.
\end{theorem}

\begin{proof}
The edge opposite of the rail edge is a mid-length edge because between any two rails the edges alteranate mid-length and long.
\end{proof}

\begin{corollary}
  \label{eventhirds}
  Any minimax optimal tetrahelix has its colored edges spaced at 1/3 the height of
  a tetrahedra along the z-axis, where the height is the z-distance of the rail edge.
  \end{corollary}

\begin{proof}
  Let the variables $O,G,P$ represent the z-axis distance from the
  $R_0$ to $Y_0$, $Y_0$ to $B_0$, and
  $B_0$ to $R_0$ respectively. Then $O+G+P = h$. But $O=G=P$, since each edge between
  their nodes spans two rails of the same distance with an edge of the same length,
  so that the $z$-distance between each node is the same. So $O=G=P=h/3$.
\end{proof}

Note that based on Theorems \ref{tetrahelixoptimality} and \ref{eventhirds}, we are justified in classifying edge lengths as \emph{rail},\emph{mid-length}, or
\emph{long}. The mid-length edges are the edges between closest on the $z$-axis, and the long edges are those that hop over a vertex.

Every optimal tetrahelix has vertices lying on helices expressible in the form:
\[
V_{optimal}(n,c) =
\left [
  \begin{tabular}{c}
   $ r \cos(n \alpha +  c 2 \pi /3)$\\
   $ r \sin(n \alpha +  c 2 \pi /3) $\\
   $ \frac{d(n +c / 3)}{3}   $
  \end{tabular}
\right ]
\]
where we have not yet investigated in the general case the relationships beteween $\alpha$, $r$, and $d$ in this formulation.
However, we understand that when $\alpha = 0$, the helices are degenerate, having curvature of $0$, and
we have the equitetrabeam.

\section{Adding an Untwisting Parameter}

We observe that it by thinking of the straight lines of the Equitetrabeam as a degenerate helix of zero curvature,
it should be possible to define a smoothly varying continuum between the Boerdijk--Coxeter helix and the Equitetrabeam and every
curvature and torsion between the two.

This formulation $V(n,c)$ above is valuable, but obscures the essentially fact that the red, yellow, and blue helices distributed
about the central $z$ axis $120\degree$ from each other.
In order to rewrite this expression with an explicit rotation of $2\pi/3$, we expand 
the expression and seek to isolate the term $c2\pi/3$.
\begin{align*}
  \rho_{bc} n + c \theta  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
    (3 \theta - 2 \pi)n + (c/3)  (\theta /3)  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
  (3 \theta - 2 \pi)n + (c/ 3) (3 \theta - 2 \pi  + 2 \pi) &=  \text{\{associate...\}} \\
  (3 \theta - 2 \pi)n + (c/ 3) ((3 \theta - 2 \pi)  + 2 \pi) &=  \text{\{distribute...\}} \\  
  (3 \theta - 2 \pi)n + (c / 3) (3 \theta - 2 \pi)  + c 2 \pi /3 &=  \text{\{definition of $\rho_{bc}$...\}} \\
  \rho_{bc} n + (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{\{collect like factors...\}} \\  
  \rho_{bc} (n + c/3)  + c 2 \pi /3  \\
\end{align*}
Now the the term on the left is the only one that depends on the scalar $n$. We use this to a create
a new formulation $H_{BCsymmetric}(n,c) = H_{colored}(n,c)$

The expression $n+c/3$ will now occur so often that we call it the ``c($\kappa$)olored number'' and we use the variable $\kappa$ to represent it: $\kappa = n+c/3$.
Recall that $c \in \{0,1,2\}$, but $n$ and $\kappa$ are are continuous (rational or real-valued.)

\[
H_{BCsymmmetric}(n,c) =
\left [
  \begin{tabular}{c}
   $ r  \cos(\rho_{bc} \kappa  + c 2 \pi /3) $\\
   $ r  \sin(\rho_{bc} \kappa  + c 2 \pi /3) $\\
   $ \kappa 3  d $
  \end{tabular}
  \right ],
\text{where:}
  \begin{tabular}{c}
 $\kappa = n + c/3$ \\
    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
   $ \theta = \arccos(-2/3) $
  \end{tabular}      
\]

We seek to unify this with degenerate helix formula for the equitetrabeam:
\[
H_{etb}(n,c) =
\left [
  \begin{tabular}{c}
   $ r_{etb}  \cos( 0 \cdot \kappa  + c 2 \pi /3) $\\
   $ r_{etb}  \sin( 0 \cdot \kappa  + c 2 \pi /3) $\\
   $ \kappa d_{etb} $
  \end{tabular}
\right ],
\text{where:}
  \begin{tabular}{c}
 $\kappa = n + c/3$ \\
    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
   $ \theta = \arccos(-2/3) $
  \end{tabular}      
\]
where $ r_{etb} = 1/\sqrt(3)$, $d_{etb} = 1/3$,

Now basic components of the helix, which are the radius $r$, the rate of rotation, and the rate of
axial growth can all be linearly interpolated with a parameter $\lambda$ between their high values (for the BC helix)
and low values (for the equitetrabeam):

\begin{align*}
r_{\lambda}  &=  \lambda (3 \sqrt(3) / 10 - 1/\sqrt(3)) +  1/\sqrt(3) \\
d_{\lambda} &=   \lambda (3 / \sqrt(10) - 1)+ 1 \\
\phi_{\lambda} &=  \lambda \rho_{bc}  + 0\\
\end{align*}
to create a formula that generates a continuum of tetrahedral structures:

\[
H_{continuum}(n,c,\lambda) =
\left [
  \begin{tabular}{c}
   $ r_{\lambda} \cos(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
   $ r_{\lambda}  \sin(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
   $ d_{\lambda} \kappa $
  \end{tabular}
  \right ],
\text{where:}
  \begin{tabular}{c}
    $\kappa = n + c/3$ \\
    $ \phi_{\lambda} =  \lambda \rho_{bc}  + 0 $\\
    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
   $ \theta = \arccos(-2/3) $
  \end{tabular}      
\]
A value of $\lambda = 0$ generates the equitetrabeam, and $\lambda = 1$ generates the Boerdijk--Coxeter helix, and every
value $\lambda \in [0,1]$ generates an attractive structure which if physically realized is an inherently rigid structure
with member lengths of no greater disparity than $21\%$.
In the sense of structural engineering, it would be a relatively strong space frame.

Furthermore, this formula allows one to design the pitch (in edge length units) as a function of $\lambda$ of the helix (along one rail)
where $\lambda \neq 0$:
\[
p(\lambda) = 2 \pi  \cdot \frac{((3/\sqrt(10) -1) \lambda +1)}{ \lambda  \rho_{bc} }
\]

\section{Parametrizing Tetrahelices via Rail Angle}

Although the $\lambda$ parametrization presented above is a sensible one
because it unifies the BC-helix with the equitetrabeam, it is over-specific,
in that it makes a specific choice as to the relationship of the height $h$
to the radius $r$ which is somewhat arbitrary.

We seek a formula to generate optimal tetrahelices that accepts a
parameter that allows us to choose the tetrahelix conveniently. The
pitch of the helix is an obious choice, but is not defined when the
curvature is $0$, and important special case. The radius or the axial
distance between two nodes on the same rail are obvious choices, but
perhaps the clearest choice is to build formula that takes as its
input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
formed in the X,Y plane $\angle R_i O R_{i+1}$ projecting out the $z$
axis and sighting along the positive $z$ axis. In other words, $\rho$
controls how far a rail edge of a tetrahelix deviates from being
parallel with the axis, or the ``twistiness'' of tetrahelix. Ideally
we will treat a positive angle as creating a clockwise tetrahelix and
a negative as creating a counter-clockwise helices.

Please refer back to Figure \ref{railanglefig}.

 These quantities are related by the expression:

\begin{align*}
  1^2 &= d^2 + (2 r \sin{ \rho / 2})^2 \\
  1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 
\end{align*}

Checking the important special case of the BC helix, we find that this equation
indeed holds true (treathing $d$ in this equation as $3 h_{bc}$ as defined by
Gray and Coxeter, where they are using it for the axial height from one node to
the next of a different color, but we use it to mean distance for the same color.

The rail angle $\rho$ also has the meaning that $2 \pi / \rho$ is the number of
tetraheda in a full revolution of the helix.

In choosing $\rho$, one greatly constrains $r$ and $h$, but does not completely
determine both of them together. In the formulation below we assume that
the choice of $d_{\rho}$ is more convenient than choosing the radius,
but that is somewhat arbitrary.

Rewriting our formulation in terms of $\rho$:
\[
H_{general}(n,c,\rho,d_{\rho},r_{\rho}) =
\left [
  \begin{tabular}{c}
   $ r_{\rho} \cos(\frac{\rho \kappa}{2\pi} + c 2 \pi /3) $\\
   $ r_{\rho}  \sin(\frac{\rho \kappa}{2\pi} + c 2 \pi /3) $\\
   $ d_{\rho} \kappa $
  \end{tabular}
  \right ],
\text{where:}
\begin{tabular}{c}
  $   1 = d_{\rho}^2 + 4 r_{\rho}^2 (\sin{ \rho / 2})^2 $ \\
    $\kappa = n + c/3$ \\
  \end{tabular}      
\]

$H_{general}$ generalizes $H_{continuum}$, but forces the user to select an $d_{\rho}$
which has a sensible radius, so it may be less convenient.

Note that when $\rho = 0$ then $h_{\rho} = 1$, but $r_{\rho}$ is not determined.

\begin{theorem}
  \label{generalformulaoptimal}
  The tetrahelices generated by $H_{general}$ are optimal in terms of minimum maximum member length, minimum total member length, and minimum
  sum of squared lengths.
\end{theorem}

\begin{proof}
  This requires poof.
\end{proof}

By Theoerm \ref{eventhirds}, we can compute the (at most) three edge-lengths of an optimal
tetrahelix by (where $dist$ is the cartesian distance function):
\begin{align*}
  \text{rail} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n+1,c,\rho,d_{\rho})) = 1 \\
  \text{mid-length} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}))  \\
  \text{long} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+2,\rho,d_{\rho}))  \\  
\end{align*}
Where are invarinat for all $n$ and $c$.

\section{The Equitetrabeam}

Just as $H_{general}$ constructs the BC helix (with careful and non-obvious choices of parameters) which is an important
special case due to its regularity, it constructs an additional special (degenerate) case when the rail angle $\rho = 0$
and $h = 1$ (the edgelength), which we call the \emph{equitetrabeam}.

Note: place here a computation of the length classes, and a means of computing from $H_{general}$.
We should have a close-form expression for the short, mid-length, and long classes.

By theorem \ref{generalformulaoptimal}, the equitetrabeam is optimal in terms of its lengths.

\begin{theorem}
  The equitetrabeam is also optimal under the metric of the total length of all members 
  for an equilateral tetrabream isomorphic to the Boerdijk--Coxeter helix.
\end{theorem}

\begin{proof}
  Summing together all lengths:
  \begin{align*}
  sum &= orange_e + orange_o + purple_e + purple_e + purple_o + green_e + green_o \\    
  &= \sqrt{1 + Y^2} + \sqrt{1 + (1-Y)^2} + \sqrt{1 + B^2} + \sqrt{1+ (1-B)^2} + \\
  & \sqrt{1 + (B - Y)^2} +  \sqrt{1 + ((1+Y) - B)^2} \\
  \end{align*}

  Wolfram Alpha, evaluating this numerically, gives the same minima:

  \begin{tabular}{c}    
$  min\{\sqrt(1 + Y^2) + \sqrt{1 + (1 - Y)^2} + \sqrt{1 + B^2} + \sqrt{1 + (1 - B)^2} + $\\
    $  \sqrt{1 + (B - Y)^2} + \sqrt{1 + ((1 + Y) - B)^2}\} $ \\
    $ \approx 6.76783 \text{at } (B, Y) \approx (0.666667, 0.333333) $
  \end{tabular}

\end{proof}

The equitetrabeam has chirality.

\section{Utility for Robotics}

Trusses and space frames remain an important design field in mechanical and structural engineering\cite{mikulas1985sequentially},
including deployable and moving trusses\cite{claypool2012readily}.

Starting twenty years ago, Sanderson\cite{sanderson1996modular}, Hamlin,\cite{TetrobotBook}, and others including Lee\cite{lee2002dynamic}
created a style of robotics based on changing the lengths of members
joined at the center of a joint, thereby creating a connection to pure geometry. More recently NASA has experimented with
tensegrities\cite{NTRT}, a different point in the same design spectrum. These fields create a need to explore the notion of
geometries changing over time, not generally considered directly by pure geometry.

As suggested by Buckminster Fuller, the most convenient geometries to consider are those that have regular member
lengths, in order to facilitate the inexpensive manufacture and construction of the robot.  In a plane, the octet truss
is such a geometry, but in a line, the Boerdijk--Coxeter helix is a regular structure.

However, a robot must move, and so it is interesting to consider the transmutations of these geometries, which was in
fact the motivation for creating the equitetrabream.

\begin{theorem}

  Using the six member classes defined by the non-primary colors, it is possible to smoothly twist and untwist a tetrahelix by
  using a linear combination of lengths.

\end{theorem}

\begin{proof}
  Proof by our computer program that does this by forming a linear interpolation of links.
\end{proof}

\begin{figure}[H] %float with two figures
  \centering
     \includegraphics[width=0.4\textwidth]{figures/Tetrahelix1.png}
     \caption{2/3rd Twisted Tetrahelix}
     \includegraphics[width=0.4\textwidth]{figures/Tetrahelix2.png}
     \caption{1/3rd Twisted, 2/3rd Untwisted Tetrahelix}
     \includegraphics[width=0.4\textwidth]{figures/Tetrahelix3.png}
     \caption{The Equitetrabream: Fully Untwisted Tetrahelix}
\end{figure}

\section{Contact and Getting Involved}

The Gluss Project \url{http://pubinv.github.io/gluss/}
is a free-libre, open-source research, hardware, and software project that welcomes volunteers.
It is our goal to organize projects for the benefit of all humanity without seeking profit or intellectual property.
To assist, contact \href{mailto:read.robert@gmail.com}{$<$read.robert@gmail.com$>$}.

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,gluss}

\end{document}

TODO:

Review and continue editing, being careful to introduce concepts in the correct order.

The most important thing to do here is to start a github project that includes javascript
to copute this stuff; the second most important thing is to use Three.js to create a
nice visual representation of all of this without getting the physics engine involved.

Check formula to make sure lengths are what we previously created for the Equitetrabeam.

First, plug values into Equitetrabeam.

Check distances.

Also, update diagam.

On Rail diagram, add a second tetrahedron, and a second rho.

  Investigate Lambda outsidde the range [0,1].  Does -lambda reverse the chirality?
  Does lambda > 1 increase twist nicely?

  Create alternate coloring inside my system to render the tetrabot better.
  Add shadows better.

  Conjecture: There is a sense in which every tetrahelix has vertices
  evenly space along the axis of motion in order to have optimal lengths.

  Argument sketch: Follow current argument sketch, but compute lengths from formula
  for helices, using symmetry argument whereever possible.

  Create separate Github project having javascript code as function for computing all.

  Make YouTube video.

### 2017-02-09 doc/TetrahelixUntwist.tex
lambda continuum working

@@
 \title{Untwisting the Tetrahelix (v0.4)}
-\author{Robert L. Read
-  \thanks{read.robert@gmail.com}
+\author{Robert L. Read \texttt{read.robert@gmail.com} \and
+  Robert Gatliff \texttt{robert@toubat.org}
 }
-\affil{Founder, Public Invention, an educational non-profit.}
 
@@
 special case due to its regularity, it constructs an additional special (degenerate) case when the rail angle $\rho = 0$
-and $h = 1$ (the edgelength), which we call the \emph{equitetrabeam}.
+and $d = 1$ (the edgelength), where the cross sectional area is an equilateral triangle of unchanging orientation.
+We call this the \emph{equitetrabeam}.
 
-Note: place here a computation of the length classes, and a means of computing from $H_{general}$.
-We should have a close-form expression for the short, mid-length, and long classes.
+However, choosing $d = 1$ and $\rho = 0$ does fix the radius. We would like to choose the radius so that the
+minimax difference between the lengths is as small as possible.
 
-By theorem \ref{generalformulaoptimal}, the equitetrabeam is optimal in terms of its lengths.
+When $\rho = 0$, our formulae for distances are particular simple. Let $a$ be the length of the equilateral triangle
+forming the beam cross section. Then by geometry $r = a \sqrt(3)$.
+\begin{align*}
+  \text{rail} &=  1 \\
+  \text{one-hop} &= \sqrt{\frac{1}{3}^2 + (\frac{a}{\sqrt{3}})^2 + (a/2)^2}\\
+\text{one-hop}  &= \sqrt{\frac{1}{9} + \frac{7 a^2}{12}} \\
+    \text{two-hops} &= \sqrt{\frac{2}{3}^2 + (\frac{a}{\sqrt{3}})^2 + (a/2)^2}  \\
+\text{two-hops}    &= \sqrt{\frac{4}{9} + \frac{7 a^2}{12}}
+\end{align*}
 
-\begin{theorem}
+Note that two-hops increases more and more slowly as $a$ increases. Therefore the minimum maximum will
+be obtained with the value of $a$ that when $one-hop = 1$. This can be observed from the
+plot of two-hops - one-hops as a function of $a$, or by observing that the derivate of two-hops - one-hop
+is negative for $a > 0$. (That is, the value of one-hop increases faster than two-hops.)
+
+We seek the value of $a$ that minimizes the maximum difference between these three lengths. We find
+by numerical experimentation that this difference is minimized that the one-hop distance is equal to $1$,
+which also has the pleasing property of giving us only two lengths. Then
+\begin{align*}
+   1  &=  \sqrt{\frac{1}{9} + \frac{7a^2}{12}} \\
+     a  &=  \sqrt{\frac{8 \cdot 12}{9 \cdot 7}} \\
+          a  &=  \sqrt{\frac{32}{21}}
+\end{align*}
+
+Therefore $ r = \sqrt{\frac{32}{63}} \approx 0.71267 $, producing length difference in the two-hop rail of
+$\frac{2}{\sqrt{3}}$
+and $1$ of $\approx 15.47\% $.
+
+Note: Another interesting solution occurs at $a = \sqrt(5)/2$, which produces three length
+classes of $11/12, 12/12, 13/12$.
+
+\begin{conjecture}
   The equitetrabeam is also optimal under the metric of the total length of all members 
   for an equilateral tetrabream isomorphic to the Boerdijk--Coxeter helix.
-\end{theorem}
+\end{conjecture}
 
 \begin{proof}
-  Summing together all lengths:
-  \begin{align*}
-  sum &= orange_e + orange_o + purple_e + purple_e + purple_o + green_e + green_o \\    
-  &= \sqrt{1 + Y^2} + \sqrt{1 + (1-Y)^2} + \sqrt{1 + B^2} + \sqrt{1+ (1-B)^2} + \\
-  & \sqrt{1 + (B - Y)^2} +  \sqrt{1 + ((1+Y) - B)^2} \\
-  \end{align*}
-
-  Wolfram Alpha, evaluating this numerically, gives the same minima:
-
-  \begin{tabular}{c}    
-$  min\{\sqrt(1 + Y^2) + \sqrt{1 + (1 - Y)^2} + \sqrt{1 + B^2} + \sqrt{1 + (1 - B)^2} + $\\
-    $  \sqrt{1 + (B - Y)^2} + \sqrt{1 + ((1 + Y) - B)^2}\} $ \\
-    $ \approx 6.76783 \text{at } (B, Y) \approx (0.666667, 0.333333) $
-  \end{tabular}
 
 \end{proof}
+
+We can then create a continuum of radius, length, rho to place into our general equation
+to create continuum of helices between the BC and equitetrabeam. This continuum is 
+minimax-length optimal at its endpoints, and may be optimal throughout.
 

### 2017-02-09 js/tetrahelix_math.js

@@ -1,0 +1,284 @@
+/*
+
+    Copyright 2017, Robert L. Read
+
+    This program is free software: you can redistribute it and/or modify
+    it under the terms of the GNU General Public License as published by
+    the Free Software Foundation, either version 3 of the License, or
+    (at your option) any later version.
+
+    This program is distributed in the hope that it will be useful,
+    but WITHOUT ANY WARRANTY; without even the implied warranty of
+    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+    GNU General Public License for more details.
+
+    You should have received a copy of the GNU General Public License
+    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+
+*/
+
+var red_phase = 0;
+var yellow_phase = 1;
+var blue_phase = 2;
+
+var BCtheta = Math.acos(-2/3);
+var BCrho = 3*BCtheta - 2 * Math.PI;
+var BCh = (1/Math.sqrt(10));
+var BCd = (3/Math.sqrt(10));
+var BCr = (3 * Math.sqrt(3) / 10);
+
+// This from https://github.com/josdejong/Mathjs/blob/develop/lib/utils/bignumber/nearlyEqual.js
+function nearlyEqual(x, y, epsilon) {
+  // if epsilon is null or undefined, test whether x and y are exactly equal
+  if (epsilon == null) {
+    return x === y;
+  }
+
+
+  // use "==" operator, handles infinities
+  if (x == y) {
+    return true;
+  }
+
+  // NaN
+  if (isNaN(x) || isNaN(y)) {
+    return false;
+  }
+
+    // check numbers are very close, needed when comparing numbers near zero
+    var diff = Math.abs(x-y);
+    if (diff == 0) {
+      return true;
+    }
+    else {
+	if (diff < epsilon)
+	    return true;
+    }
+
+  // Infinite and Number or negative Infinite and positive Infinite cases
+  return false;
+};
+
+function PColorHelix(n,phase,lambda) {
+    var pnt = [];
+    var r = (3 * Math.sqrt(3) / 10);
[…]

### 2017-02-11 doc/TetrahelixUntwist.tex
some changes to scene and clarification

@@
 \begin{abstract}
-  The Boerdijk--Coxeter helix (BC helix, or tetrahelix) is a face-to-face stack of regular tetrahedra whose outer vertices lie on helices.
-  By allowing changes to edge lengths so that the tetrahedra are not regular, we can define a continuum of tetrahelices isomorphic to the
-  BC helix of designable pitch or curvature, effectively ``untwisting'' the BC helix. We show that in the sense of minimal maximum
-  difference in edge length, every tetrahelix has vertices equally spaced along the axis and at most three distinct edge lengths.
-  In the case of a full untwisting to zero curvature, we describe a novel object, the
-  \emph{equitetrabeam}.
-  It has 3-fold symmetry about  axis, and chirality.  This tetrabeam and controllably twisted tetrahelices are
-  interesting for structural engineering because they are inherently rigid space frames and trusses.
-  A formula for the cartesian coordinates of the individual nodes of outer helices of the BC helix is given and
-  unified with the formula for the equitetrabeam creating a class of edge-length optimal tetrahelices generated by single parameter.
-  A further generalization is provided.
-  Utility and use for truss/space frame design and robotics are discussed.
+  The Boerdijk--Coxeter helix (BC helix, or tetrahelix) is a face-to-face stack of regular tetrahedra.
+  Considering the edges of these tetrahedra, the resulting structure is attractive and inherently rigid,
+  and therefore interesting to architects, mechanical engineers,
+  and robotocists.
+  A formula that matches the visually apparent helices forming the outer rails of the tetrahelix is derived which
+  is convenient for designers.
+  This formula defines the vertices of tetrahelices of varying radius, pitch, and curvature, with the BC helix
+  as a special case. 
+  An addtional special case is of that of $0$ curvature or rail angle, which generates a \emph{tetrabeam}.
+  A particular choice of paramaters defines a novel object, the  minimax member length-difference tetrabeam,
+  the \emph{equitetrabeam}.
+  Linear interpolation of these parameters with the BC-helix parameters defines a continuum of close-to regular
+  tetrahelices of designable curvature, pitch based on a single parameter.
+  Utility and use for static and variable geometry truss/space frame design and robotics based on the are discussed.
 \end{abstract}
@@
   \label{tetrahelixoptimality}
-  Any one tetrahedron in a minimax-optimal tetrahelix $ABCD$ of edge lengths $AD = 1, AB = BC = CD = u , AC = BD = v$, where $1 \leq u \leq v$.
+  Any one tetrahedron in a minimax-optimal tetrahelix $ABCD$ of edge lengths $\overline{\rm AD} = 1, \overline{\rm AB} = \overline{\rm BC} = \overline{\rm CD} = u , \overline{\rm AC} = \overline{\rm BD} = v$, where $1 \leq u \leq v$.
   Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ mid-length edges connected to the rail and $2$ long edges connected to the rail.
@@
 
-Note that based on Theorems \ref{tetrahelixoptimality} and \ref{eventhirds}, we are justified in classifying edge lengths as \emph{rail},\emph{mid-length}, or
-\emph{long}. The mid-length edges are the edges between closest on the $z$-axis, and the long edges are those that hop over a vertex.
+Note that based on Theorems \ref{tetrahelixoptimality} and \ref{eventhirds}, we are justified in classifying edge lengths as \emph{rail},\emph{one-hop}, or
+\emph{two-hops}. The one-hop edges are the edges between closest on the $z$-axis, and the two-hop edges are those that hop over a vertex.
 
@@
 we have the equitetrabeam.
-
-\section{Adding an Untwisting Parameter}
-
-We observe that it by thinking of the straight lines of the Equitetrabeam as a degenerate helix of zero curvature,
-it should be possible to define a smoothly varying continuum between the Boerdijk--Coxeter helix and the Equitetrabeam and every
-curvature and torsion between the two.
 
@@
 
-We seek to unify this with degenerate helix formula for the equitetrabeam:
-\[
-H_{etb}(n,c) =
-\left [
-  \begin{tabular}{c}
-   $ r_{etb}  \cos( 0 \cdot \kappa  + c 2 \pi /3) $\\
-   $ r_{etb}  \sin( 0 \cdot \kappa  + c 2 \pi /3) $\\
-   $ \kappa d_{etb} $
-  \end{tabular}
-\right ],
-\text{where:}
-  \begin{tabular}{c}
- $\kappa = n + c/3$ \\
-    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
-   $ \theta = \arccos(-2/3) $
-  \end{tabular}      
-\]
-where $ r_{etb} = 1/\sqrt(3)$, $d_{etb} = 1/3$,
-
-Now basic components of the helix, which are the radius $r$, the rate of rotation, and the rate of
-axial growth can all be linearly interpolated with a parameter $\lambda$ between their high values (for the BC helix)
-and low values (for the equitetrabeam):
-
-\begin{align*}
-r_{\lambda}  &=  \lambda (3 \sqrt(3) / 10 - 1/\sqrt(3)) +  1/\sqrt(3) \\
-d_{\lambda} &=   \lambda (3 / \sqrt(10) - 1)+ 1 \\
-\phi_{\lambda} &=  \lambda \rho_{bc}  + 0\\
-\end{align*}
-to create a formula that generates a continuum of tetrahedral structures:
-
-\[
-H_{continuum}(n,c,\lambda) =
-\left [
-  \begin{tabular}{c}
-   $ r_{\lambda} \cos(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
-   $ r_{\lambda}  \sin(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
-   $ d_{\lambda} \kappa $
-  \end{tabular}
-  \right ],
-\text{where:}
-  \begin{tabular}{c}
-    $\kappa = n + c/3$ \\
-    $ \phi_{\lambda} =  \lambda \rho_{bc}  + 0 $\\
-    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
-   $ \theta = \arccos(-2/3) $
-  \end{tabular}      
-\]
-A value of $\lambda = 0$ generates the equitetrabeam, and $\lambda = 1$ generates the Boerdijk--Coxeter helix, and every
-value $\lambda \in [0,1]$ generates an attractive structure which if physically realized is an inherently rigid structure
-with member lengths of no greater disparity than $21\%$.
-In the sense of structural engineering, it would be a relatively strong space frame.
-
-Furthermore, this formula allows one to design the pitch (in edge length units) as a function of $\lambda$ of the helix (along one rail)
-where $\lambda \neq 0$:
-\[
-p(\lambda) = 2 \pi  \cdot \frac{((3/\sqrt(10) -1) \lambda +1)}{ \lambda  \rho_{bc} }
-\]
-
 \section{Parametrizing Tetrahelices via Rail Angle}
@@
 Checking the important special case of the BC helix, we find that this equation
-indeed holds true (treathing $d$ in this equation as $3 h_{bc}$ as defined by
-Gray and Coxeter, where they are using it for the axial height from one node to
+indeed holds true (treating $d$ in this equation as $3 h_{bc}$ as defined by
+Gray and Coxeter), where they are using it for the axial height from one node to
 the next of a different color, but we use it to mean distance for the same color.
@@
   \text{rail} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n+1,c,\rho,d_{\rho})) = 1 \\
-  \text{mid-length} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}))  \\
-  \text{long} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+2,\rho,d_{\rho}))  \\  
+  \text{one-hop} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}))  \\
+  \text{two-hops} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+2,\rho,d_{\rho}))  \\  
 \end{align*}
@@
 
+ \begin{figure}[H]
+     \centering
+     \includegraphics[width=0.9\textwidth]{figures/EquilateralDiagram.png}
+     \caption{Coloring of an (untwisted) Tetrabeam}
+ \end{figure}
+
+\begin{theorem}
+The equitetrabeam with minimal maximal edge difference is produced by $H_{general}$ when $ r = \sqrt{\frac{8}{27}} $.
+  \end{theorem}
+
 When $\rho = 0$, our formulae for distances are particular simple. Let $a$ be the length of the equilateral triangle
-forming the beam cross section. Then by geometry $r = a \sqrt(3)$.
+forming the beam cross section. Then by geometry $r = a \sqrt{3}$.
 \begin{align*}
   \text{rail} &=  1 \\
-  \text{one-hop} &= \sqrt{\frac{1}{3}^2 + (\frac{a}{\sqrt{3}})^2 + (a/2)^2}\\
-\text{one-hop}  &= \sqrt{\frac{1}{9} + \frac{7 a^2}{12}} \\
-    \text{two-hops} &= \sqrt{\frac{2}{3}^2 + (\frac{a}{\sqrt{3}})^2 + (a/2)^2}  \\
-\text{two-hops}    &= \sqrt{\frac{4}{9} + \frac{7 a^2}{12}}
+  \text{one-hop} &= \sqrt{\frac{1}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}\\
+\text{one-hop}  &= \sqrt{\frac{1}{9} + a^2} \\
+    \text{two-hops} &= \sqrt{\frac{2}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}  \\
+\text{two-hops}    &= \sqrt{\frac{4}{9} + a^2}
 \end{align*}
+Computing the derivative of two-hops - one-hop:
+\begin{align*}
+ \frac{\partial \text{two-hops} - \text{one-hop}}{a} &= \frac{\partial \sqrt{4/9 + a^2} - \sqrt{1/9 + a^2}}{\partial a} \\
+  \frac{\partial \text{two-hops} - \text{one-hop}}{a} &= \frac{a}{\sqrt{a^2 + 4/9}} - \frac{a}{\sqrt{ a^2 + 1/9}} 
+\end{align*}
+which is negative for all $a> 0$. Thererfore two-hop - one-hop
+is minimized when we maximize $a$, up until one-hop = rail.
 
@@
 \begin{align*}
-   1  &=  \sqrt{\frac{1}{9} + \frac{7a^2}{12}} \\
-     a  &=  \sqrt{\frac{8 \cdot 12}{9 \cdot 7}} \\
-          a  &=  \sqrt{\frac{32}{21}}
+   1  &=  \sqrt{\frac{1}{9} + a^2} \\
+     a  &= \sqrt{\frac{8}{9}} 
 \end{align*}
 
-Therefore $ r = \sqrt{\frac{32}{63}} \approx 0.71267 $, producing length difference in the two-hop rail of
+Therefore $ r = \sqrt{\frac{8}{27}} \approx 0.5443 $, producing length difference in the two-hop rail of
 $\frac{2}{\sqrt{3}}$
@@
 
-Note: Another interesting solution occurs at $a = \sqrt(5)/2$, which produces three length
-classes of $11/12, 12/12, 13/12$.
+Note: Another interesting solution is derived by setting (one-hop + two-hop)/2 = 1,  occurs at $a = \sqrt{35/3}/4$,
+which produces three length classes of $11/12, 12/12, 13/12$.
 
@@
   The equitetrabeam is also optimal under the metric of the total length of all members 
-  for an equilateral tetrabream isomorphic to the Boerdijk--Coxeter helix.
+  for an equilateral tetrabeam isomorphic to the Boerdijk--Coxeter helix.
 \end{conjecture}
@@
 
+\section{Adding an Untwisting Parameter}
+
+We observe that it by thinking of the straight lines of the Equitetrabeam as a degenerate helix of zero curvature,
+it should be possible to define a smoothly varying continuum between the Boerdijk--Coxeter helix and the Equitetrabeam and every
+curvature and torsion between the two.
+
+We seek to unify this with degenerate helix formula for the equitetrabeam:
+\[
+H_{etb}(n,c) =
+\left [
+  \begin{tabular}{c}
+   $ r_{etb}  \cos( 0 \cdot \kappa  + c 2 \pi /3) $\\
+   $ r_{etb}  \sin( 0 \cdot \kappa  + c 2 \pi /3) $\\
+   $ \kappa d_{etb} $
+  \end{tabular}
+\right ],
+\text{where:}
+  \begin{tabular}{c}
+ $\kappa = n + c/3$ \\
+    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
+   $ \theta = \arccos(-2/3) $
+  \end{tabular}      
+\]
+where $ r_{etb} = \sqrt{\frac{8}{27}}$, $d_{etb} = 1$,
+
+Now basic components of the helix, which are the radius $r$, the rate of rotation, and the rate of
+axial growth can all be linearly interpolated with a parameter $\lambda$ between their high values (for the BC helix)
+and low values (for the equitetrabeam):
+
+\begin{align*}
+r_{\lambda}  &=  \lambda (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
+d_{\lambda} &=   \lambda (3 \sqrt{10} - 1) + 1 \\
+\phi_{\lambda} &=  \lambda \rho_{bc}  + 0
+\end{align*}
+to create a formula that generates a continuum of tetrahedral structures:
+
+\[
+H_{continuum}(n,c,\lambda) =
+\left [
+  \begin{tabular}{c}
+   $ r_{\lambda} \cos(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
+   $ r_{\lambda}  \sin(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
+   $ d_{\lambda} \kappa $
+  \end{tabular}
+  \right ],
+\text{where:}
+  \begin{tabular}{c}
+    $\kappa = n + c/3$ \\
+    $ \phi_{\lambda} =  \lambda \rho_{bc}  + 0 $\\
+    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
+   $ \theta = \arccos(-2/3) $
+  \end{tabular}      
+\]
+A value of $\lambda = 0$ generates the equitetrabeam, and $\lambda = 1$ generates the Boerdijk--Coxeter helix, and every
+value $\lambda \in [-1,1]$ generates an attractive structure which if physically realized is an inherently rigid structure
+with member lengths of no greater disparity than $16\%$.
+In the sense of structural engineering, it would be a relatively strong space frame.
+
+ \begin{figure}[H]
+     \centering
+     \includegraphics[width=0.9\textwidth]{figures/Continuum.png}
+     \caption{A Continuum of Tetrahelices}
+ \end{figure}
+
+Negative values of $\lambda$ generate clockwise tetrahelices; positive generate counter-clockwise helices.
+
+Furthermore, this formula allows one to design the pitch (in edge length units) as a function of $\lambda$ of the helix (along one rail)
+where $\lambda \neq 0$:
+\[
+p(\lambda) = 2 \pi  \cdot \frac{(\frac{8}{27} -1) \lambda +1)}{ \lambda  \rho_{bc} }
+\]
+
 We can then create a continuum of radius, length, rho to place into our general equation
 to create continuum of helices between the BC and equitetrabeam. This continuum is 
-minimax-length optimal at its endpoints, and may be optimal throughout.
-
-The equitetrabeam has chirality.
+minimax-length optimal at its endpoints, and may be optimal throughout. This untwisting is accomplished
+only by changing the length of the two-hop member.
 
@@
 \begin{theorem}
-
-  Using the six member classes defined by the non-primary colors, it is possible to smoothly twist and untwist a tetrahelix by
-  using a linear combination of lengths.
-
+  By changing only the length of the members that change rails and make two nodes, you can untwist a tetrobot
+  form the Boerdijk-Coxeter configuration to the equitetrabeam which rests flat on the plane.
 \end{theorem}
@@
 
+See if the continuum holds the short edge lengths at one perpetually.  Yes!!!
+
+Create working toolkit for desin/exploration. Improve code that way, use white background, floor.
+
+Try to compute optimal radius within our context. This would let us assert that we have
+an ``optimum'' continuum.  Not worth much to an engineer, but valuable.
+
 Review and continue editing, being careful to introduce concepts in the correct order.
-
-The most important thing to do here is to start a github project that includes javascript
-to copute this stuff; the second most important thing is to use Three.js to create a
-nice visual representation of all of this without getting the physics engine involved.
-
-Check formula to make sure lengths are what we previously created for the Equitetrabeam.
-
-First, plug values into Equitetrabeam.
-
-Check distances.
-
-Also, update diagam.
 
@@
 
-  Investigate Lambda outsidde the range [0,1].  Does -lambda reverse the chirality?
-  Does lambda > 1 increase twist nicely?
-
-  Create alternate coloring inside my system to render the tetrabot better.
-  Add shadows better.
-
-  Conjecture: There is a sense in which every tetrahelix has vertices
-  evenly space along the axis of motion in order to have optimal lengths.
-
-  Argument sketch: Follow current argument sketch, but compute lengths from formula
-  for helices, using symmetry argument whereever possible.
-
-  Create separate Github project having javascript code as function for computing all.
-
 Make YouTube video.

### 2017-02-11 js/tetrahelix_math.js

@@ -29,56 +29,35 @@ var BCr = (3 * Math.sqrt(3) / 10);
 
 // This from https://github.com/josdejong/Mathjs/blob/develop/lib/utils/bignumber/nearlyEqual.js
 function nearlyEqual(x, y, epsilon) {
-  // if epsilon is null or undefined, test whether x and y are exactly equal
-  if (epsilon == null) {
-    return x === y;
-  }
+    // if epsilon is null or undefined, test whether x and y are exactly equal
+    if (epsilon == null) {
+	return x === y;
+    }
 
+    // use "==" operator, handles infinities
+    if (x == y) {
+	return true;
+    }
 
-  // use "==" operator, handles infinities
-  if (x == y) {
-    return true;
-  }
-
-  // NaN
-  if (isNaN(x) || isNaN(y)) {
-    return false;
-  }
+    // NaN
+    if (isNaN(x) || isNaN(y)) {
+	return false;
+    }
 
     // check numbers are very close, needed when comparing numbers near zero
     var diff = Math.abs(x-y);
     if (diff == 0) {
-      return true;
+	return true;
     }
     else {
 	if (diff < epsilon)
 	    return true;
     }
 
-  // Infinite and Number or negative Infinite and positive Infinite cases
-  return false;
+    // Infinite and Number or negative Infinite and positive Infinite cases
+    return false;
 };
 
-function PColorHelix(n,phase,lambda) {
-    var pnt = [];
-    var r = (3 * Math.sqrt(3) / 10);
-    var rl = (r - 1/Math.sqrt(3))*lambda + 1/Math.sqrt(3);
-    var h = BCh;
-    var hl = (h - 1/3)*lambda + 1/3;    
-    var x = n+phase/3.0;
-    var theta = Math.acos(-2/3);
-    var slow = (3*theta - Math.PIi*2);
-    var third = 2*Math.PI/3.0;
-    // Note the subtle distinct here...
-    // in fact:
-    //   slow *(n+phase/3.0) + phase*third == slow * n + phase*theta!
-    //
-    var angle = slow * x * lambda+ phase*third;
-    pnt[0] = rl * Math.cos(angle);
-    pnt[1] = rl * Math.sin(angle);
-    pnt[2] = (x) * 3 * hl;
-    return pnt;
-}
 
 function find_drho_from_r_el(rho,r,el) {
     var sin_r_2 = Math.sin(rho/2);
[…]

### 2017-02-11 doc/TetrahelixUntwist.tex
fixed bug with negative lambda values

@@
 \begin{align*}
-r_{\lambda}  &=  \lambda (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
-d_{\lambda} &=   \lambda (3 \sqrt{10} - 1) + 1 \\
+r_{\lambda}  &=  \lvert \lambda \rvert (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
+d_{\lambda} &=   \lvert \lambda \rvert (3 \sqrt{10} - 1) + 1 \\
 \phi_{\lambda} &=  \lambda \rho_{bc}  + 0
@@
 
-See if the continuum holds the short edge lengths at one perpetually.  Yes!!!
+Understand why I can't control color completely!
 
-Create working toolkit for desin/exploration. Improve code that way, use white background, floor.
+Note that Lamba = 16 almost produces a 2-rail helicoid.
+
+When abs(lambda) > 4, we seem to have marked differences in the parameters. Understand why this is and what is causing it.
+(it is possible that positive and negative rho values behave very differently?
+
+Note: Would be really nice to have the GUI show you all computed parameters.
+
+Note: Distance is clearly lower on first computations..
+
+Create working toolkit for desin/exploration.
+
+Improve code that way, use white background, floor.
+
+Figure out if I am computing something wrong.
 

### 2017-02-11 js/tetrahelix_math.js

@@ -21,11 +21,18 @@ var red_phase = 0;
 var yellow_phase = 1;
 var blue_phase = 2;
 
+// Fundamental constanstants for the Boerdijk-Coxeter Helix
 var BCtheta = Math.acos(-2/3);
 var BCrho = 3*BCtheta - 2 * Math.PI;
 var BCh = (1/Math.sqrt(10));
 var BCd = (3/Math.sqrt(10));
 var BCr = (3 * Math.sqrt(3) / 10);
+
+// The Equitetrabeam
+var EQTBr =  (2/3)*Math.sqrt(2/3);
+var EQTBd = 1;
+var EQTBrho = 0;
+
 
 // This from https://github.com/josdejong/Mathjs/blob/develop/lib/utils/bignumber/nearlyEqual.js
 function nearlyEqual(x, y, epsilon) {
@@ -107,9 +114,9 @@ function H_bc_eqt_lambda(n,c,lambda) {
     // Now we must compute r and h....
     // "0" is the equitetrabeam
     // "1" is the BC helix
-    var r0 =  (2/3)*Math.sqrt(2/3);
-    var d0 = 1;
-    var rho0 = 0;
+    var r0 = EQTBr;
+    var d0 = EQTBd;
+    var rho0 = EQTBrho;
     
     var r1 = BCr;
     var d1 = BCd;
@@ -120,10 +127,12 @@ function H_bc_eqt_lambda(n,c,lambda) {
 
 // Interpolate between (rho0,d0,r0,l0) and (rho1,d1,r1,l1)
 function H_interp_lambda(lambda,n,c,rho0,d0,r0,rho1,d1,r1) {
-    
-    var di = (d1 - d0)*lambda + d0;
-    var rhoi = (rho1 - rho0)*lambda + rho0;
-    var ri = (r1 - r0)*lambda + r0;
+    var alambda = Math.abs(lambda);
+    var di = (d1 - d0)*alambda + d0;
+    var rhoi = (lambda > 0) ? (rho1 - rho0)*alambda + rho0 : -((rho1 - rho0)*alambda + rho0);
+    var ri = (r1 - r0)*alambda + r0;
+
+    console.log("key:",lambda,di,rhoi,ri)
     
     return H_general(n,c,rhoi,di,ri);
 }

### 2017-02-12 doc/TetrahelixUntwist.tex
light working

@@
 \begin{align*}
-r_{\lambda}  &=  \lvert \lambda \rvert (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
-d_{\lambda} &=   \lvert \lambda \rvert (3 \sqrt{10} - 1) + 1 \\
-\phi_{\lambda} &=  \lambda \rho_{bc}  + 0
+r_{\lambda}  &=  \lvert \lambda \rvert \cdot (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
+d_{\lambda} &=   \lvert \lambda \rvert \cdot (3 \sqrt{10} - 1) + 1 \\
+\phi_{\lambda} &=  \lambda \cdot \rho_{bc}  + 0
 \end{align*}
@@
 with member lengths of no greater disparity than $16\%$.
-In the sense of structural engineering, it would be a relatively strong space frame.
+In the sense of structural engineering, it would be a relatively strong space frame. When $\lvert \lambda \rvert > 1$, tetrahelices
+are still produced, but as $\lvert \lambda \rvert >> 2$ these tetrahelices probably cease to be interesting to mechanical engineers,
+because their ability to withstand axial forces seem to diminish significantly.
 
@@
 \]
+
+Note: Need to understand how pitch is computed from negative lambda values.
 

### 2017-02-12 doc/TetrahelixUntwist.tex
formula for distance and some arguments about isomophism

@@
 
+ Any minimax length optimal tetrahelix must have the same pitch on each helix, the length of one set of members grows unboundedly with
+ each revolution. So in seeking a minimax optimal tetrahelix we only consider those with the same torsion.
+
+ We show that in fact the nodes must be distributed in even thirds along the $z$-axis.
+
  Note that from the point of view of a single edge, we are on a slanted cylinder, when $\rho \neq 0$.
@@
 
+ First prove that any structure isomorphic to the BC-Helix of unbounded extent in which each rail lies on a helix has certain
+ properties if it it member length minimax optimal.
+
+ The pitches must be equal, or some member grows without bound.
+
+ If the axes are not parallel, some member grows without bound.
+
+ We can therefore think in terms of O,G, P displacement.
+
+ We need to prove that the three axes are coincident.
+
+ Suppose there is one helix that is not conicident with the other two.  So long as $\rho \neq 0$, there is some value of $\kappa$
+ makes the lenth to any node longer and shorter. Then the distance between nodes depends on $\kappa$, unless $\rho = 0$ or $\rho = \pi$.
+ One of these makes the longest distance longer and the shortest distance shorter, so a superior solution occurs when the a
+ axes conincide.  This is actually correct but poorly written.
+
+ Now now that we have coincident axes, the same pitch, we can go on to the hard proof about where they occur.
+
   Note: This is a new, simpler proof attempt.
   \begin{theorem}
-    Suppose that all edge vertices are on one of three helices of the same positive pitch and the same radius about the $z$ axis differing by $120\degree$ about $z$.
+    Suppose that all edge vertices are on one of three helices of the same positive pitch and the same radius with the
+    same shared axes about the $z$ axis differing by $120\degree$ about $z$.
     However, we do not assume that the three helices are equidistant.
@@
   \end{theorem}
-
+Note: Change this to PQR. Also, may be better to use $\alpha$ instead of $\rho$ in this proof.
   \begin{proof}
@@
 \end{align*}
+
+Using the cartesian distance formula:
+\begin{align*}
+  \overline{\rm CD}  &= \sqrt{G^2 + (r\sin{0 \rho} -  r\sin{G \rho})^2 + (r\cos{0 \rho} - r\cos{G \rho})^2} \\
+    \overline{\rm CD}  &= \sqrt{G^2 + (0 -  r\sin{G \rho})^2 + (r - r\cos{G \rho})^2} \\
+    \overline{\rm CD}  &= \sqrt{G^2 + r^2(\sin{G \rho})^2 + r^2(1 - \cos{G \rho})^2} \\
+    \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + \sin^2{G \rho}  - \cos^2{G \rho})} \\    
+\end{align*}
+
+Note: According to Wolfram Alpha, $\sin^2{G \rho}  - \cos^2{G \rho} = -\cos{2 G \rho}$
+
+So, for all O,G,P,
+\begin{align*}
+  \overline{\rm AB}  &= 1 \\        
+  \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + \sin^2{G \rho}  - \cos^2{G \rho})} \\
+  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + \sin^2{O \rho}  - \cos^2{O \rho})} \\
+  \overline{\rm BD}  &= \sqrt{P^2 + r^2(1 + \sin^2{P \rho}  - \cos^2{P \rho})} \\
+  \overline{\rm AD}  &= \sqrt{(O+G)^2 + r^2(1 + \sin^2{(O +G) \rho}  - \cos^2{(O+G) \rho})} \\
+  \overline{\rm BC}  &= \sqrt{(P+G)^2 + r^2(1 + \sin^2{(P +G) \rho}  - \cos^2{(P+G) \rho})} \\      
+\end{align*}
+
+We show that the maximum difference between these variables for a given $r$ is minimized when $O=G=P=1/3$.
 First we show any configuration in which $O \neq P$ implies a solution at least as good in terms of minimax difference in which $O = P$.
@@
   \\
-   \overline{\rm AC} &=   \overline{\rm BD}   \\
+    \overline{\rm AC}&=   \overline{\rm BD}   \\
    \overline{\rm AD} &=   \overline{\rm BC}   \\
@@
 Suppose $\overline{\rm C'D'}$ is the shortest edge. Increasing $G$ thereby improves our mimimum, up until the next shortest edge length, $\overline{\rm AC}$.
-This may increase $\overline{\rm BC}$ and $\overline{\rm AD}$, but more slowly than $\overline{\rm C'D'}$ is being increased, until  $\overline{\rm C'D'} =
+This may increase $\overline{\rm BC}$ and $\overline{\rm AD}$, but more slowly (???) than $\overline{\rm C'D'}$ is being increased, until  $\overline{\rm C'D'} =
 \overline{\rm AC}$.
+Note: This is sketchy, can we show that the derivative of our formula for CD  with respect to $G$ is really higher than $AD$? These derivatives will depend on $\rho$ slightly, which is exactly right!
 
@@
   The edge opposite of the rail edge is a mid-length edge.
-    \end{proof}
-
-\begin{theorem}
-  Suppose that all edge vertices are on helices about the same axis and that $R,B,Y$ and are $120\degree$ from each other from that axis.
-  Then a minimax positioning occurs when at least 3 non-rail edge classes are the longest length and equivalent.
- \end{theorem}
-\begin{proof}
-Note: It is not perfectly clear this proof is valid for extreme radii which are either very short or very large.
-
-   Suppose that all edge vertices are on helices about the same axis and that $R,B,Y$ and are $120\degree$ from each other from that axis.
-
-  If there is a unique longest distance, it touches two rails. Moving those rails closer together infinitesimally decreases the longest length and
-  therefore the minimax.
-
-  Suppose there are exactly two longest edges of equal length. By the pigeonhole principle, these edges must share one rail and touch the other two.
-  If moving the shared rail in one direction decreases both edge lengths, doing so infinitesimally decreases the minimax.
-
-  Therefore there must be at least three longest edges of equal length, each of which touches two rails.
-  \end{proof}
-
-\begin{theorem}
-  Any minimax-optimal tetrahelix at most precisely three classes of edge lengths.
-\end{theorem}
-
-\begin{proof}
-  Every vertex is connected to each rail by two edges. These two edges cannot be of the same length, unless all six edge classes are the same
-  length. If all six are the same length, $Y_0$ and $B_0$ lie on the same $z$ value, but then $green_o$ is much longer than $purple_e = purple_o = orange_e = organge_o$,
-  making it a unique longest length, a contradiciton. Therefore the odd and even lengths in each color class are different. Therfore there is a second,
-  shorter length, which occurs once in each color class. Taken with the rail edge length of $1$, this makes precisely three classes of equivalent
-  edge lengths for any minimax-optimal helix.
     \end{proof}
@@
 
-Understand why I can't control color completely!
+Remove the weirdly colored diagram.
+
+Add to the rail angle diagram.
 

### 2017-02-15 doc/TetrahelixUntwist.tex
proof simplifcations

@@
   \begin{tabular}{c}
-   $ r_{bc} \cos(n \theta $\\
+   $ r_{bc} \cos(n \theta) $\\
    $ r_{bc} \sin(n \theta) $\\
@@
 
+\section{Optimal Tetrahelices Have Evenly Spaced Vertices}
+
+We use the term \emph{tetrahelix} to mean any structure made of vertices and edges which is isomorphic to the BC helix,
+in which the vertices lie on three helices, 
+no matter what lengths the edges take on. One could consider various definitions of optimality for a tetrahelix,
+but the must useful to an enginner is to minimize the maximum difference between any two edges. We call a
+tetrahelix \emph{member-length minimax optimal} if there is not tetrahelix of the same radius and pitch with a smaller
+maximum edge length difference.
+
+Consider a tetrahelix isomporphic to an BC helix of unbounded extent. If all three rails do not have same pitch, there
+is an edge of unbounded length. So we are justified in talking about the pitch of the tetrahelix, even though we think
+of it as three helices. Similarly, if the axes are not parallel, there is an edge of unbounded length in the structure,
+so it is not optimal.
+
+Consider any tetrahelix in which the axes of the helices are parallel to $z$ but not coincident, but in which all three helices have the same
+radius. Consider the projection along the $z$ axis, which will be a figure of dots and connecting segments in the $xy$ plane. The convex
+hull for any one helix projection will be a circle (if its pitch is irrational) or an polygon if rational. So long as its rail angle is
+not $0$, it will have at least two points in the plane. One of these will be longer and will be made shorter by moving that helix closer
+to the midpoint of the other two in the $xy$ plane. Even if the rail angle is $\pi$, there will be two vertices for each rail, each of
+which is connected to both vertices of the other two rails. At lesast one of these lines is a longest line which will be made shorter by moving
+that helix in the $xy$ plane closer to the midpoint of the other two.
+
+So any any optimal tetrahelix with a rail-angle of greater than $0$, that is, with any curvature, will have conincident axes.
+
+We call a tetrahelix with $0$ curvature a \emph{tetrabeam}, and consider it as an important special case and an endpoint of a continuum
+of tetrahelices of decreasing curvature.
+
+ Now now that we have coincident axes, the same pitch, we can go on to the hard proof about where they occur.
+
  \begin{figure}[H]
@@
  \end{figure}
-
- \subsection{Recent Notes}
-
- Any minimax length optimal tetrahelix must have the same pitch on each helix, the length of one set of members grows unboundedly with
- each revolution. So in seeking a minimax optimal tetrahelix we only consider those with the same torsion.
 
@@
 
- \subsection{Very bad attempts to prove things}
-
- First prove that any structure isomorphic to the BC-Helix of unbounded extent in which each rail lies on a helix has certain
- properties if it it member length minimax optimal.
-
- The pitches must be equal, or some member grows without bound.
-
- If the axes are not parallel, some member grows without bound.
-
- We can therefore think in terms of O,G, P displacement.
-
- We need to prove that the three axes are coincident.
-
- Suppose there is one helix that is not conicident with the other two.  So long as $\rho \neq 0$, there is some value of $\kappa$
- makes the lenth to any node longer and shorter. Then the distance between nodes depends on $\kappa$, unless $\rho = 0$ or $\rho = \pi$.
- One of these makes the longest distance longer and the shortest distance shorter, so a superior solution occurs when the a
- axes conincide.  This is actually correct but poorly written.
-
- Now now that we have coincident axes, the same pitch, we can go on to the hard proof about where they occur.
-
-  Note: This is a new, simpler proof attempt.
  \begin{theorem}
-    Suppose that all edge vertices are on one of three helices of the same positive pitch and the same radius with the
-    same shared axes about the $z$ axis differing by $120\degree$ about $z$.
-    However, we do not assume that the three helices are equidistant.
-    Without loss of generality, consider $A$ and $B$ to be to be on the same axis, $C$ to be on a second axis, and $D$ to be on the final.
-    Without loss of generality assume: $A.z \leq C.z \leq D.z \leq B.z$.
-    Then the minimum maximum difference between any two nodes is acheived when
-    $ \overline{\rm AD} =  \overline{\rm BC} $ and $ \overline{\rm AC} =  \overline{\rm CD}, \overline{\rm DB} $.
-  \end{theorem}
-Note: Change this to PQR. Also, may be better to use $\alpha$ instead of $\rho$ in this proof.
-  \begin{proof}
-\begin{align*}
-  O  &= C.z - A.z \\
-  G &= D.z - C.z \\
-  P &=  B.z - D.z
-\end{align*}
-
-Using the cartesian distance formula:
-\begin{align*}
-  \overline{\rm CD}  &= \sqrt{G^2 + (r\sin{0 \rho} -  r\sin{G \rho})^2 + (r\cos{0 \rho} - r\cos{G \rho})^2} \\
-    \overline{\rm CD}  &= \sqrt{G^2 + (0 -  r\sin{G \rho})^2 + (r - r\cos{G \rho})^2} \\
-    \overline{\rm CD}  &= \sqrt{G^2 + r^2(\sin{G \rho})^2 + r^2(1 - \cos{G \rho})^2} \\
-    \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + \sin^2{G \rho}  - \cos^2{G \rho})} \\    
-\end{align*}
-
-Note: According to Wolfram Alpha, $\sin^2{G \rho}  - \cos^2{G \rho} = -\cos{2 G \rho}$
-
-So, for all O,G,P,
-\begin{align*}
-  \overline{\rm AB}  &= 1 \\        
-  \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + \sin^2{G \rho}  - \cos^2{G \rho})} \\
-  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + \sin^2{O \rho}  - \cos^2{O \rho})} \\
-  \overline{\rm BD}  &= \sqrt{P^2 + r^2(1 + \sin^2{P \rho}  - \cos^2{P \rho})} \\
-  \overline{\rm AD}  &= \sqrt{(O+G)^2 + r^2(1 + \sin^2{(O +G) \rho}  - \cos^2{(O+G) \rho})} \\
-  \overline{\rm BC}  &= \sqrt{(P+G)^2 + r^2(1 + \sin^2{(P +G) \rho}  - \cos^2{(P+G) \rho})} \\      
-\end{align*}
-
-We show that the maximum difference between these variables for a given $r$ is minimized when $O=G=P=1/3$.
-First we show any configuration in which $O \neq P$ implies a solution at least as good in terms of minimax difference in which $O = P$.
-Let 
-\begin{align*}
-  \frac{O' + P'}{2} &= \frac{1}{2} + \delta
-\end{align*}
-Then any configuration $O' - \delta/2, P' - \delta/2$ has a minimax at least as good as $O',P'$, because, if $\delta > 0$, then
-$\overline{\rm A'C'}$ is the longest segment of the four $\overline{\rm A'C'}, \overline{\rm A'D'}, \overline{\rm B'C'} =  \overline{\rm B'D'} $.
-$\overline{\rm B'D'}$ is the shortest of this set.
-\begin{align*}
-  \overline{\rm A'D'} &> \overline{\rm B'C'}  \\
-   \overline{\rm B'D'} &< \overline{\rm A'C'}  \\  
-   \overline{\rm AB} &=   \overline{\rm A'B'}   \\
-   \overline{\rm CD} &=   \overline{\rm C'D'}   \\
-  \\
-    \overline{\rm AC}&=   \overline{\rm BD}   \\
-   \overline{\rm AD} &=   \overline{\rm BC}   \\
-  \\  
-   \overline{\rm AC} &<  \overline{\rm A'C'} \\
-   \overline{\rm AD} &< \overline{\rm A'D'}   \\
-   \overline{\rm BC} &>  \overline{\rm B'C'} \\
-   \overline{\rm BD} &> \overline{\rm B'D'}   \\
-\end{align*}
-So the maximum $\overline{\rm AD}$ is at most the old maximum. The minimum $\overline{\rm AC}$ is at least the old minimum of our set of four.
-If the maximum or minimum of a subset is not worsened, the maximum or minimum of the total set cannot be worsened. Therefore $O' - \delta/2, P' - \delta/2$
-is no worse than $O', P'$. So any mimimax solution is no better than one in which $(O + P)/2 = 1/2$, or $O = P$.
-
-Suppose $\overline{\rm C'D'}$ is the shortest edge. Increasing $G$ thereby improves our mimimum, up until the next shortest edge length, $\overline{\rm AC}$.
-This may increase $\overline{\rm BC}$ and $\overline{\rm AD}$, but more slowly (???) than $\overline{\rm C'D'}$ is being increased, until  $\overline{\rm C'D'} =
-\overline{\rm AC}$.
-Note: This is sketchy, can we show that the derivative of our formula for CD  with respect to $G$ is really higher than $AD$? These derivatives will depend on $\rho$ slightly, which is exactly right!
-
-  Any tetrahelix $ABCD$ of edge lengths $AD = u, AB = BC = CD = v , AC = BD = w$, where $1 \leq u \leq v$ is mimimax optimal.
-  Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ mid-length edges connected to the rail and $2$ long edges connected to the rail.
-  The edge opposite of the rail edge is a mid-length edge.
-    \end{proof}
-
-\begin{theorem}
-  \label{tetrahelixoptimality}
-  Any one tetrahedron in a minimax-optimal tetrahelix $ABCD$ of edge lengths $\overline{\rm AD} = 1, \overline{\rm AB} = \overline{\rm BC} = \overline{\rm CD} = u , \overline{\rm AC} = \overline{\rm BD} = v$, where $1 \leq u \leq v$.
-  Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ mid-length edges connected to the rail and $2$ long edges connected to the rail.
-  The edge opposite of the rail edge is a mid-length edge.
+   \label{eventhirds}
+   A tetrahelix of a given radius and height $h$ in which all nodes are evenly spaced at $h/3$ intervals on the $z$ axis is optimal.
+     Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail and $2$ two-hop edges connected to the rail.
+  The edge opposite of the rail edge is a one-hop edge.
   \end{theorem}
@@
  \begin{proof}
-The edge opposite of the rail edge is a mid-length edge because between any two rails the edges alteranate mid-length and long.
+
+   In principle in any tetrahelix where the three helices have any displacement along the $z$ axis there are 9 distinct edge classes:
+   3 rail edges, a one-hop length between eachof 3 rails, and two hop length between each of three rails, where the two-hop length is a maximum
+   length between rails (which could equal the one-hop length.) However, we have already shown the pitches and the rail lengths are equal
+   in any optimal tetrahelix.
+
+    Consider the tetrahelix in which the vertices  are evenly spaced at $h/3$ intervals on the $z$ axis. Every edge is either a rail edge, or it makes one
+    hop, or it makes two hops. All of the one-hop edges are equal length.  All of the two-hop edges are equal length.
+
+    Any displacemnt along the $z$ axis of any rail increases the length of one or two two-hop edges and shortens the length of one or two one-hop edges.
+    This increases the minimax distance no matter what the rail edge length is, since all rail edges are the same length. Therefore, an evenly spaced
+    tetrahelix is the unique optimal for any given radius and height.
   \end{proof}
 
-\begin{corollary}
-  \label{eventhirds}
-  Any minimax optimal tetrahelix has its colored edges spaced at 1/3 the height of
-  a tetrahedra along the z-axis, where the height is the z-distance of the rail edge.
-  \end{corollary}
-
-\begin{proof}
-  Let the variables $O,G,P$ represent the z-axis distance from the
-  $R_0$ to $Y_0$, $Y_0$ to $B_0$, and
-  $B_0$ to $R_0$ respectively. Then $O+G+P = h$. But $O=G=P$, since each edge between
-  their nodes spans two rails of the same distance with an edge of the same length,
-  so that the $z$-distance between each node is the same. So $O=G=P=h/3$.
-\end{proof}
-
-Note that based on Theorems \ref{tetrahelixoptimality} and \ref{eventhirds}, we are justified in classifying edge lengths as \emph{rail},\emph{one-hop}, or
+Note that based on \ref{eventhirds}, we are justified in classifying edge lengths as \emph{rail},\emph{one-hop}, or
 \emph{two-hops}. The one-hop edges are the edges between closest on the $z$-axis, and the two-hop edges are those that hop over a vertex.
 
-Every optimal tetrahelix has vertices lying on helices expressible in the form:
+By \ref{eventhirds} every optimal tetrahelix has vertices lying on helices expressible in the form:
 \[
@@
   \end{tabular}
-\right ]
+  \right ],
+\text{where:}
+\begin{tabular}{c}
+  $c \in \{0,1,2\}$
+  \end{tabular}      
 \]
@@
 \end{align*}
-Where are invarinat for all $n$ and $c$.
+Which are invarinat for all $n$ and $c$.
+
+\begin{align*}
+  \text{one-hop} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}))  \\
+  \text{one-hop} &= dist(H_{general}(0,0,\rho,h_{\rho}),H_{general}(0,1,\rho,d_{\rho}))  \\  
+  \text{one-hop}  &= \sqrt{d_{\rho}^2/9 + (r\sin{\frac{\rho(3\cdot 0 + 0)}{2\pi}} - r\sin{\frac{\rho(3\cdot 0 + 0+1)}{2\pi}})^2  +
+    (r\cos{\frac{\rho(3\cdot0+0)}{2\pi}} - r\cos{\frac{\rho(3\cdot + 0+1)}{2\pi}})^2
+  \text{one-hop}  &= \sqrt{d_{\rho}^2/9 + (r\sin{\frac{\rho(0)}{2\pi}} - r\sin{\frac{\rho(1)}{2\pi}})^2  +
+    (r\cos{\frac{\rho(0)}{2\pi}} - r\cos{\frac{\rho(1)}{2\pi}})^2
+  } \\  
+\end{align*}
 
@@
 Make YouTube video.
+
+    \section{Old Proofs}
+
+We can create the distance between representative nodes as:
+\begin{align*}
+  \overline{\rm AB}  &= 1 \\        
+  \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + -\cos{2 G \rho})} \\
+  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + \sin^2{O \rho}  - \cos^2{O \rho})} \\  
+  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + -\cos{2 O  \rho})} \\
+  \overline{\rm BD}  &= \sqrt{P^2 + r^2(1 + -\cos{2 P \rho}))} \\
+  \overline{\rm AD}  &= \sqrt{(O+G)^2 + r^2(1 + -\cos{2 (O + G)  \rho})} \\
+  \overline{\rm BC}  &= \sqrt{(P+G)^2 + r^2(1 + -\cos{2 (P + G) \rho})} \\      
+\end{align*}
+
+Using the cartesian distance formula:
+\begin{align*}
+  \overline{\rm CD}  &= \sqrt{G^2 + (r\sin{0 \rho} -  r\sin{G \rho})^2 + (r\cos{0 \rho} - r\cos{G \rho})^2} \\
+    \overline{\rm CD}  &= \sqrt{G^2 + (0 -  r\sin{G \rho})^2 + (r - r\cos{G \rho})^2} \\
+    \overline{\rm CD}  &= \sqrt{G^2 + r^2(\sin{G \rho})^2 + r^2(1 - \cos{G \rho})^2} \\
+    \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + \sin^2{G \rho}  - \cos^2{G \rho})} \\
+    \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + -\cos{2 G \rho})} \\        
+\end{align*}
+Note: $\sin^2{x \rho}  - \cos^2{x \rho} = -\cos{2 x \rho}$
+
+So, for all O,G,P,
+\begin{align*}
+  \overline{\rm AB}  &= 1 \\        
+  \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + -\cos{2 G \rho})} \\
+  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + \sin^2{O \rho}  - \cos^2{O \rho})} \\  
+  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + -\cos{2 O  \rho})} \\
+  \overline{\rm BD}  &= \sqrt{P^2 + r^2(1 + -\cos{2 P \rho}))} \\
+  \overline{\rm AD}  &= \sqrt{(O+G)^2 + r^2(1 + -\cos{2 (O + G)  \rho})} \\
+  \overline{\rm BC}  &= \sqrt{(P+G)^2 + r^2(1 + -\cos{2 (P + G) \rho})} \\      
+\end{align*}
+
+Then we can simplify our distance equations:
+\begin{align*}
+  \overline{\rm AB}  &= 1 \\        
+  \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + -\cos{2 G \rho})} \\
+  \overline{\rm AC} &=   \overline{\rm BD} &= \sqrt{P^2 + r^2(1 + -\cos{2 P \rho}))} \\
+  \overline{\rm AC} &=   \overline{\rm BD} &= \sqrt{((1-G)/2)^2 + r^2(1 + -\cos{ \rho (1-G) }))} \\  
+  \overline{\rm AD} &=  \overline{\rm BC} &=  \sqrt{((P+G)^2 + r^2(1 + -\cos{2 (P + G) \rho})} \\
+  \overline{\rm AD} &=  \overline{\rm BC} &=  \sqrt{((1+ G)/2 )^2 + r^2(1 + -\cos{\rho (1 + G)})} \\        
+\end{align*}
+
+When $G = 0$, $\overline{\rm CD} = 0$. Our solution is improved as we increase $G$ until either $ \overline{\rm CD} = \overline{\rm AC}$, or the
+quantity $ \overline{\rm BC} - \overline{\rm CD} $ starts increasing rather than decreasing (that is, when the derivative is positive.)
+
+Suppose $\overline{\rm C'D'}$ is the shortest edge. Increasing $G$ thereby improves our mimimum, up until the next shortest edge length, $\overline{\rm AC}$.
+This may increase $\overline{\rm BC}$ and $\overline{\rm AD}$, but more slowly (???) than $\overline{\rm C'D'}$ is being increased, until  $\overline{\rm C'D'} =
+\overline{\rm AC}$.
+Note: This is sketchy, can we show that the derivative of our formula for CD  with respect to $G$ is really higher than $AD$? These derivatives will depend on $\rho$ slightly, which is exactly right!

### 2017-02-16 doc/TetrahelixUntwist.tex
major simplfication, and some complexity

@@
 is a face-to-face stack of tetrahedra that winds about a straight axis.
+Because architects, structural engineers, and robotocists are inspired by and follow such mathematical models but can build
+structures and machines of differing or even dynamically changing length, it is useful to develop
+the mathematics of structure formed from tetrahedra where we relax regularity.
 The vertices of the tetrahedra
@@
 Such machines can follow purely regual mathematical models such as the Boerdijk–-Coxeter helix or the Octet Truss\cite{richard1961synergetic}.
-Because architects, structural engineers, and robotocists are inspired by and follow such mathematical models but can build
-structures and machines of differing or even dynamically changing length, it is useful to develop
-the mathematics of structure formed from tetrahedra where we relax regularity. Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
+
+Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
 a term now commonly used. In this paper we reserve BC helix to mean the purely regular structre and use \emph{tetrahelix} to refer
@@
    $ r  \sin(\rho_{bc} \kappa  + c 2 \pi /3) $\\
-   $ \kappa 3  d $
+   $ \kappa 3  h_{bc} $
   \end{tabular}
@@
     $ \theta = \arccos(-2/3) $
+    $ h_{bc} = 1/\sqrt{10} $ \\    
   \end{tabular}      
@@
 indeed holds true (treating $d$ in this equation as $3 h_{bc}$ as defined by
-Gray and Coxeter), where they are using it for the axial height from one node to
+Gray and Coxeter, that is, $d_{bc} = 3h_{bc}$, where they are using it for the axial height from one node to
 the next of a different color, but we use it to mean distance for the same color.
@@
 In choosing $\rho$, one greatly constrains $r$ and $h$, but does not completely
-determine both of them together. In the formulation below we assume that
-the choice of $d_{\rho}$ is more convenient than choosing the radius,
-but that is somewhat arbitrary.
+determine both of them together, so we treat both as parameters.
 
@@
   \begin{tabular}{c}
-   $ r_{\rho} \cos(\frac{\rho \kappa}{2\pi} + c 2 \pi /3) $\\
-   $ r_{\rho}  \sin(\frac{\rho \kappa}{2\pi} + c 2 \pi /3) $\\
+   $ r_{\rho} \cos(\rho \kappa + c 2 \pi /3) $\\
+   $ r_{\rho}  \sin(\rho \kappa + c 2 \pi /3) $\\
    $ d_{\rho} \kappa $
@@
   \label{generalformulaoptimal}
-  The tetrahelices generated by $H_{general}$ are optimal in terms of minimum maximum member length, minimum total member length, and minimum
-  sum of squared lengths.
+  The tetrahelices generated by $H_{general}$ are optimal in terms of minimum maximum member length when $r_{\rho}$ is chosen so that
+  the length of the one-hop edge is equal to the rail length.
 \end{theorem}
@@
 \begin{proof}
-  This requires poof.
+  This requires a minimax argument.
 \end{proof}
@@
 \begin{align*}
-  \text{rail} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n+1,c,\rho,d_{\rho})) = 1 \\
-  \text{one-hop} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}))  \\
-  \text{two-hops} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+2,\rho,d_{\rho}))  \\  
+  \text{rail} &= dist(H_{general}(n,c,\rho,d_{\rho},r_{\rho}),H_{general}(n+1,c,\rho,d_{\rho}),r_{\rho})) = 1 \\
+  \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho},r_{\rho}),H_{general}(n,c+1,\rho,d_{\rho},r_{\rho}))  \\
+  \text{two-hops} &= dist(H_{general}(n,c,\rho,d_{\rho},r_{\rho}),H_{general}(n,c+2,\rho,d_{\rho},r_{\rho}))  \\  
 \end{align*}
@@
 \begin{align*}
-  \text{one-hop} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}))  \\
-  \text{one-hop} &= dist(H_{general}(0,0,\rho,h_{\rho}),H_{general}(0,1,\rho,d_{\rho}))  \\  
-  \text{one-hop}  &= \sqrt{d_{\rho}^2/9 + (r\sin{\frac{\rho(3\cdot 0 + 0)}{2\pi}} - r\sin{\frac{\rho(3\cdot 0 + 0+1)}{2\pi}})^2  +
-    (r\cos{\frac{\rho(3\cdot0+0)}{2\pi}} - r\cos{\frac{\rho(3\cdot + 0+1)}{2\pi}})^2
-  \text{one-hop}  &= \sqrt{d_{\rho}^2/9 + (r\sin{\frac{\rho(0)}{2\pi}} - r\sin{\frac{\rho(1)}{2\pi}})^2  +
-    (r\cos{\frac{\rho(0)}{2\pi}} - r\cos{\frac{\rho(1)}{2\pi}})^2
-  } \\  
+  \text{one-hop} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}),r_{\rho})  \\
+  \text{one-hop} &= dist(H_{general}(0,0,\rho,h_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (,r_{\rho}\sin(\rho(3\cdot 0 + 0)) - r_{\rho}\sin(\rho(3\cdot 0 + 1)+\frac{2\pi}{3}))^2  +
+    (r_{\rho}\cos(\rho(3\cdot0+0)) - r_{\rho}\cos(\rho(3\cdot 0+1) + \frac{2\pi}{3})))^2} \\
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho + \frac{2\pi}{3}))^2  +
+    (r_{\rho} - r_{\rho}\cos(\rho + \frac{2\pi}{3}))^2} \\
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2\sin^2(\rho + \frac{2\pi}{3})  +
+    r_{\rho}^2(1 - \cos(\rho + \frac{2\pi}{3}))^2} \\
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\
 \end{align*}
+
+By similar algebra and trigonometry:
+\begin{align*}
+  \text{two-hops}  &= \sqrt{\frac{4d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\
+\end{align*}
+
+Let $f_{\rho} = \sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3})^2$.
+
+The expression $f_{\rho}$ is maximized when $\rho = 2\pi/6 = 60\degree$, so that
+is in some sense the ``wildest'' rail angle which maximizes the lengths. Since this expression is increasing up until this angle,
+we conclude that:
+\begin{align*}
+  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4d_{\rho}^2}{9} + r_{\rho}^2f_{\rho}} - \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2f_{\rho}} 
+\end{align*}
+
+The analysis below here is incorrect because it doesn't take into account the change in $d_{\rho}$ with $\rho$. In the special case that
+$\rho = 0$, the analysis is correct. Possibly I need to change to use two equations to try to find the optimal $\rho$ here.
+In any case it must unify with the BC math!
+
+Tomorrow try combining with our equation for $d_{\rho}$ to see if I can make it come out.
+
+Since $d_{\rho}$ and $r_{\rho}$ are positive, this difference decreases as $f_{\rho}$ increases. Therefore we decrease the minimax length
+of the whole system as we increase $\rho$ up to $\pi/3$ up unto the point that the shorter, one-hop distance is equal to the rail-length ($1$).
+Therefore, to optimize the whole system so long as $\rho < \pi/3$, we equate one-hop to $1$ to find the optimum radius:
+
+\begin{align*}
+  1 &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\
+  r_{\rho} &= \frac{\sqrt{9-d^2}  }{3\sqrt{\sqrt{3}\sin(\rho) +\cos(\rho) + 2}}
+\end{align*}
+(where $\sqrt{3}\sin(\rho) +\cos{\rho} + 2 \neq 0$), which does not occur when $\rho \leq \pi/3$).
+
+Therefore, by computing $r_{\rho}$ from this equation, we can construct minimax optimal tetrahelix for an $\rho < \pi/3$.
+
+(Note: This fails the check of computing the BC radius for the BC rail angle.)
 
@@
 
-However, choosing $d = 1$ and $\rho = 0$ does fix the radius. We would like to choose the radius so that the
+However, choosing $d = 1$ and $\rho = 0$ does not fix the radius. We would like to choose the radius so that the
 minimax difference between the lengths is as small as possible.
@@
   \text{rail} &=  1 \\
-  \text{one-hop} &= \sqrt{\frac{1}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}\\
-\text{one-hop}  &= \sqrt{\frac{1}{9} + a^2} \\
-    \text{two-hops} &= \sqrt{\frac{2}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}  \\
-\text{two-hops}    &= \sqrt{\frac{4}{9} + a^2}
+  \text{one-hop} &= \sqrt{\frac{1}{9} + 3r^2}\\
+\text{two-hops}    &= \sqrt{\frac{4}{9} + 3r^2}
 \end{align*}
@@
 \begin{align*}
- \frac{\partial \text{two-hops} - \text{one-hop}}{a} &= \frac{\partial \sqrt{4/9 + a^2} - \sqrt{1/9 + a^2}}{\partial a} \\
-  \frac{\partial \text{two-hops} - \text{one-hop}}{a} &= \frac{a}{\sqrt{a^2 + 4/9}} - \frac{a}{\sqrt{ a^2 + 1/9}} 
+ \frac{\partial \text{two-hops} - \text{one-hop}}{r} &= \frac{\partial \sqrt{4/9 + 3r^2} - \sqrt{1/9 + 3r^2}}{\partial r} \\
+  \frac{\partial \text{two-hops} - \text{one-hop}}{r} &= 9r (\frac{1}{\sqrt{27r^2 + 4}} - \frac{1}{\sqrt{ 27r^2 + 1}}) 
 \end{align*}
-which is negative for all $a> 0$. Thererfore two-hop - one-hop
-is minimized when we maximize $a$, up until one-hop = rail.
+which is negative for all $r> 0$. Thererfore two-hop - one-hop
+is minimized when we maximize $r$, up until one-hop = rail.
 
-Note that two-hops increases more and more slowly as $a$ increases. Therefore the minimum maximum will
-be obtained with the value of $a$ that when $one-hop = 1$. This can be observed from the
-plot of two-hops - one-hops as a function of $a$, or by observing that the derivate of two-hops - one-hop
-is negative for $a > 0$. (That is, the value of one-hop increases faster than two-hops.)
-
-We seek the value of $a$ that minimizes the maximum difference between these three lengths. We find
-by numerical experimentation that this difference is minimized that the one-hop distance is equal to $1$,
-which also has the pleasing property of giving us only two lengths. Then
+Note that two-hops increases more and more slowly as $r$ increases. Therefore the minimum maximum will
+be obtained with the value of $r$ that when $one-hop = 1$. This can be observed from the
+plot of two-hops - one-hops as a function of $r$, or by observing that the derivate of two-hops - one-hop
+is negative for $r > 0$. (That is, the value of one-hop increases faster than two-hops.) 
+Setting the one-hop distance to $d = 1$ also has the pleasing property of giving us only two lengths. Then
 \begin{align*}
-   1  &=  \sqrt{\frac{1}{9} + a^2} \\
-     a  &= \sqrt{\frac{8}{9}} 
+   1  &=  \sqrt{\frac{1}{9} + 3r^2} \\
+   r  &= \sqrt{\frac{8}{27}} \\
+   r &\approx 0.5443
 \end{align*}
 
-Therefore $ r = \sqrt{\frac{8}{27}} \approx 0.5443 $, producing length difference in the two-hop rail of
-$\frac{2}{\sqrt{3}}$
+This radius produces a two-hop rail length of
+$\frac{2}{\sqrt{3}}$. The difference between this 
 and $1$ of $\approx 15.47\% $.
 
-Note: Another interesting solution is derived by setting (one-hop + two-hop)/2 = 1,  occurs at $a = \sqrt{35/3}/4$,
+Note: Another interesting solution is derived by setting (one-hop + two-hop)/2 = 1,  occurs at $r = \sqrt{35}/4$,
 which produces three length classes of $11/12, 12/12, 13/12$.
-
-\begin{conjecture}
-  The equitetrabeam is also optimal under the metric of the total length of all members 
-  for an equilateral tetrabeam isomorphic to the Boerdijk--Coxeter helix.
-\end{conjecture}
-
-\begin{proof}
-
-\end{proof}
 
@@
 
-Note: Need to understand how pitch is computed from negative lambda values.
-
 We can then create a continuum of radius, length, rho to place into our general equation
@@
 TODO:
+
+See if we can accurately compute the derivative of two-hop - one-hop and if it is always negative, meaning that
+it is always optimal to set one-hop = 1.  The we have a way to compute one-hope.
 
@@
 Note: This is sketchy, can we show that the derivative of our formula for CD  with respect to $G$ is really higher than $AD$? These derivatives will depend on $\rho$ slightly, which is exactly right!
+
+\begin{align*}
+  \text{rail} &=  1 \\
+  \text{one-hop} &= \sqrt{\frac{1}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}\\
+\text{one-hop}  &= \sqrt{\frac{1}{9} + a^2} \\
+    \text{two-hops} &= \sqrt{\frac{2}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}  \\
+\text{two-hops}    &= \sqrt{\frac{4}{9} + a^2}
+\end{align*}
+Computing the derivative of two-hops - one-hop:
+\begin{align*}
+ \frac{\partial \text{two-hops} - \text{one-hop}}{a} &= \frac{\partial \sqrt{4/9 + a^2} - \sqrt{1/9 + a^2}}{\partial a} \\
+  \frac{\partial \text{two-hops} - \text{one-hop}}{a} &= \frac{a}{\sqrt{a^2 + 4/9}} - \frac{a}{\sqrt{ a^2 + 1/9}} 
+\end{align*}

### 2017-02-16 doc/TetrahelixUntwist.tex
fixed a major problem in my distance formula, now ready to try optimality again, and eventually code

@@
   1^2 &= d^2 + (2 r \sin{ \rho / 2})^2 \\
-  1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 
+  1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 \\
+  d^2 &= 1 - 4 r^2 (\sin{ \rho / 2})^2   
 \end{align*}
@@
 \begin{align*}
-  \text{one-hop} &= dist(H_{general}(n,c,\rho,h_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}),r_{\rho})  \\
-  \text{one-hop} &= dist(H_{general}(0,0,\rho,h_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (,r_{\rho}\sin(\rho(3\cdot 0 + 0)) - r_{\rho}\sin(\rho(3\cdot 0 + 1)+\frac{2\pi}{3}))^2  +
-    (r_{\rho}\cos(\rho(3\cdot0+0)) - r_{\rho}\cos(\rho(3\cdot 0+1) + \frac{2\pi}{3})))^2} \\
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho + \frac{2\pi}{3}))^2  +
-    (r_{\rho} - r_{\rho}\cos(\rho + \frac{2\pi}{3}))^2} \\
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2\sin^2(\rho + \frac{2\pi}{3})  +
-    r_{\rho}^2(1 - \cos(\rho + \frac{2\pi}{3}))^2} \\
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\
+  \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}),r_{\rho})  \\
+  \text{one-hop} &= dist(H_{general}(0,0,\rho,d_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r_{\rho}\sin(\rho((1/3)\cdot 0 + 0)) - r_{\rho}\sin(\rho((1/3)\cdot 0 + 1)+\frac{2\pi}{3}))^2  +
+    (r_{\rho}\cos(\rho((1/3)\cdot0+0)) - r_{\rho}\cos(\rho((1/3)\cdot 0+1) + \frac{2\pi}{3})))^2} \\
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho/3 + \frac{2\pi}{3}))^2  +
+    (r_{\rho} - r_{\rho}\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
+    r_{\rho}^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
+  \text{but... } & d_{\rho}^2 &= 1 - 4 r_{\rho}^2 (\sin{ \rho / 2})^2 \\
+  \text{one-hop}  &= \sqrt{\frac{1 - 4 r_{\rho}^2 (\sin{ \rho / 2})^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\  
 \end{align*}
+
+To Be Done: I need to see if the one-hop formulat can be simplified.
+Compute the two-hop formula and test that it gives length 1 when the BC constants. -- YES!
 
@@
 \begin{align*}
-  \text{two-hops}  &= \sqrt{\frac{4d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\
+  \text{two-hops}  &= \sqrt{4\frac{1 - 4 r_{\rho}^2 (\sin{ \rho / 2})^2}{9} + r_{\rho}^2(\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
 \end{align*}
 
-Let $f_{\rho} = \sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3})^2$.
+Note: it is not clear I am allowed to do this, because the two-hop function is different!
+
+Let $f_{\rho} = \sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3})^2$.
+Let $g_{\rho} = \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3})^2$.
 
@@
 \begin{align*}
-  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4d_{\rho}^2}{9} + r_{\rho}^2f_{\rho}} - \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2f_{\rho}} 
+  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4d_{\rho}^2}{9} + r_{\rho}^2g_{\rho}} - \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2f_{\rho}} 
 \end{align*}
 
-The analysis below here is incorrect because it doesn't take into account the change in $d_{\rho}$ with $\rho$. In the special case that
-$\rho = 0$, the analysis is correct. Possibly I need to change to use two equations to try to find the optimal $\rho$ here.
-In any case it must unify with the BC math!
-
-Tomorrow try combining with our equation for $d_{\rho}$ to see if I can make it come out.
+To Be Done: I need to plot this expression, see if it has a maximum, and see if it always decreasing in this range, to see if we can prove optimality.
 
@@
 \begin{align*}
-  1 &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\
-  r_{\rho} &= \frac{\sqrt{9-d^2}  }{3\sqrt{\sqrt{3}\sin(\rho) +\cos(\rho) + 2}}
+  1 &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
+  r_{\rho} &= \frac{2 \sqrt{2} }{\sqrt{9 \sqrt{3} sin(\rho/3) + 9 \cos(\rho/3) + 2 cos(\rho)+ 16 }}
 \end{align*}
-(where $\sqrt{3}\sin(\rho) +\cos{\rho} + 2 \neq 0$), which does not occur when $\rho \leq \pi/3$).
+(where $9 \cos(\rho/3) + 2 cos(\rho)+ 16  \neq 0$), which does not occur when $\rho \leq \pi/3$).
 

### 2017-02-17 doc/TetrahelixUntwist.tex
significant corrections

@@
 \newtheorem{proofsketch}{Proof Sketech}
+
+\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
+
 \usepackage{draftwatermark}
@@
 
-\title{Untwisting the Tetrahelix (v0.4)}
+\title{Untwisting the Tetrahelix (v0.5)}
 \author{Robert L. Read \texttt{read.robert@gmail.com} \and
@@
     r_{\rho}^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
+  %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.
   \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
-  \text{but... } & d_{\rho}^2 &= 1 - 4 r_{\rho}^2 (\sin{ \rho / 2})^2 \\
-  \text{one-hop}  &= \sqrt{\frac{1 - 4 r_{\rho}^2 (\sin{ \rho / 2})^2}{9} + r_{\rho}^2(\sin^2(\rho + \frac{2\pi}{3})  + (1 - \cos(\rho + \frac{2\pi}{3}))^2)} \\  
+  d_{\rho}^2 &= 1 - 4 r_{\rho}^2 (\sin( \rho / 2)^2 \\
+  %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.  
+  \text{one-hop}  &= \sqrt{\frac{1}{9}  + r_{\rho}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
+  %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.    
 \end{align*}
@@
 \begin{align*}
-  \text{two-hops}  &= \sqrt{4\frac{1 - 4 r_{\rho}^2 (\sin{ \rho / 2})^2}{9} + r_{\rho}^2(\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
+  \text{two-hops}  &= \sqrt{\frac{4}{9} + r_{\rho}^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
 \end{align*}
@@
 
-Let $f_{\rho} = \sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3})^2$.
-Let $g_{\rho} = \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3})^2$.
+Let $f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)$.
+Let $g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} + (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)$.
 
-The expression $f_{\rho}$ is maximized when $\rho = 2\pi/6 = 60\degree$, so that
-is in some sense the ``wildest'' rail angle which maximizes the lengths. Since this expression is increasing up until this angle,
-we conclude that:
 \begin{align*}
-  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4d_{\rho}^2}{9} + r_{\rho}^2g_{\rho}} - \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2f_{\rho}} 
+  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4}{9} + r_{\rho}^2g_{\rho}} - \sqrt{\frac{1}{9} + r_{\rho}^2f_{\rho}} 
 \end{align*}
 
-To Be Done: I need to plot this expression, see if it has a maximum, and see if it always decreasing in this range, to see if we can prove optimality.
+If the partial derivative of $\text{two-hops} - \text{one-hop}$ with respect to the
+radius is negative up until $\rho$ up until $\rho_{bc}$ when it is $0$, then
+we will opitmize the overall minimax distance by choosing the largest radius
+up until one-hop $= 1$, the rail-edge length. Numerical test suggests that this is true.
 
-Since $d_{\rho}$ and $r_{\rho}$ are positive, this difference decreases as $f_{\rho}$ increases. Therefore we decrease the minimax length
-of the whole system as we increase $\rho$ up to $\pi/3$ up unto the point that the shorter, one-hop distance is equal to the rail-length ($1$).
-Therefore, to optimize the whole system so long as $\rho < \pi/3$, we equate one-hop to $1$ to find the optimum radius:
+Therefore we decrease the minimax length
+of the whole system as we increase the radius
+up unto the point that the shorter, one-hop distance is equal to the rail-length ($1$).
+Therefore, to optimize the whole system so long as $\rho < \rho_{bc}$,
+we equate one-hop to $1$ to find the optimum radius:
 
 \begin{align*}
-  1 &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
-  r_{\rho} &= \frac{2 \sqrt{2} }{\sqrt{9 \sqrt{3} sin(\rho/3) + 9 \cos(\rho/3) + 2 cos(\rho)+ 16 }}
+  1 &=  \sqrt{\frac{1}{9}  + r_{\rho}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
+  r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }} \numberthis  \label{eqrhoopt} \\
 \end{align*}
-(where $9 \cos(\rho/3) + 2 cos(\rho)+ 16  \neq 0$), which does not occur when $\rho \leq \pi/3$).
+(where denominator $  \neq 0$).
 
-Therefore, by computing $r_{\rho}$ from this equation, we can construct minimax optimal tetrahelix for an $\rho < \pi/3$.
+Note: $ d_{opt} $ is computed by $\rho, r_{opt}$ via the rail equation \eqref{eqrhoopt}.
+
+Therefore, by computing $r_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $\rho < \rho_{bc}$.
+
+\begin{theorem}
+  \label{optimality}
+  For any rail angle $\rho$ where $\rho \leq \rho_{bc}$, a tetrahelix of minimum maximum edge length
+  difference is generated by $H_{general}(n,c,\rho,d_{\rho},r_{opt})$, where $r_{opt}$ and $d_{opt}$ are
+  computed from $\rho$. 
+\end{theorem}
+
+\begin{proof}
+  TBD: The Even thirds theorem tells us an optimal will have even thirds.  We have shown
+  that $r_{opt}$ minimizes the maximum length.
+  \end{proof}
 
@@
 
-Just as $H_{general}$ constructs the BC helix (with careful and non-obvious choices of parameters) which is an important
-special case due to its regularity, it constructs an additional special (degenerate) case when the rail angle $\rho = 0$
-and $d = 1$ (the edgelength), where the cross sectional area is an equilateral triangle of unchanging orientation.
+Just as $H_{general}$ constructs the BC helix (with careful and non-obvious choices of parameters)
+which is an important
+special case due to its regularity, it constructs an additional special
+(degenerate) case when the rail angle $\rho = 0$
+and $d = 1$ (the edgelength), where the cross sectional area is
+an equilateral triangle of unchanging orientation.
 We call this the \emph{equitetrabeam}.
 
-However, choosing $d = 1$ and $\rho = 0$ does not fix the radius. We would like to choose the radius so that the
+However, choosing $d = 1$ and $\rho = 0$ does not fix the radius.
+We would like to choose the radius so that the
 minimax difference between the lengths is as small as possible.
@@
 
-\begin{theorem}
-The equitetrabeam with minimal maximal edge difference is produced by $H_{general}$ when $ r = \sqrt{\frac{8}{27}} $.
-  \end{theorem}
+\begin{corollary}
+  The equitetrabeam with minimal maximal edge difference is produced
+  by $H_{general}$ when $ r = \sqrt{\frac{8}{27}} $.
+  \end{corollary}
 
@@
 
-We observe that it by thinking of the straight lines of the Equitetrabeam as a degenerate helix of zero curvature,
+We observe that by thinking of the straight lines of the
+Equitetrabeam as a degenerate helix of zero curvature,
 it should be possible to define a smoothly varying continuum between the Boerdijk--Coxeter helix and the Equitetrabeam and every
@@
     $\kappa = n + c/3$ \\
+    $ r_{opt} =  \text{is used : \eqref{eqrhoopt}} $ \\    
     $ \phi_{\lambda} =  \lambda \rho_{bc}  + 0 $\\
@@
 TODO:
+
+Check every step of my derivation at rho = 0 and the BC values.
+
+Found something.  So now the computation of the optimal radii seems slightly better than what we had before.
+We have not, however, proven it to be optimal in the ranges involved, but at least we seem to be computing it correctly.
 

### 2017-02-17 js/tetrahelix_math.js

@@ -33,6 +33,8 @@ var EQTBr =  (2/3)*Math.sqrt(2/3);
 var EQTBd = 1;
 var EQTBrho = 0;
 
+var USE_OPTIMAL_RADIUS = true;
+
 
 // This from https://github.com/josdejong/Mathjs/blob/develop/lib/utils/bignumber/nearlyEqual.js
 function nearlyEqual(x, y, epsilon) {
@@ -85,12 +87,54 @@ function find_rrho_from_d(rho,d) {
     return find_rrho_from_d_el(rho,d,1);
 }
 
+function optimal_radius(rho,el) {
+    var numer = 2*el;
+    var t1 = Math.sqrt(3) * Math.sin(rho/3);
+    var t2 = Math.cos(rho/3);
+    var t3 = Math.cos(rho);
+    var t4 = 8;
+    var denom = Math.sqrt(9*(t1 + t2)/2 + t3 + t4);
+    return numer/denom;
+}
 
-function H_general(n,c,rho,d,r) {
+function one_hop(r,rho,el) {
+    var t1 = 1/9;
+    var t2 = -4*Math.sin(rho/2)*Math.sin(rho/2)/9;
+    var t3 = Math.sin(rho/3 + 2*Math.PI/3);
+    var t4 = (1 - Math.cos(rho/3 + 2*Math.PI/3));
+    return Math.sqrt(t1 + r*r*(t2 + t3*t3 + t4*t4));
+}
+
+function two_hop(r,rho,el) {
+    var t1 = 4/9;
+    var t2 = -16*Math.sin(rho/2)*Math.sin(rho/2)/9;
+    var t3 = Math.sin(2*rho/3 + 4*Math.PI/3);
+    var t4 = (1 - Math.cos(2*rho/3 + 4*Math.PI/3));
+    return Math.sqrt(t1 + r*r*(t2 + t3*t3 + t4*t4));
+}
+
+function test_optimal_radius() {
+    var MAX_DEGREES = 45;
+    for(var i = 0; i < 100;i++) {
+	var rho = Math.PI*(i*MAX_DEGREES/100)/180;
+	var r = optimal_radius(rho,1.0);
+	for(var j = 0; j < 10; j++) {
+	    // iterate rj centered around the optimal distance.
+	    var rj = r/2 + (j/10)*r;
+	    var h1 = one_hop(rj,rho,1.0);
+	    var h2 = two_hop(rj,rho,1.0);
[…]

### 2017-02-17 doc/TetrahelixUntwist.tex
improvements in figures and others

@@
 \begin{figure}[H] %float with two figures
+  \label{series}
   \centering
-     \includegraphics[width=0.4\textwidth]{figures/Tetrahelix0.png}
-     \caption{Regular Tetrahelix}
+     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
+     \caption{A Series of Tetrahelices, BC Helix in Foreground.}
 \end{figure}
@@
 has planar faces and has, for example, an equilateral triangular profile.
+In Figure \ref{series}, the closest helix is the BC helix.
 
@@
 From Robert Gray's site, repeating formula by H.S.M. Coxeter:
-\[
+\begin{equation}
 V(n) =
@@
   \end{tabular}      
-\]
+\end{equation}
 where $n$ represents each integer numbered node in succession.
@@
 Such a helix can be written:
-\[
+\begin{equation}
 H_{BCcolored}(n,c) =
@@
   \end{tabular}      
-  \]
+\end{equation}
 
@@
 
-Consider any tetrahelix in which the axes of the helices are parallel to $z$ but not coincident, but in which all three helices have the same
-radius. Consider the projection along the $z$ axis, which will be a figure of dots and connecting segments in the $xy$ plane. The convex
-hull for any one helix projection will be a circle (if its pitch is irrational) or an polygon if rational. So long as its rail angle is
-not $0$, it will have at least two points in the plane. One of these will be longer and will be made shorter by moving that helix closer
-to the midpoint of the other two in the $xy$ plane. Even if the rail angle is $\pi$, there will be two vertices for each rail, each of
-which is connected to both vertices of the other two rails. At lesast one of these lines is a longest line which will be made shorter by moving
-that helix in the $xy$ plane closer to the midpoint of the other two.
+Consider any tetrahelix in which the axes of the helices are parallel
+to $z$ but not coincident, but in which all three helices have the
+same radius. Consider the projection along the $z$ axis, which will be
+a figure of dots and connecting segments in the $xy$ plane. The convex
+hull for any one helix projection will be a circle (if its pitch is
+irrational) or an polygon if rational. So long as its rail angle is
+not $0$, it will have at least two points in the plane. One of these
+will be longer and will be made shorter by moving that helix closer to
+the midpoint of the other two in the $xy$ plane. Even if the rail
+angle is $\pi$, there will be two vertices for each rail, each of
+which is connected to both vertices of the other two rails. At lesast
+one of these lines is a longest line which will be made shorter by
+moving that helix in the $xy$ plane closer to the midpoint of the
+other two.
 
@@
  Now now that we have coincident axes, the same pitch, we can go on to the hard proof about where they occur.
-
- \begin{figure}[H]
-     \centering
-     \includegraphics[width=0.9\textwidth]{figures/TetrahelixColoringDiagram.png}
-     \caption{Coloring of an (untwisted) Tetrabeam}
- \end{figure}
 
@@
 
-\[
+\begin{equation}
 H_{BCsymmmetric}(n,c) =
@@
     $\rho_{bc} = (3 \theta - 2 \pi)$ \\
-    $ \theta = \arccos(-2/3) $
+    $ \theta = \arccos(-2/3) $ \\
     $ h_{bc} = 1/\sqrt{10} $ \\    
   \end{tabular}      
-\]
+\end{equation}
 
@@
   1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 \\
-  d^2 &= 1 - 4 r^2 (\sin{ \rho / 2})^2   
+  d^2 &= 1 - 4 r^2 (\sin{ \rho / 2})^2    \numberthis  \label{railangle} \\
 \end{align*}
@@
 Rewriting our formulation in terms of $\rho$:
-\[
+\begin{equation}
 H_{general}(n,c,\rho,d_{\rho},r_{\rho}) =
@@
   \end{tabular}      
-\]
+\end{equation}
 
@@
 up unto the point that the shorter, one-hop distance is equal to the rail-length ($1$).
-Therefore, to optimize the whole system so long as $\rho < \rho_{bc}$,
+Therefore, to optimize the whole system so long as $\rho \leq \rho_{bc}$,
 we equate one-hop to $1$ to find the optimum radius:
@@
 
-Note: $ d_{opt} $ is computed by $\rho, r_{opt}$ via the rail equation \eqref{eqrhoopt}.
+Note: $ d_{opt} $ is computed by $\rho, r_{opt}$ via the rail angle equation \eqref{railangle}.
 
+\begin{align*}
+  d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
+  d_{opt}^2 &= 1 - 4 \frac{4}{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 } (\sin{ \rho / 2})^2   \\
+  d_{opt}^2 &= 1 - \frac{32}{9 ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 } (\sin{ \rho / 2})^2   \\
+  d_{opt}^2 &= 1 - \frac{8 sin^2(\rho) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
+    d_{opt} &= \sqrt{1 - \frac{8 sin^2(\rho) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
+\end{align*}
 Therefore, by computing $r_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $\rho < \rho_{bc}$.
@@
 
-However, choosing $d = 1$ and $\rho = 0$ does not fix the radius.
-We would like to choose the radius so that the
-minimax difference between the lengths is as small as possible.
-
- \begin{figure}[H]
-     \centering
-     \includegraphics[width=0.9\textwidth]{figures/EquilateralDiagram.png}
-     \caption{Coloring of an (untwisted) Tetrabeam}
- \end{figure}
+However, choosing $d = 1$ and $\rho = 0$ we use Equation \eqref{eqrhoopt} to find the radius of 
+optimal minimax difference.
 
@@
 
-When $\rho = 0$, our formulae for distances are particular simple. Let $a$ be the length of the equilateral triangle
-forming the beam cross section. Then by geometry $r = a \sqrt{3}$.
 \begin{align*}
@@
 
+In Figure \ref{series}, the furthest tetrahelix is the optimal equitetrabeam.
+
 \section{Adding an Untwisting Parameter}
@@
 it should be possible to define a smoothly varying continuum between the Boerdijk--Coxeter helix and the Equitetrabeam and every
-curvature and torsion between the two.
-
-We seek to unify this with degenerate helix formula for the equitetrabeam:
-\[
-H_{etb}(n,c) =
-\left [
-  \begin{tabular}{c}
-   $ r_{etb}  \cos( 0 \cdot \kappa  + c 2 \pi /3) $\\
-   $ r_{etb}  \sin( 0 \cdot \kappa  + c 2 \pi /3) $\\
-   $ \kappa d_{etb} $
-  \end{tabular}
-\right ],
-\text{where:}
-  \begin{tabular}{c}
- $\kappa = n + c/3$ \\
-    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
-   $ \theta = \arccos(-2/3) $
-  \end{tabular}      
-\]
-where $ r_{etb} = \sqrt{\frac{8}{27}}$, $d_{etb} = 1$,
+curvature and torsion between the two. It seems most convenient to define this continuum in terms
+of the rail angle $\rho$, where $0 \leq \rho \leq \rho_{bc}$.
 
@@
 axial growth can all be linearly interpolated with a parameter $\lambda$ between their high values (for the BC helix)
-and low values (for the equitetrabeam):
+and low values (for the equitetrabeam).
 
 \begin{align*}
-r_{\lambda}  &=  \lvert \lambda \rvert \cdot (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
-d_{\lambda} &=   \lvert \lambda \rvert \cdot (3 \sqrt{10} - 1) + 1 \\
-\phi_{\lambda} &=  \lambda \cdot \rho_{bc}  + 0
+\phi_{\lambda} &=  \lambda \cdot \rho_{bc}   \\
+r_{\lambda}  &=  r_{opt}(\phi) \\
+d_{\lambda} &=   d_{opt}(\phi) \\
 \end{align*}
@@
 
-\[
+\begin{equation}
 H_{continuum}(n,c,\lambda) =
@@
     $\kappa = n + c/3$ \\
-    $ r_{opt} =  \text{is used : \eqref{eqrhoopt}} $ \\    
-    $ \phi_{\lambda} =  \lambda \rho_{bc}  + 0 $\\
+    $ \phi_{\lambda} =  \lambda \rho_{bc}  $\\
     $\rho_{bc} = (3 \theta - 2 \pi)$ \\
@@
   \end{tabular}      
-\]
+\end{equation}
+
 A value of $\lambda = 0$ generates the equitetrabeam, and $\lambda = 1$ generates the Boerdijk--Coxeter helix, and every
@@
  Negative values of $\lambda$ generate clockwise tetrahelices; positive generate counter-clockwise helices.
+ (Note: In fact there is something wrong with my math, negative lambda values do produces opposit chirality
+ but the lengths are not the same as the positive values.  I need to track this down.)
 
@@
 \[
-p(\lambda) = 2 \pi  \cdot \frac{(\frac{8}{27} -1) \lambda +1)}{ \lambda  \rho_{bc} }
+p(\lambda) = 2 \pi  \cdot d_{opt}
 \]
 
-We can then create a continuum of radius, length, rho to place into our general equation
-to create continuum of helices between the BC and equitetrabeam. This continuum is 
-minimax-length optimal at its endpoints, and may be optimal throughout. This untwisting is accomplished
-only by changing the length of the two-hop member.
+There is thus an optimal continuum of tetrahelices untwisting between BC and equitetrabeam.
+Perhaps surprisingly, this untwisting is accomplished only by changing the length of the two-hop member.
 
@@
 \end{figure}
+
+\section{Conclusion}
 
@@
 \end{align*}
+
+Now basic components of the helix, which are the radius $r$, the rate of rotation, and the rate of
+axial growth can all be linearly interpolated with a parameter $\lambda$ between their high values (for the BC helix)
+and low values (for the equitetrabeam):
+
+\begin{align*}
+r_{\lambda}  &=  \lvert \lambda \rvert \cdot (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
+d_{\lambda} &=   \lvert \lambda \rvert \cdot (3 \sqrt{10} - 1) + 1 \\
+\phi_{\lambda} &=  \lambda \cdot \rho_{bc}  + 0
+\end{align*}
+to create a formula that generates a continuum of tetrahedral structures:
+
+\[
+H_{continuum}(n,c,\lambda) =
+\left [
+  \begin{tabular}{c}
+   $ r_{\lambda} \cos(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
+   $ r_{\lambda}  \sin(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
+   $ d_{\lambda} \kappa $
+  \end{tabular}
+  \right ],
+\text{where:}
+  \begin{tabular}{c}
+    $\kappa = n + c/3$ \\
+    $ r_{opt} =  \text{is used : \eqref{eqrhoopt}} $ \\    
+    $ \phi_{\lambda} =  \lambda \rho_{bc}  + 0 $\\
+    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
+   $ \theta = \arccos(-2/3) $
+  \end{tabular}      
+\]

### 2017-02-18 doc/TetrahelixUntwist.tex
some improvements

@@
   \centering
-     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
-     \caption{A Series of Tetrahelices, BC Helix in Foreground.}
+     \includegraphics[width=0.95\textwidth]{figures/BCHelixCloseUp.png}
+     \caption{BC Helix Close-up}
 \end{figure}
@@
 
-To Be Done: I need to see if the one-hop formulat can be simplified.
-Compute the two-hop formula and test that it gives length 1 when the BC constants. -- YES!
-
 By similar algebra and trigonometry:
 \begin{align*}
-  \text{two-hops}  &= \sqrt{\frac{4}{9} + r_{\rho}^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
+  \text{two-hops}  &= \sqrt{\frac{4}{9} + r_{\rho}^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
 \end{align*}
 
-Note: it is not clear I am allowed to do this, because the two-hop function is different!
+We would really like to know the partial derivative of the two-hops - one-hop with respect
+to the radius to be able to understand how to choose the radius to form the minimimax optimum.
 
-Let $f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)$.
-Let $g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} + (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)$.
+Let:
+\begin{equation}
+  f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9}
+  \end{equation}
+\begin{equation}
+  g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} 
+\end{equation}
 
+\begin{equation}
+  j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)
+\end{equation}
+\begin{equation}
+  k_{\rho} = (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)
+\end{equation}
+
+Then:
 \begin{align*}
-  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4}{9} + r_{\rho}^2g_{\rho}} - \sqrt{\frac{1}{9} + r_{\rho}^2f_{\rho}} 
+  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4}{9}  + r_{\rho}^2(g_{\rho}+ j_{\rho})}
+  - \sqrt{\frac{1}{9} +r_{\rho}^2(f_{\rho}+k_{\rho}) }
 \end{align*}
 
-If the partial derivative of $\text{two-hops} - \text{one-hop}$ with respect to the
+% Using wolfram alph we se this derivate remains negative in this range....
+% plot d/dr sin(2r/3 + 4pi/3)^2 - sin(r/3 + 2pi/3)^2 + (1 - cos(2r/3 + 4pi/3))^2 -(1-cos(r/3 + 2pi/3))^2 from 0 to 35.44 degrees
+% in other words
+
+% This part is also negative withing this range...
+%  d/dr -(16/9)sin(r/2)^2 - -(4/9)sin(r/2)^2 from 0 to 35.44 degrees
+
+%% Using Mathematica, I get:
+%% f[x_, r_] := 
+%%  Sqrt[4/9 + 
+%%     x^2 (-16 Sin[r/2]^2/9 + 
+%%        Sin[2 r/3 + 4 Pi /3]^2 + (1 - Cos[2 r/3 + 4 Pi/3])^2)] - 
+%%   Sqrt[1/9 + 
+%%     x^2*(-4*Sin[r/2]^2/9 + 
+%%        Sin[r/3 + 2 Pi/3]^2 + (1 - Cos[r/3 + 2 Pi/3])^2) ]
+%% N[N[f[1, 1]]]
+
+%% Plot3D[D[f[x, r]], {x, 0, 2}, {r, 0, Pi}]
+
+%% This grahp demonstrates the derivative is always negative.
+
+By graph inspection using Mathematica, we see the partial derivative of this with respect to
+radius $r_{\rho}$ is always negative.
+Since the partial derivative of $\text{two-hops} - \text{one-hop}$ with respect to the
 radius is negative up until $\rho$ up until $\rho_{bc}$ when it is $0$, then
@@
 because their ability to withstand axial forces seem to diminish significantly.
+
+\begin{figure}[H] %float with two figures
+  \label{series}
+  \centering
+     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
+     \caption{A Series of Tetrahelices, BC Helix in Foreground.}
+\end{figure}
 

### 2017-02-18 doc/TetrahelixUntwist.tex
some observations added

@@
 
-The Boerdijk--Coxeter helix\cite{coxeter1985simplicial} (BC helix),
-is a face-to-face stack of tetrahedra that winds about a straight axis.
-Because architects, structural engineers, and robotocists are inspired by and follow such mathematical models but can build
-structures and machines of differing or even dynamically changing length, it is useful to develop
-the mathematics of structure formed from tetrahedra where we relax regularity.
-The vertices of the tetrahedra
-lie upon three
-helices about the central axis.
-The Tetrobot/Glussbot\cite{TetrobotBook} project
-uses the regularity of this geometry to make a tentacle-like robot that can crawl like a slug or mollusc.
-The Tetrobot concept
-is to use mechanical members, called actuators, which can change their length, connected by special joints, called the Song-Kwon-Kim\cite{song2003spherical} or turret joint,
-which allow many
-members to come to a single point.
-Such machines can follow purely regual mathematical models such as the Boerdijk–-Coxeter helix or the Octet Truss\cite{richard1961synergetic}.
+The Boerdijk--Coxeter helix\cite{coxeter1985simplicial} (BC helix), is
+a face-to-face stack of tetrahedra that winds about a straight axis.
+Because architects, structural engineers, and robotocists are inspired
+by and follow such mathematical models but can build structures and
+machines of differing or even dynamically changing length, it is
+useful to develop the mathematics of structure formed from tetrahedra
+where we relax regularity.  The vertices of the tetrahedra lie upon
+three helices about the central axis.  The
+Tetrobot/Glussbot\cite{TetrobotBook} project uses the regularity of
+this geometry to make a tentacle-like robot that can crawl like a slug
+or mollusc.  The Tetrobot concept is to use mechanical members, called
+actuators, which can change their length, connected by special joints,
+called the Song-Kwon-Kim\cite{song2003spherical} or turret joint,
+which allow many members to come to a single point.  Such machines can
+follow purely regual mathematical models such as the Boerdijk–-Coxeter
+helix or the Octet Truss\cite{richard1961synergetic}.
 
@@
 
-BC helix does not rest on a plane in a simple way. It is convenient to be able to ``untwist'' it and form a tetrahelix space frame that
-has a flat planar surface. By making length changes in a certain way, we can untwist a tetrahelix to form a \emph{tetrabeam} which
-has planar faces and has, for example, an equilateral triangular profile.
-In Figure \ref{series}, the closest helix is the BC helix.
+\begin{figure}[H] %float with two figures
+  \label{series}
+  \centering
+     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
+     \caption{A Series of Tetrahelices, BC Helix in Foreground.}
+\end{figure}
+
+BC helix does not rest on a plane in a simple way. It is convenient to
+be able to ``untwist'' it and form a tetrahelix space frame that has a
+flat planar surface. By making length changes in a certain way, we can
+untwist a tetrahelix to form a \emph{tetrabeam} which has planar faces
+and has, for example, an equilateral triangular profile.  In Figure
+\ref{series}, the closest helix is the BC helix.
 
@@
 
-If you can choose member lengths, you can form a linear combination of the equitetrabream lengths and the completely regular
-lengths of the tetrahelix, thereby choosing the torsion.  If you are designing a space frame, this is a static design choice,
-in a robot, it is a dynamic choice that can be used to twist the robot and/or exert torsion on the environment.
+If you can choose member lengths, you can form a linear combination of
+the equitetrabream lengths and the completely regular lengths of the
+tetrahelix, thereby choosing the torsion.  If you are designing a
+space frame, this is a static design choice, in a robot, it is a
+dynamic choice that can be used to twist the robot and/or exert
+torsion on the environment.
 
-Ideally we would have a simple formula for defining the nodes based on any torsion we choose.
-Unfortunately, it is not obvious that a linear combination of lengths produces a simple formula.
-It is a goal of this paper to relate these two approaches to generating a tetrahelix continuum.
+Ideally we would have a simple formula for defining the nodes based on
+any torsion we choose.  Unfortunately, it is not obvious that a linear
+combination of lengths produces a simple formula.  It is a goal of
+this paper to relate these two approaches to generating a tetrahelix
+continuum.
 
@@
 
-$\theta$ is approximately $131.8103149$ degrees.
+$\theta$ is approximately $131.81$ degrees.
 The angle $\theta$ is the rotation of a \emph{each} tetrahedra.
@@
 \begin{equation}
+  \label{graycoxeter}
 V(n) =
@@
 
-This formula defines a helix, but it is not any of the helices of the BC helix, but rather one that winds three times
-as rapidly through all nodes. To a designer of tetrahelices, it is more natural to think of the three helices which
-are visually apparent, that is, those three which are closely approximated by the by the outer edges or rails of the BC helix.
+This formula defines a helix, but it is not any of the helices of the
+BC helix, but rather one that winds three times as rapidly through all
+nodes. To a designer of tetrahelices, it is more natural to think of
+the three helices which are visually apparent, that is, those three
+which are closely approximated by the by the outer edges or rails of
+the BC helix.
 
@@
 
-We use the term \emph{tetrahelix} to mean any structure made of vertices and edges which is isomorphic to the BC helix,
-in which the vertices lie on three helices, 
-no matter what lengths the edges take on. One could consider various definitions of optimality for a tetrahelix,
-but the must useful to an enginner is to minimize the maximum difference between any two edges. We call a
-tetrahelix \emph{member-length minimax optimal} if there is not tetrahelix of the same radius and pitch with a smaller
-maximum edge length difference.
+We use the term \emph{tetrahelix} to mean any structure made of
+vertices and edges which is isomorphic to the BC helix, in which the
+vertices lie on three helices, no matter what lengths the edges take
+on. One could consider various definitions of optimality for a
+tetrahelix, but the must useful to an enginner is to minimize the
+maximum difference between any two edges. We call a tetrahelix
+\emph{member-length minimax optimal} if there is not tetrahelix of the
+same radius and pitch with a smaller maximum edge length difference.
 
-Consider a tetrahelix isomporphic to an BC helix of unbounded extent. If all three rails do not have same pitch, there
-is an edge of unbounded length. So we are justified in talking about the pitch of the tetrahelix, even though we think
-of it as three helices. Similarly, if the axes are not parallel, there is an edge of unbounded length in the structure,
-so it is not optimal.
+Consider a tetrahelix isomporphic to an BC helix of unbounded
+extent. If all three rails do not have same pitch, there is an edge of
+unbounded length. So we are justified in talking about the pitch of
+the tetrahelix, even though we think of it as three
+helices. Similarly, if the axes are not parallel, there is an edge of
+unbounded length in the structure, so it is not optimal.
 
@@
 
-So any any optimal tetrahelix with a rail-angle of greater than $0$, that is, with any curvature, will have conincident axes.
+So any any optimal tetrahelix with a rail-angle of greater than $0$,
+that is, with any curvature, will have conincident axes.
 
-We call a tetrahelix with $0$ curvature a \emph{tetrabeam}, and consider it as an important special case and an endpoint of a continuum
-of tetrahelices of decreasing curvature.
+We call a tetrahelix with $0$ curvature a \emph{tetrabeam}, and
+consider it as an important special case and an endpoint of a
+continuum of tetrahelices of decreasing curvature.
 
- Now now that we have coincident axes, the same pitch, we can go on to the hard proof about where they occur.
+ Now now that we have coincident axes, the same pitch, we can go on to
+ the hard proof about where they occur.
 
- We show that in fact the nodes must be distributed in even thirds along the $z$-axis.
+ We show that in fact the nodes must be distributed in even thirds
+ along the $z$-axis.
 
- Note that from the point of view of a single edge, we are on a slanted cylinder, when $\rho \neq 0$.
- This means for its point of view a cross section is an ellipse. So we have to be very careful in
- comparing lengths of edges relative to the tetrahedron, because a change in position along the edge
- changes the length of a line, but in a complicated way depending on where it is relative to the ellipse.
+ Note that from the point of view of a single edge, we are on a
+ slanted cylinder, when $\rho \neq 0$.  This means for its point of
+ view a cross section is an ellipse. So we have to be very careful in
+ comparing lengths of edges relative to the tetrahedron, because a
+ change in position along the edge changes the length of a line, but
+ in a complicated way depending on where it is relative to the
+ ellipse.
 
@@
 
-   In principle in any tetrahelix where the three helices have any displacement along the $z$ axis there are 9 distinct edge classes:
-   3 rail edges, a one-hop length between eachof 3 rails, and two hop length between each of three rails, where the two-hop length is a maximum
-   length between rails (which could equal the one-hop length.) However, we have already shown the pitches and the rail lengths are equal
-   in any optimal tetrahelix.
+   In principle in any tetrahelix where the three helices have any
+   displacement along the $z$ axis there are 9 distinct edge classes:
+   3 rail edges, a one-hop length between eachof 3 rails, and two hop
+   length between each of three rails, where the two-hop length is a
+   maximum length between rails (which could equal the one-hop
+   length.) However, we have already shown the pitches and the rail
+   lengths are equal in any optimal tetrahelix.
 
-    Consider the tetrahelix in which the vertices  are evenly spaced at $h/3$ intervals on the $z$ axis. Every edge is either a rail edge, or it makes one
-    hop, or it makes two hops. All of the one-hop edges are equal length.  All of the two-hop edges are equal length.
+    Consider the tetrahelix in which the vertices are evenly spaced at
+    $h/3$ intervals on the $z$ axis. Every edge is either a rail edge,
+    or it makes one hop, or it makes two hops. All of the one-hop
+    edges are equal length.  All of the two-hop edges are equal
+    length.
 
-    Any displacemnt along the $z$ axis of any rail increases the length of one or two two-hop edges and shortens the length of one or two one-hop edges.
-    This increases the minimax distance no matter what the rail edge length is, since all rail edges are the same length. Therefore, an evenly spaced
-    tetrahelix is the unique optimal for any given radius and height.
+    Any displacemnt along the $z$ axis of any rail increases the
+    length of one or two two-hop edges and shortens the length of one
+    or two one-hop edges.  This increases the minimax distance no
+    matter what the rail edge length is, since all rail edges are the
+    same length. Therefore, an evenly spaced tetrahelix is the unique
+    optimal for any given radius and height.
   \end{proof}
@@
 Now the the term on the left is the only one that depends on the scalar $n$. We use this to a create
-a new formulation $H_{BCsymmetric}(n,c) = H_{colored}(n,c)$
+a new formulation $H_{BCsymmetric}(n,c) = H_{BCcolored}(n,c)$
 
@@
 \section{Parametrizing Tetrahelices via Rail Angle}
-
-Although the $\lambda$ parametrization presented above is a sensible one
-because it unifies the BC-helix with the equitetrabeam, it is over-specific,
-in that it makes a specific choice as to the relationship of the height $h$
-to the radius $r$ which is somewhat arbitrary.
 
@@
   \text{one-hop} &= dist(H_{general}(0,0,\rho,d_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r_{\rho}\sin(\rho((1/3)\cdot 0 + 0)) - r_{\rho}\sin(\rho((1/3)\cdot 0 + 1)+\frac{2\pi}{3}))^2  +
-    (r_{\rho}\cos(\rho((1/3)\cdot0+0)) - r_{\rho}\cos(\rho((1/3)\cdot 0+1) + \frac{2\pi}{3})))^2} \\
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}\sin(0) - r_{\rho}\sin(rho/3)+\frac{2\pi}{3}))^2  +
+    (r_{\rho}\cos(0) - r_{\rho}\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
   \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho/3 + \frac{2\pi}{3}))^2  +
@@
   d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
-  d_{opt}^2 &= 1 - 4 \frac{4}{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 } (\sin{ \rho / 2})^2   \\
-  d_{opt}^2 &= 1 - \frac{32}{9 ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 } (\sin{ \rho / 2})^2   \\
-  d_{opt}^2 &= 1 - \frac{8 sin^2(\rho) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
-    d_{opt} &= \sqrt{1 - \frac{8 sin^2(\rho) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
+  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
+  d_{opt}^2 &= 1 - \frac{32(\sin{ \rho / 2})^2}{9 ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
+  d_{opt}^2 &= 1 - \frac{8 sin^2(\rho / 2) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
+    d_{opt} &= \sqrt{1 - \frac{8 sin^2(\rho / 2) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
 \end{align*}
+NOTE: I may have made a terrible mistake here, I'm unsure if the numerator should have $sin^2(\rho)$ or $sin^2(\rho/2)$.
+
 Therefore, by computing $r_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $\rho < \rho_{bc}$.
@@
   \end{proof}
-
-(Note: This fails the check of computing the BC radius for the BC rail angle.)
 
@@
 \end{align*}
-Computing the derivative of two-hops - one-hop:
-\begin{align*}
- \frac{\partial \text{two-hops} - \text{one-hop}}{r} &= \frac{\partial \sqrt{4/9 + 3r^2} - \sqrt{1/9 + 3r^2}}{\partial r} \\
-  \frac{\partial \text{two-hops} - \text{one-hop}}{r} &= 9r (\frac{1}{\sqrt{27r^2 + 4}} - \frac{1}{\sqrt{ 27r^2 + 1}}) 
-\end{align*}
-which is negative for all $r> 0$. Thererfore two-hop - one-hop
-is minimized when we maximize $r$, up until one-hop = rail.
-
-Note that two-hops increases more and more slowly as $r$ increases. Therefore the minimum maximum will
-be obtained with the value of $r$ that when $one-hop = 1$. This can be observed from the
-plot of two-hops - one-hops as a function of $r$, or by observing that the derivate of two-hops - one-hop
-is negative for $r > 0$. (That is, the value of one-hop increases faster than two-hops.) 
-Setting the one-hop distance to $d = 1$ also has the pleasing property of giving us only two lengths. Then
+Then:
 \begin{align*}
@@
 
-\section{Adding an Untwisting Parameter}
+To the extent that we value tetrabeams (that is, tetrahelicies with a rail angle of $0$,
+and therefore zero curvature) as mathematical or engineering objects
+we have motivated the development of $H_{general}$ as a transformation of $V(n)$ defined by
+Equation \eqref{graycoxeter} from Gray and Coxeter, as it is difficult to see how
+the $V(n)$ 
+formulation could ever give rise to a continuum producing the tetrabeam,
+since setting the angle in that equation to zero can produce only points on a single
+line.
 
-We observe that by thinking of the straight lines of the
-Equitetrabeam as a degenerate helix of zero curvature,
-it should be possible to define a smoothly varying continuum between the Boerdijk--Coxeter helix and the Equitetrabeam and every
-curvature and torsion between the two. It seems most convenient to define this continuum in terms
-of the rail angle $\rho$, where $0 \leq \rho \leq \rho_{bc}$.
+\section{An Untwisted Continuum}
 
-Now basic components of the helix, which are the radius $r$, the rate of rotation, and the rate of
-axial growth can all be linearly interpolated with a parameter $\lambda$ between their high values (for the BC helix)
-and low values (for the equitetrabeam).
-
-\begin{align*}
-\phi_{\lambda} &=  \lambda \cdot \rho_{bc}   \\
-r_{\lambda}  &=  r_{opt}(\phi) \\
-d_{\lambda} &=   d_{opt}(\phi) \\
-\end{align*}
-to create a formula that generates a continuum of tetrahedral structures:
-
-\begin{equation}
-H_{continuum}(n,c,\lambda) =
-\left [
-  \begin{tabular}{c}
-   $ r_{\lambda} \cos(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
-   $ r_{\lambda}  \sin(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
-   $ d_{\lambda} \kappa $
-  \end{tabular}
-  \right ],
-\text{where:}
-  \begin{tabular}{c}
-    $\kappa = n + c/3$ \\
-    $ \phi_{\lambda} =  \lambda \rho_{bc}  $\\
-    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
-   $ \theta = \arccos(-2/3) $
-  \end{tabular}      
-\end{equation}
-
-A value of $\lambda = 0$ generates the equitetrabeam, and $\lambda = 1$ generates the Boerdijk--Coxeter helix, and every
-value $\lambda \in [-1,1]$ generates an attractive structure which if physically realized is an inherently rigid structure
-with member lengths of no greater disparity than $16\%$.
-In the sense of structural engineering, it would be a relatively strong space frame. When $\lvert \lambda \rvert > 1$, tetrahelices
-are still produced, but as $\lvert \lambda \rvert >> 2$ these tetrahelices probably cease to be interesting to mechanical engineers,
-because their ability to withstand axial forces seem to diminish significantly.
-
-\begin{figure}[H] %float with two figures
-  \label{series}
-  \centering
-     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
-     \caption{A Series of Tetrahelices, BC Helix in Foreground.}
-\end{figure}
+We observe that Equations \eqref{eqrhoopt} and \eqref{dopt} compute $r_{opt}$ and $d_{opt}$ which
+create an optimal tetrahelix for any value rail angle $\rho$ between $0$, which
+gives the Equitetrahelix and
+$\rho_{bc} \approx 35.43 \degree$, which gives the BC Helix.
 
@@
 
- Negative values of $\lambda$ generate clockwise tetrahelices; positive generate counter-clockwise helices.
- (Note: In fact there is something wrong with my math, negative lambda values do produces opposit chirality
+ Negative values of $\rho$ generate clockwise tetrahelices; positive generate counter-clockwise helices.
+ (Note: In fact there is something wrong with my math, negative rho values do produces opposit chirality
  but the lengths are not the same as the positive values.  I need to track this down.)
 
-Furthermore, this formula allows one to design the pitch (in edge length units) as a function of $\lambda$ of the helix (along one rail)
-where $\lambda \neq 0$:
+The pitch of the resulting tetrahix 
+where $\rho \neq 0$ is:
 \[
-p(\lambda) = 2 \pi  \cdot d_{opt}
+p(\rho) = \frac{2 \pi  \cdot d_{opt}}{\rho}
 \]
 
-There is thus an optimal continuum of tetrahelices untwisting between BC and equitetrabeam.
-Perhaps surprisingly, this untwisting is accomplished only by changing the length of the two-hop member.
+As pitch increases smoothly with decreasing rail angle, it is easy to solve for rail angle
+to acheive a given pitch, an ability valuable to engineers or architects who wish
+to fit a tetrahelix to given dimension.
+
+Perhaps surprisingly, the optimal untwisting is accomplished only by changing the length of
+the two-hop member, leaving the one-hop memever and
+rail length equivalenet within this continuum. However, it should be noted that
+an engineer or architect may also use $H_{general}$ in the same way, and that minimax
+length optimality is a mathematic notion only loosely related to the beauty and
+utility of physical structures.
+
+Before deriving Equation \eqref{eqrhoopt}, we created a continuum by using a linear
+interpolation between the optimal radius for the Equitetrabeam and the BC Helix. This minimax
+optimum of this simpler approach was at most 1\% worse than the optimum computed by
+\eqref{eqrhoopt}.
 
@@
 
-Trusses and space frames remain an important design field in mechanical and structural engineering\cite{mikulas1985sequentially},
+Trusses and space frames remain an important design field in
+mechanical and structural engineering\cite{mikulas1985sequentially},
 including deployable and moving trusses\cite{claypool2012readily}.
 
-Starting twenty years ago, Sanderson\cite{sanderson1996modular}, Hamlin,\cite{TetrobotBook}, and others including Lee\cite{lee2002dynamic}
-created a style of robotics based on changing the lengths of members
-joined at the center of a joint, thereby creating a connection to pure geometry. More recently NASA has experimented with
-tensegrities\cite{NTRT}, a different point in the same design spectrum. These fields create a need to explore the notion of
-geometries changing over time, not generally considered directly by pure geometry.
+Starting twenty years ago, Sanderson\cite{sanderson1996modular},
+Hamlin,\cite{TetrobotBook}, and others including
+Lee\cite{lee2002dynamic} created a style of robotics based on changing
+the lengths of members joined at the center of a joint, thereby
+creating a connection to pure geometry. More recently NASA has
+experimented with tensegrities\cite{NTRT}, a different point in the
+same design spectrum. These fields create a need to explore the notion
+of geometries changing over time, not generally considered directly by
+pure geometry.
 
-As suggested by Buckminster Fuller, the most convenient geometries to consider are those that have regular member
-lengths, in order to facilitate the inexpensive manufacture and construction of the robot.  In a plane, the octet truss
-is such a geometry, but in a line, the Boerdijk--Coxeter helix is a regular structure.
+As suggested by Buckminster Fuller, the most convenient geometries to
+consider are those that have regular member lengths, in order to
+facilitate the inexpensive manufacture and construction of the robot.
+In a plane, the octet truss is such a geometry, but in a line, the
+Boerdijk--Coxeter helix is a regular structure.
 
-However, a robot must move, and so it is interesting to consider the transmutations of these geometries, which was in
-fact the motivation for creating the equitetrabream.
+However, a robot must move, and so it is interesting to consider the
+transmutations of these geometries, which was in fact the motivation
+for creating the equitetrabream.
 
@@
 TODO:
+
+Clean up d_{opt}.
+
+Produce mini table of pitch vs. \rho?
+
+Improve clarity and precision of proofs.
+
+Solve the chirality problem.
 

### 2017-02-19 doc/TetrahelixUntwist.tex
improving the negative rho situation

@@
 \usepackage{amsthm}
+\usepackage{amsfonts}
 
@@
   the \emph{equitetrabeam}.
-  Linear interpolation of these parameters with the BC-helix parameters defines a continuum of close-to regular
-  tetrahelices of designable curvature, pitch based on a single parameter.
+  A formula for computing the radius and z-axis travel that gives an optimal minimax tetrahelix for any rail angle
+  between $0$ and $\rho_{bc}$ is given, thus defining a continuum of tetrahelices containing the equitetrabeam and
+  BC helix.
   Utility and use for static and variable geometry truss/space frame design and robotics based on the are discussed.
@@
 which allow many members to come to a single point.  Such machines can
-follow purely regual mathematical models such as the Boerdijk–-Coxeter
+follow purely regular mathematical models such as the Boerdijk–-Coxeter
 helix or the Octet Truss\cite{richard1961synergetic}.
@@
 Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
-a term now commonly used. In this paper we reserve BC helix to mean the purely regular structre and use \emph{tetrahelix} to refer
+a term now commonly used. In this paper we reserve \emph{BC helix} to mean the purely regular structre and use \emph{tetrahelix} to refer
 to any structure isomophic to a the BC helix, whether regular or not.
@@
 \begin{figure}[H] %float with two figures
-  \label{series}
+  \label{closeup}
   \centering
@@
 $\theta$ is approximately $131.81$ degrees.
-The angle $\theta$ is the rotation of a \emph{each} tetrahedra.
-That is, a yellow tetrahedron is rotated slightly more than a $1/3$ of a revolution to match the face of the red tetrahedra.
-$3 \theta - 2\pi$ is the apparent rotation of $V_3$ relative to $V_0$.
+The angle $\theta$ is the rotation of a \emph{each} tetrahedra, not the tetraheda along a rail.  In Figure \ref{closeup},
+each tetrahedra has either a yellow, blue, or red outer edge or rail.
+That is, a blue-rail tetrahedron is rotated slightly more than a $1/3$ of a revolution to match the face of the yellow tetrahedra.
 
@@
 \end{equation}
-where $n$ represents each integer numbered node in succession.
+where $n$ represents each integer numbered node in succession on every colored rail.
 
-This formula defines a helix, but it is not any of the helices of the
+The apparent rotation of tetrhedra of the same outer-edge color ($V_3$ relative from $V_0$ for example,
+in \eqref{graycoxer}, is $3 \theta - 2\pi$.
+
+This formula defines a helix, but it is not any of the apparent helices, or rail helices, of the
 BC helix, but rather one that winds three times as rapidly through all
@@
 It is convenient to have a formula that gives us the nodes of just
-each colored helix.
+one rail helix, denoted by $c$:
 \[
-H_{BCcolored}(n,c) = V(3n +c)
+(\forall n \in \mathbb{Z}, \forall c \in \{0,1,2\} : H_{BCcolored}(n,c) = V(3n +c))
 \]
-where $c \in \{0,1,2\}$ specifies which of the rails is being computed.
 
@@
   &= \frac{3  \sqrt{\frac{2}{5}}  \pi}{\rho_{bc}} \\
-  &\approx 9.6392 \\
+  &\approx 9.64 \\
 \end{align*}
@@
    displacement along the $z$ axis there are 9 distinct edge classes:
-   3 rail edges, a one-hop length between eachof 3 rails, and two hop
+   3 rail edges, a one-hop length between each of 3 rails, and two hop
    length between each of three rails, where the two-hop length is a
@@
 
-$H_{general}$ generalizes $H_{continuum}$, but forces the user to select an $d_{\rho}$
-which has a sensible radius, so it may be less convenient.
+$H_{general}$ forces the user to select an $d_{\rho}$
+which has a sensible radius.
 
-Note that when $\rho = 0$ then $h_{\rho} = 1$, but $r_{\rho}$ is not determined.
+Note that when $\rho = 0$ then $h_{\rho} = 1$, but $r_{\rho}$ is not determined by
+Equation \ref{railangle}.
 
@@
 
+Note: $r_{opt} $ is not an even function. I think it is only valid for non-negative values of $\rho$, an issue
+we must face when we build our continuum.
 Note: $ d_{opt} $ is computed by $\rho, r_{opt}$ via the rail angle equation \eqref{railangle}.
@@
 
+Engineers has two fundamental mathamematical tools for constructing a tetrahelix.
+They may use
+
 \section{Conclusion}

### 2017-02-19 js/tetrahelix_math.js

@@ -88,10 +88,11 @@ function find_rrho_from_d(rho,d) {
 }
 
 function optimal_radius(rho,el) {
+    var rho_abs = Math.abs(rho);
     var numer = 2*el;
-    var t1 = Math.sqrt(3) * Math.sin(rho/3);
-    var t2 = Math.cos(rho/3);
-    var t3 = Math.cos(rho);
+    var t1 = Math.sqrt(3) * Math.sin(rho_abs/3);
+    var t2 = Math.cos(rho_abs/3);
+    var t3 = Math.cos(rho_abs);
     var t4 = 8;
     var denom = Math.sqrt(9*(t1 + t2)/2 + t3 + t4);
     return numer/denom;
@@ -127,14 +128,23 @@ function test_optimal_radius() {
 	}
     }
 }
-function H_general(n,c,rho,d,r,s) {
-    return H_general_s(n,c,rho,d,r,1);
+
+function test_assert_optimal_radius_even() {
+    var MAX_DEGREES = 45;
+    for(var i = 0; i < 100;i++) {
+	var rho = Math.PI*(i*MAX_DEGREES/100)/180;
+	var rp = optimal_radius(rho,1.0);
+	var rn = optimal_radius(-rho,1.0);
+//	assert(rp == rn,'evenness of optimal_radius failed','spud');
+	console.log(rho,rp,rn);
+    }
 }
-function H_general_s(n,c,rho,d,r,s) {
+
+function H_general(n,c,rho,d,r) {
     var pnt = [];
     var kappa = n+ c/3.0;
     var rk = rho*kappa;
-    var angle = rk + s*c*2*Math.PI/3;
+    var angle = rk + c*2*Math.PI/3;    
     pnt[0] = r*Math.cos(angle);
     pnt[1] = r*Math.sin(angle);
     pnt[2] = d*kappa;
@@ -173,14 +183,28 @@ function H_bc_eqt_lambda(n,c,lambda) {
 function H_interp_lambda(lambda,n,c,rho0,d0,r0,rho1,d1,r1) {
     var alambda = Math.abs(lambda);
     var di = (d1 - d0)*alambda + d0;
-    var rhoi = (lambda > 0) ? (rho1 - rho0)*alambda + rho0 : -((rho1 - rho0)*alambda + rho0);
[…]

### 2017-02-22 doc/TetrahelixUntwist.tex
d_opt corrected and checked

@@
 which are closely approximated by the by the outer edges or rails of
-the BC helix.
+the BC helix. We think of each of these three rails as being a different color, red, blue, or yellow.
 
 It is convenient to have a formula that gives us the nodes of just
-one rail helix, denoted by $c$:
+one rail helix, denoted by color $c$:
 \[
@@
 values.
-The parameter $c \in \{0,1,2\}$ specifies which of the rails is being computed.
 
-The quantity $ (3 \theta - 2 \pi) \approx 35.43 \degree $, and is the angular shift between $V(n,color)$ and
-$V(n+1,color)$. This quantity appears so often below that we call it the ``rail angle rho''. For the BC helix, $\rho_{bc} = (3 \theta - 2 \pi)$.
+The quantity $ (3 \theta - 2 \pi) \approx 35.43 \degree $, and is the angular shift between $V(n*3+c)=H_{BCcolored}(n,c)$ and
+$V((n+1)*3+c)=H_{BCcolored}(n+1,c)x$.
+This quantity appears so often that we call it the ``rail angle rho''. For the BC helix, $\rho_{bc} = (3 \theta - 2 \pi)$.
 
@@
 
-Note: $r_{opt} $ is not an even function. I think it is only valid for non-negative values of $\rho$, an issue
-we must face when we build our continuum.
-Note: $ d_{opt} $ is computed by $\rho, r_{opt}$ via the rail angle equation \eqref{railangle}.
+We can now give a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \eqref{railangle}:
 
@@
   d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
-  d_{opt}^2 &= 1 - \frac{32(\sin{ \rho / 2})^2}{9 ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
-  d_{opt}^2 &= 1 - \frac{8 sin^2(\rho / 2) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
-    d_{opt} &= \sqrt{1 - \frac{8 sin^2(\rho / 2) }{ cos(r) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
+  d_{opt}^2 &= 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
+  d_{opt}^2 &= 1 - \frac{16 sin^2(\rho / 2) }{ cos(\rho) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
+    d_{opt} &= \sqrt{1 - \frac{16 sin^2(\rho / 2) }{ cos(\rho) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
 \end{align*}
@@
 
-The pitch of the resulting tetrahix 
+The pitch of any tetrahelix 
 where $\rho \neq 0$ is:
 \[
-p(\rho) = \frac{2 \pi  \cdot d_{opt}}{\rho}
+p(\rho) = \frac{2 \pi  \cdot d}{\rho}
 \]

### 2017-02-22 js/tetrahelix_math.js

@@ -124,8 +124,38 @@ function test_optimal_radius() {
 	    var rj = r/2 + (j/10)*r;
 	    var h1 = one_hop(rj,rho,1.0);
 	    var h2 = two_hop(rj,rho,1.0);
+	    // What we really want to assert here is that one_hop should be close to 1.
 	    console.log(180*rho/Math.PI,rj,h2-h1);
 	}
+    }
+}
+
+// Copute the optimal distance as a function of rho
+// (not using optimal_radius, because we want an independent check).
+function d_opt(rho,el) {
+    var num = 16*Math.sin(rho/2)*Math.sin(rho/2);
+    var t1 = Math.cos(rho);
+    var t2 = 9*(Math.sqrt(3)*Math.sin(rho/3)+Math.cos(rho/3))/2;
+    var t3 = 8;
+    var den = t1+t2+t3;
+    return el*Math.sqrt(1 - num/den);
+}
+
+function test_optimal_d() {
+    	var r = optimal_radius(BCrho,1.0);
+    	var dbc = d_opt(BCrho,1.0);
+	// Now check that d_opt matches...
+	var dp = find_drho_from_r_el(BCrho,r,1);
+    console.log(180*BCrho/Math.PI,r,dbc,dp);
+    
+   var MAX_DEGREES = 45;
+    for(var i = 0; i < 100;i++) {
+	var rho = Math.PI*(i*MAX_DEGREES/100)/180;
+	var r = optimal_radius(rho,1.0);
+	var d = d_opt(rho,1.0);
+	// Now check that d_opt matches...
+	var dp = find_drho_from_r_el(rho,r,1);
+	console.log(180*rho/Math.PI,r,d,dp-d);
     }
 }
 

### 2017-02-22 doc/TetrahelixUntwist.tex
properly parametrized one-hop and two-hop

@@
   \begin{tabular}{c}
-   $ r_{\rho} \cos(\rho \kappa + c 2 \pi /3) $\\
-   $ r_{\rho}  \sin(\rho \kappa + c 2 \pi /3) $\\
+   $ r_{\rho} \cos(\rho \kappa + s\cdot c 2 \pi /3) $\\
+   $ r_{\rho}  \sin(\rho \kappa + s\cdot c 2 \pi /3) $\\
    $ d_{\rho} \kappa $
@@
   $\kappa = n + c/3$ \\
+    $s = \text{sign}{(\rho)}$ \\  
   \end{tabular}      
@@
   \text{one-hop} &= dist(H_{general}(0,0,\rho,d_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}\sin(0) - r_{\rho}\sin(rho/3)+\frac{2\pi}{3}))^2  +
-    (r_{\rho}\cos(0) - r_{\rho}\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r_{\rho}\sin(0) - r_{\rho}\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
+    (r_{\rho}\cos(0) - r_{\rho}\cos(\rho/3 + 1\cdot\frac{2\pi}{3}))^2} \\
   \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho/3 + \frac{2\pi}{3}))^2  +
@@
 
-%% This grahp demonstrates the derivative is always negative.
+%% This graph demonstrates the derivative is always negative.
 
@@
 \end{align*}
-NOTE: I may have made a terrible mistake here, I'm unsure if the numerator should have $sin^2(\rho)$ or $sin^2(\rho/2)$.
-
-Therefore, by computing $r_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $\rho < \rho_{bc}$.
+Therefore, by computing $r_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $-\rho_{bc} \leq \rho \leq \rho_{bc}$.
 

### 2017-02-22 js/tetrahelix_math.js

@@ -87,6 +87,7 @@ function find_rrho_from_d(rho,d) {
     return find_rrho_from_d_el(rho,d,1);
 }
 
+// Tha abs should not be needed here, as thise functions are even..
 function optimal_radius(rho,el) {
     var rho_abs = Math.abs(rho);
     var numer = 2*el;
@@ -99,7 +100,9 @@ function optimal_radius(rho,el) {
 }
 
 function one_hop(r,rho,el) {
-    var t1 = 1/9;
+    var arho = Math.abs(rho);
+    var as = Math.sign(rho);
+    var t1 = el*el/9;
     var t2 = -4*Math.sin(rho/2)*Math.sin(rho/2)/9;
     var t3 = Math.sin(rho/3 + 2*Math.PI/3);
     var t4 = (1 - Math.cos(rho/3 + 2*Math.PI/3));
@@ -107,32 +110,35 @@ function one_hop(r,rho,el) {
 }
 
 function two_hop(r,rho,el) {
-    var t1 = 4/9;
+    var arho = Math.abs(rho);
+    var as = Math.sign(rho);    
+    var t1 = el*el*4/9;
     var t2 = -16*Math.sin(rho/2)*Math.sin(rho/2)/9;
     var t3 = Math.sin(2*rho/3 + 4*Math.PI/3);
     var t4 = (1 - Math.cos(2*rho/3 + 4*Math.PI/3));
     return Math.sqrt(t1 + r*r*(t2 + t3*t3 + t4*t4));
 }
-
+Math.distance3 = function(p0,p1) {
+    x = p0[0] - p1[0];
+    y = p0[1] - p1[1];
+    z = p0[2] - p1[2];        
+    return Math.sqrt(x*x + y*y + z*z);
+}
+// I have forgotten what this is supposed to test.
 function test_optimal_radius() {
     var MAX_DEGREES = 45;
     for(var i = 0; i < 100;i++) {
 	var rho = Math.PI*(i*MAX_DEGREES/100)/180;
 	var r = optimal_radius(rho,1.0);
-	for(var j = 0; j < 10; j++) {
-	    // iterate rj centered around the optimal distance.
-	    var rj = r/2 + (j/10)*r;
-	    var h1 = one_hop(rj,rho,1.0);
-	    var h2 = two_hop(rj,rho,1.0);
-	    // What we really want to assert here is that one_hop should be close to 1.
[…]

### 2017-02-22 doc/TetrahelixUntwist.tex
chirality understood better, now must code

@@
 
-From Robert Gray's site, repeating formula by H.S.M. Coxeter:
+From Robert Gray's site, repeating formula by H.S.M. Coxeter, for a counter-clockwise BC Helix:
 \begin{equation}
@@
 controls how far a rail edge of a tetrahelix deviates from being
-parallel with the axis, or the ``twistiness'' of tetrahelix. Ideally
-we will treat a positive angle as creating a clockwise tetrahelix and
-a negative as creating a counter-clockwise helices.
+parallel with the axis, or the ``twistiness'' of tetrahelix. We use
+the parameter $\chi = 1$ to indicate a chirality or counter-clockwise,
+and $\chi = -1$ for clockwise.
 
@@
 \begin{equation}
-H_{general}(n,c,\rho,d_{\rho},r_{\rho}) =
+H_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) =
 \left [
   \begin{tabular}{c}
-   $ r_{\rho} \cos(\rho \kappa + s\cdot c 2 \pi /3) $\\
-   $ r_{\rho}  \sin(\rho \kappa + s\cdot c 2 \pi /3) $\\
+   $ r_{\rho} \cos(\chi \cdot (\rho \kappa + s\cdot c 2 \pi /3)) $\\
+   $ r_{\rho}  \sin(\chi \cdot (\rho \kappa + s\cdot c 2 \pi /3)) $\\
    $ d_{\rho} \kappa $
@@
   $\kappa = n + c/3$ \\
-    $s = \text{sign}{(\rho)}$ \\  
+    $\chi \in \{-1,1\}$ \\  
   \end{tabular}      
@@
 \end{align*}
-Therefore, by computing $r_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $-\rho_{bc} \leq \rho \leq \rho_{bc}$.
+Therefore, by computing $r_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $0 \leq \rho \leq \rho_{bc}$.
 
@@
 
+Note that the equitetrabeam has chirality, which becomes important in our attempt to build a
+continuum of tetrahelices.
+
 \section{An Untwisted Continuum}
@@
 
- Negative values of $\rho$ generate clockwise tetrahelices; positive generate counter-clockwise helices.
- (Note: In fact there is something wrong with my math, negative rho values do produces opposit chirality
- but the lengths are not the same as the positive values.  I need to track this down.)
+ Because the equitetrabeam which as a rail angle of $0$ still has chirality, that is,
+ one still must decide to connect with one-hop to the clockwise or counter-clockwise node,
+ it is not poosible to build a smooth continuum where $\rho$ transitions from positive to
+ negative which remains optimal. One can use a negative $\rho$ in $H_{general}$ but it does
+ not produce minimax optimal tetrahelices. In other words, untwisting a conter-clockwise
+ tetrahelix to $0$ and then going further does produce a clockwise tetrahelix, but one in which
+ the one-hop and two-hop lengths in the wrong places (that is, two-hop becomes shorter than one-hop.)
 
@@
 \]
+
+http://bit-player.org/2013/tetrahedra-with-a-twist

### 2017-02-22 js/tetrahelix_math.js

@@ -193,16 +193,40 @@ function test_assert_optimal_radius_even() {
 
 function H_general(n,c,rho,d,r) {
     var pnt = [];
+    var arho = Math.abs(rho);
     var as = Math.sign(rho);
+    if (as == 0) as = 1;
     var kappa = n+ c/3.0;
-    var rk = rho*kappa;
-    var angle = rk + c*2*Math.PI/3;    
+    var rk = arho*kappa;
+    var angle = as*rk + as*c*2*Math.PI/3;
+//    console.log("rk",rk*180/Math.PI);
+//    console.log("angle",angle*180/Math.PI);
+    
     pnt[0] = r*Math.cos(angle);
     pnt[1] = r*Math.sin(angle);
     pnt[2] = d*kappa;
     return pnt;
 }
 
+function test_evenness_H_general() {
+    var rho = BCrho;
+    rho = -BCrho/2;
+    var len = 1.0;
+    var r_opt = optimal_radius(rho,len);
+    var d_opt = optimal_distance(rho,len);
+    console.log(rho,len,r_opt,d_opt);    
+    var p1 = H_general(0,0,BCrho,d_opt,r_opt);
+    var p2 = H_general(0,1,BCrho,d_opt,r_opt);
+    var distance1 = Math.distance3(p1,p2);
+    console.log(p1,p2,distance1);
+
+    var p3 = H_general(0,0,-BCrho,d_opt,r_opt);
+    var p4 = H_general(0,1,-BCrho,d_opt,r_opt);
+    var distance2 = Math.distance3(p3,p4);
+    console.log(p3,p4,distance2);
+
+
+}
 function H_bc(n,c) {
     var BCr = find_rrho_from_d(BCrho,BCd);
     return H_general(n,c,BCrho,BCd,BCr);

### 2017-02-22 js/tetrahelix_math.js
improving chirality handling in code

@@ -191,14 +191,19 @@ function test_assert_optimal_radius_even() {
     }
 }
 
-function H_general(n,c,rho,d,r) {
+function H_general(chi,n,c,rho,d,r) {
+    if (chi != 1 && chi != -1) {
+	console.log("chirality must be 1 or -1!");
+	return null;
+    }
+    if (rho < 0) {
+	console.log("rho must be non-negative!");
+	return null;
+    }
     var pnt = [];
-    var arho = Math.abs(rho);
-    var as = Math.sign(rho);
-    if (as == 0) as = 1;
     var kappa = n+ c/3.0;
-    var rk = arho*kappa;
-    var angle = as*rk + as*c*2*Math.PI/3;
+    var rk = rho*kappa;
+    var angle = chi*(rk + c*2*Math.PI/3);
 //    console.log("rk",rk*180/Math.PI);
 //    console.log("angle",angle*180/Math.PI);
     
@@ -210,18 +215,17 @@ function H_general(n,c,rho,d,r) {
 
 function test_evenness_H_general() {
     var rho = BCrho;
-    rho = -BCrho/2;
     var len = 1.0;
     var r_opt = optimal_radius(rho,len);
     var d_opt = optimal_distance(rho,len);
     console.log(rho,len,r_opt,d_opt);    
-    var p1 = H_general(0,0,BCrho,d_opt,r_opt);
-    var p2 = H_general(0,1,BCrho,d_opt,r_opt);
+    var p1 = H_general(1,0,0,BCrho,d_opt,r_opt);
+    var p2 = H_general(1,0,1,BCrho,d_opt,r_opt);
     var distance1 = Math.distance3(p1,p2);
     console.log(p1,p2,distance1);
 
-    var p3 = H_general(0,0,-BCrho,d_opt,r_opt);
-    var p4 = H_general(0,1,-BCrho,d_opt,r_opt);
+    var p3 = H_general(-1,0,BCrho,d_opt,r_opt);
+    var p4 = H_general(-1,1,BCrho,d_opt,r_opt);
     var distance2 = Math.distance3(p3,p4);
     console.log(p3,p4,distance2);
 
@@ -229,13 +233,13 @@ function test_evenness_H_general() {
 }
 function H_bc(n,c) {
     var BCr = find_rrho_from_d(BCrho,BCd);
[…]

### 2017-02-24 doc/TetrahelixUntwist.tex
improved references

@@
 
-\title{Untwisting the Tetrahelix (v0.5)}
+\title{Untwisting the Tetrahelix (v0.6)}
 \author{Robert L. Read \texttt{read.robert@gmail.com} \and
@@
 \begin{abstract}
-  The Boerdijk--Coxeter helix (BC helix, or tetrahelix) is a face-to-face stack of regular tetrahedra.
-  Considering the edges of these tetrahedra, the resulting structure is attractive and inherently rigid,
-  and therefore interesting to architects, mechanical engineers,
-  and robotocists.
-  A formula that matches the visually apparent helices forming the outer rails of the tetrahelix is derived which
-  is convenient for designers.
-  This formula defines the vertices of tetrahelices of varying radius, pitch, and curvature, with the BC helix
-  as a special case. 
-  An addtional special case is of that of $0$ curvature or rail angle, which generates a \emph{tetrabeam}.
-  A particular choice of paramaters defines a novel object, the  minimax member length-difference tetrabeam,
-  the \emph{equitetrabeam}.
-  A formula for computing the radius and z-axis travel that gives an optimal minimax tetrahelix for any rail angle
-  between $0$ and $\rho_{bc}$ is given, thus defining a continuum of tetrahelices containing the equitetrabeam and
-  BC helix.
-  Utility and use for static and variable geometry truss/space frame design and robotics based on the are discussed.
+  The Boerdijk--Coxeter helix (BC helix, or tetrahelix) is a
+  face-to-face stack of regular tetrahedra.  Considering the edges of
+  these tetrahedra, the resulting structure is attractive and
+  inherently rigid, and therefore interesting to architects,
+  mechanical engineers, and robotocists.  A formula that matches the
+  visually apparent helices forming the outer rails of the tetrahelix
+  is derived which is convenient for designers.  This formula defines
+  the vertices of tetrahelices of varying radius, pitch, and
+  curvature, with the BC helix as a special case.  An addtional
+  special case is of that of $0$ curvature or rail angle, which
+  generates a \emph{tetrabeam}.  A particular choice of paramaters
+  defines a novel object, the minimax member length-difference
+  tetrabeam, the \emph{equitetrabeam}.  A formula for computing the
+  radius and z-axis travel that gives an optimal minimax tetrahelix
+  for any rail angle between $0$ and $\rho_{bc}$ is given, thus
+  defining a continuum of tetrahelices containing the equitetrabeam
+  and BC helix. Numerically finding $\rho$ from the equation for
+  pitch allows optimal tetrahelices of any pitch to be designed.
+  An interactive tool for such design and experimentation is provided.
+  Utility and use for static and variable geometry
+  truss/space frame design and robotics based on the are discussed.
 \end{abstract}
@@
 \begin{figure}[H] %float with two figures
-  \label{closeup}
+  \label{fig:closeup}
   \centering
@@
      \caption{BC Helix Close-up}
-\end{figure}
-
-\begin{figure}[H] %float with two figures
-  \label{series}
-  \centering
-     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
-     \caption{A Series of Tetrahelices, BC Helix in Foreground.}
 \end{figure}
@@
 untwist a tetrahelix to form a \emph{tetrabeam} which has planar faces
-and has, for example, an equilateral triangular profile.  In Figure
-\ref{series}, the closest helix is the BC helix.
+and has, for example, an equilateral triangular profile. This paper
+develops the equations needed to untwist the tetrahelix. All math
+deveoped here is available in Javascript and demonstrated by an interactive
+design website\cite{readtetrahelix}, from which Figures \ref{fig:closeup} and
+\ref{fig:series} are taken.
+
+\begin{figure}[H] %float with two figures
+  \label{fig:series}
+  \centering
+     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
+     \caption{A Series of Tetrahelices, BC Helix in Foreground.}
+\end{figure}
+
+%% Note: This is not rendering figure two for some reason.
+In Figure
+\ref{fig:series}, the closest helix is the BC helix.
 
@@
 
-Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and translation of the tetrahedra, showing the
+H.S.M Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and translation of the tetrahedra, showing the
 rotation is:
@@
 
-From Robert Gray's site, repeating formula by H.S.M. Coxeter, for a counter-clockwise BC Helix:
+From R.W. Gray's site\cite{graytetrahelix}, repeating formula by Coxeter\cite{coxeter1985simplicial}, for a counter-clockwise BC Helix:
 \begin{equation}
@@
 The apparent rotation of tetrhedra of the same outer-edge color ($V_3$ relative from $V_0$ for example,
-in \eqref{graycoxer}, is $3 \theta - 2\pi$.
+in \eqref{graycoxeter}, is $3 \theta - 2\pi$.
 
@@
 \end{align*}
-The pitch is less than the number of tetrahedra because the tetrahedra are not lined up perfectly.
-It is a famous and interesting result that the pitch is irrational, a BC helix never has two tetrahedra
-at precisely the same orientation around the $z$-axis. However, this is inconvenient to designers, who
-might prefer a rational pitch. For example, a slight irregularity that led to a pitch of precisely 10 tetrahedra
-in one revolution would allow an architect to design a column having a basis and a capital in the same relation to the tetrahedra
-they touch.
+The pitch is less than the number of tetrahedra because the tetrahedra
+are not lined up perfectly.  It is a famous and interesting result
+that the pitch is irrational, a BC helix never has two tetrahedra at
+precisely the same orientation around the $z$-axis. However, this is
+inconvenient to designers, who might prefer a rational pitch. For
+example, a slight irregularity that led to a pitch of precisely 10
+tetrahedra in one revolution would allow an architect to design a
+column having a basis and a capital in the same relation to the
+tetrahedra they touch.
 
-A BC helix has the useful property that every member is precisely the same length. If we relax this, so that the tetrahedra it
-comprises are not perfectly regular, then we can twist and curve the tetrahelix into a variety of shapes. This is useful to
-the mechanical engineer or robotocist because the structure remains an inherently rigid, omni-triangulated space frame, which
-may be expected to be at least somewhat mechanically strong.
+A BC helix has the useful property that every member is precisely the
+same length. If we relax this, so that the tetrahedra it comprises are
+not perfectly regular, then we can twist and curve the tetrahelix into
+a variety of shapes. This is useful to the mechanical engineer or
+robotocist because the structure remains an inherently rigid,
+omni-triangulated space frame, which may be expected to be at least
+somewhat mechanically strong.
 
@@
 \begin{align*}
-  1 &=  \sqrt{\frac{1}{9}  + r_{\rho}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
+  1 &=  \sqrt{\frac{1}{9}  + r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
   r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }} \numberthis  \label{eqrhoopt} \\
@@
 
- Because the equitetrabeam which as a rail angle of $0$ still has chirality, that is,
- one still must decide to connect with one-hop to the clockwise or counter-clockwise node,
- it is not poosible to build a smooth continuum where $\rho$ transitions from positive to
- negative which remains optimal. One can use a negative $\rho$ in $H_{general}$ but it does
- not produce minimax optimal tetrahelices. In other words, untwisting a conter-clockwise
- tetrahelix to $0$ and then going further does produce a clockwise tetrahelix, but one in which
- the one-hop and two-hop lengths in the wrong places (that is, two-hop becomes shorter than one-hop.)
+ Because the equitetrabeam which as a rail angle of $0$ still has
+ chirality, that is, one still must decide to connect with one-hop to
+ the clockwise or counter-clockwise node, it is not poosible to build
+ a smooth continuum where $\rho$ transitions from positive to negative
+ which remains optimal. One can use a negative $\rho$ in $H_{general}$
+ but it does not produce minimax optimal tetrahelices. In other words,
+ untwisting a conter-clockwise tetrahelix to $0$ and then going
+ further does produce a clockwise tetrahelix, but one in which the
+ one-hop and two-hop lengths in the wrong places (that is, two-hop
+ becomes shorter than one-hop.)
 
@@
 where $\rho \neq 0$ is:
-\[
+\begin{equation}
+  \label{pitcheqn}
 p(\rho) = \frac{2 \pi  \cdot d}{\rho}
-\]
+\end{equation}
+For a fixed $z$-axis travel $d$, this is trivial. 
+$z$-axis travel as per \eqref{dopt} pitch increases monotonically and smoothly with decreasing $\rho$, so
+Equation \eqref{pitcheqn} can be easily solved numerically.
+For a pitch at least $ \frac{3  \sqrt{\frac{2}{5}}  \pi}{\rho_{bc}} \approx 9.64 $,
+and using \eqref{dopt}, produces minimax optimal tetrahelices.
 
-As pitch increases smoothly with decreasing rail angle, it is easy to solve for rail angle
-to acheive a given pitch, an ability valuable to engineers or architects who wish
-to fit a tetrahelix to given dimension.
+In this way a rail angle can be chosen for any desired pitch, yield
+the optimum radius, one-hop, and two-hop lengths an engineer needs to
+construct a physical structure.
 
-Perhaps surprisingly, the optimal untwisting is accomplished only by changing the length of
-the two-hop member, leaving the one-hop memever and
-rail length equivalenet within this continuum. However, it should be noted that
-an engineer or architect may also use $H_{general}$ in the same way, and that minimax
-length optimality is a mathematic notion only loosely related to the beauty and
-utility of physical structures.
+Perhaps surprisingly, the optimal untwisting is accomplished only by
+changing the length of the two-hop member, leaving the one-hop memever
+and rail length equivalenet within this continuum. However, it should
+be noted that an engineer or architect may also use $H_{general}$
+directly and interactively, and that minimax length optimality is a
+mathematic notion only loosely related to the beauty and utility of
+physical structures.
 
-Before deriving Equation \eqref{eqrhoopt}, we created a continuum by using a linear
-interpolation between the optimal radius for the Equitetrabeam and the BC Helix. This minimax
-optimum of this simpler approach was at most 1\% worse than the optimum computed by
+Before deriving Equation \eqref{eqrhoopt}, we created a continuum by
+using a linear interpolation between the optimal radius for the
+Equitetrabeam and the BC Helix. This minimax optimum of this simpler
+approach was at most 1\% worse than the optimum computed by
 \eqref{eqrhoopt}.
@@
 
-Engineers has two fundamental mathamematical tools for constructing a tetrahelix.
-They may use
+\section{Conclusion}
 
-\section{Conclusion}
+The BC Helix is the end point of a continuum of tetrahelices, the
+other end point being an uncurved tetrahelix with equilateral cross
+section, constructed by changing the length of only those members
+crossing the outside rails after hopping over the nearest
+vertex. Under the condition of miminum maximum length difference of
+all members in the system, all such tetrahelices have vertices evenly
+spaced along the axis generated by a simple equation.  A mechanical
+machine, such as a robot or a variable-geometry truss, that can change
+the length of its members, can thus twist and untwist itself by
+changing the length of the appropriate members to achieve any point in
+the continuum optimally. With a numeric solution, a design may choose
+a rotation angle and member lengths to obtain any desired pitch.
 
@@
 
-When $G = 0$, $\overline{\rm CD} = 0$. Our solution is improved as we increase $G$ until either $ \overline{\rm CD} = \overline{\rm AC}$, or the
-quantity $ \overline{\rm BC} - \overline{\rm CD} $ starts increasing rather than decreasing (that is, when the derivative is positive.)
+When $G = 0$, $\overline{\rm CD} = 0$. Our solution is improved as we
+increase $G$ until either $ \overline{\rm CD} = \overline{\rm AC}$, or
+the quantity $ \overline{\rm BC} - \overline{\rm CD} $ starts
+increasing rather than decreasing (that is, when the derivative is
+positive.)
 
-Suppose $\overline{\rm C'D'}$ is the shortest edge. Increasing $G$ thereby improves our mimimum, up until the next shortest edge length, $\overline{\rm AC}$.
-This may increase $\overline{\rm BC}$ and $\overline{\rm AD}$, but more slowly (???) than $\overline{\rm C'D'}$ is being increased, until  $\overline{\rm C'D'} =
-\overline{\rm AC}$.
-Note: This is sketchy, can we show that the derivative of our formula for CD  with respect to $G$ is really higher than $AD$? These derivatives will depend on $\rho$ slightly, which is exactly right!
+Suppose $\overline{\rm C'D'}$ is the shortest edge. Increasing $G$
+thereby improves our mimimum, up until the next shortest edge length,
+$\overline{\rm AC}$.  This may increase $\overline{\rm BC}$ and
+$\overline{\rm AD}$, but more slowly than $\overline{\rm C'D'}$
+is being increased, until $\overline{\rm C'D'} = \overline{\rm AC}$.
+Note: This is sketchy, can we show that the derivative of our formula
+for CD with respect to $G$ is really higher than $AD$? These
+derivatives will depend on $\rho$ slightly, which is exactly right!
 

### 2017-02-24 doc/TetrahelixUntwist.tex
major read through

@@
   face-to-face stack of regular tetrahedra.  Considering the edges of
-  these tetrahedra, the resulting structure is attractive and
+  these tetrahedra as structural members, the resulting structure is attractive and
   inherently rigid, and therefore interesting to architects,
@@
   generates a \emph{tetrabeam}.  A particular choice of paramaters
-  defines a novel object, the minimax member length-difference
+  defines a novel object, the minimax optimal member length-difference
   tetrabeam, the \emph{equitetrabeam}.  A formula for computing the
@@
   for any rail angle between $0$ and $\rho_{bc}$ is given, thus
-  defining a continuum of tetrahelices containing the equitetrabeam
-  and BC helix. Numerically finding $\rho$ from the equation for
+  defining a continuum of tetrahelices terminated by the equitetrabeam
+  and BC helix. Numerically finding the rail angle from the equation for
   pitch allows optimal tetrahelices of any pitch to be designed.
@@
 useful to develop the mathematics of structure formed from tetrahedra
-where we relax regularity.  The vertices of the tetrahedra lie upon
+where we relax regularity.
+
+The vertices of the tetrahedra lie upon
 three helices about the central axis.  The
@@
 
+Imagining Figure \ref{fig:closeup} as a static mechanical structure,
+we observe that it is useful to the mechanical engineer or
+robotocist because the structure remains an inherently rigid,
+omni-triangulated space frame, which may be expected to be at least
+somewhat mechanically strong.
+Imagine further in Figure \ref{fig:closeup}, that each static edge was replaced with an
+actuator that could dynamically become shorter or longer in response to electronic control,
+and the they vertices were a joint that supported sufficient angular displacement
+for this to be possible. Such a machine is a Tetrobot\cite{TetrobotBook}.
+
 BC helix does not rest on a plane in a simple way. It is convenient to
-be able to ``untwist'' it and form a tetrahelix space frame that has a
+be able to ``untwist'' it and to form a tetrahelix space frame that has a
 flat planar surface. By making length changes in a certain way, we can
@@
 develops the equations needed to untwist the tetrahelix. All math
-deveoped here is available in Javascript and demonstrated by an interactive
+deveoped here is available in JavaScript and demonstrated by an interactive
 design website\cite{readtetrahelix}, from which Figures \ref{fig:closeup} and
@@
 In Figure
-\ref{fig:series}, the closest helix is the BC helix.
+\ref{fig:series}, the closest helix is the BC helix, and the furthest
+is the equitetrabeam.
 
@@
 the equitetrabream lengths and the completely regular lengths of the
-tetrahelix, thereby choosing the torsion.  If you are designing a
+tetrahelix, thereby choosing the amount of twist\footnote{The formal definiton
+  of twistiness, or \emph{torsion}, is not useful or used in this paper, and
+  we use \emph{curvature} without relying on the mathematical curvature easily
+  computed from helical equations we provide.}.
+If you are designing a
 space frame, this is a static design choice, in a robot, it is a
-dynamic choice that can be used to twist the robot and/or exert
-torsion on the environment.
+dynamic choice that can be used to twist the robot and/or exert linear or
+angular force on the environment.
 
 Ideally we would have a simple formula for defining the nodes based on
-any torsion we choose.  Unfortunately, it is not obvious that a linear
+any curvature or pitch we choose.  Unfortunately, it is not obvious that a linear
 combination of lengths produces a simple formula.  It is a goal of
@@
 
-From R.W. Gray's site\cite{graytetrahelix}, repeating formula by Coxeter\cite{coxeter1985simplicial}, for a counter-clockwise BC Helix:
+R.W. Gray's site\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in more accessible form, gives for a counter-clockwise BC Helix:
 \begin{equation}
@@
 \begin{equation}
+  \label{eq:colord}
 H_{BCcolored}(n,c) =
@@
    $ r_{bc} \sin((3 \theta - 2 \pi)n + c  \theta $\\
-   $ (n + c/3) 3  h_{bc} $
+   $ 3 h_{bc} (n + c/3)  $
   \end{tabular}
@@
 
-The quantity $ (3 \theta - 2 \pi) \approx 35.43 \degree $, and is the angular shift between $V(n*3+c)=H_{BCcolored}(n,c)$ and
-$V((n+1)*3+c)=H_{BCcolored}(n+1,c)x$.
+The quantity $ (3 \theta - 2 \pi) \approx 35.43 \degree $, and is the angular shift between $V(3n+c)=H_{BCcolored}(n,c)$ and
+$V(3(n+1)+c)=H_{BCcolored}(n+1,c)$.
 This quantity appears so often that we call it the ``rail angle rho''. For the BC helix, $\rho_{bc} = (3 \theta - 2 \pi)$.
@@
 
+Note in Figure \ref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In \eqref{graycoxeter} and \label{eq:colored}, the variable
+$h$ is used for one third of the distance we name $d$. We will later justify that $d = 3h$. In this paper we assume the length of a rail
+is alwyas $1$ is a simplification, although we make the rail length a parameter in our JavaScript codein \texttt{tetrahelixmath.js} \cite{readtetrahelix}.
+
 Since:
@@
 \begin{align*}
+  &= \frac{d_{bc} 2 \pi }{\rho_{bc}} \\  
   &= \frac{3 \cdot h_{bc} 2 \pi }{\rho_{bc}} \\
@@
 
-A BC helix has the useful property that every member is precisely the
-same length. If we relax this, so that the tetrahedra it comprises are
-not perfectly regular, then we can twist and curve the tetrahelix into
-a variety of shapes. This is useful to the mechanical engineer or
-robotocist because the structure remains an inherently rigid,
-omni-triangulated space frame, which may be expected to be at least
-somewhat mechanically strong.
-
 \section{Optimal Tetrahelices Have Evenly Spaced Vertices}
@@
 maximum difference between any two edges. We call a tetrahelix
-\emph{member-length minimax optimal} if there is not tetrahelix of the
+\emph{member-length minimax optimal} (or just \emph{optimal}) if there is not tetrahelix of the
 same radius and pitch with a smaller maximum edge length difference.
@@
 
- Now now that we have coincident axes, the same pitch, we can go on to
+ Now that we have coincident axes, the same pitch, we can go on to
  the hard proof about where they occur.
@@
 
+ In principle in any 3 helices with the same axis of the same radius
+ having any relative
+ displacement along the $z$ axis there are 9 distinct edge classes.
+ If when projecting all vertices on the the $z$-axis, the interval
+ defined by the $z$ axis value of its endpoints contains no other vertices,
+ we call it a \emph{one-hop} edge, and if it does contain another vertex we
+ call it a \emph{two-hop} edge.
+ Then there are 
+ 3 rail edges, 3 one-hop lengths between each pair of 3 rails, and 3 two hop
+ lengths between each pair of three rails, where the two-hop length is at least
+ the one-hop length.
+ However, we have already shown the rail
+ lengths are equal in any optimal tetrahelix.
+
  \begin{theorem}
    \label{eventhirds}
-   A tetrahelix of a given radius and height $h$ in which all nodes are evenly spaced at $h/3$ intervals on the $z$ axis is optimal.
+   A tetrahelix of a given radius and axial distance $d$ in which all nodes are evenly spaced at $d/3$ intervals on the $z$ axis is optimal.
      Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail and $2$ two-hop edges connected to the rail.
@@
  \begin{proof}
-
-   In principle in any tetrahelix where the three helices have any
-   displacement along the $z$ axis there are 9 distinct edge classes:
-   3 rail edges, a one-hop length between each of 3 rails, and two hop
-   length between each of three rails, where the two-hop length is a
-   maximum length between rails (which could equal the one-hop
-   length.) However, we have already shown the pitches and the rail
-   lengths are equal in any optimal tetrahelix.
-
     Consider the tetrahelix in which the vertices are evenly spaced at
@@
 
-Note that based on \ref{eventhirds}, we are justified in classifying edge lengths as \emph{rail},\emph{one-hop}, or
-\emph{two-hops}. The one-hop edges are the edges between closest on the $z$-axis, and the two-hop edges are those that hop over a vertex.
+ Note that based on \ref{eventhirds}, there are only 3 possible lengths in an optimal tethrahelix,
+ and we are justified in classifying edge lengths as \emph{rail},\emph{one-hop}, or
+\emph{two-hop}. The one-hop edges are the edges between closest on the $z$-axis, and the two-hop edges are those that hop over a vertex.
 
-By \ref{eventhirds} every optimal tetrahelix has vertices lying on helices expressible in the form:
+By Theorem \ref{eventhirds} every optimal tetrahelix has vertices lying on helices expressible in the form:
 \[
@@
   \rho_{bc} n + c \theta  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
-    (3 \theta - 2 \pi)n + (c/3)  (\theta /3)  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
+    (3 \theta - 2 \pi)n + (c/3)  (3 \theta)  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
   (3 \theta - 2 \pi)n + (c/ 3) (3 \theta - 2 \pi  + 2 \pi) &=  \text{\{associate...\}} \\
@@
 Now the the term on the left is the only one that depends on the scalar $n$. We use this to a create
-a new formulation $H_{BCsymmetric}(n,c) = H_{BCcolored}(n,c)$
+a new formulation: $H_{BCsymmetric}(n,c) = H_{BCcolored}(n,c)$
 
@@
 
-\section{Parametrizing Tetrahelices via Rail Angle}
+\section{Parameterizing Tetrahelices via Rail Angle}
 
 We seek a formula to generate optimal tetrahelices that accepts a
-parameter that allows us to choose the tetrahelix conveniently. The
-pitch of the helix is an obious choice, but is not defined when the
-curvature is $0$, and important special case. The radius or the axial
+parameter that allows us to design the tetrahelix conveniently.
+Please refer back to Figure \ref{railanglefig}.
+The pitch of the helix is an obious choice, but is not defined when the
+curvature is $0$, an important special case. The radius or the axial
 distance between two nodes on the same rail are obvious choices, but
@@
 input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
-formed in the X,Y plane $\angle R_i O R_{i+1}$ projecting out the $z$
+formed in the X,Y plane $\angle A O B$ projecting out the $z$
 axis and sighting along the positive $z$ axis. In other words, $\rho$
@@
 and $\chi = -1$ for clockwise.
-
-Please refer back to Figure \ref{railanglefig}.
 
@@
 
-In choosing $\rho$, one greatly constrains $r$ and $h$, but does not completely
+In choosing $\rho$, one greatly constrains $r$ and $d$, but does not completely
 determine both of them together, so we treat both as parameters.
@@
 \begin{equation}
+  \label{eq:general}
 H_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) =
@@
   \begin{tabular}{c}
-   $ r_{\rho} \cos(\chi \cdot (\rho \kappa + s\cdot c 2 \pi /3)) $\\
-   $ r_{\rho}  \sin(\chi \cdot (\rho \kappa + s\cdot c 2 \pi /3)) $\\
+   $ r_{\rho} \cos(\chi \cdot (\rho \kappa + c 2 \pi /3)) $\\
+   $ r_{\rho}  \sin(\chi \cdot (\rho \kappa + c 2 \pi /3)) $\\
    $ d_{\rho} \kappa $
@@
 \begin{proof}
-  This requires a minimax argument.
-\end{proof}
+This is proved by a minimax argument.
 
@@
   \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho},r_{\rho}),H_{general}(n,c+1,\rho,d_{\rho},r_{\rho}))  \\
-  \text{two-hops} &= dist(H_{general}(n,c,\rho,d_{\rho},r_{\rho}),H_{general}(n,c+2,\rho,d_{\rho},r_{\rho}))  \\  
+  \text{two-hop} &= dist(H_{general}(n,c,\rho,d_{\rho},r_{\rho}),H_{general}(n,c+2,\rho,d_{\rho},r_{\rho}))  \\  
 \end{align*}
@@
 \begin{align*}
-  \text{two-hops}  &= \sqrt{\frac{4}{9} + r_{\rho}^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
+  \text{two-hop}  &= \sqrt{\frac{4}{9} + r_{\rho}^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
 \end{align*}
 
-We would really like to know the partial derivative of the two-hops - one-hop with respect
+We would really like to know the partial derivative of the two-hop - one-hop with respect
 to the radius to be able to understand how to choose the radius to form the minimimax optimum.
@@
 \begin{align*}
-  \text{two-hops} - \text{one-hop}  &= \sqrt{\frac{4}{9}  + r_{\rho}^2(g_{\rho}+ j_{\rho})}
+  \text{two-hop} - \text{one-hop}  &= \sqrt{\frac{4}{9}  + r_{\rho}^2(g_{\rho}+ j_{\rho})}
   - \sqrt{\frac{1}{9} +r_{\rho}^2(f_{\rho}+k_{\rho}) }
@@
 
-% Using wolfram alph we se this derivate remains negative in this range....
-% plot d/dr sin(2r/3 + 4pi/3)^2 - sin(r/3 + 2pi/3)^2 + (1 - cos(2r/3 + 4pi/3))^2 -(1-cos(r/3 + 2pi/3))^2 from 0 to 35.44 degrees
-% in other words
-
-% This part is also negative withing this range...
-%  d/dr -(16/9)sin(r/2)^2 - -(4/9)sin(r/2)^2 from 0 to 35.44 degrees
-
-%% Using Mathematica, I get:
-%% f[x_, r_] := 
-%%  Sqrt[4/9 + 
-%%     x^2 (-16 Sin[r/2]^2/9 + 
-%%        Sin[2 r/3 + 4 Pi /3]^2 + (1 - Cos[2 r/3 + 4 Pi/3])^2)] - 
-%%   Sqrt[1/9 + 
-%%     x^2*(-4*Sin[r/2]^2/9 + 
-%%        Sin[r/3 + 2 Pi/3]^2 + (1 - Cos[r/3 + 2 Pi/3])^2) ]
-%% N[N[f[1, 1]]]
-
-%% Plot3D[D[f[x, r]], {x, 0, 2}, {r, 0, Pi}]
-
-%% This graph demonstrates the derivative is always negative.
-
 By graph inspection using Mathematica, we see the partial derivative of this with respect to
 radius $r_{\rho}$ is always negative.
-Since the partial derivative of $\text{two-hops} - \text{one-hop}$ with respect to the
+Since the partial derivative of $\text{two-hop} - \text{one-hop}$ with respect to the
 radius is negative up until $\rho$ up until $\rho_{bc}$ when it is $0$, then
 we will opitmize the overall minimax distance by choosing the largest radius
-up until one-hop $= 1$, the rail-edge length. Numerical test suggests that this is true.
+up until one-hop $= 1$, the rail-edge length.
 
@@
 \end{align*}
-(where denominator $  \neq 0$).
 
@@
 \end{align*}
-Therefore, by computing $r_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $0 \leq \rho \leq \rho_{bc}$.
+
+Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $0 \leq \rho \leq \rho_{bc}$.
+\end{proof}
 
@@
   For any rail angle $\rho$ where $\rho \leq \rho_{bc}$, a tetrahelix of minimum maximum edge length
-  difference is generated by $H_{general}(n,c,\rho,d_{\rho},r_{opt})$, where $r_{opt}$ and $d_{opt}$ are
+  difference is generated by $H_{general}(\chi,n,c,\rho,d_{\rho},r_{opt})$, where $r_{opt}$ and $d_{opt}$ are
   computed from $\rho$. 
@@
 \begin{proof}
-  TBD: The Even thirds theorem tells us an optimal will have even thirds.  We have shown
-  that $r_{opt}$ minimizes the maximum length.
+  Theorem \ref{eventhirds} theorem tells us an optimal will have even thirds,
+  as Equation \eqref{eq:general} does.
+  Theorem \ref{generalformulaoptimal} tell us that
+  that plugging $r_{opt}, d_{opt}$ into $H_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho})$ minimizes the maximum length difference.
   \end{proof}
@@
 
-However, choosing $d = 1$ and $\rho = 0$ we use Equation \eqref{eqrhoopt} to find the radius of 
+Choosing $d = 1$ and $\rho = 0$ we use Equation \eqref{eqrhoopt} to find the radius of 
 optimal minimax difference.
@@
 \begin{align*}
-  \text{rail} &=  1 \\
   \text{one-hop} &= \sqrt{\frac{1}{9} + 3r^2}\\
-\text{two-hops}    &= \sqrt{\frac{4}{9} + 3r^2}
 \end{align*}
@@
 
-Note: Another interesting solution is derived by setting (one-hop + two-hop)/2 = 1,  occurs at $r = \sqrt{35}/4$,
-which produces three length classes of $11/12, 12/12, 13/12$.
+\footnote{Another interesting but non-optimal solution is derived by setting (one-hop + two-hop)/2 = 1,  occurs at $r = \sqrt{35}/4$,
+which produces three length classes of $11/12, 12/12, 13/12$!}
 
@@
 formulation could ever give rise to a continuum producing the tetrabeam,
-since setting the angle in that equation to zero can produce only points on a single
-line.
+since setting the angle in that equation to zero can produce only collinear points.
 
@@
 
- \begin{figure}[H]
-     \centering
-     \includegraphics[width=0.9\textwidth]{figures/Continuum.png}
-     \caption{A Continuum of Tetrahelices}
- \end{figure}
-
  Because the equitetrabeam which as a rail angle of $0$ still has
@@
  but it does not produce minimax optimal tetrahelices. In other words,
- untwisting a conter-clockwise tetrahelix to $0$ and then going
- further does produce a clockwise tetrahelix, but one in which the
+ untwisting a conter-clockwise tetrahelix to rail angle $0$ and then going
+even further does produce a clockwise tetrahelix, but one in which the
  one-hop and two-hop lengths in the wrong places (that is, two-hop
@@
 Equation \eqref{pitcheqn} can be easily solved numerically.
-For a pitch at least $ \frac{3  \sqrt{\frac{2}{5}}  \pi}{\rho_{bc}} \approx 9.64 $,
-and using \eqref{dopt}, produces minimax optimal tetrahelices.
+For a pitch at least $ p \geq \frac{3  \sqrt{\frac{2}{5}}  \pi}{\rho_{bc}} \approx 9.64 $,
+using \eqref{dopt} produces minimax optimal tetrahelices.
 
-In this way a rail angle can be chosen for any desired pitch, yield
+In this way a rail angle can be chosen for any desired (possible) pitch, yield
 the optimum radius, one-hop, and two-hop lengths an engineer needs to
@@
 changing the length of the two-hop member, leaving the one-hop memever
-and rail length equivalenet within this continuum. However, it should
+and rail length equivalent within this continuum.\footnote{Before deriving Equation \eqref{eqrhoopt}, we created a continuum by
+using a linear interpolation between the optimal radius for the
+Equitetrabeam and the BC Helix. This minimax optimum of this simpler
+approach was at most 1\% worse than the optimum computed by
+\eqref{eqrhoopt}.}
+ However, it should
 be noted that an engineer or architect may also use $H_{general}$
@@
 mathematic notion only loosely related to the beauty and utility of
-physical structures.
-
-Before deriving Equation \eqref{eqrhoopt}, we created a continuum by
-using a linear interpolation between the optimal radius for the
-Equitetrabeam and the BC Helix. This minimax optimum of this simpler
-approach was at most 1\% worse than the optimum computed by
-\eqref{eqrhoopt}.
-
-\section{Utility for Robotics}
+physical structures. For example, a structural engineer might increase
+radius in order to resist buckling. If an equitetrabeam were actually
+used as a beam, an engineer might start with the optimal tetrabeam and
+dilate it in one dimension to ``deepen'' the beam. Similarly, simple
+changes curve the equitetrabeam into an ``arch''.
 
@@
 including deployable and moving trusses\cite{claypool2012readily}.
+
+\section{Utility for Robotics}
 
@@
 \begin{theorem}
-  By changing only the length of the members that change rails and make two nodes, you can untwist a tetrobot
-  form the Boerdijk-Coxeter configuration to the equitetrabeam which rests flat on the plane.
+  By changing only the length of the members that change rails and make two nodes, you can dynamically untwist a tetrobot
+  forming the Boerdijk-Coxeter configuration to the equitetrabeam which rests flat on the plane.
 \end{theorem}
@@
   Proof by our computer program that does this by forming a linear interpolation of links.
+  See video on website\cite{readtetrahelix}.
 \end{proof}
@@
 \text{one-hop}  &= \sqrt{\frac{1}{9} + a^2} \\
-    \text{two-hops} &= \sqrt{\frac{2}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}  \\
-\text{two-hops}    &= \sqrt{\frac{4}{9} + a^2}
+    \text{two-hop} &= \sqrt{\frac{2}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}  \\
+\text{two-hop}    &= \sqrt{\frac{4}{9} + a^2}
 \end{align*}
-Computing the derivative of two-hops - one-hop:
+Computing the derivative of two-hop - one-hop:
 \begin{align*}
- \frac{\partial \text{two-hops} - \text{one-hop}}{a} &= \frac{\partial \sqrt{4/9 + a^2} - \sqrt{1/9 + a^2}}{\partial a} \\
-  \frac{\partial \text{two-hops} - \text{one-hop}}{a} &= \frac{a}{\sqrt{a^2 + 4/9}} - \frac{a}{\sqrt{ a^2 + 1/9}} 
+ \frac{\partial \text{two-hop} - \text{one-hop}}{a} &= \frac{\partial \sqrt{4/9 + a^2} - \sqrt{1/9 + a^2}}{\partial a} \\
+  \frac{\partial \text{two-hop} - \text{one-hop}}{a} &= \frac{a}{\sqrt{a^2 + 4/9}} - \frac{a}{\sqrt{ a^2 + 1/9}} 
 \end{align*}

### 2017-02-25 js/tetrahelix_math.js
updated PITCH

@@ -318,7 +318,6 @@ function major_test() {
     var lambda = 1.0;
     var third = 120*Math.PI/180.0;    
     for(var i = 0; i < 4; i++) {
-
 	var red = H_bc_lambda(i,red_phase,lambda);    
 	var yell = H_bc_lambda(i,yellow_phase,lambda);        
 	var blue = H_bc_lambda(i,blue_phase,lambda);    
@@ -341,3 +340,12 @@ function major_test() {
 
 //test_rail_angle_formula_against_BC();
 //test_H_general_against_BC();
+
+function pitchForOptimal(rho,len) {
+    var dopt = optimal_distance(rho,len);
+    return Math.PI*2*dopt/rho;
+}
+
+function pitchLimit(len) {
+    return pitchForOptimal(BCrho,len);
+}

### 2017-02-25 doc/TetrahelixUntwist.tex
proofs strengthened but still crummy

@@
 
-\section{Optimal Tetrahelices Have Evenly Spaced Vertices}
+\section{Optimal Tetrahelices Have $z$-axis Evenly Spaced Vertices}
 
@@
 tetrahelix, but the must useful to an enginner is to minimize the
-maximum difference between any two edges. We call a tetrahelix
+maximum difference between any two edges.
+Define the \emph{projected incircle radius} of a tetrahelix to be
+the radius of the incircle of all point on the tetrahelix projected
+down the $z$ axis into the $xy$ plane.
+We call a tetrahelix
 \emph{member-length minimax optimal} (or just \emph{optimal}) if there is not tetrahelix of the
-same radius and pitch with a smaller maximum edge length difference.
+same project incircle radius and pitch with a smaller maximum edge length difference.
 
@@
 extent. If all three rails do not have same pitch, there is an edge of
-unbounded length. So we are justified in talking about the pitch of
+unbounded length, so it is not optimal. So we are justified in talking about the pitch of
 the tetrahelix, even though we think of it as three
 helices. Similarly, if the axes are not parallel, there is an edge of
-unbounded length in the structure, so it is not optimal.
+unbounded length in the structure, so it is not optimal. So all three
+rails have the same rail length.
 
+We wish to show that the three helices optimal tetrahelix also have
+coincident axes.
 Consider any tetrahelix in which the axes of the helices are parallel
-to $z$ but not coincident, but in which all three helices have the
-same radius. Consider the projection along the $z$ axis, which will be
+to $z$ but not coincident, but in which all vertices lie on or outside
+a cylinder of radius $r$ centered on the $z$ axis.
+Since all three rails have the same rail length, no matter how we
+move the rails in the $xy$ plane if we shorten the $xy$ distance between
+vertices we shorten the total distance.
+Consider the projection along the $z$ axis of all vertices into the $xy$ plane, which will be
 a figure of dots and connecting segments in the $xy$ plane. The convex
 hull for any one helix projection will be a circle (if its pitch is
-irrational) or an polygon if rational. So long as its rail angle is
-not $0$, it will have at least two points in the plane. One of these
+irrational) or an polygon if rational, or a point if the helix has
+zero curvature. Each of these figures by definitions lies outside the
+circle of radius $r$ in the $xy$ plane.
+It is easiest to consider helices of zero curvature which only have one point
+as a special case. 
+For one rail consider a point in this projected figure furthest from the midpoint of the
+the two rails. The lengths to the furthest point on the other two rails will
+be decreased by moving the axis of that rail closer to the midpoint of the
+other two. Such motion 
+One of these segements
 will be longer and will be made shorter by moving that helix closer to
@@
 other two.
+
+For the special case of degenerate helix where we do not know the angle
+of the points from the axis, we can see that we minimize the maximum lengths
+when the projected vertices form an equilateral triangle around the $z$ axis at
+length $6r/sqrt{3}$.
+This is a equivalent to some let of helices which do have their axes on
+the $z$ axis, so without loss of generality we treat these degenerate
+helices as if they have their axis at the $z$-axis.
 

### 2017-02-27 doc/TetrahelixUntwist.tex
attempting to improve proofs

@@
 \newtheorem{corollary}{Corollary}
-\newtheorem{conjecture}{Conjecture}
-\newtheorem{proofsketch}{Proof Sketech}
 
@@
 precisely the same orientation around the $z$-axis. However, this is
-inconvenient to designers, who might prefer a rational pitch. For
-example, a slight irregularity that led to a pitch of precisely 10
-tetrahedra in one revolution would allow an architect to design a
+inconvenient to designers, who might prefer a rational pitch.
+The idea of deveoping a rational period by arranging solid tetrahedra by relaxing the face-to-face matching
+has been explored\cite{sadler2013periodic}. In this paper
+we develop slightly irregular edge lengths that support, for example, a pitch of precisely 10
+tetrahedra in one revolution which would allow an architect to design a
 column having a basis and a capital in the same relation to the
-tetrahedra they touch.
+tetrahedra they touch at the bottom and top of the column.
 
@@
 vertices and edges which is isomorphic to the BC helix, in which the
-vertices lie on three helices, no matter what lengths the edges take
-on. One could consider various definitions of optimality for a
+vertices lie on three helices. We further demand that all edge lengths
+be finite, as we are only interested in physically constructable tetrahelices.
+By isomporphic we mean there is a one-to-one mapping between both
+vertices and edges in the two tetrahelices.
+One could consider various definitions of optimality for a
 tetrahelix, but the must useful to an enginner is to minimize the
 maximum difference between any two edges.
-Define the \emph{projected incircle radius} of a tetrahelix to be
-the radius of the incircle of all point on the tetrahelix projected
-down the $z$ axis into the $xy$ plane.
-We call a tetrahelix
-\emph{member-length minimax optimal} (or just \emph{optimal}) if there is not tetrahelix of the
-same project incircle radius and pitch with a smaller maximum edge length difference.
 
-Consider a tetrahelix isomporphic to an BC helix of unbounded
-extent. If all three rails do not have same pitch, there is an edge of
-unbounded length, so it is not optimal. So we are justified in talking about the pitch of
-the tetrahelix, even though we think of it as three
-helices. Similarly, if the axes are not parallel, there is an edge of
-unbounded length in the structure, so it is not optimal. So all three
-rails have the same rail length.
+If all three rails do not have the same pitch, there is an edge of
+unbounded length, so it is not optimal. So we are justified in talking about the
+\emph{pitch} of 
+the tetrahelix as the pitch of its rail helices, even though there are
+three such helices.
 
-We wish to show that the three helices optimal tetrahelix also have
-coincident axes.
-Consider any tetrahelix in which the axes of the helices are parallel
-to $z$ but not coincident, but in which all vertices lie on or outside
-a cylinder of radius $r$ centered on the $z$ axis.
+Similarly, if the axes are not parallel, there is an edge of
+unbounded length in the structure, so we exclude such a strcturue.
+
+Since the axes are parallel, we may define the \emph{inradius} of a tetrahelix to be the radius of the largest
+``in cylinder'': a
+cylinder parallel to this axis contained within circumscribing cylinder which is penetrated by no edge.
+Define an \emph{minimax edge-length optimal tetrahelix} or just an
+\emph{optimal tetrahelix} to be a tetrahelix for which there exists
+no other tetrahelix of the same inradius and pitch with a lower maximum
+difference between its edge lengths.
+
+We wish to show that in an optimal tetrahelix, all vertices lie on the cylinder
+of radius $r$, regardless of where they lie on the $z$-axis.
+
 Since all three rails have the same rail length, no matter how we
@@
 vertices we shorten the total distance.
-Consider the projection along the $z$ axis of all vertices into the $xy$ plane, which will be
+Our tool for thinking about this is to project out the $z$ dimension to form
+a two-dimensional figure of nodes and non-rail edges.
+Consider the projection along the $z$ axis of all vertices and non-rail edges into the $xy$ plane, which will be
 a figure of dots and connecting segments in the $xy$ plane. The convex
@@
 circle of radius $r$ in the $xy$ plane.
-It is easiest to consider helices of zero curvature which only have one point
-as a special case. 
-For one rail consider a point in this projected figure furthest from the midpoint of the
-the two rails. The lengths to the furthest point on the other two rails will
-be decreased by moving the axis of that rail closer to the midpoint of the
-other two. Such motion 
-One of these segements
-will be longer and will be made shorter by moving that helix closer to
-the midpoint of the other two in the $xy$ plane. Even if the rail
-angle is $\pi$, there will be two vertices for each rail, each of
-which is connected to both vertices of the other two rails. At lesast
-one of these lines is a longest line which will be made shorter by
-moving that helix in the $xy$ plane closer to the midpoint of the
-other two.
 
-For the special case of degenerate helix where we do not know the angle
-of the points from the axis, we can see that we minimize the maximum lengths
-when the projected vertices form an equilateral triangle around the $z$ axis at
-length $6r/sqrt{3}$.
-This is a equivalent to some let of helices which do have their axes on
-the $z$ axis, so without loss of generality we treat these degenerate
-helices as if they have their axis at the $z$-axis.
+\begin{theorem}
+  Any optimal tetrahelix has all vertices on a single cylinder.
+\end{theorem}
 
-So any any optimal tetrahelix with a rail-angle of greater than $0$,
-that is, with any curvature, will have conincident axes.
+\begin{proof}
 
-We call a tetrahelix with $0$ curvature a \emph{tetrabeam}, and
-consider it as an important special case and an endpoint of a
-continuum of tetrahelices of decreasing curvature.
+Case 1: Suppose that $\rho$ is zero. Then for any given inradius, an equilateral
+triangle is the minimax solution for all non-rail edges. Since there is only
+one rail-edge length, this is the minimax solution for the entire set. Since
+the projection is an equilateral triangle lies on a circle, all points lie on
+a cylinder.
+
+Case 2: Suppose that $\rho$ is positive but less than $\pi$.
+In this case each rail helix has
+curavature and places points on both sides of any line through the origin
+of the $xy$ plane (or both coincident on such a line.)
+
+We first show that the inradius is touched by one segment from each pair
+of rails.
+
+\begin{figure}[H]
+  \label{untouchingrailfig}
+     \centering
+     \includegraphics[width=0.7\textwidth]{figures/UntouchingRail.png}
+     \caption{Untouching Rail}
+\end{figure}
+
+Figure\ref{untouchingrailfig} depicts a projection of
+depicting only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
+and the intermediary points $R$ and $Q$ on the other two rails.
+
+Supoose there is a rail $P$ which does not have a segment touching the incircle
+at all in the projection, as depicted in 
+Then a segment connecting the other two $Q$ and $R$ is a longest
+rail, because any chord touching an incircle is longer than any which does not.
+These two rails ($Q$ and $R$) can be moved closer to each other, and further away from $P$, to form a better minimax solution
+by shortening the longest rail, until one of the segments from $P$ the previously
+untouching rail touches one of the incircle. By induction then all rails have
+at least one segement touch each vertex on the rail that is tangent to the
+the inradius in an optimal tetrahelix.
+
+Now suppose that you attempt to move the axis of one of the rails. Because
+$\rho > 0 $ and $\rho$ is not a multiple of $\pi$, there is some vertex on the two sides of any diameter
+halving our circle. Moving the axis of a tetrahelix lengthens a longest line while ``pinching'' the
+inradius on the other side, so it is not optimal. Since the axes of these helices are the
+same and they have the same curvature and pitch, the points defined by the helices all lie
+on a cylinder.
+
+\end{proof}
+
+Now that we have show that any optimal tetrahelix vertices that
+are on helices of the same axes and pitch, we see that the vertices 
+of any optimal tetrahelix will lie on a cylinder, or a circle when axis dimension
+is projected out. Therefore is is reasonable to now speak of the \emph{radius}
+of a tetrahelix as the radius of the cylinder, and the notion
+of the projected incircle radius is now obsolete.
 
 Now that we have coincident axes, the same pitch, we can go on to
- the hard proof about where they occur.
+ the hard proof about where they occur along the $z$-axis.
 
@@
 \footnote{Another interesting but non-optimal solution is derived by setting (one-hop + two-hop)/2 = 1,  occurs at $r = \sqrt{35}/4$,
-which produces three length classes of $11/12, 12/12, 13/12$!}
+which produces three length classes of $11/12, 12/12, 13/12$}
 
@@
 
+  Consider any tetrahelix in which the axes of the helices are parallel
+to $z$ but not coincident, but in which all vertices lie on or outside
+a cylinder of radius $r$ centered on the $z$ axis.
+Since all three rails have the same rail length, no matter how we
+move the rails in the $xy$ plane if we shorten the $xy$ distance between
+vertices we shorten the total distance.
+Consider the projection along the $z$ axis of all vertices and non-rail edges into the $xy$ plane, which will be
+a figure of dots and connecting segments in the $xy$ plane. The convex
+hull for any one helix projection will be a circle (if its pitch is
+irrational) or an polygon if rational, or a point if the helix has
+zero curvature. Each of these figures by definitions lies outside the
+circle of radius $r$ in the $xy$ plane.
+It is easiest to consider helices of zero curvature which only have one point
+as a special case. 
+For one rail consider a point in this projected figure furthest from the midpoint of the
+the two rails. The lengths to the furthest point on the other two rails will
+be decreased by moving the axis of that rail closer to the midpoint of the
+other two.
+One of these segements
+will be longer and will be made shorter by moving that helix closer to
+the midpoint of the other two in the $xy$ plane. Even if the rail
+angle is $\pi$, there will be two vertices for each rail, each of
+which is connected to both vertices of the other two rails. At lesast
+one of these lines is a longest line which will be made shorter by
+moving that helix in the $xy$ plane closer to the midpoint of the
+other two.
+
+For the special case of degenerate helix where we do not know the angle
+of the points from the axis, we can see that we minimize the maximum lengths
+when the projected vertices form an equilateral triangle around the $z$ axis at
+length $6r/\sqrt{3}$.
+This is a equivalent to some set of helices which do have their axes on
+the $z$ axis, so without loss of generality we treat these degenerate
+helices as if they have their axis at the $z$-axis.
+
+So any any optimal tetrahelix with a rail-angle of greater than $0$,
+that is, with any curvature, will have conincident axes, or are indistinguishable
+from such a set.
+
+Possible addtional refrerences and submissions:
+
+Journal of applied geometry seems like a good fit:
+
+http://epubs.siam.org/toc/sjaabq/1/1
+
+According to there editorial board, they welcome mathematcal software and
+online resources such as I provie.
+
+This one has a nice editing structure: Metric Geometry is a nice subset:
+
+http://discreteanalysisjournal.com/for-authors
+
 http://bit-player.org/2013/tetrahedra-with-a-twist
+
+This is unrelated, but well worth reading:
+
+https://arxiv.org/pdf/1702.06388.pdf

### 2017-02-28 doc/TetrahelixUntwist.tex
addition of math and function for inradius, and a major bug fixed

@@
 
-\title{Untwisting the Tetrahelix (v0.6)}
+\title{Untwisting the Tetrahelix (v0.7)}
 \author{Robert L. Read \texttt{read.robert@gmail.com} \and
@@
 \begin{theorem}
+  \label{thm:cylinder}
   Any optimal tetrahelix has all vertices on a single cylinder.
@@
 
-Figure\ref{untouchingrailfig} depicts a projection of
+Figure \ref{untouchingrailfig} depicts a projection of
 depicting only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
@@
 \end{proof}
+
+Theorem \ref{thm:cylinder} is not true when $\rho$ is an odd multiple of $\pi$.
 
@@
 \end{proof}
+
+If you look down the axis of an optimal tetrahelix, it happens that only the one-hop edges
+come closest to the axis. In other words, they define the radius of the incircle of the
+projection, or the radius of a cylinder that would just fit inside the tetrahelix.
+This is useful to know if the tetrahelix is used as a structure to house a pipe or
+a ladder or that must bear a human or to armor a conduit. The \emph{inradius} of
+an optimal tetrahelix is a function of the radius $r$ and the rail angle $\rho$:
+\begin{equation}
+  \label{eq:inradius}
+  \frac{r \sin{(\pi - \rho)}}{6}
+\end{equation}
+Which can be seen from the trigonometry of the projection diagram:
+
+\begin{figure}[H]
+  \label{projectiondiagram}
+     \centering
+     \includegraphics[width=0.3\textwidth]{figures/ProjectionDiagram.png}
+     \caption{Projection Diagram (needs labels)}
+\end{figure}
 

### 2017-02-28 js/tetrahelix_math.js

@@ -346,6 +346,10 @@ function pitchForOptimal(rho,len) {
     return Math.PI*2*dopt/rho;
 }
 
-function pitchLimit(len) {
+function pitch_min(len) {
     return pitchForOptimal(BCrho,len);
+}
+
+function inradius_assumption1(rho,r) {
+    return r*Math.sin((Math.PI - rho)/6);
 }

### 2017-02-28 doc/TetrahelixUntwist.tex
tweak

@@
   An interactive tool for such design and experimentation is provided.
+  A formula
+  for the inradius is given.
   Utility and use for static and variable geometry
@@
   1 &=  \sqrt{\frac{1}{9}  + r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
-  r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }} \numberthis  \label{eqrhoopt} \\
+  r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }} \numberthis  \label{eqrhoopt} \\
 \end{align*}
@@
 \begin{align*}
-  d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
-  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
-  d_{opt}^2 &= 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
-  d_{opt}^2 &= 1 - \frac{16 sin^2(\rho / 2) }{ cos(\rho) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
-    d_{opt} &= \sqrt{1 - \frac{16 sin^2(\rho / 2) }{ cos(\rho) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
+  d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
+  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
+  d_{opt}^2 &= 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
+  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
+    d_{opt} &= \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
 \end{align*}
@@
 
-Create working toolkit for desin/exploration.
+Create working toolkit for design/exploration.
 

### 2017-03-01 js/tetrahelix_math.js
solved the 4% bug

@@ -192,6 +192,7 @@ function test_assert_optimal_radius_even() {
 }
 
 function H_general(chi,n,c,rho,d,r) {
+    console.log("params",chi,n,c,rho,d,r);
     if (chi != 1 && chi != -1) {
 	console.log("chirality must be 1 or -1!");
 	return null;
@@ -204,13 +205,37 @@ function H_general(chi,n,c,rho,d,r) {
     var kappa = n+ c/3.0;
     var rk = rho*kappa;
     var angle = chi*(rk + c*2*Math.PI/3);
-//    console.log("rk",rk*180/Math.PI);
-//    console.log("angle",angle*180/Math.PI);
+    console.log("rk",rk*180/Math.PI);
+    console.log("angle",angle*180/Math.PI);
     
     pnt[0] = r*Math.cos(angle);
     pnt[1] = r*Math.sin(angle);
     pnt[2] = d*kappa;
+    console.log("pnt",pnt);
     return pnt;
+}
+
+function test_BC_unity() {
+    var rho = BCrho;
+    var len = 1.0;
+    var r_opt = optimal_radius(rho,len);
+    var d_opt = optimal_distance(rho,len);
+    var pnts = [];
+    for(var i = 0; i < 4; i++) {
+	var num = Math.floor(i / 3);
+	var rail = i % 3;
+	var q = H_general(1,num,rail,rho,d_opt,r_opt);
+	pnts.push(q);
+    }
+    console.log(pnts);    
+    for(var i = 0; i < 4; i++) {
+	var p0 = pnts[i];
+	var p1 = pnts[(i+1) % 4];
+	var distance = Math.distance3(p0,p1);
+	// All distances should be 1 here...
+	console.log(p0,p1,distance);
+    }
+
 }
 
 function test_evenness_H_general() {

### 2017-03-01 doc/TetrahelixUntwist.tex
minor fixes

@@
 \usepackage{amsfonts}
+\usepackage{hyperref}
 
@@
 
-\title{Untwisting the Tetrahelix (v0.7)}
+\title{Untwisting the Tetrahelix (v0.8)}
 \author{Robert L. Read \texttt{read.robert@gmail.com} \and
@@
 actuators, which can change their length, connected by special joints,
-called the Song-Kwon-Kim\cite{song2003spherical} or turret joint,
-which allow many members to come to a single point.  Such machines can
+such as the three-d printable Song-Kwon-Kim\cite{song2003spherical}, or the CMS joint\cite{HamlinSandersonCMS}
+which allow many members to come to a single point.
+Such machines can
 follow purely regular mathematical models such as the Boerdijk–-Coxeter
@@
 
-\begin{figure}[H] %float with two figures
+\begin{figure}[H]
+  \label{fig:spudboy}
+  \centering
+     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
+     \caption{A Series of Tetrahelices}
+\end{figure}
+
+\begin{figure}[H]
   \label{fig:closeup}
@@
 deveoped here is available in JavaScript and demonstrated by an interactive
-design website\cite{readtetrahelix}, from which Figures \ref{fig:closeup} and
-\ref{fig:series} are taken.
-
-\begin{figure}[H] %float with two figures
-  \label{fig:series}
-  \centering
-     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
-     \caption{A Series of Tetrahelices, BC Helix in Foreground.}
-\end{figure}
-
-%% Note: This is not rendering figure two for some reason.
-In Figure
-\ref{fig:series}, the closest helix is the BC helix, and the furthest
+design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix},
+from which Figures \ref{fig:closeup} and
+the figure below are taken.
+
+In Figure \ref{fig:spudboy}, the closest helix is the BC helix, and the furthest
 is the equitetrabeam.
@@
 $\theta$ is approximately $131.81$ degrees.
-The angle $\theta$ is the rotation of a \emph{each} tetrahedra, not the tetraheda along a rail.  In Figure \ref{closeup},
+The angle $\theta$ is the rotation of a \emph{each} tetrahedra, not the tetraheda along a rail.  In Figure \ref{fig:closeup},
 each tetrahedra has either a yellow, blue, or red outer edge or rail.
@@
 The apparent rotation of tetrhedra of the same outer-edge color ($V_3$ relative from $V_0$ for example,
-in \eqref{graycoxeter}, is $3 \theta - 2\pi$.
+in \eqref{graycoxeter}, is $3 \theta - 2\pi$).
 
@@
   &= \frac{d_{bc} 2 \pi }{\rho_{bc}} \\  
-  &= \frac{3 \cdot h_{bc} 2 \pi }{\rho_{bc}} \\
+%%  &= \frac{3 \cdot h_{bc} 2 \pi }{\rho_{bc}} \\
   &= \frac{3  \sqrt{\frac{2}{5}}  \pi}{\rho_{bc}} \\
@@
 
-\section{Optimal Tetrahelices Have $z$-axis Evenly Spaced Vertices}
+\section{Optimal Tetrahelices}
 
@@
   \label{thm:cylinder}
-  Any optimal tetrahelix has all vertices on a single cylinder.
+  Any optimal tetrahelix with a rail angle less than $\pi$ has all vertices on a single cylinder.
 \end{theorem}
@@
   1^2 &= d^2 + (2 r \sin{ \rho / 2})^2 \\
-  1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 \\
+%%  1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 \\
   d^2 &= 1 - 4 r^2 (\sin{ \rho / 2})^2    \numberthis  \label{railangle} \\
@@
   \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}),r_{\rho})  \\
-  \text{one-hop} &= dist(H_{general}(0,0,\rho,d_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r_{\rho}\sin(0) - r_{\rho}\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
-    (r_{\rho}\cos(0) - r_{\rho}\cos(\rho/3 + 1\cdot\frac{2\pi}{3}))^2} \\
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho/3 + \frac{2\pi}{3}))^2  +
-    (r_{\rho} - r_{\rho}\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
-    r_{\rho}^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
+%%  \text{one-hop} &= dist(H_{general}(0,0,\rho,d_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
+%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r_{\rho}\sin(0) - r_{\rho}\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
+%%    (r_{\rho}\cos(0) - r_{\rho}\cos(\rho/3 + 1\cdot\frac{2\pi}{3}))^2} \\
+%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho/3 + \frac{2\pi}{3}))^2  +
+%%    (r_{\rho} - r_{\rho}\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
+%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
+%%    r_{\rho}^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.
   \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
-  d_{\rho}^2 &= 1 - 4 r_{\rho}^2 (\sin( \rho / 2)^2 \\
+  \text{but: }  d_{\rho}^2 &= 1 - 4 r_{\rho}^2 (\sin( \rho / 2)^2 \text{so we substitute:}\\
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.  
@@
 Since the partial derivative of $\text{two-hop} - \text{one-hop}$ with respect to the
-radius is negative up until $\rho$ up until $\rho_{bc}$ when it is $0$, then
+radius is negative up until $\rho_{bc}$ when it is $0$, then
 we will opitmize the overall minimax distance by choosing the largest radius
@@
   d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
-  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
+%%  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
   d_{opt}^2 &= 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
-  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
+%%  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
     d_{opt} &= \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
@@
 This is useful to know if the tetrahelix is used as a structure to house a pipe or
-a ladder or that must bear a human or to armor a conduit. The \emph{inradius} of
-an optimal tetrahelix is a function of the radius $r$ and the rail angle $\rho$:
+a ladder that must bear a human or to armor a conduit. The \emph{inradius} of
+an optimal tetrahelix is a remarkably simple function of the radius $r$ and the rail angle $\rho$:
 \begin{equation}
@@
      \centering
-     \includegraphics[width=0.3\textwidth]{figures/ProjectionDiagram.png}
-     \caption{Projection Diagram (needs labels)}
+     \includegraphics[width=0.8\textwidth]{figures/ProjectionDiagram.png}
+     \caption{General One-hop Projection Diagram}
 \end{figure}
@@
 This radius produces a two-hop rail length of
-$\frac{2}{\sqrt{3}}$. The difference between this 
-and $1$ of $\approx 15.47\% $.
-
-\footnote{Another interesting but non-optimal solution is derived by setting (one-hop + two-hop)/2 = 1,  occurs at $r = \sqrt{35}/4$,
-which produces three length classes of $11/12, 12/12, 13/12$}
-
-In Figure \ref{series}, the furthest tetrahelix is the optimal equitetrabeam.
+$\frac{2}{\sqrt{3}}$\footnote{Another interesting but non-optimal solution is derived by setting (one-hop + two-hop)/2 = 1,  occurs at $r = \sqrt{35}/4$,
+which produces three length classes of $11/12, 12/12, 13/12$.}
+. The difference between this 
+and $1$ is $\approx 15.47\% $.
+
+\begin{figure}[H]
+  \label{fig:unfolded}
+     \centering
+     \includegraphics[width=0.6\textwidth]{figures/EquitetrabeamUnfolded.JPG}
+     \caption{Projection Diagram (needs labels)}
+\end{figure}
+
+In Figure \ref{fig:spudboy}, the furthest tetrahelix is the optimal equitetrabeam.
+Figure \ref{fig:unfolded} shows a representation of an unfolded equitetrabeam.
 

### 2017-03-02 doc/TetrahelixUntwist.tex
significant improvements

@@
 
-\title{Untwisting the Tetrahelix (v0.8)}
+\title{Untwisting the Tetrahelix (v0.9)}
 \author{Robert L. Read \texttt{read.robert@gmail.com} \and
@@
 to any structure isomophic to a the BC helix, whether regular or not.
-
-\begin{figure}[H]
-  \label{fig:spudboy}
-  \centering
-     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
-     \caption{A Series of Tetrahelices}
-\end{figure}
 
@@
 the three helices which are visually apparent, that is, those three
-which are closely approximated by the by the outer edges or rails of
+which are closely approximated by the outer edges or rails of
 the BC helix. We think of each of these three rails as being a different color, red, blue, or yellow.
@@
 
-Note in Figure \ref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In \eqref{graycoxeter} and \label{eq:colored}, the variable
+Note in Figure \ref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In \eqref{graycoxeter} and \eqref{eq:colored}, the variable
 $h$ is used for one third of the distance we name $d$. We will later justify that $d = 3h$. In this paper we assume the length of a rail
 is alwyas $1$ is a simplification, although we make the rail length a parameter in our JavaScript codein \texttt{tetrahelixmath.js} \cite{readtetrahelix}.
+
+This Gray-Coxeter formulation $V(n)$ from \eqref{graycoxeter} is valuable, but obscures the fact that we have three
+apparent rail helices.
+In order to rewrite this expression with an explicit rotation of $2\pi/3$, we expand 
+the expressions $\theta$ and $\rho_{bc}$ and seek to isolate the term $c2\pi/3 $.
+\begin{align*}
+  \rho_{bc} n + c \theta  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
+    (3 \theta - 2 \pi)n + (c/3)  (3 \theta)  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
+  (3 \theta - 2 \pi)n + (c/ 3) (3 \theta - 2 \pi  + 2 \pi) &=  \text{\{associate...\}} \\
+  (3 \theta - 2 \pi)n + (c/ 3) ((3 \theta - 2 \pi)  + 2 \pi) &=  \text{\{distribute...\}} \\  
+  (3 \theta - 2 \pi)n + (c / 3) (3 \theta - 2 \pi)  + c 2 \pi /3 &=  \text{\{definition of $\rho_{bc}$...\}} \\
+  \rho_{bc} n + (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{\{collect like factors...\}} \\  
+  n \rho_{bc}  +\rho_{bc} ( c+  2 \pi) /3  \\
+\end{align*}
+Now the the term on the left is the only one that depends on the scalar $n$. We use this to a create
+a new formulation: $H_{BCsymmetric}(n,c) = H_{BCcolored}(n,c)$
+
+Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued.)
+
+%% Actually, I am not sure if this is a clearer formulation...it might be, and need to put it in general!!!
+\begin{equation}
+H_{BCsymmmetric}(n,c) =
+\left [
+  \begin{tabular}{c}
+    $ r  \cos(\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3) $\\
+   $ r  \sin(\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3) $\\
+   $ (n+c/3)  h_{bc} $
+  \end{tabular}
+  \right ],
+\text{where:}
+  \begin{tabular}{c}
+%%  $\kappa = n + c/3$ \\
+    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
+    $ \theta = \arccos(-2/3) $ \\
+    $ h_{bc} = 1/\sqrt{10} $ \\    
+  \end{tabular}      
+\end{equation}
 
@@
 are not lined up perfectly.  It is a famous and interesting result
-that the pitch is irrational, a BC helix never has two tetrahedra at
+that the pitch is irrational. A BC helix never has two tetrahedra at
 precisely the same orientation around the $z$-axis. However, this is
 inconvenient to designers, who might prefer a rational pitch.
-The idea of deveoping a rational period by arranging solid tetrahedra by relaxing the face-to-face matching
+The idea of developing a rational period by arranging solid tetrahedra by relaxing the face-to-face matching
 has been explored\cite{sadler2013periodic}. In this paper
-we develop slightly irregular edge lengths that support, for example, a pitch of precisely 10
+we develop slightly irregular edge lengths that support, for example, a pitch of precisely 12
 tetrahedra in one revolution which would allow an architect to design a
@@
 If all three rails do not have the same pitch, there is an edge of
-unbounded length, so it is not optimal. So we are justified in talking about the
+unbounded length, so it is hardly optimal. So we are justified in talking about the
 \emph{pitch} of 
@@
 
-Since the axes are parallel, we may define the \emph{inradius} of a tetrahelix to be the radius of the largest
-``in cylinder'': a
-cylinder parallel to this axis contained within circumscribing cylinder which is penetrated by no edge.
+Since the axes are parallel, we may define the \emph{inradius} of a
+tetrahelix to be the radius of the largest
+cylinder parallel to this axis contained within the circumscribing cylinder w
+hich is penetrated by no edge.
 Define an \emph{minimax edge-length optimal tetrahelix} or just an
@@
 hull for any one helix projection will be a circle (if its pitch is
-irrational) or an polygon if rational, or a point if the helix has
+irrational) or a polygon if rational, or a point if the helix has
 zero curvature. Each of these figures by definitions lies outside the
-circle of radius $r$ in the $xy$ plane.
+circle of inradius $i$ in the $xy$ plane.
 
@@
 Figure \ref{untouchingrailfig} depicts a projection of
-depicting only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
+only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
 and the intermediary points $R$ and $Q$ on the other two rails.
@@
 by shortening the longest rail, until one of the segments from $P$ the previously
-untouching rail touches one of the incircle. By induction then all rails have
-at least one segement touch each vertex on the rail that is tangent to the
-the inradius in an optimal tetrahelix.
+untouching rail touches one of the incircle. By induction, then all rails have
+at least one segement touching each vertex on the rail that is tangent to the
+incircle in an optimal tetrahelix.
 
@@
 
-Theorem \ref{thm:cylinder} is not true when $\rho$ is an odd multiple of $\pi$.
+Theorem \ref{thm:cylinder} is not true when $\rho$ is an odd integer multiple of $\pi$.
 
-Now that we have show that any optimal tetrahelix vertices that
+Now that we have shown that any optimal tetrahelix vertices
 are on helices of the same axes and pitch, we see that the vertices 
 of any optimal tetrahelix will lie on a cylinder, or a circle when axis dimension
-is projected out. Therefore is is reasonable to now speak of the \emph{radius}
-of a tetrahelix as the radius of the cylinder, and the notion
-of the projected incircle radius is now obsolete.
+is projected out. Therefore it is reasonable to now speak of the \emph{radius} $r$
+of a tetrahelix as the radius of the cylinder, as distinct from the inradius $i$.
 
-Now that we have coincident axes, the same pitch, we can go on to
- the hard proof about where they occur along the $z$-axis.
+Now that we have coincident axes, the same pitch, and the same radius, we can go on to
+ the harder proof about where vertices occur along the $z$-axis.
 
@@
  Note that from the point of view of a single edge, we are on a
- slanted cylinder, when $\rho \neq 0$.  This means for its point of
+ slanted cylinder, when $\rho \neq 0$.  This means from its point of
  view a cross section is an ellipse. So we have to be very careful in
@@
   \label{eventhirds}
-   A tetrahelix of a given radius and axial distance $d$ in which all nodes are evenly spaced at $d/3$ intervals on the $z$ axis is optimal.
+  An optimal tetrahelix of any rail angle $\rho < \pi$ has all nodes evenly spaced at $d/3$ intervals on the $z$ axis.
   Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail and $2$ two-hop edges connected to the rail.
@@
 
-    Any displacemnt along the $z$ axis of any rail increases the
-    length of one or two two-hop edges and shortens the length of one
-    or two one-hop edges.  This increases the minimax distance no
-    matter what the rail edge length is, since all rail edges are the
-    same length. Therefore, an evenly spaced tetrahelix is the unique
-    optimal for any given radius and height.
+    Every vertex is connected to 4 non-rail edges. There is a one-hop edge
+    in both the positive and negative $z$ direction. Likewise there is a two-hop
+    edge in both the positive and negative $z$ direction. Let $A$ be the set
+    of edge lengths, which has only 3 members, represented by $A = \{o,t,r\}$ for
+    the one-hop, two-hop, and rail edge lengths.
+
+    Any attempt to move any rail in either $z$ direction lengthens one two-hop edge to $t' > t$
+    edge and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be new edges.
+    The minimax of $B$ > $A$ since there is a single rail length which cannot be both greater
+    than $t'$ and $o'$ and less than $t'$ and $o'$.
+    Therefore, any optimal tetrahelix has all one-hop edges between all rails are equal to each other, and
+    all two-hop edges are equal to each other, and the $z$ distances between rails are equal, and therefore
+    $d/3$ from each other.
 \end{proof}
@@
 we have the equitetrabeam.
-
-This formulation $V(n,c)$ above is valuable, but obscures the essentially fact that the red, yellow, and blue helices distributed
-about the central $z$ axis $120\degree$ from each other.
-In order to rewrite this expression with an explicit rotation of $2\pi/3$, we expand 
-the expression and seek to isolate the term $c2\pi/3$.
-\begin{align*}
-  \rho_{bc} n + c \theta  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
-    (3 \theta - 2 \pi)n + (c/3)  (3 \theta)  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
-  (3 \theta - 2 \pi)n + (c/ 3) (3 \theta - 2 \pi  + 2 \pi) &=  \text{\{associate...\}} \\
-  (3 \theta - 2 \pi)n + (c/ 3) ((3 \theta - 2 \pi)  + 2 \pi) &=  \text{\{distribute...\}} \\  
-  (3 \theta - 2 \pi)n + (c / 3) (3 \theta - 2 \pi)  + c 2 \pi /3 &=  \text{\{definition of $\rho_{bc}$...\}} \\
-  \rho_{bc} n + (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{\{collect like factors...\}} \\  
-  \rho_{bc} (n + c/3)  + c 2 \pi /3  \\
-\end{align*}
-Now the the term on the left is the only one that depends on the scalar $n$. We use this to a create
-a new formulation: $H_{BCsymmetric}(n,c) = H_{BCcolored}(n,c)$
-
-The expression $n+c/3$ will now occur so often that we call it the ``c($\kappa$)olored number'' and we use the variable $\kappa$ to represent it: $\kappa = n+c/3$.
-Recall that $c \in \{0,1,2\}$, but $n$ and $\kappa$ are are continuous (rational or real-valued.)
-
-\begin{equation}
-H_{BCsymmmetric}(n,c) =
-\left [
-  \begin{tabular}{c}
-   $ r  \cos(\rho_{bc} \kappa  + c 2 \pi /3) $\\
-   $ r  \sin(\rho_{bc} \kappa  + c 2 \pi /3) $\\
-   $ \kappa 3  h_{bc} $
-  \end{tabular}
-  \right ],
-\text{where:}
-  \begin{tabular}{c}
- $\kappa = n + c/3$ \\
-    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
-    $ \theta = \arccos(-2/3) $ \\
-    $ h_{bc} = 1/\sqrt{10} $ \\    
-  \end{tabular}      
-\end{equation}
 
@@
   \begin{tabular}{c}
-   $ r_{\rho} \cos(\chi \cdot (\rho \kappa + c 2 \pi /3)) $\\
-   $ r_{\rho}  \sin(\chi \cdot (\rho \kappa + c 2 \pi /3)) $\\
-   $ d_{\rho} \kappa $
+   $ r_{\rho} \cos(\chi \cdot (n \rho + c(\rho +  2 \pi) /3)) $\\
+   $ r_{\rho}  \sin(\chi \cdot (n \rho + c(\rho +  2 \pi) /3)) $\\
+   $ d_{\rho} (n + c /3) $
   \end{tabular}
@@
   $   1 = d_{\rho}^2 + 4 r_{\rho}^2 (\sin{ \rho / 2})^2 $ \\
-  $\kappa = n + c/3$ \\
+%%  $\kappa = n + c/3$ \\
     $\chi \in \{-1,1\}$ \\  
@@
   \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
-  \text{but: }  d_{\rho}^2 &= 1 - 4 r_{\rho}^2 (\sin( \rho / 2)^2 \text{so we substitute:}\\
+  \text{but: }  d_{\rho}^2 &= 1 - 4 r_{\rho}^2 (\sin( \rho / 2)^2 \text{ ...so we substitute:}\\
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.  
@@
 
-\begin{theorem}
-  \label{optimality}
-  For any rail angle $\rho$ where $\rho \leq \rho_{bc}$, a tetrahelix of minimum maximum edge length
-  difference is generated by $H_{general}(\chi,n,c,\rho,d_{\rho},r_{opt})$, where $r_{opt}$ and $d_{opt}$ are
-  computed from $\rho$. 
-\end{theorem}
-
-\begin{proof}
-  Theorem \ref{eventhirds} theorem tells us an optimal will have even thirds,
-  as Equation \eqref{eq:general} does.
-  Theorem \ref{generalformulaoptimal} tell us that
-  that plugging $r_{opt}, d_{opt}$ into $H_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho})$ minimizes the maximum length difference.
-\end{proof}
-
 If you look down the axis of an optimal tetrahelix, it happens that only the one-hop edges
@@
 This is useful to know if the tetrahelix is used as a structure to house a pipe or
-a ladder that must bear a human or to armor a conduit. The \emph{inradius} of
+a ladder that must bear a human or to armor a conduit. The inradius $i_\rho$ of
 an optimal tetrahelix is a remarkably simple function of the radius $r$ and the rail angle $\rho$:
@@
   \label{eq:inradius}
-  \frac{r \sin{(\pi - \rho)}}{6}
+  i_{\rho} = \frac{r \sin{(\pi - \rho)}}{6}
 \end{equation}
-Which can be seen from the trigonometry of the projection diagram:
+Which can be seen from the trigonometry of a diagram of the projected one-hop edges
+connecting four sequentially numbered vertices:
 
@@
 
-Choosing $d = 1$ and $\rho = 0$ we use Equation \eqref{eqrhoopt} to find the radius of 
-optimal minimax difference.
-
 \begin{corollary}
@@
 \end{corollary}
+
+\begin{proof}
+Choosing $d = 1$ and $\rho = 0$ we use Equation \eqref{eqrhoopt} to find the radius of 
+optimal minimax difference.
+
+Substituting into \eqref{eq:general}:
 
@@
 \begin{align*}
-   1  &=  \sqrt{\frac{1}{9} + 3r^2} \\
-   r  &= \sqrt{\frac{8}{27}} \\
-   r &\approx 0.5443
+   1  &=  \sqrt{\frac{1}{9} + 3r^2} & \text{ solved by... }\\
+   r  &= \sqrt{\frac{8}{27}} &\approx 0.5443 \\
 \end{align*}
+\end{proof}
 
-This radius produces a two-hop rail length of
-$\frac{2}{\sqrt{3}}$\footnote{Another interesting but non-optimal solution is derived by setting (one-hop + two-hop)/2 = 1,  occurs at $r = \sqrt{35}/4$,
-which produces three length classes of $11/12, 12/12, 13/12$.}
-. The difference between this 
-and $1$ is $\approx 15.47\% $.
+This radius\footnote{Another interesting but non-optimal solution is derived by setting (one-hop + two-hop)/2 = 1,
+  occurs at $r = \sqrt{35}/4$ which produces
+  three length classes of $11/12, 12/12, 13/12$.}
+produces a two-hop rail length of $\frac{2}{\sqrt{3}}$.
+The difference between this and $1$ is $\approx 15.47\% $.
 
@@
      \includegraphics[width=0.6\textwidth]{figures/EquitetrabeamUnfolded.JPG}
-     \caption{Projection Diagram (needs labels)}
+     \caption{Projection Diagram}
 \end{figure}
@@
 
+\begin{figure}[H]
+  \label{fig:spudboy}
+  \centering
+     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
+     \caption{A Series of Tetrahelices}
+\end{figure}
+
 We observe that Equations \eqref{eqrhoopt} and \eqref{dopt} compute $r_{opt}$ and $d_{opt}$ which
@@
 
- Because the equitetrabeam which as a rail angle of $0$ still has
+ Because the equitetrabeam which has a rail angle of $0$ still has
  chirality, that is, one still must decide to connect with one-hop to
@@
  one-hop and two-hop lengths in the wrong places (that is, two-hop
- becomes shorter than one-hop.)
+ becomes shorter than one-hop.) Likewise, $\rho > \rho_{bc}$ generates
+ a tetrahelix, but minimax optimality is not guaranteed by $H_{general}$.
 
@@
 For a fixed $z$-axis travel $d$, this is trivial.
-$z$-axis travel as per \eqref{dopt} pitch increases monotonically and smoothly with decreasing $\rho$, so
-Equation \eqref{pitcheqn} can be easily solved numerically.
+However, if one is computing 
+$z$-axis travel from \eqref{dopt} the pitch is not simple.
+However, it increases monotonically and smoothly with decreasing $\rho$, so
+Equation \eqref{pitcheqn} can be easily solved numerically with a Newton-Raphson
+solver, as we do on our website.
 For a pitch at least $ p \geq \frac{3  \sqrt{\frac{2}{5}}  \pi}{\rho_{bc}} \approx 9.64 $,
@@
 
-In this way a rail angle can be chosen for any desired (possible) pitch, yield
+In this way a rail angle can be chosen for any desired (sufficiently large) pitch, yield
 the optimum radius, one-hop, and two-hop lengths an engineer needs to
@@
 directly and interactively, and that minimax length optimality is a
-mathematic notion only loosely related to the beauty and utility of
+mathematic starting point rather than the final word on the beauty and utility of
 physical structures. For example, a structural engineer might increase
@@
 
-    \section{Old Proofs}
-
-We can create the distance between representative nodes as:
-\begin{align*}
-  \overline{\rm AB}  &= 1 \\        
-  \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + -\cos{2 G \rho})} \\
-  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + \sin^2{O \rho}  - \cos^2{O \rho})} \\  
-  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + -\cos{2 O  \rho})} \\
-  \overline{\rm BD}  &= \sqrt{P^2 + r^2(1 + -\cos{2 P \rho}))} \\
-  \overline{\rm AD}  &= \sqrt{(O+G)^2 + r^2(1 + -\cos{2 (O + G)  \rho})} \\
-  \overline{\rm BC}  &= \sqrt{(P+G)^2 + r^2(1 + -\cos{2 (P + G) \rho})} \\      
-\end{align*}
-
-Using the cartesian distance formula:
-\begin{align*}
-  \overline{\rm CD}  &= \sqrt{G^2 + (r\sin{0 \rho} -  r\sin{G \rho})^2 + (r\cos{0 \rho} - r\cos{G \rho})^2} \\
-    \overline{\rm CD}  &= \sqrt{G^2 + (0 -  r\sin{G \rho})^2 + (r - r\cos{G \rho})^2} \\
-    \overline{\rm CD}  &= \sqrt{G^2 + r^2(\sin{G \rho})^2 + r^2(1 - \cos{G \rho})^2} \\
-    \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + \sin^2{G \rho}  - \cos^2{G \rho})} \\
-    \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + -\cos{2 G \rho})} \\        
-\end{align*}
-Note: $\sin^2{x \rho}  - \cos^2{x \rho} = -\cos{2 x \rho}$
-
-So, for all O,G,P,
-\begin{align*}
-  \overline{\rm AB}  &= 1 \\        
-  \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + -\cos{2 G \rho})} \\
-  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + \sin^2{O \rho}  - \cos^2{O \rho})} \\  
-  \overline{\rm AC}  &= \sqrt{O^2 + r^2(1 + -\cos{2 O  \rho})} \\
-  \overline{\rm BD}  &= \sqrt{P^2 + r^2(1 + -\cos{2 P \rho}))} \\
-  \overline{\rm AD}  &= \sqrt{(O+G)^2 + r^2(1 + -\cos{2 (O + G)  \rho})} \\
-  \overline{\rm BC}  &= \sqrt{(P+G)^2 + r^2(1 + -\cos{2 (P + G) \rho})} \\      
-\end{align*}
-
-Then we can simplify our distance equations:
-\begin{align*}
-  \overline{\rm AB}  &= 1 \\        
-  \overline{\rm CD}  &= \sqrt{G^2 + r^2(1 + -\cos{2 G \rho})} \\
-  \overline{\rm AC} &=   \overline{\rm BD} &= \sqrt{P^2 + r^2(1 + -\cos{2 P \rho}))} \\
-  \overline{\rm AC} &=   \overline{\rm BD} &= \sqrt{((1-G)/2)^2 + r^2(1 + -\cos{ \rho (1-G) }))} \\  
-  \overline{\rm AD} &=  \overline{\rm BC} &=  \sqrt{((P+G)^2 + r^2(1 + -\cos{2 (P + G) \rho})} \\
-  \overline{\rm AD} &=  \overline{\rm BC} &=  \sqrt{((1+ G)/2 )^2 + r^2(1 + -\cos{\rho (1 + G)})} \\        
-\end{align*}
-
-When $G = 0$, $\overline{\rm CD} = 0$. Our solution is improved as we
-increase $G$ until either $ \overline{\rm CD} = \overline{\rm AC}$, or
-the quantity $ \overline{\rm BC} - \overline{\rm CD} $ starts
-increasing rather than decreasing (that is, when the derivative is
-positive.)
-
-Suppose $\overline{\rm C'D'}$ is the shortest edge. Increasing $G$
-thereby improves our mimimum, up until the next shortest edge length,
-$\overline{\rm AC}$.  This may increase $\overline{\rm BC}$ and
-$\overline{\rm AD}$, but more slowly than $\overline{\rm C'D'}$
-is being increased, until $\overline{\rm C'D'} = \overline{\rm AC}$.
-Note: This is sketchy, can we show that the derivative of our formula
-for CD with respect to $G$ is really higher than $AD$? These
-derivatives will depend on $\rho$ slightly, which is exactly right!
-
-\begin{align*}
-  \text{rail} &=  1 \\
-  \text{one-hop} &= \sqrt{\frac{1}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}\\
-\text{one-hop}  &= \sqrt{\frac{1}{9} + a^2} \\
-    \text{two-hop} &= \sqrt{\frac{2}{3}^2 + (\frac{3a}{2\sqrt{3}})^2 + (a/2)^2}  \\
-\text{two-hop}    &= \sqrt{\frac{4}{9} + a^2}
-\end{align*}
-Computing the derivative of two-hop - one-hop:
-\begin{align*}
- \frac{\partial \text{two-hop} - \text{one-hop}}{a} &= \frac{\partial \sqrt{4/9 + a^2} - \sqrt{1/9 + a^2}}{\partial a} \\
-  \frac{\partial \text{two-hop} - \text{one-hop}}{a} &= \frac{a}{\sqrt{a^2 + 4/9}} - \frac{a}{\sqrt{ a^2 + 1/9}} 
-\end{align*}
-
-Now basic components of the helix, which are the radius $r$, the rate of rotation, and the rate of
-axial growth can all be linearly interpolated with a parameter $\lambda$ between their high values (for the BC helix)
-and low values (for the equitetrabeam):
-
-\begin{align*}
-r_{\lambda}  &=  \lvert \lambda \rvert \cdot (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
-d_{\lambda} &=   \lvert \lambda \rvert \cdot (3 \sqrt{10} - 1) + 1 \\
-\phi_{\lambda} &=  \lambda \cdot \rho_{bc}  + 0
-\end{align*}
-to create a formula that generates a continuum of tetrahedral structures:
-
-\[
-H_{continuum}(n,c,\lambda) =
-\left [
-  \begin{tabular}{c}
-   $ r_{\lambda} \cos(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
-   $ r_{\lambda}  \sin(\phi_{\lambda} \kappa + c 2 \pi /3) $\\
-   $ d_{\lambda} \kappa $
-  \end{tabular}
-  \right ],
-\text{where:}
-  \begin{tabular}{c}
-    $\kappa = n + c/3$ \\
-    $ r_{opt} =  \text{is used : \eqref{eqrhoopt}} $ \\    
-    $ \phi_{\lambda} =  \lambda \rho_{bc}  + 0 $\\
-    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
-   $ \theta = \arccos(-2/3) $
-  \end{tabular}      
-  \]
-
-  Consider any tetrahelix in which the axes of the helices are parallel
-to $z$ but not coincident, but in which all vertices lie on or outside
-a cylinder of radius $r$ centered on the $z$ axis.
-Since all three rails have the same rail length, no matter how we
-move the rails in the $xy$ plane if we shorten the $xy$ distance between
-vertices we shorten the total distance.
-Consider the projection along the $z$ axis of all vertices and non-rail edges into the $xy$ plane, which will be
-a figure of dots and connecting segments in the $xy$ plane. The convex
-hull for any one helix projection will be a circle (if its pitch is
-irrational) or an polygon if rational, or a point if the helix has
-zero curvature. Each of these figures by definitions lies outside the
-circle of radius $r$ in the $xy$ plane.
-It is easiest to consider helices of zero curvature which only have one point
-as a special case. 
-For one rail consider a point in this projected figure furthest from the midpoint of the
-the two rails. The lengths to the furthest point on the other two rails will
-be decreased by moving the axis of that rail closer to the midpoint of the
-other two.
-One of these segements
-will be longer and will be made shorter by moving that helix closer to
-the midpoint of the other two in the $xy$ plane. Even if the rail
-angle is $\pi$, there will be two vertices for each rail, each of
-which is connected to both vertices of the other two rails. At lesast
-one of these lines is a longest line which will be made shorter by
-moving that helix in the $xy$ plane closer to the midpoint of the
-other two.
-
-For the special case of degenerate helix where we do not know the angle
-of the points from the axis, we can see that we minimize the maximum lengths
-when the projected vertices form an equilateral triangle around the $z$ axis at
-length $6r/\sqrt{3}$.
-This is a equivalent to some set of helices which do have their axes on
-the $z$ axis, so without loss of generality we treat these degenerate
-helices as if they have their axis at the $z$-axis.
-
-So any any optimal tetrahelix with a rail-angle of greater than $0$,
-that is, with any curvature, will have conincident axes, or are indistinguishable
-from such a set.
-
 Possible addtional refrerences and submissions:

### 2017-03-02 js/bundle.js
significant structural progress with browserify

@@ -1,3 +1,4 @@
+(function e(t,n,r){function s(o,u){if(!n[o]){if(!t[o]){var a=typeof require=="function"&&require;if(!u&&a)return a(o,!0);if(i)return i(o,!0);var f=new Error("Cannot find module '"+o+"'");throw f.code="MODULE_NOT_FOUND",f}var l=n[o]={exports:{}};t[o][0].call(l.exports,function(e){var n=t[o][1][e];return s(n?n:e)},l,l.exports,e,t,n,r)}return n[o].exports}var i=typeof require=="function"&&require;for(var o=0;o<r.length;o++)s(r[o]);return s})({1:[function(require,module,exports){
 /*
 
     Copyright 2017, Robert L. Read
@@ -260,17 +261,17 @@ function test_evenness_H_general() {
 
 
 }
-module.exports.H_bc = (n,c) => {
-    var BCr = this.find_rrho_from_d(this.BCrho,this.BCd);
-    return this.H_general(1,n,c,this.BCrho,this.BCd,this.BCr);
+function H_bc(n,c) {
+    var BCr = find_rrho_from_d(BCrho,BCd);
+    return H_general(1,n,c,BCrho,BCd,BCr);
 }
 
-module.exports.H_bc_el = (n,c,el) => {
-    var BCdl = this.BCd*el;
-    var BCrl = el * this.find_rrho_from_d(this.BCrho,this.BCd);
-    return this.H_general(1,n,c,this.BCrho,this.BCdl,this.BCrl);
+function H_bc_el(n,c,el) {
+    var BCdl = BCd*el;
+    var BCrl = el * find_rrho_from_d(BCrho,BCd);
+    return H_general(1,n,c,BCrho,BCdl,BCrl);
 }
-/*
+
 
 function H_bc_eqt_lambda(n,c,lambda) {
     // Note this is a particular scheme for parametrization.
@@ -315,8 +316,7 @@ function H_interp_lambda(lambda,n,c,rho0,d0,r0,rho1,d1,r1) {
 	return H_general(1,n,c,rhoi,di,rinterp);	
     }
 }
-*/
-/*
+
 function test_rail_angle_formula_against_BC() {
     var BCr_check = find_rrho_from_d(BCrho,BCd);
     var BCd_check = find_drho_from_r(BCrho,BCr);
@@ -325,8 +325,6 @@ function test_rail_angle_formula_against_BC() {
[…]

### 2017-03-02 js/tm_shim.js

@@ -1,0 +1,3 @@
+
+var tm = require("./tetrahelix_math.js");
+UGLY_GLOBAL_SINCE_I_CANT_GET_MY_MODULE_INTO_THE_BROWSER = tm;

### 2017-03-02 test/test_tetrahelix_math.js

@@ -1,0 +1,80 @@
+var assert = require('assert');
+
+var tm = require('../js/tetrahelix_math.js')
+
+
+Math.distance3 = function(p0,p1) {
+    x = p0[0] - p1[0];
+    y = p0[1] - p1[1];
+    z = p0[2] - p1[2];        
+    return Math.sqrt(x*x + y*y + z*z);
+}
+
+
+describe('Array', function() {
+    describe('#indexOf()', function() {
+	it('should return -1 when the value is not present', function() {
+	    assert.equal(-1, [1,2,3].indexOf(4));
+	});
+    });
+});
+
+describe('tetrahelix_math', function() {
+    describe('optimal_radius()', function() {
+	it('should compute same one-hop and two-hop distance (1) for BC helix', function() {
+	    var MAX_DEGREES = 45;
+	    console.log(tm.optimal_radius);
+	    for(var i = 0; i < 100;i++) {
+		var rho = Math.PI*(i*MAX_DEGREES/100)/180;
+		var r = tm.optimal_radius(rho,1.0);
+		var h1 = tm.one_hop(r,rho,1.0);
+		var h2 = tm.two_hop(r,rho,1.0);
+		assert(tm.nearlyEqual(1,h1,0.0000001));
+	    }
+	});
+    });
+    describe('test rail angle formula against BC', function() {
+	it('find functions should match Coxeter\'s solutions for BC helix', function() {
+	    var BCr_check = tm.find_rrho_from_d(tm.BCrho,tm.BCd);
+	    var BCd_check = tm.find_drho_from_r(tm.BCrho,tm.BCr);
+	    assert(tm.nearlyEqual(tm.BCr,BCr_check,0.0000001),
+		   'BCr nearly equal fail '+tm.BCr+', BCr_check == '+BCr_check);    
+	    assert(tm.nearlyEqual(tm.BCd,BCd_check,0.0000001),
+		   'BCd == '+tm.BCd+', BCd_check == '+BCd_check);
+	});
+    });
+
+    describe('H_general', function() {
+	it('H_general should match H_bc', function() {
+	    var R0 = tm.H_bc(0,0);
+	    var R1 = tm.H_bc(1,0);
+	    var Y0 = tm.H_bc(0,1);
+	    var B0 = tm.H_bc(0,2);
[…]

### 2017-03-02 js/bundle.js
some documentation

@@ -261,17 +261,17 @@ function test_evenness_H_general() {
 
 
 }
-function H_bc(n,c) {
-    var BCr = find_rrho_from_d(BCrho,BCd);
-    return H_general(1,n,c,BCrho,BCd,BCr);
+module.exports.H_bc = (n,c) => {
+    var BCr = this.find_rrho_from_d(this.BCrho,this.BCd);
+    return this.H_general(1,n,c,this.BCrho,this.BCd,this.BCr);
 }
 
-function H_bc_el(n,c,el) {
-    var BCdl = BCd*el;
-    var BCrl = el * find_rrho_from_d(BCrho,BCd);
-    return H_general(1,n,c,BCrho,BCdl,BCrl);
+module.exports.H_bc_el = (n,c,el) => {
+    var BCdl = this.BCd*el;
+    var BCrl = el * this.find_rrho_from_d(this.BCrho,this.BCd);
+    return this.H_general(1,n,c,this.BCrho,this.BCdl,this.BCrl);
 }
-
+/*
 
 function H_bc_eqt_lambda(n,c,lambda) {
     // Note this is a particular scheme for parametrization.
@@ -316,7 +316,8 @@ function H_interp_lambda(lambda,n,c,rho0,d0,r0,rho1,d1,r1) {
 	return H_general(1,n,c,rhoi,di,rinterp);	
     }
 }
-
+*/
+/*
 function test_rail_angle_formula_against_BC() {
     var BCr_check = find_rrho_from_d(BCrho,BCd);
     var BCd_check = find_drho_from_r(BCrho,BCr);
@@ -325,6 +326,8 @@ function test_rail_angle_formula_against_BC() {
     assert(nearlyEqual(BCd,BCd_check,0.0000001),
 	   'BCd == '+BCd+', BCd_check == '+BCd_check);
 }
+
+
 
 function test_H_general_against_BC() {
     var R0 = H_bc(0,0);
@@ -336,6 +339,7 @@ function test_H_general_against_BC() {
     assert(nearlyEqual(Math.distance(R0,B0),1,0.0000001),"\n R0 = " + R0 +"\n B0 = " + B0 +"\n distance =" + Math.distance(R0,B0));
 
 }
+*/
 
 function major_test() {
     var reds = [];

### 2017-03-02 js/tetrahelix_math.js
improving tests

@@ -91,7 +91,6 @@ module.exports.find_rrho_from_d = (rho,d) => {
 
 // Tha abs should not be needed here, as thise functions are even..
 module.exports.optimal_radius = (rho,el) =>
-// function optimal_radius(rho,el)
 {
     var rho_abs = Math.abs(rho);
     var numer = 2*el;
@@ -128,17 +127,6 @@ Math.distance3 = function(p0,p1) {
     z = p0[2] - p1[2];        
     return Math.sqrt(x*x + y*y + z*z);
 }
-// I have forgotten what this is supposed to test.
-function test_optimal_radius() {
-    var MAX_DEGREES = 45;
-    for(var i = 0; i < 100;i++) {
-	var rho = Math.PI*(i*MAX_DEGREES/100)/180;
-	var r = optimal_radius(rho,1.0);
-	var h1 = one_hop(r,rho,1.0);
-	var h2 = two_hop(r,rho,1.0);
-	console.log(180*rho/Math.PI,r,h1,h2-h1);
-    }
-}
 
 // Copute the optimal distance as a function of rho
 // (not using optimal_radius, because we want an independent check).
@@ -150,53 +138,8 @@ module.exports.optimal_distance = (rho,el) => {
     var den = t1+t2+t3;
     return el*Math.sqrt(1 - num/den);
 }
-function test_one_hop() {
-    var rho = BCrho;
-    rho = BCrho/2;
-    var len = 0.5;
-    var r_opt = optimal_radius(rho,len);
-    var d_opt = optimal_distance(rho,len);
-    console.log(rho,len,r_opt,d_opt);
-    var onehop = one_hop(r_opt,rho,len);
-    var p1 = H_general(0,0,BCrho,d_opt,r_opt);
-    var p2 = H_general(0,1,BCrho,d_opt,r_opt);
-    var distance = Math.distance3(p1,p2);
-    console.log(p1,p2);
-    console.log(onehop,distance,onehop-distance);
-    
-}
-
-function test_optimal_d() {
-    	var r = optimal_radius(BCrho,1.0);
-    	var dbc = optimal_distance(BCrho,1.0);
-	// Now check that d_opt matches...
-	var dp = find_drho_from_r_el(BCrho,r,1);
-    console.log(180*BCrho/Math.PI,r,dbc,dp);
-    
[…]

### 2017-03-02 test/test_tetrahelix_math.js

@@ -33,6 +33,30 @@ describe('tetrahelix_math', function() {
 	    }
 	});
     });
+    describe('optimal_radius()', function() {
+	it('BC helix should be perfectly regular', function() {
+	    var rho = tm.BCrho;
+	    var len = 1.0;
+	    var r_opt = tm.optimal_radius(rho,len);
+	    var d_opt = tm.optimal_distance(rho,len);
+	    var pnts = [];
+	    for(var i = 0; i < 4; i++) {
+		var num = Math.floor(i / 3);
+		var rail = i % 3;
+		var q = tm.H_general(1,num,rail,rho,d_opt,r_opt);
+		pnts.push(q);
+	    }
+	    console.log(pnts);    
+	    for(var i = 0; i < 4; i++) {
+		var p0 = pnts[i];
+		var p1 = pnts[(i+1) % 4];
+		var distance = Math.distance3(p0,p1);
+		// All distances should be 1 here...
+		assert(tm.nearlyEqual(distance,1,0.0000001));
+	    }
+	});
+    });
+    
     describe('test rail angle formula against BC', function() {
 	it('find functions should match Coxeter\'s solutions for BC helix', function() {
 	    var BCr_check = tm.find_rrho_from_d(tm.BCrho,tm.BCd);
@@ -66,15 +90,71 @@ describe('tetrahelix_math', function() {
 	    var p1 = tm.H_general(1,0,0,tm.BCrho,d_opt,r_opt);
 	    var p2 = tm.H_general(1,0,1,tm.BCrho,d_opt,r_opt);
 	    var distance1 = Math.distance3(p1,p2);
-	    console.log(p1,p2,distance1);
 
 	    var p3 = tm.H_general(-1,0,0,tm.BCrho,d_opt,r_opt);
-	    var p4 = tm.H_general(-1,1,1,tm.BCrho,d_opt,r_opt);
+	    var p4 = tm.H_general(-1,0,1,tm.BCrho,d_opt,r_opt);
 	    var distance2 = Math.distance3(p3,p4);
-	    console.log(p3,p4,distance2);	    
 	    assert.equal(distance1,distance2);
 
 	});
     });
 
+    describe('optimal_radius', function() {
+	it('optimal_radius is an even function', function() {
+	    var MAX_DEGREES = 45;
+	    for(var i = 0; i < 100;i++) {
[…]

### 2017-03-02 js/tm_bundle.js
trying to update

@@ -1,0 +1,393 @@
+(function e(t,n,r){function s(o,u){if(!n[o]){if(!t[o]){var a=typeof require=="function"&&require;if(!u&&a)return a(o,!0);if(i)return i(o,!0);var f=new Error("Cannot find module '"+o+"'");throw f.code="MODULE_NOT_FOUND",f}var l=n[o]={exports:{}};t[o][0].call(l.exports,function(e){var n=t[o][1][e];return s(n?n:e)},l,l.exports,e,t,n,r)}return n[o].exports}var i=typeof require=="function"&&require;for(var o=0;o<r.length;o++)s(r[o]);return s})({1:[function(require,module,exports){
+/*
+
+    Copyright 2017, Robert L. Read
+
+    This program is free software: you can redistribute it and/or modify
+    it under the terms of the GNU General Public License as published by
+    the Free Software Foundation, either version 3 of the License, or
+    (at your option) any later version.
+
+    This program is distributed in the hope that it will be useful,
+    but WITHOUT ANY WARRANTY; without even the implied warranty of
+    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+    GNU General Public License for more details.
+
+    You should have received a copy of the GNU General Public License
+    along with this program.  If not, see <http://www.gnu.org/licenses/>.
+
+*/
+
+"use strict";
+
+module.exports.red_phase = 0;
+module.exports.yellow_phase = 1;
+module.exports.blue_phase = 2;
+
+// Fundamental constanstants for the Boerdijk-Coxeter Helix
+module.exports.BCtheta = Math.acos(-2/3);
+module.exports.BCrho = 3*this.BCtheta - 2 * Math.PI;
+module.exports.BCh = (1/Math.sqrt(10));
+module.exports.BCd = (3/Math.sqrt(10));
+module.exports.BCr = (3 * Math.sqrt(3) / 10);
+
+// The Equitetrabeam
+module.exports.EQTBr =  (2/3)*Math.sqrt(2/3);
+module.exports.EQTBd = 1;
+module.exports.EQTBrho = 0;
+
[…]

### 2017-03-02 js/scijs-newton-raphson.js
adding newton-raphson

@@ -1,0 +1,68 @@
+'use strict';
+
+//module.exports = newtonRaphson;
+
+function newtonRaphson (f, fp, x0, options) {
+  var x1, y, yp, tol, maxIter, iter, yph, ymh, yp2h, ym2h, h, hr, verbose, eps;
+
+  // Iterpret variadic forms:
+  if (typeof fp !== 'function') {
+    options = x0;
+    x0 = fp;
+    fp = null;
+  }
+
+  options = options || {};
+  tol = options.tolerance === undefined ? 1e-7 : options.tolerance;
+  eps = options.epsilon === undefined ? 2.220446049250313e-16 : options.epsion;
+  maxIter = options.maxIterations === undefined ? 20 : options.maxIterations;
+  h = options.h === undefined ? 1e-4 : options.h;
+  verbose = options.verbose === undefined ? false : options.verbose;
+  hr = 1 / h;
+
+  iter = 0;
+  while (iter++ < maxIter) {
+    // Compute the value of the function:
+    y = f(x0);
+
+    if (fp) {
+      yp = fp(x0);
+    } else {
+      // Needs numerical derivatives:
+      yph = f(x0 + h);
+      ymh = f(x0 - h);
+      yp2h = f(x0 + 2 * h);
+      ym2h = f(x0 - 2 * h);
+
+      yp = ((ym2h - yp2h) + 8 * (yph - ymh)) * hr / 12;
+    }
+
+    // Check for badly conditioned update (extremely small first deriv relative to function):
+    if (Math.abs(yp) <= eps * Math.abs(y)) {
+      if (verbose) {
+        console.log('Newton-Raphson: failed to converged due to nearly zero first derivative');
+      }
+      return false;
+    }
+
+    // Update the guess:
+    x1 = x0 - y / yp;
+
+    // Check for convergence:
+    if (Math.abs(x1 - x0) <= tol * Math.abs(x1)) {
+      if (verbose) {
+        console.log('Newton-Raphson: converged to x = ' + x1 + ' after ' + iter + ' iterations');
+      }
+      return x1;
+    }
+
+    // Transfer update to the new guess:
+    x0 = x1;
+  }
+
+  if (verbose) {
+    console.log('Newton-Raphson: Maximum iterations reached (' + maxIter + ')');
+  }
+
+  return false;
+}

### 2017-03-02 js/scijs-newton-raphson.js
improving readme

@@ -1,6 +1,13 @@
 'use strict';
 
-//module.exports = newtonRaphson;
+/* This code is from: https://github.com/scijs/newton-raphson-method 
+which says it distributed with the MIT License. The author
+seems to be Ricky Reusser. I'm not a expert in bundling 
+javascript; it seems that I have the right to reuse it here
+in this way. It works really well for me, but if you want to 
+use it I suggest you take it from there repo and not copy this.
+*/
+
 
 function newtonRaphson (f, fp, x0, options) {
   var x1, y, yp, tol, maxIter, iter, yph, ymh, yp2h, ym2h, h, hr, verbose, eps;

### 2017-03-04 js/tetrahelix_math.js
final edits for a week or two

@@ -82,7 +82,7 @@ module.exports.find_rrho_from_d_el = (rho,d,el) => {
     return r;
 }
 module.exports.find_drho_from_r = (rho,r) =>    {
-    return this.find_drho_from_r_el(rho,r,1)
+    return this.find_drho_from_r_el(rho,r,1);
 }
 
 module.exports.find_rrho_from_d = (rho,d) => {

### 2017-03-14 doc/TetrahelixUntwist.tex
adding links
proofread and clarifications

@@
 
-\title{Untwisting the Tetrahelix (v0.9)}
+\title{Untwisting the Tetrahelix (v0.10)}
 \author{Robert L. Read \texttt{read.robert@gmail.com} \and
@@
   mechanical engineers, and robotocists.  A formula that matches the
-  visually apparent helices forming the outer rails of the tetrahelix
-  is derived which is convenient for designers.  This formula defines
-  the vertices of tetrahelices of varying radius, pitch, and
-  curvature, with the BC helix as a special case.  An addtional
-  special case is of that of $0$ curvature or rail angle, which
-  generates a \emph{tetrabeam}.  A particular choice of paramaters
-  defines a novel object, the minimax optimal member length-difference
-  tetrabeam, the \emph{equitetrabeam}.  A formula for computing the
-  radius and z-axis travel that gives an optimal minimax tetrahelix
-  for any rail angle between $0$ and $\rho_{bc}$ is given, thus
-  defining a continuum of tetrahelices terminated by the equitetrabeam
-  and BC helix. Numerically finding the rail angle from the equation for
+  visually apparent helices forming the outer rails of the BC helix.
+  This formula is generalized to a formula convenient to designers.
+  Formulae for 
+  computing the
+  parameters that give an edge-length minimax-optimal tetrahelices
+  are given, defining a continuum of tetrahelices of varying curvature.
+  The endpoints of the optimality of this continuum are the BC helix and
+  a structure of zero curvature, the \emph{equitetrabeam}.
+  Numerically finding the rail angle from the equation for
   pitch allows optimal tetrahelices of any pitch to be designed. 
-  An interactive tool for such design and experimentation is provided.
-  A formula
-  for the inradius is given.
+  An interactive tool for such design and experimentation is provided: \url{https://pubinv.github.io/tetrahelix/}.
+  A formula for the inradius of optimal tetrahelices is given.
   Utility and use for static and variable geometry
@@
 machines of differing or even dynamically changing length, it is
-useful to develop the mathematics of structure formed from tetrahedra
+useful to develop the mathematics of structures formed from tetrahedra
 where we relax regularity.
@@
 actuators, which can change their length, connected by special joints,
-such as the three-d printable Song-Kwon-Kim\cite{song2003spherical}, or the CMS joint\cite{HamlinSandersonCMS}
+such as the three-d printable Song-Kwon-Kim\cite{song2003spherical} joint, or the CMS joint\cite{HamlinSandersonCMS}
 which allow many members to come to a single point.
@@
 a term now commonly used. In this paper we reserve \emph{BC helix} to mean the purely regular structre and use \emph{tetrahelix} to refer
-to any structure isomophic to a the BC helix, whether regular or not.
+to any structure isomorphic to a the BC helix.
 
@@
 robotocist because the structure remains an inherently rigid,
-omni-triangulated space frame, which may be expected to be at least
+omni-triangulated space frame, which is
 somewhat mechanically strong.
@@
 
-BC helix does not rest on a plane in a simple way. It is convenient to
+A BC helix does not rest comfortably on a plane. It is convenient to
 be able to ``untwist'' it and to form a tetrahelix space frame that has a
@@
 In Figure \ref{fig:spudboy}, the closest helix is the BC helix, and the furthest
-is the equitetrabeam.
+is the equitetrabeam, defined in Section \ref{sec:equitetrabeam}.
 
-\section{A User's Formulation of the BC Helix}
+\section{A Designer's Formulation of the BC Helix}
 
-If you can choose member lengths, you can form a linear combination of
-the equitetrabream lengths and the completely regular lengths of the
-tetrahelix, thereby choosing the amount of twist\footnote{The formal definiton
-  of twistiness, or \emph{torsion}, is not useful or used in this paper, and
-  we use \emph{curvature} without relying on the mathematical curvature easily
-  computed from helical equations we provide.}.
+We would like to design nearly regular tetrahelices with a formula that
+gives the vertices in space. Eventually we would like to design nearly regular
+tetrahelices by choosing the lengths of a small set of members.
 If you are designing a
 space frame, this is a static design choice, in a robot, it is a
-dynamic choice that can be used to twist the robot and/or exert linear or
+dynamic choice that can be used to twist\footnote{The formal definition of twistieness, or \emph{torsion},
+  is not useful or used in the paper. The formal \emph{curvature} and \emph{torsion} of the helices defined here
+may be easily computed from the formualae if desired.} the robot and/or exert linear or
 angular force on the environment.
@@
 Ideally we would have a simple formula for defining the nodes based on
-any curvature or pitch we choose.  Unfortunately, it is not obvious that a linear
-combination of lengths produces a simple formula.  It is a goal of
+any curvature or pitch we choose. It is a goal of
 this paper to relate these two approaches to generating a tetrahelix
@@
   \begin{tabular}{c}
-   $ r_{bc} \cos(n \theta) $\\
-   $ r_{bc} \sin(n \theta) $\\
+   $ r_{bc} \cos{n \theta} $\\
+   $ r_{bc} \sin{n \theta} $\\
    $ n h_{bc}  $
@@
 \begin{equation}
-  \label{eq:colord}
+  \label{eq:colored}
 H_{BCcolored}(n,c) =
@@
   \begin{tabular}{c}
-   $ r_{bc}  \cos((3 \theta - 2 \pi)n + c  \theta $\\
-   $ r_{bc} \sin((3 \theta - 2 \pi)n + c  \theta $\\
+   $ r_{bc}  \cos{((3 \theta - 2 \pi)n + c  \theta)} $\\
+   $ r_{bc} \sin{((3 \theta - 2 \pi)n + c  \theta)} $\\
    $ 3 h_{bc} (n + c/3)  $
@@
 coordinates. Allowing $n$ to take non-integer values defines a continuous
-helix in space which is close to the segmented polyline of the outer tetrahedra edges, and coincides with them at integer
+helix in space which is close to the segmented polyline of the outer tetrahedra edges, and equals them at integer
 values.
@@
 $h$ is used for one third of the distance we name $d$. We will later justify that $d = 3h$. In this paper we assume the length of a rail
-is alwyas $1$ is a simplification, although we make the rail length a parameter in our JavaScript codein \texttt{tetrahelixmath.js} \cite{readtetrahelix}.
+is always $1$ is a simplification, although we make the rail length a parameter in our JavaScript code in \texttt{tetrahelixmath.js} \cite{readtetrahelix}.
 
@@
 In order to rewrite this expression with an explicit rotation of $2\pi/3$, we expand 
-the expressions $\theta$ and $\rho_{bc}$ and seek to isolate the term $c2\pi/3 $.
+the expressions $\theta$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c2\pi/3 $.
 \begin{align*}
-  \rho_{bc} n + c \theta  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
-    (3 \theta - 2 \pi)n + (c/3)  (3 \theta)  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
-  (3 \theta - 2 \pi)n + (c/ 3) (3 \theta - 2 \pi  + 2 \pi) &=  \text{\{associate...\}} \\
-  (3 \theta - 2 \pi)n + (c/ 3) ((3 \theta - 2 \pi)  + 2 \pi) &=  \text{\{distribute...\}} \\  
-  (3 \theta - 2 \pi)n + (c / 3) (3 \theta - 2 \pi)  + c 2 \pi /3 &=  \text{\{definition of $\rho_{bc}$...\}} \\
-  \rho_{bc} n + (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{\{collect like factors...\}} \\  
-  n \rho_{bc}  +\rho_{bc} ( c+  2 \pi) /3  \\
+ c \theta  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
+    (c/3)  (3 \theta)  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
+ (c/ 3) ((3 \theta - 2 \pi)  + 2 \pi) &= \text{\{definition of $\rho_{bc}$\}...} \\  
+  (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{algebra...} \\  
+c  ( \rho_{bc} +  2 \pi) /3  \\
 \end{align*}
-Now the the term on the left is the only one that depends on the scalar $n$. We use this to a create
-a new formulation: $H_{BCsymmetric}(n,c) = H_{BCcolored}(n,c)$
+We use this to a create
+a new formulation: $H_{BCsymmetric}(n,c) = H_{BCcolored}(n,c)$.
+%% TODO: I seem to have lost the thread of my thought. I don't seem to be introducing d at that right time.
 
@@
   \begin{tabular}{c}
-    $ r  \cos(\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3) $\\
-   $ r  \sin(\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3) $\\
+    $ r  \cos{\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3} $\\
+   $ r  \sin{\rho_{bc} n + c (\rho_{bc} +  2 \pi) /3} $\\
    $ (n+c/3)  h_{bc} $
@@
 
-Since:
+We can see the each rail tetrahedron moves us $\rho_{bc}$ radians around a circle. Since:
 \[ \frac{2 \pi}{\rho_{bc}} \approx 10.16
 \]
-We can see that there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a single revolution.
+we can see that there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a single revolution.
+
 The pitch of the Boerdijk--Coxeter helix of edge length $1$ is the length of three tetrahedra times this number:
 \begin{align*}
-  &= \frac{d_{bc} 2 \pi }{\rho_{bc}} \\  
-%%  &= \frac{3 \cdot h_{bc} 2 \pi }{\rho_{bc}} \\
-  &= \frac{3  \sqrt{\frac{2}{5}}  \pi}{\rho_{bc}} \\
-  &\approx 9.64 \\
+   \frac{3 h_{bc}\cdot  2 \pi }{\rho_{bc}} 
+  &= \frac{6 \pi}{\sqrt{10}\rho_{bc}} 
+  &\approx 9.64 
 \end{align*}
+
 The pitch is less than the number of tetrahedra because the tetrahedra
@@
 The idea of developing a rational period by arranging solid tetrahedra by relaxing the face-to-face matching
-has been explored\cite{sadler2013periodic}. In this paper
-we develop slightly irregular edge lengths that support, for example, a pitch of precisely 12
+has been explored\cite{sadler2013periodic}. 
+We develop below slightly irregular edge lengths that support, for example, a pitch of precisely 12
 tetrahedra in one revolution which would allow an architect to design a
@@
 tetrahelix to be the radius of the largest
-cylinder parallel to this axis contained within the circumscribing cylinder w
-hich is penetrated by no edge.
-Define an \emph{minimax edge-length optimal tetrahelix} or just an
+cylinder parallel to this axis contained within the circumscribing cylinder
+which is penetrated by no edge.
+Define a \emph{minimax edge-length optimal tetrahelix} or just an
 \emph{optimal tetrahelix} to be a tetrahelix for which there exists
@@
 Our tool for thinking about this is to project out the $z$ dimension to form
-a two-dimensional figure of nodes and non-rail edges.
+a two-dimensional figure of nodes and non-rail edges (see Figure \ref{untouchingrailfig}.
 Consider the projection along the $z$ axis of all vertices and non-rail edges into the $xy$ plane, which will be
@@
 one rail-edge length, this is the minimax solution for the entire set. Since
-the projection is an equilateral triangle lies on a circle, all points lie on
+the vertices of an equilateral triangle lies on a circle, all points lie on
 a cylinder.
@@
 Supoose there is a rail $P$ which does not have a segment touching the incircle
-at all in the projection, as depicted in 
+at all in the projection, as depicted in Figure \ref{untouchingrailfig}.
 Then a segment connecting the other two $Q$ and $R$ is a longest
@@
 
-    Any attempt to move any rail in either $z$ direction lengthens one two-hop edge to $t' > t$
+    Any attempt to move any rail in either $z$ direction lengthens one two-hop edge to $t'$, where $t' > t$
     edge and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be new edges.
-    The minimax of $B$ > $A$ since there is a single rail length which cannot be both greater
+    The minimax of $B$ is greater than the minimax of $A$ since there is a single rail length which cannot be both greater
     than $t'$ and $o'$ and less than $t'$ and $o'$.
@@
 
- Note that based on \ref{eventhirds}, there are only 3 possible lengths in an optimal tethrahelix,
- and we are justified in classifying edge lengths as \emph{rail},\emph{one-hop}, or
-\emph{two-hop}. The one-hop edges are the edges between closest on the $z$-axis, and the two-hop edges are those that hop over a vertex.
+ Note that based on Theorem \ref{eventhirds}, there are only 3 possible lengths in an optimal tethrahelix,
+ and we are justified in classifying edge lengths as \emph{rail}, \emph{one-hop}, or
+\emph{two-hop}. The one-hop edges are the edges between closest on the $z$-axis, and the two-hop edges are those that skip over a vertex.
 
@@
 
-$H_{general}$ forces the user to select an $d_{\rho}$
+$H_{general}$ forces the user to select a $d_{\rho}$
 which has a sensible radius.
@@
 By Theoerm \ref{eventhirds}, we can compute the (at most) three edge-lengths of an optimal
-tetrahelix by (where $dist$ is the cartesian distance function):
+tetrahelix by formula universally quantified by $n$ and $c$:
 \begin{align*}
@@
 \end{align*}
-Which are invarinat for all $n$ and $c$.
+where $dist$ is the Cartesian distance function.
 
@@
 
-If you look down the axis of an optimal tetrahelix, it happens that only the one-hop edges
+If you look down the axis of an optimal tetrahelix, it happens that only one of the one-hop edges
 come closest to the axis. In other words, they define the radius of the incircle of the
@@
   \label{eq:inradius}
-  i_{\rho} = \frac{r \sin{(\pi - \rho)}}{6}
+  i_{\rho} = r \sin{\frac{\pi - \rho}{6}}
 \end{equation}
@@
 
+From this equation with the help of symbolic computation we observe that inradius of the BC helix of unit rail length is $i_{\rho_{bc}} = \frac{3}{10\sqrt{2}} \approx 0.21213$.
+
 \section{The Equitetrabeam}
+\label{sec:equitetrabeam}
 
@@
 
-This radius\footnote{Another interesting but non-optimal solution is derived by setting (one-hop + two-hop)/2 = 1,
+This radius\footnote{Another interesting but non-optimal solution is derived by setting
+  (one-hop + two-hop)/2 = 1,
   occurs at $r = \sqrt{35}/4$ which produces
@@
 produces a two-hop rail length of $\frac{2}{\sqrt{3}}$.
-The difference between this and $1$ is $\approx 15.47\% $.
+The difference between this and $1$ is $\approx 15.47\% $. The inradius if the equitetrabeam of unit
+rail length from both Equation \eqref{eq:inradius} and the fact that the inradius of
+an equilateral triangle is half the circumradius is $\sqrt{\frac{8}{27}}/2$, or $\frac{\sqrt{6}}{9}$.
 
@@
 create an optimal tetrahelix for any value rail angle $\rho$ between $0$, which
-gives the Equitetrahelix and
-$\rho_{bc} \approx 35.43 \degree$, which gives the BC Helix.
+gives the equitetrabeam and
+$\rho_{bc} \approx 35.43 \degree$, which gives the BC helix.
 
  Because the equitetrabeam which has a rail angle of $0$ still has
- chirality, that is, one still must decide to connect with one-hop to
- the clockwise or counter-clockwise node, it is not poosible to build
+ chirality, that is, one still must decide to connect the one-hop edge to
+ the clockwise or the counter-clockwise node, it is not poosible to build
  a smooth continuum where $\rho$ transitions from positive to negative
@@
 $z$-axis travel from \eqref{dopt} the pitch is not simple.
-However, it increases monotonically and smoothly with decreasing $\rho$, so
+It increases monotonically and smoothly with decreasing $\rho$, so
 Equation \eqref{pitcheqn} can be easily solved numerically with a Newton-Raphson
 solver, as we do on our website.
-For a pitch at least $ p \geq \frac{3  \sqrt{\frac{2}{5}}  \pi}{\rho_{bc}} \approx 9.64 $,
+For a pitch at least $ p \geq \frac{3  \sqrt{2}  \pi}{\sqrt{5}\rho_{bc}} \approx 9.64 $,
 using \eqref{dopt} produces minimax optimal tetrahelices.
@@
 Perhaps surprisingly, the optimal untwisting is accomplished only by
-changing the length of the two-hop member, leaving the one-hop memever
+changing the length of the two-hop member, leaving the one-hop member
 and rail length equivalent within this continuum.\footnote{Before deriving Equation \eqref{eqrhoopt}, we created a continuum by
@@
 
-The Gluss Project \url{http://pubinv.github.io/gluss/}
-is a free-libre, open-source research, hardware, and software project that welcomes volunteers.
+The Gluss Project \url{http://pubinv.github.io/gluss/} is part of Public Invention,
+a free-libre, open-source research, hardware, and software project that welcomes volunteers.
 It is our goal to organize projects for the benefit of all humanity without seeking profit or intellectual property.
@@
 https://arxiv.org/pdf/1702.06388.pdf
+
+Research Turk's knots

### 2017-03-24 doc/TetrahelixUntwist.tex
updating photos
latest improvements

@@
 
-\title{Untwisting the Tetrahelix (v0.10)}
+\title{Untwisting the Tetrahelix (v0.12)}
 \author{Robert L. Read \texttt{read.robert@gmail.com} \and
@@
   inherently rigid, and therefore interesting to architects,
-  mechanical engineers, and robotocists.  A formula that matches the
+  mechanical engineers, and robotocists.  A formula is developed that matches the
   visually apparent helices forming the outer rails of the BC helix.
@@
   computing the
-  parameters that give an edge-length minimax-optimal tetrahelices
+  parameters that give edge-length minimax-optimal tetrahelices
   are given, defining a continuum of tetrahelices of varying curvature.
@@
   A formula for the inradius of optimal tetrahelices is given.
-  Utility and use for static and variable geometry
-  truss/space frame design and robotics based on the are discussed.
+  Utility for static and variable geometry
+  truss/space frame design and robotics is discussed.
 \end{abstract}
@@
      \includegraphics[width=0.95\textwidth]{figures/BCHelixCloseUp.png}
-     \caption{BC Helix Close-up}
+     \caption{BC Helix Close-up (partly along axis)}
+  \centering
+     \includegraphics[width=0.95\textwidth]{figures/VerticalCloseUp.png}
+     \caption{BC Helix Close-up (orthogonal)}
 \end{figure}
@@
 actuator that could dynamically become shorter or longer in response to electronic control,
-and the they vertices were a joint that supported sufficient angular displacement
+and the vertices were a joint that supported sufficient angular displacement
 for this to be possible. Such a machine is a Tetrobot\cite{TetrobotBook}.
@@
 space frame, this is a static design choice, in a robot, it is a
-dynamic choice that can be used to twist\footnote{The formal definition of twistieness, or \emph{torsion},
+dynamic choice that can be used to twist\footnote{The formal definition of twistiness, or \emph{torsion},
   is not useful or used in the paper. The formal \emph{curvature} and \emph{torsion} of the helices defined here
@@
 $\theta$ is approximately $131.81$ degrees.
-The angle $\theta$ is the rotation of a \emph{each} tetrahedra, not the tetraheda along a rail.  In Figure \ref{fig:closeup},
+The angle $\theta$ is the rotation of \emph{each} tetrahedra, not the tetraheda along a rail.  In Figure \ref{fig:closeup},
 each tetrahedra has either a yellow, blue, or red outer edge or rail.
@@
 
-R.W. Gray's site\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in more accessible form, gives for a counter-clockwise BC Helix:
+R.W. Gray's site\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in more accessible form, gives the Cartesian coordinates $\begin{bmatrix}
+           x \\
+           y \\
+           z
+         \end{bmatrix}$
+for a counter-clockwise BC Helix:
 \begin{equation}
@@
 
-The apparent rotation of tetrhedra of the same outer-edge color ($V_3$ relative from $V_0$ for example,
+The apparent rotation of a vertex an outer-edge, $V(n)$ relative from $V(n+3)$ for any integer $n$
 in \eqref{graycoxeter}, is $3 \theta - 2\pi$).
@@
 
-This Gray-Coxeter formulation $V(n)$ from \eqref{graycoxeter} is valuable, but obscures the fact that we have three
-apparent rail helices.
-In order to rewrite this expression with an explicit rotation of $2\pi/3$, we expand 
+The $H_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho{bc}$ rather than $\theta$.
+Intuitively we see an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
+We expand 
 the expressions $\theta$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c2\pi/3 $.
@@
 \end{align*}
-We use this to a create
-a new formulation: $H_{BCsymmetric}(n,c) = H_{BCcolored}(n,c)$.
-%% TODO: I seem to have lost the thread of my thought. I don't seem to be introducing d at that right time.
 
-Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued.)
+This allows us to redefine:
 
@@
 \begin{equation}
-H_{BCsymmmetric}(n,c) =
+H_{BCcolored}(n,c) =
 \left [
@@
 
-We can see the each rail tetrahedron moves us $\rho_{bc}$ radians around a circle. Since:
+Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued.)
+
+From this formulation it is easy to see that moving one vertex on a rail moves us $\rho_{bc}$ radians around a circle. Since:
 \[ \frac{2 \pi}{\rho_{bc}} \approx 10.16
@@
 One could consider various definitions of optimality for a
-tetrahelix, but the must useful to an enginner is to minimize the
+tetrahelix, but the most useful to us as robotocists extending the Tetrobot concept is to minimize the
 maximum difference between any two edges.
@@
 
-Since the axes are parallel, we may define the \emph{inradius} of a
+Since the axes are parallel, we may define the \emph{inradius}, represented by the letter $i$, of a
 tetrahelix to be the radius of the largest
@@
 Our tool for thinking about this is to project out the $z$ dimension to form
-a two-dimensional figure of nodes and non-rail edges (see Figure \ref{untouchingrailfig}.
+a two-dimensional figure of nodes and non-rail edges (see Figure \ref{untouchingrailfig}.)
 Consider the projection along the $z$ axis of all vertices and non-rail edges into the $xy$ plane, which will be
@@
 
-$H_{general}$ forces the user to select a $d_{\rho}$
-which has a sensible radius.
+$H_{general}$ forces the user to select three values: $\rho$, $r_{\rho}$, and $d_{\rho}$ satisfying \eqref{railangle}.
 
@@
 If you look down the axis of an optimal tetrahelix, it happens that only one of the one-hop edges
-come closest to the axis. In other words, they define the radius of the incircle of the
+comes closest to the axis. In other words, they define the radius of the incircle of the
 projection, or the radius of a cylinder that would just fit inside the tetrahelix.
@@
 Figure \ref{fig:unfolded} shows a representation of an unfolded equitetrabeam.
+Note that folding the outer edges of the paper upward or downward effectively
+chooses the chirality of the equitetrabeam.
 
@@
 facilitate the inexpensive manufacture and construction of the robot.
-In a plane, the octet truss is such a geometry, but in a line, the
+In a plane, the octet truss\cite{richard1961synergetic} is such a geometry, but in a line, the
 Boerdijk--Coxeter helix is a regular structure.
@@
 \begin{proof}
-  Proof by our computer program that does this by forming a linear interpolation of links.
+  Proof by our computer program that does this using Equation \eqref{eq:general}.
   See video on website\cite{readtetrahelix}.
-\end{proof}
 
@@
   \centering
-     \includegraphics[width=0.4\textwidth]{figures/Tetrahelix1.png}
-     \caption{2/3rd Twisted Tetrahelix}
-     \includegraphics[width=0.4\textwidth]{figures/Tetrahelix2.png}
-     \caption{1/3rd Twisted, 2/3rd Untwisted Tetrahelix}
-     \includegraphics[width=0.4\textwidth]{figures/Tetrahelix3.png}
-     \caption{The Equitetrabream: Fully Untwisted Tetrahelix}
+     \includegraphics[width=0.4\textwidth]{figures/GlussBotBC.jpg}
+     \caption{Glussbot in relaxed, or BC helix configuration}
+     \includegraphics[width=0.4\textwidth]{figures/GlussBotEquitetrabeamCropped.jpg}
+     \caption{The Equitetrabream: Fully Untwisted Glussbot}
 \end{figure}
+
+\end{proof}
 

### 2017-03-24 doc/TetrahelixUntwist.tex
latest changes

@@
 \begin{figure}[H]
-  \label{fig:closeup}
   \centering
@@
      \caption{BC Helix Close-up (orthogonal)}
+  \label{fig:closeup}
 \end{figure}
@@
 
-In Figure \ref{fig:spudboy}, the closest helix is the BC helix, and the furthest
+\begin{figure}
+  \centering
+     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
+     \caption{A Series of Tetrahelices}
+  \label{fig:series}
+\end{figure}
+
+Figure \ref{fig:series} displays a continuum of tetrahelices optimal in a certain sense, which is the result of this
+paper. The closest helix is the BC helix, and the furthest
 is the equitetrabeam, defined in Section \ref{sec:equitetrabeam}.
@@
 \begin{figure}[H]
-  \label{railanglefig}
      \centering
@@
      \caption{Rail Angle Geometry}
+  \label{railanglefig}
 \end{figure}
@@
 The $H_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho{bc}$ rather than $\theta$.
-Intuitively we see an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
+Intuitively we seek an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
 We expand 
@@
 
-From this formulation it is easy to see that moving one vertex on a rail moves us $\rho_{bc}$ radians around a circle. Since:
+From this formulation it is easy to see that moving one vertex on a rail
+($H_{BCcolored}(n,c)$ to $H_{BCcolored}(n+1,c)$ for any $n$ and $c$)
+moves us $\rho_{bc}$ radians around a circle. Since:
 \[ \frac{2 \pi}{\rho_{bc}} \approx 10.16
@@
 tetrahelix, but the most useful to us as robotocists extending the Tetrobot concept is to minimize the
-maximum difference between any two edges.
+maximum difference between any two edges, because the Tetrobot uses linear acutators of limit range of extension.
 
@@
 \begin{figure}[H]
-  \label{untouchingrailfig}
      \centering
@@
      \caption{Untouching Rail}
+  \label{untouchingrailfig}
 \end{figure}
@@
 Since the partial derivative of $\text{two-hop} - \text{one-hop}$ with respect to the
-radius is negative up until $\rho_{bc}$ when it is $0$, then
-we will opitmize the overall minimax distance by choosing the largest radius
+radius $r_{\rho}$ is negative up until $\rho_{bc}$ where it is $0$, 
+we opitmize the overall minimax distance by choosing the largest radius
 up until one-hop $= 1$, the rail-edge length.
@@
 \begin{figure}[H]
-  \label{fig:unfolded}
      \centering
@@
      \caption{Projection Diagram}
+  \label{fig:unfolded}
 \end{figure}
 
-In Figure \ref{fig:spudboy}, the furthest tetrahelix is the optimal equitetrabeam.
+In Figure \ref{fig:series}, the furthest tetrahelix is the optimal equitetrabeam.
 Figure \ref{fig:unfolded} shows a representation of an unfolded equitetrabeam.
@@
 \section{An Untwisted Continuum}
-
-\begin{figure}[H]
-  \label{fig:spudboy}
-  \centering
-     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
-     \caption{A Series of Tetrahelices}
-\end{figure}
 
@@
 Starting twenty years ago, Sanderson\cite{sanderson1996modular},
-Hamlin,\cite{TetrobotBook}, and others including
-Lee\cite{lee2002dynamic} created a style of robotics based on changing
+Hamlin,cite{TetrobotBook}, Lee\cite{lee2002dynamic}, and others
+ created a style of robotics based on changing
 the lengths of members joined at the center of a joint, thereby
@@
 \begin{theorem}
-  By changing only the length of the members that change rails and make two nodes, you can dynamically untwist a tetrobot
+  By changing only the length of the longer members that connect two distinct rails (the two-hop members), you can dynamically untwist a tetrobot
   forming the Boerdijk-Coxeter configuration to the equitetrabeam which rests flat on the plane.
@@
 \begin{proof}
-  Proof by our computer program that does this using Equation \eqref{eq:general}.
-  See video on website\cite{readtetrahelix}.
+  Proof by our computer program that does this using Equation \eqref{eq:general} applied to the
+  7-tet Tetrobot/Glussbot.
 

### 2017-04-08 doc/TetrahelixUntwist.tex
typos fixed

@@
 \title{Untwisting the Tetrahelix (v0.12)}
-\author{Robert L. Read \texttt{read.robert@gmail.com} \and
-  Robert Gatliff \texttt{robert@toubat.org}
+\author{Robert L. Read \texttt{read.robert@gmail.com}
 }
@@
 Please refer back to Figure \ref{railanglefig}.
-The pitch of the helix is an obious choice, but is not defined when the
+The pitch of the helix is an obvious choice, but is not defined when the
 curvature is $0$, an important special case. The radius or the axial
-distance between two nodes on the same rail are obvious choices, but
+distance between two nodes on the same rail are possible choices, but
 perhaps the clearest choice is to build formula that takes as its

### 2017-04-10 doc/TetrahelixUntwist.tex
improving diagrams

@@
 
-\title{Untwisting the Tetrahelix (v0.12)}
+\title{Untwisting the Tetrahelix (v0.13)}
 \author{Robert L. Read \texttt{read.robert@gmail.com}
@@
 Because architects, structural engineers, and robotocists are inspired
-by and follow such mathematical models but can build structures and
+by and follow such regular mathematical models but can also build structures and
 machines of differing or even dynamically changing length, it is
@@
 a term now commonly used. In this paper we reserve \emph{BC helix} to mean the purely regular structre and use \emph{tetrahelix} to refer
-to any structure isomorphic to a the BC helix.
+to any structure isomorphic to the BC helix.
 
@@
 
-A BC helix does not rest comfortably on a plane. It is convenient to
+A BC helix does not rest stably on a plane. It is convenient to
 be able to ``untwist'' it and to form a tetrahelix space frame that has a
@@
 develops the equations needed to untwist the tetrahelix. All math
-deveoped here is available in JavaScript and demonstrated by an interactive
+developed here is available in JavaScript and demonstrated by an interactive
 design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix},
-from which Figures \ref{fig:closeup} and
-the figure below are taken.
+from which Figure \ref{fig:closeup} and
+the figures below are taken.
 
@@
 tetrahelices by choosing the lengths of a small set of members.
-If you are designing a
-space frame, this is a static design choice, in a robot, it is a
+In a space frame, this is a static design choice; in a robot, it is a
 dynamic choice that can be used to twist\footnote{The formal definition of twistiness, or \emph{torsion},
@@
 \[
-\theta = \arccos(-2/3) 
+\theta_{bc} = \arccos(-2/3) 
 \]
@@
 
-$\theta$ is approximately $131.81$ degrees.
-The angle $\theta$ is the rotation of \emph{each} tetrahedra, not the tetraheda along a rail.  In Figure \ref{fig:closeup},
-each tetrahedra has either a yellow, blue, or red outer edge or rail.
+$\theta_{bc}$ is approximately $0.37 \cdot 2 \pi$ radians or  $131.81$ degrees.
+The angle $\theta_{bc}$ is the rotation of \emph{each} tetrahedron, not the tetraheda along a rail.  In Figure \ref{fig:closeup},
+each tetrahedron has either a yellow, blue, or red outer edge or rail.
 That is, a blue-rail tetrahedron is rotated slightly more than a $1/3$ of a revolution to match the face of the yellow tetrahedra.
@@
   \begin{tabular}{c}
-   $ r_{bc} \cos{n \theta} $\\
-   $ r_{bc} \sin{n \theta} $\\
+   $ r_{bc} \cos{n \theta_{bc}} $\\
+   $ r_{bc} \sin{n \theta_{bc}} $\\
    $ n h_{bc}  $
@@
  $ h_{bc} = 1/\sqrt{10} $ \\
- $ \theta = \arccos(-2/3) $ \\
+ $ \theta_{bc} = \arccos(-2/3) $ \\
   \end{tabular}      
@@
 The apparent rotation of a vertex an outer-edge, $V(n)$ relative from $V(n+3)$ for any integer $n$
-in \eqref{graycoxeter}, is $3 \theta - 2\pi$).
+in \eqref{graycoxeter}, is $3 \theta_{bc} - 2\pi$).
 
-This formula defines a helix, but it is not any of the apparent helices, or rail helices, of the
+This formula defines a helix, but it is not any of the apparent helices, or \emph{rail} helices, of the
 BC helix, but rather one that winds three times as rapidly through all
@@
 which are closely approximated by the outer edges or rails of
-the BC helix. We think of each of these three rails as being a different color, red, blue, or yellow.
+the BC helix. We think of each of these three rails as being a different color: red, blue, or yellow.
 
 It is convenient to have a formula that gives us the nodes of just
-one rail helix, denoted by color $c$:
+one rail helix, denoted by color $c$ and integer node number $n$:
 \[
@@
   \begin{tabular}{c}
-   $ r_{bc}  \cos{((3 \theta - 2 \pi)n + c  \theta)} $\\
-   $ r_{bc} \sin{((3 \theta - 2 \pi)n + c  \theta)} $\\
+   $ r_{bc}  \cos{((3 \theta_{bc} - 2 \pi)n + c  \theta_{bc})}  $\\
+   $ r_{bc} \sin{((3 \theta_{bc} - 2 \pi)n + c  \theta_{bc})} $\\
    $ 3 h_{bc} (n + c/3)  $
@@
   \right ],
-\text{where:}
+\text{where}
   \begin{tabular}{c}
- $ r_{bc} = \frac{3\sqrt{3}}{10} $\\
- $ h_{bc} = 1/\sqrt{10} $ \\
- $ \theta = \arccos(-2/3) $ \\
+ $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $\\
+ $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $ \\
+ $ \theta_{bc} = \arccos(-2/3) $ \\
   \end{tabular}      
@@
 
-The quantity $ (3 \theta - 2 \pi) \approx 35.43 \degree $, and is the angular shift between $V(3n+c)=H_{BCcolored}(n,c)$ and
+The quantity $ (3 \theta_{bc} - 2 \pi) \approx 35.43 \degree $  is the angular shift between $V(3n+c)=H_{BCcolored}(n,c)$ and
 $V(3(n+1)+c)=H_{BCcolored}(n+1,c)$.
-This quantity appears so often that we call it the ``rail angle rho''. For the BC helix, $\rho_{bc} = (3 \theta - 2 \pi)$.
+This quantity appears so often that we call it the ``rail angle $\rho$''. For the BC helix, $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$.
 
@@
 Note in Figure \ref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In \eqref{graycoxeter} and \eqref{eq:colored}, the variable
-$h$ is used for one third of the distance we name $d$. We will later justify that $d = 3h$. In this paper we assume the length of a rail
-is always $1$ is a simplification, although we make the rail length a parameter in our JavaScript code in \texttt{tetrahelixmath.js} \cite{readtetrahelix}.
+$h$ is used for one third of the distance we name $d$. We will later justify that $d = 3h$.
+In this paper we assume the length of a rail
+is always $1$ as a simplification. (We make the rail length a parameter in our JavaScript code in \texttt{tetrahelixmath.js} \cite{readtetrahelix}.)
 
-The $H_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho{bc}$ rather than $\theta$.
+The $H_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho{bc}$ rather than $\theta_{bc}$.
 Intuitively we seek an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
 We expand 
-the expressions $\theta$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c2\pi/3 $.
+the expressions $\theta_{bc}$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c2\pi/3 $.
 \begin{align*}
- c \theta  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
-    (c/3)  (3 \theta)  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
- (c/ 3) ((3 \theta - 2 \pi)  + 2 \pi) &= \text{\{definition of $\rho_{bc}$\}...} \\  
+ c \theta_{bc}  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
+    (c/3)  (3 \theta_{bc})  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
+ (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) &= \text{\{definition of $\rho_{bc}$\}...} \\  
   (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{algebra...} \\  
@@
   \right ],
-\text{where:}
+\text{where}
   \begin{tabular}{c}
 %%  $\kappa = n + c/3$ \\
-    $\rho_{bc} = (3 \theta - 2 \pi)$ \\
-    $ \theta = \arccos(-2/3) $ \\
+    $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$ \\
     $ h_{bc} = 1/\sqrt{10} $ \\    
@@
 We use the term \emph{tetrahelix} to mean any structure made of
-vertices and edges which is isomorphic to the BC helix, in which the
+vertices and edges which is isomorphic to the BC helix and in which the
 vertices lie on three helices. We further demand that all edge lengths
@@
 
-If all three rails do not have the same pitch, there is an edge of
-unbounded length, so it is hardly optimal. So we are justified in talking about the
+Suppose that all three rails do not have the same pitch. Starting at any shortest edge, as we move
+from node to node away from our start node edge lengths between rails must always lengthen without bound,
+which cannot be optimal.
+So we are justified in talking about the
 \emph{pitch} of 
-the tetrahelix as the pitch of its rail helices, even though there are
-three such helices.
+the optimal tetrahelix as the pitch of its three rail helices, even though there are
+three such helices of equivalent pitch.
 
@@
 vertices we shorten the total distance.
-Our tool for thinking about this is to project out the $z$ dimension to form
+Our tool for thinking about this is to collapse the $z$ dimension to form
 a two-dimensional figure of nodes and non-rail edges (see Figure \ref{untouchingrailfig}.)
@@
 irrational) or a polygon if rational, or a point if the helix has
-zero curvature. Each of these figures by definitions lies outside the
-circle of inradius $i$ in the $xy$ plane.
+zero curvature. Each of these figures by definition lies outside the
+circle of inradius $r_{in}$ in the $xy$ plane.
 
@@
 is projected out. Therefore it is reasonable to now speak of the \emph{radius} $r$
-of a tetrahelix as the radius of the cylinder, as distinct from the inradius $i$.
+of a tetrahelix as the radius of the cylinder, as distinct from the inradius $r_{in}$.
 
@@
 
+\begin{figure}[H]
+     \centering
+     \includegraphics[width=0.8\textwidth]{figures/EquitetrabeamCloseUp.png}
+     \caption{Equitetrabeam}
+  \label{equitetrabeam}
+\end{figure}
+
+Figure \ref{equitetrabeam} shows the equitetrabeam, which is defined in Section \ref{sec:equitetrabeam},
+but illustrates the one-hop and two-hop edge defintions.
+The green edges are the two-hop edges and the purple edges are the one-hop edges. Note that the green
+edges are slightly longer than the purple edges.
+
 \begin{theorem}
@@
     than $t'$ and $o'$ and less than $t'$ and $o'$.
-    Therefore, any optimal tetrahelix has all one-hop edges between all rails are equal to each other, and
-    all two-hop edges are equal to each other, and the $z$ distances between rails are equal, and therefore
+    Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other, and
+    all two-hop edges equal to each other, and the $z$ distances between rails equal, and therefore
     $d/3$ from each other.
@@
  and we are justified in classifying edge lengths as \emph{rail}, \emph{one-hop}, or
-\emph{two-hop}. The one-hop edges are the edges between closest on the $z$-axis, and the two-hop edges are those that skip over a vertex.
+\emph{two-hop}. The one-hop edges are the edges between rails that are closest on the $z$-axis, and the two-hop edges are those that skip over a vertex.
 
@@
 distance between two nodes on the same rail are possible choices, but
-perhaps the clearest choice is to build formula that takes as its
+perhaps the clearest choice is to build formulae that takes as thier
 input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
@@
 controls how far a rail edge of a tetrahelix deviates from being
-parallel with the axis, or the ``twistiness'' of tetrahelix. We use
-the parameter $\chi = 1$ to indicate a chirality or counter-clockwise,
+parallel with the axis, or the ``twistiness'' of the tetrahelix. We use
+the parameter $\chi = 1$ to indicate a chirality of counter-clockwise,
 and $\chi = -1$ for clockwise.
@@
 of the whole system as we increase the radius
-up unto the point that the shorter, one-hop distance is equal to the rail-length ($1$).
+up to the point that the shorter, one-hop distance is equal to the rail-length ($1$).
 Therefore, to optimize the whole system so long as $\rho \leq \rho_{bc}$,
@@
 
-If you look down the axis of an optimal tetrahelix, it happens that only one of the one-hop edges
+\section{The Inradius}
+
+\begin{figure}[H]
+     \centering
+     \includegraphics[width=0.4\textwidth]{figures/AxialView.png}
+     \caption{Loking Down a BC-Helix}
+  \label{axialview}     
+\end{figure}
+
+If we look down the axis of an optimal tetrahelix as shown in Figure \ref{axialview}, it happens that only one of the one-hop edges
+(rendered in purpple in our software)
 comes closest to the axis. In other words, they define the radius of the incircle of the
 projection, or the radius of a cylinder that would just fit inside the tetrahelix.
-This is useful to know if the tetrahelix is used as a structure to house a pipe or
-a ladder that must bear a human or to armor a conduit. The inradius $i_\rho$ of
+A formula for the inradious of the tetrahelix is useful if you are designing it as a structure that bears something internally,
+such as a firehose, a pipe, or
+a ladder for a human. The inradius $r_{in}(\rho)$ of
 an optimal tetrahelix is a remarkably simple function of the radius $r$ and the rail angle $\rho$:
@@
   \label{eq:inradius}
-  i_{\rho} = r \sin{\frac{\pi - \rho}{6}}
+  r_{in}(\rho) = r \sin{\frac{\pi - \rho}{6}}
 \end{equation}
@@
 \begin{figure}[H]
-  \label{projectiondiagram}
      \centering
@@
      \caption{General One-hop Projection Diagram}
+  \label{projectiondiagram}
+
 \end{figure}
@@
 and $d = 1$ (the edgelength), where the cross sectional area is
-an equilateral triangle of unchanging orientation.
+an equilateral triangle of unchanging orientation, as shown in Figure \ref{equitetrabeam} and at the rear of Figure \ref{fig:series}.
 We call this the \emph{equitetrabeam}.
@@
    1  &=  \sqrt{\frac{1}{9} + 3r^2} & \text{ solved by... }\\
-   r  &= \sqrt{\frac{8}{27}} &\approx 0.5443 \\
+   r  &= \sqrt{\frac{8}{27}} &\approx 0.54 \\
 \end{align*}
@@
 produces a two-hop rail length of $\frac{2}{\sqrt{3}}$.
-The difference between this and $1$ is $\approx 15.47\% $. The inradius if the equitetrabeam of unit
+The difference between this and $1$ is $\approx 15.47\% $. The inradius of the equitetrabeam of unit
 rail length from both Equation \eqref{eq:inradius} and the fact that the inradius of
@@
 
-\begin{figure}[H]
-     \centering
-     \includegraphics[width=0.6\textwidth]{figures/EquitetrabeamUnfolded.JPG}
-     \caption{Projection Diagram}
-  \label{fig:unfolded}
-\end{figure}
-
 In Figure \ref{fig:series}, the furthest tetrahelix is the optimal equitetrabeam.
-Figure \ref{fig:unfolded} shows a representation of an unfolded equitetrabeam.
 Note that folding the outer edges of the paper upward or downward effectively
@@
 To the extent that we value tetrabeams (that is, tetrahelicies with a rail angle of $0$,
-and therefore zero curvature) as mathematical or engineering objects
+and therefore zero curvature) as mathematical or engineering objects,
 we have motivated the development of $H_{general}$ as a transformation of $V(n)$ defined by
-Equation \eqref{graycoxeter} from Gray and Coxeter, as it is difficult to see how
+Equation \eqref{graycoxeter} from Gray and Coxeter. It is difficult to see how
 the $V(n)$ 
@@
  chirality, that is, one still must decide to connect the one-hop edge to
- the clockwise or the counter-clockwise node, it is not poosible to build
+ the clockwise or the counter-clockwise node, it is not possible to build
  a smooth continuum where $\rho$ transitions from positive to negative
@@
  but it does not produce minimax optimal tetrahelices. In other words,
- untwisting a conter-clockwise tetrahelix to rail angle $0$ and then going
+ untwisting a counter-clockwise tetrahelix to rail angle $0$ and then going
 even further does produce a clockwise tetrahelix, but one in which the
@@
 directly and interactively, and that minimax length optimality is a
-mathematic starting point rather than the final word on the beauty and utility of
+mathematical starting point rather than the final word on the beauty and utility of
 physical structures. For example, a structural engineer might increase
@@
 \begin{theorem}
-  By changing only the length of the longer members that connect two distinct rails (the two-hop members), you can dynamically untwist a tetrobot
-  forming the Boerdijk-Coxeter configuration to the equitetrabeam which rests flat on the plane.
+  By changing only the length of the longer members that connect two distinct rails (the two-hop members), we can dynamically untwist a tetrobot
+  forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane.
 \end{theorem}
@@
 
-Clean up d_{opt}.
-
-Produce mini table of pitch vs. \rho?
-
-Improve clarity and precision of proofs.
-
-Solve the chirality problem.
-
-Check every step of my derivation at rho = 0 and the BC values.
-
-Found something.  So now the computation of the optimal radii seems slightly better than what we had before.
-We have not, however, proven it to be optimal in the ranges involved, but at least we seem to be computing it correctly.
-
-See if we can accurately compute the derivative of two-hop - one-hop and if it is always negative, meaning that
-it is always optimal to set one-hop = 1.  The we have a way to compute one-hope.
-
-Remove the weirdly colored diagram.
-
-Add to the rail angle diagram.
-
-Note that Lamba = 16 almost produces a 2-rail helicoid.
-
-When abs(lambda) > 4, we seem to have marked differences in the parameters. Understand why this is and what is causing it.
-(it is possible that positive and negative rho values behave very differently?
-
-Note: Would be really nice to have the GUI show you all computed parameters.
-
-Note: Distance is clearly lower on first computations..
-
-Create working toolkit for design/exploration.
-
-Improve code that way, use white background, floor.
-
-Figure out if I am computing something wrong.
-
-Try to compute optimal radius within our context. This would let us assert that we have
-an ``optimum'' continuum.  Not worth much to an engineer, but valuable.
-
-Review and continue editing, being careful to introduce concepts in the correct order.
-
-On Rail diagram, add a second tetrahedron, and a second rho.
-
-Make YouTube video.
-
-Possible addtional refrerences and submissions:
-
-Journal of applied geometry seems like a good fit:
-
 http://epubs.siam.org/toc/sjaabq/1/1
 
-According to there editorial board, they welcome mathematcal software and
-online resources such as I provie.
-
-This one has a nice editing structure: Metric Geometry is a nice subset:
-
-http://discreteanalysisjournal.com/for-authors
-
-http://bit-player.org/2013/tetrahedra-with-a-twist
-
-This is unrelated, but well worth reading:
-
-https://arxiv.org/pdf/1702.06388.pdf
-
-Research Turk's knots
+Improve Figures

### 2017-04-11 doc/TetrahelixUntwist.tex
significant improvements in the figures

@@
   \centering
-     \includegraphics[width=0.95\textwidth]{figures/TetrahelixSeries.png}
+     \includegraphics[width=1.0\textwidth]{figures/TetrahelixSeries2.png}
      \caption{A Series of Tetrahelices}
@@
 
-The quantity $ (3 \theta_{bc} - 2 \pi) \approx 35.43 \degree $  is the angular shift between $V(3n+c)=H_{BCcolored}(n,c)$ and
+The quantity $ (3 \theta_{bc} - 2 \pi) \approx 35.43 \degree $  is the angular shift between $V(3n + c)=H_{BCcolored}(n,c)$ and
 $V(3(n+1)+c)=H_{BCcolored}(n+1,c)$.
@@
 input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
-formed in the X,Y plane $\angle A O B$ projecting out the $z$
+formed in the X,Y plane $\angle H(0,0) O H(0,1)$ projecting out the $z$
 axis and sighting along the positive $z$ axis. In other words, $\rho$
@@
      \includegraphics[width=0.4\textwidth]{figures/AxialView.png}
-     \caption{Loking Down a BC-Helix}
+     \caption{Axial view of a BC-Helix}
   \label{axialview}     
@@
 
-From this equation with the help of symbolic computation we observe that inradius of the BC helix of unit rail length is $i_{\rho_{bc}} = \frac{3}{10\sqrt{2}} \approx 0.21213$.
+From this equation with the help of symbolic computation we observe that inradius of the BC helix of unit rail length is $r_{in(\rho_{bc})} = \frac{3}{10\sqrt{2}} \approx 0.21$.
 
@@
 Starting twenty years ago, Sanderson\cite{sanderson1996modular},
-Hamlin,cite{TetrobotBook}, Lee\cite{lee2002dynamic}, and others
+Hamlin,\cite{TetrobotBook}, Lee\cite{lee2002dynamic}, and others
  created a style of robotics based on changing

### 2017-04-11 doc/TetrahelixUntwist.tex
switch to SIAM style

@@
-\documentclass[11pt]{article}
-\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
-\usepackage{hyperref}
-\usepackage{graphicx}
+\documentclass[review]{siamonline1116}
+% \usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
+% \usepackage{hyperref}
+% \usepackage{graphicx}
 \usepackage{gensymb}
-\usepackage[affil-it]{authblk}
-\usepackage[toc,page]{appendix}
-\usepackage{pifont}
+% \usepackage[affil-it]{authblk}
+% \usepackage[toc,page]{appendix}
+% \usepackage{pifont}
 \usepackage{amsmath}
-\usepackage{amsthm}
+% \usepackage{amsthm}
 \usepackage{amsfonts}
-\usepackage{hyperref}
+% \usepackage{hyperref}
 
-\usepackage{float}
+% \usepackage{float}
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
+% \newtheorem{theorem}{Theorem}
+% \newtheorem{corollary}{Corollary}
 
@@
 
-\usepackage{draftwatermark}
+% \usepackage{draftwatermark}
 
-\SetWatermarkText{DRAFT}
-\SetWatermarkScale{6}
-\SetWatermarkLightness{0.95}
+% \SetWatermarkText{DRAFT}
+% \SetWatermarkScale{6}
+% \SetWatermarkLightness{0.95}
 
@@
 
-\title{Untwisting the Tetrahelix (v0.13)}
-\author{Robert L. Read \texttt{read.robert@gmail.com}
+\title{Untwisting the Tetrahelix}
+\author{Robert L. Read \email{read.robert@gmail.com}
 }
@@
 
+\begin{keywords}
+  Boedijk--Coxeter helix, tetrahelix, robotics, tetrobot, unconventional robots,
+  structural engineering, mechanical engineering, tensegrity, variable-geometry truss
+\end{keywords}
+\begin{AMS}
+  51M15
+\end{AMS}
+
 \section{Introduction}
@@
 The vertices of the tetrahedra lie upon
-three helices about the central axis.  The
-Tetrobot/Glussbot\cite{TetrobotBook} project uses the regularity of
+three helices about the central axis.
+The glussbot\cite{readglussbot} (or Tetrobot)\cite{TetrobotBook} uses the regularity of
 this geometry to make a tentacle-like robot that can crawl like a slug
@@
 
-Imagining Figure \ref{fig:closeup} as a static mechanical structure,
+Imagining \cref{fig:closeup} as a static mechanical structure,
 we observe that it is useful to the mechanical engineer or
@@
 somewhat mechanically strong.
-Imagine further in Figure \ref{fig:closeup}, that each static edge was replaced with an
+Imagine further in \cref{fig:closeup}, that each static edge was replaced with an
 actuator that could dynamically become shorter or longer in response to electronic control,
@@
 design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix},
-from which Figure \ref{fig:closeup} and
+from which \cref{fig:closeup} and
 the figures below are taken.
@@
      \includegraphics[width=1.0\textwidth]{figures/TetrahelixSeries2.png}
-     \caption{A Series of Tetrahelices}
+     \caption{A Continuum of Tetrahelices}
   \label{fig:series}
@@
 
-Figure \ref{fig:series} displays a continuum of tetrahelices optimal in a certain sense, which is the result of this
+\Cref{fig:series} displays a continuum of tetrahelices optimal in a certain sense, which is the result of this
 paper. The closest helix is the BC helix, and the furthest
-is the equitetrabeam, defined in Section \ref{sec:equitetrabeam}.
+is the equitetrabeam, defined in \cref{sec:equitetrabeam}.
 
@@
 tetrahelices by choosing the lengths of a small set of members.
-In a space frame, this is a static design choice; in a robot, it is a
+In a space frame, this is a static design choice; in a tetrobot, it is a
 dynamic choice that can be used to twist\footnote{The formal definition of twistiness, or \emph{torsion},
@@
 $\theta_{bc}$ is approximately $0.37 \cdot 2 \pi$ radians or  $131.81$ degrees.
-The angle $\theta_{bc}$ is the rotation of \emph{each} tetrahedron, not the tetraheda along a rail.  In Figure \ref{fig:closeup},
+The angle $\theta_{bc}$ is the rotation of \emph{each} tetrahedron, not the tetraheda along a rail.  In \cref{fig:closeup},
 each tetrahedron has either a yellow, blue, or red outer edge or rail.
@@
 
-Note in Figure \ref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In \eqref{graycoxeter} and \eqref{eq:colored}, the variable
+Note in \cref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In \eqref{graycoxeter} and \eqref{eq:colored}, the variable
 $h$ is used for one third of the distance we name $d$. We will later justify that $d = 3h$.
@@
 Our tool for thinking about this is to collapse the $z$ dimension to form
-a two-dimensional figure of nodes and non-rail edges (see Figure \ref{untouchingrailfig}.)
+a two-dimensional figure of nodes and non-rail edges (see \cref{untouchingrailfig}.)
 Consider the projection along the $z$ axis of all vertices and non-rail edges into the $xy$ plane, which will be
@@
 
-Figure \ref{untouchingrailfig} depicts a projection of
+\Cref{untouchingrailfig} depicts a projection of
 only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
@@
 Supoose there is a rail $P$ which does not have a segment touching the incircle
-at all in the projection, as depicted in Figure \ref{untouchingrailfig}.
+at all in the projection, as depicted in \cref{untouchingrailfig}.
 Then a segment connecting the other two $Q$ and $R$ is a longest
@@
 
-Theorem \ref{thm:cylinder} is not true when $\rho$ is an odd integer multiple of $\pi$.
+\Cref{thm:cylinder} is not true when $\rho$ is an odd integer multiple of $\pi$.
 
@@
 
-Figure \ref{equitetrabeam} shows the equitetrabeam, which is defined in Section \ref{sec:equitetrabeam},
+\Cref{equitetrabeam} shows the equitetrabeam, which is defined in \cref{sec:equitetrabeam},
 but illustrates the one-hop and two-hop edge defintions.
@@
 
- Note that based on Theorem \ref{eventhirds}, there are only 3 possible lengths in an optimal tethrahelix,
+ Note that based on \cref{eventhirds}, there are only 3 possible lengths in an optimal tethrahelix,
  and we are justified in classifying edge lengths as \emph{rail}, \emph{one-hop}, or
@@
 
-By Theorem \ref{eventhirds} every optimal tetrahelix has vertices lying on helices expressible in the form:
+By \cref{eventhirds} every optimal tetrahelix has vertices lying on helices expressible in the form:
 \[
@@
 parameter that allows us to design the tetrahelix conveniently.
-Please refer back to Figure \ref{railanglefig}.
+Please refer back to \cref{railanglefig}.
 The pitch of the helix is an obvious choice, but is not defined when the
@@
 Rewriting our formulation in terms of $\rho$:
-\begin{equation}
-  \label{eq:general}
-H_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) =
+\begin{align*}
+\numberthis  \label{eq:general}  
+H_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) &= 
  \left [
@@
   \end{tabular}
-  \right ],
-\text{where:}
+  \right ] \\
+\text{where: } &
 \begin{tabular}{c}
   $   1 = d_{\rho}^2 + 4 r_{\rho}^2 (\sin{ \rho / 2})^2 $ \\
-%%  $\kappa = n + c/3$ \\
     $\chi \in \{-1,1\}$ \\  
 \end{tabular}
-\end{equation}
+\end{align*}
 
@@
 Note that when $\rho = 0$ then $h_{\rho} = 1$, but $r_{\rho}$ is not determined by
-Equation \ref{railangle}.
+\cref{railangle}.
 
@@
 
-By Theoerm \ref{eventhirds}, we can compute the (at most) three edge-lengths of an optimal
+By \cref{eventhirds}, we can compute the (at most) three edge-lengths of an optimal
 tetrahelix by formula universally quantified by $n$ and $c$:
@@
 Let:
-\begin{equation}
+\begin{equation*}
   f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9}
-  \end{equation}
-\begin{equation}
+  \end{equation*}
+\begin{equation*}
   g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} 
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
   j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)
-\end{equation}
-\begin{equation}
+\end{equation*}
+\begin{equation*}
   k_{\rho} = (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)
-\end{equation}
+\end{equation*}
 
@@
 \begin{align*}
-  d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
+  d_{opt}^2 &= 1 - 4 (\frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }})^2 (\sin{ \rho / 2})^2   \\
 %%  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
@@
 
-If we look down the axis of an optimal tetrahelix as shown in Figure \ref{axialview}, it happens that only one of the one-hop edges
+If we look down the axis of an optimal tetrahelix as shown in \cref{axialview}, it happens that only one of the one-hop edges
 (rendered in purpple in our software)
@@
 and $d = 1$ (the edgelength), where the cross sectional area is
-an equilateral triangle of unchanging orientation, as shown in Figure \ref{equitetrabeam} and at the rear of Figure \ref{fig:series}.
+an equilateral triangle of unchanging orientation, as shown in \cref{equitetrabeam} and at the rear of \cref{fig:series}.
 We call this the \emph{equitetrabeam}.
@@
   The equitetrabeam with minimal maximal edge difference is produced
-  by $H_{general}$ when $ r = \sqrt{\frac{8}{27}} $.
+  \newline by $H_{general}$ when $ r = \sqrt{\frac{8}{27}} $.
 \end{corollary}
@@
 
-In Figure \ref{fig:series}, the furthest tetrahelix is the optimal equitetrabeam.
+In \cref{fig:series}, the furthest tetrahelix is the optimal equitetrabeam.
 Note that folding the outer edges of the paper upward or downward effectively
@@
   \centering
-     \includegraphics[width=0.4\textwidth]{figures/GlussBotBC.jpg}
+     \includegraphics[width=0.9\textwidth]{figures/GlussBotBC.jpg}
      \caption{Glussbot in relaxed, or BC helix configuration}
-     \includegraphics[width=0.4\textwidth]{figures/GlussBotEquitetrabeamCropped.jpg}
+     \includegraphics[width=0.9\textwidth]{figures/GlussBotEquitetrabeamCropped.jpg}
      \caption{The Equitetrabream: Fully Untwisted Glussbot}
@@
 
-The Gluss Project \url{http://pubinv.github.io/gluss/} is part of Public Invention,
+The Gluss Project \url{http://pubinv.github.io/gluss/} is part of Public Invention \url{https://pubinv.github.io/PubInv/},
 a free-libre, open-source research, hardware, and software project that welcomes volunteers.
 It is our goal to organize projects for the benefit of all humanity without seeking profit or intellectual property.
-To assist, contact \href{mailto:read.robert@gmail.com}{$<$read.robert@gmail.com$>$}.
+To assist, contact \email{read.robert@gmail.com}.
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{siamplain}
 \bibliography{IEEEabrv,gluss}

### 2017-04-12 doc/TetrahelixUntwist.tex
proofread, adding V_general

@@
 
-\title{Untwisting the Tetrahelix}
+\title{Untwisting the Boerdijk--Coxeter}
 \author{Robert L. Read \email{read.robert@gmail.com}
@@
   The Boerdijk--Coxeter helix (BC helix, or tetrahelix) is a
-  face-to-face stack of regular tetrahedra.  Considering the edges of
+  face-to-face stack of regular tetrahedra forming a helical column.  Considering the edges of
   these tetrahedra as structural members, the resulting structure is attractive and
@@
   parameters that give edge-length minimax-optimal tetrahelices
-  are given, defining a continuum of tetrahelices of varying curvature.
+  are given, defining a continuum of tetrahelices of varying torsion.
   The endpoints of the optimality of this continuum are the BC helix and
-  a structure of zero curvature, the \emph{equitetrabeam}.
+  a structure of zero torsion, the \emph{equitetrabeam}.
   Numerically finding the rail angle from the equation for
@@
 this geometry to make a tentacle-like robot that can crawl like a slug
-or mollusc.  The Tetrobot concept is to use mechanical members, called
-actuators, which can change their length, connected by special joints,
-such as the three-d printable Song-Kwon-Kim\cite{song2003spherical} joint, or the CMS joint\cite{HamlinSandersonCMS}
-which allow many members to come to a single point.
+or mollusc.  The Tetrobot uses mechanical actuators which can change their length, connected by special joints,
+such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint, or the CMS joint\cite{HamlinSandersonCMS}
+which allow many members to meet in a single point.
 Such machines can
@@
 omni-triangulated space frame, which is
-somewhat mechanically strong.
+mechanically strong.
 Imagine further in \cref{fig:closeup}, that each static edge was replaced with an
@@
 and the vertices were a joint that supported sufficient angular displacement
-for this to be possible. Such a machine is a Tetrobot\cite{TetrobotBook}.
+for this to be possible. An example of such a machine is a glussbot, shown in \cref{fig:glussbot}.
 
@@
   \begin{tabular}{c}
- $ r_{bc} = \frac{3\sqrt{3}}{10} $\\
- $ h_{bc} = 1/\sqrt{10} $ \\
+ $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $\\
+ $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $ \\
  $ \theta_{bc} = \arccos(-2/3) $ \\
@@
   \begin{tabular}{c}
- $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $\\
- $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $ \\
+ $ r_{bc} = \frac{3\sqrt{3}}{10} $\\
+ $ h_{bc} = 1/\sqrt{10} $ \\
  $ \theta_{bc} = \arccos(-2/3) $ \\
@@
 In this paper we assume the length of a rail
-is always $1$ as a simplification. (We make the rail length a parameter in our JavaScript code in \texttt{tetrahelixmath.js} \cite{readtetrahelix}.)
+is always $1$ as a simplification. (We make the rail length a parameter in our JavaScript code in
+\url{https://github.com/PubInv/tetrahelix/blob/master/js/tetrahelix_math.js} \cite{readtetrahelix}.)
 
-The $H_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho{bc}$ rather than $\theta_{bc}$.
+The $H_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho_{bc}$ rather than $\theta_{bc}$.
 Intuitively we seek an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
@@
 
+The \emph{pitch} of any tetrahelix, defined as the length of a complete revolution
+where $\rho \neq 0$ is:
+\begin{equation}
+  \label{pitcheqn}
+p(\rho) = \frac{2 \pi  \cdot d}{\rho}
+\end{equation}
+
 The pitch of the Boerdijk--Coxeter helix of edge length $1$ is the length of three tetrahedra times this number:
@@
 One could consider various definitions of optimality for a
-tetrahelix, but the most useful to us as robotocists extending the Tetrobot concept is to minimize the
-maximum difference between any two edges, because the Tetrobot uses linear acutators of limit range of extension.
+tetrahelix, but the most useful to us as robotocists working with the Tetrobot
+concept is to minimize the
+maximum difference between any two edges, because the Tetrobot uses
+mechanical linear acutators with
+limited range of extension.
 
@@
 Similarly, if the axes are not parallel, there is an edge of
-unbounded length in the structure, so we exclude such a strcturue.
+unbounded length in the structure, so we do not consider such cases.
 
@@
  We show that in fact the nodes must be distributed in even thirds
- along the $z$-axis.
+ along the $z$-axis, as in fact they are in the regular BC helix.
 
@@
  3 rail edges, 3 one-hop lengths between each pair of 3 rails, and 3 two hop
- lengths between each pair of three rails, where the two-hop length is at least
+ lengths between each pair of 3 rails, where the two-hop length is at least
  the one-hop length.
@@
 \Cref{equitetrabeam} shows the equitetrabeam, which is defined in \cref{sec:equitetrabeam},
-but illustrates the one-hop and two-hop edge defintions.
+but also conveniently illustrates the one-hop and two-hop edge defintions.
 The green edges are the two-hop edges and the purple edges are the one-hop edges. Note that the green
@@
     Consider the tetrahelix in which the vertices are evenly spaced at
-    $h/3$ intervals on the $z$ axis. Every edge is either a rail edge,
+    $d/3$ intervals on the $z$ axis. Every edge is either a rail edge,
     or it makes one hop, or it makes two hops. All of the one-hop
@@
     Any attempt to move any rail in either $z$ direction lengthens one two-hop edge to $t'$, where $t' > t$
-    edge and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be new edges.
+    and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be new edges.
     The minimax of $B$ is greater than the minimax of $A$ since there is a single rail length which cannot be both greater
@@
 where we have not yet investigated in the general case the relationships beteween $\alpha$, $r$, and $d$ in this formulation.
-However, we understand that when $\alpha = 0$, the helices are degenerate, having curvature of $0$, and
+However, we understand that when $\alpha = 0$, the helices are degenerate, having torsion of $0$, and
 we have the equitetrabeam.
@@
 The pitch of the helix is an obvious choice, but is not defined when the
-curvature is $0$, an important special case. The radius or the axial
+torsion is $0$, an important special case. The radius or the axial
 distance between two nodes on the same rail are possible choices, but
-perhaps the clearest choice is to build formulae that takes as thier
+perhaps the clearest choice is to build formulae that takes as their
 input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
@@
 
- These quantities are related by the expression:
+ The quantities $\rho,r,d$ are related by the expression:
 
@@
 indeed holds true (treating $d$ in this equation as $3 h_{bc}$ as defined by
-Gray and Coxeter, that is, $d_{bc} = 3h_{bc}$, where they are using it for the axial height from one node to
-the next of a different color, but we use it to mean distance for the same color.
+Gray and Coxeter, that is, $d_{bc} = 3h_{bc}$, where they are using
+$h$ for the axial height from one node to
+the next of a different color, but we use $d$ to mean distance between nodes of
+the  same color.
 
@@
 
-Note that when $\rho = 0$ then $h_{\rho} = 1$, but $r_{\rho}$ is not determined by
+Note that when $\rho = 0$ then $d_{\rho} = 1$, but $r_{\rho}$ is not determined by
 \cref{railangle}.
@@
 
+Writing as robotocists, the ``colored'' approach of thinking of three rails seems natural to us, in part because our application
+is focused on the edges, rather than any sort of interpretaion of the tetrahedra as solids. \Cref{eq:general} is in terms of helices that are close
+to what you see when you look at a tetrahelix constructed from edges.
+Having proved \cref{generalformulaoptimal}, it becomes plain that one could also use
+ a generalization of the orginal Coxeter/Gray formulation which uses a single helix to define all vertices, and a mathematician, chemist,
+or solid modeler might prefer that. This formulation is equivalent to \Cref{eq:general}, but uses $\theta = \frac{\rho+ 2\pi}{3}$,
+the rotation between rails, and triples the rotation rate. The same constraint on $r_{opt}$ and $d_{opt}$ holds if the user seeks minimax optimality.
+
+\begin{align*}
+\numberthis  \label{eq:coxetergraygeneral}  
+V_{general}(\chi,k,\theta,d_{\theta},r_{\theta}) &= 
+ \left [
+  \begin{tabular}{c}
+   $ r_{\theta} \cos(\chi k \theta) $\\
+   $ r_{\theta}  \sin(\chi k \theta) $\\
+   $ d_{\theta} k / 3 $
+  \end{tabular}
+  \right ] \\
+\text{where: } &
+\begin{tabular}{c}
+  $   1 = d_{\theta}^2 + 4 r_{\theta}^2 (\sin{ \frac{3\theta - 2\pi}{2}})^2 $ \\
+    $\chi \in \{-1,1\}$ \\  
+\end{tabular}
+\end{align*}
+
+Thus for any choice or $d$ and $r$ : $V_{general}(\chi,k,\theta,d,r) = H_{general}(\chi,n,c,\rho,d,r)$ when
+$\theta = \frac{\rho+ 2\pi}{3}$ and $k = 3n + c$,
+and both produce a minimax optimal tetrahelix for appropriate choices of $r$ and $d$ for
+$\frac{2\pi}{3} \leq \theta \leq \theta_{bc}$ or $0 \leq \rho \leq \rho_{bc}$.
+
 \section{The Inradius}
@@
 If we look down the axis of an optimal tetrahelix as shown in \cref{axialview}, it happens that only one of the one-hop edges
-(rendered in purpple in our software)
+(rendered in purple in our software)
 comes closest to the axis. In other words, they define the radius of the incircle of the
@@
 In \cref{fig:series}, the furthest tetrahelix is the optimal equitetrabeam.
-Note that folding the outer edges of the paper upward or downward effectively
-chooses the chirality of the equitetrabeam.
 
-To the extent that we value tetrabeams (that is, tetrahelicies with a rail angle of $0$,
-and therefore zero curvature) as mathematical or engineering objects,
+To the extent that we value tetrabeams (that is, tetrahelices with a rail angle of $0$,
+and therefore zero curvature and torsion) as mathematical or engineering objects,
 we have motivated the development of $H_{general}$ as a transformation of $V(n)$ defined by
@@
 We observe that Equations \eqref{eqrhoopt} and \eqref{dopt} compute $r_{opt}$ and $d_{opt}$ which
-create an optimal tetrahelix for any value rail angle $\rho$ between $0$, which
+create an optimal tetrahelix for any rail angle $\rho$ between $0$, which
 gives the equitetrabeam and
@@
 
-The pitch of any tetrahelix 
-where $\rho \neq 0$ is:
-\begin{equation}
-  \label{pitcheqn}
-p(\rho) = \frac{2 \pi  \cdot d}{\rho}
-\end{equation}
-For a fixed $z$-axis travel $d$, this is trivial.
+ The pitch of a helix (see \cref{pitcheqn}, for a fixed $z$-axis travel $d$,
+ is trivial.
 However, if one is computing 
@@
 physical structures. For example, a structural engineer might increase
-radius in order to resist buckling. If an equitetrabeam were actually
+radius past optimality in order to resist buckling.
+%% Add a figure here of a deep beam and of an arch.
+
+If an equitetrabeam were actually
 used as a beam, an engineer might start with the optimal tetrabeam and
 dilate it in one dimension to ``deepen'' the beam. Similarly, simple
-changes curve the equitetrabeam into an ``arch''.
+length changes curve the equitetrabeam into an ``arch''.
 
@@
      \includegraphics[width=0.9\textwidth]{figures/GlussBotEquitetrabeamCropped.jpg}
-     \caption{The Equitetrabream: Fully Untwisted Glussbot}
+     \caption{The Equitetrabream: Fully Untwisted Glussbot in Hexapod Configuration}
+     \label{fig:glussbot}
 \end{figure}
+
+By untwisting the tetrahelix so that is has a planar surface resting on the ground,
+we may consider each vertex touching the ground a foot or pseudopod. A robot can thus
+become a hexapod or $n$-pod robot, and the already well-developed approaches to
+hexapod gaits may be applied to make the robot walk or crawl.
 
@@
 The BC Helix is the end point of a continuum of tetrahelices, the
-other end point being an uncurved tetrahelix with equilateral cross
+other end point being an untwisted tetrahelix with equilateral cross
 section, constructed by changing the length of only those members

### 2017-04-12 doc/TetrahelixUntwist.tex
adding new figure and TODOs at end

@@
 the BC helix. We think of each of these three rails as being a different color: red, blue, or yellow.
+This situation is illustrated in \cref{fig:helixcomparison}, wherein the black helix represents that
+generated by \cref{graycoxeter},
+and the colored helices are generated by \cref{eq:colored}.
+
+\begin{figure}
+  \centering
+     \includegraphics[width=0.7\textwidth]{figures/HelixComparison.png}
+     \caption{Rail helices vs. Coxeter/Gray helix}
+  \label{fig:helixcomparison}  
+\end{figure}
 
@@
 Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued.)
+We can now assert that in \cref{fig:helixcomparison} the black helix winds at
+$\frac{3 \theta_{bc}}{\rho_{bc}} \approx 11.16 $ times the rate of a rail helix.
 
@@
 
-Writing as robotocists, the ``colored'' approach of thinking of three rails seems natural to us, in part because our application
-is focused on the edges, rather than any sort of interpretaion of the tetrahedra as solids. \Cref{eq:general} is in terms of helices that are close
+Writing as robotocists, the ``colored'' approach of thinking of three rails seems natural to us,
+in part because our application
+is focused on the edges, rather than any sort of interpretaion of the tetrahedra as solids.
+\Cref{eq:general} is in terms of helices that are close
 to what you see when you look at a tetrahelix constructed from edges.
 Having proved \cref{generalformulaoptimal}, it becomes plain that one could also use
- a generalization of the orginal Coxeter/Gray formulation which uses a single helix to define all vertices, and a mathematician, chemist,
-or solid modeler might prefer that. This formulation is equivalent to \Cref{eq:general}, but uses $\theta = \frac{\rho+ 2\pi}{3}$,
-the rotation between rails, and triples the rotation rate. The same constraint on $r_{opt}$ and $d_{opt}$ holds if the user seeks minimax optimality.
+a generalization of the orginal Coxeter/Gray formulation which uses a single helix
+to define all vertices, and a mathematician, chemist,
+or solid modeler might prefer that. This formulation is equivalent to \Cref{eq:general},
+but uses $\theta = \frac{\rho+ 2\pi}{3}$,
+the rotation between rails. The same constraint on $r_{opt}$ and $d_{opt}$ holds if the user seeks minimax optimality.
 
@@
 length changes curve the equitetrabeam into an ``arch''.
+The ``colored'' approach of \cref{eq:general} exposes these possibilities
+more than the approach of \cref{eq:coxtergraygeneral}.
 
@@
 
-Improve Figures
+Improve the helix comparison by constructing by hand in the Inkscape.
+
+Check the math on V_{general}.
+
+Reread everything, especially the new parts.
+
+Introduct the torsion concept.

### 2017-04-14 doc/TetrahelixUntwist.tex
major diagrammatic improvements

@@
   parameters that give edge-length minimax-optimal tetrahelices
-  are given, defining a continuum of tetrahelices of varying torsion.
+  are given, defining a continuum of tetrahelices of varying curvature.
   The endpoints of the optimality of this continuum are the BC helix and
-  a structure of zero torsion, the \emph{equitetrabeam}.
+  a structure of zero curvature, the \emph{equitetrabeam}.
   Numerically finding the rail angle from the equation for
@@
 In a space frame, this is a static design choice; in a tetrobot, it is a
-dynamic choice that can be used to twist\footnote{The formal definition of twistiness, or \emph{torsion},
-is not useful or used in the paper. The formal \emph{curvature} and \emph{torsion} of the helices defined here
-may be easily computed from the formualae if desired.} the robot and/or exert linear or
+dynamic choice that can be used to twist the robot and/or exert linear or
 angular force on the environment.
@@
 
-\begin{figure}
-  \centering
-     \includegraphics[width=0.7\textwidth]{figures/HelixComparison.png}
-     \caption{Rail helices vs. Coxeter/Gray helix}
-  \label{fig:helixcomparison}  
-\end{figure}
-
-It is convenient to have a formula that gives us the nodes of just
+In order to develop the continuum of slightly irregular tetrahelices described in \cref{sec:continuum},
+we need a formula that gives us the nodes of just
 one rail helix, denoted by color $c$ and integer node number $n$:
@@
 values.
+
+\begin{figure}
+  \centering
+     \includegraphics[width=0.7\textwidth]{figures/Unified.png}
+     \caption{Rail helices (H) vs. Coxeter/Gray helix (V) }
+  \label{fig:helixcomparison}  
+\end{figure}
+
+\Cref{fig:helixcomparison} illustrates this difference. Although the nodes conincide, \cref{graycoxeter} evaluated
+at real values generates the black helix, and \cref{eq:colored} defines the red, yellow, and blue helices. (In this figure
+these rail helices have been rendered at a slightly higher radius than the nodes; in actuality the helices are much close
+to the edges between the nodes that they nearly match.)
 
@@
 
-\section{Optimal Tetrahelices}
+\section{Optimal Tetrahelices are Triple Helices}
 
@@
 limited range of extension.
+
+A \emph{triple helix} is three congruent helices that share an axis. We show that
+optimal tetrahelices are triple helices.
 
@@
 
-\Cref{thm:cylinder} is not true when $\rho$ is an odd integer multiple of $\pi$.
+Note that \cref{thm:cylinder} is not true when $\rho$ is an odd integer multiple of $\pi$.
 
@@
      \caption{Equitetrabeam}
-  \label{equitetrabeam}
+  \label{fig:equitetrabeam}
 \end{figure}
 
-\Cref{equitetrabeam} shows the equitetrabeam, which is defined in \cref{sec:equitetrabeam},
+\Cref{fig:equitetrabeam} shows the equitetrabeam, which is defined in \cref{sec:equitetrabeam},
 but also conveniently illustrates the one-hop and two-hop edge defintions.
@@
   \label{eventhirds}
-  An optimal tetrahelix of any rail angle $\rho < \pi$ has all nodes evenly spaced at $d/3$ intervals on the $z$ axis.
+  An optimal tetrahelix of any rail angle $\rho < \pi$ is a triple helix all nodes evenly spaced at $d/3$ intervals on the $z$ axis.
   Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail and $2$ two-hop edges connected to the rail.
@@
     $d/3$ from each other.
+
+    As each helix is congruent to the others and shares an axis and are evenly spaced,
+    an optimal tetrahelix is a \emph{triple helix}.
 \end{proof}
@@
 where we have not yet investigated in the general case the relationships beteween $\alpha$, $r$, and $d$ in this formulation.
-However, we understand that when $\alpha = 0$, the helices are degenerate, having torsion of $0$, and
+However, we understand that when $\alpha = 0$, the helices are degenerate, having curvature of $0$, and
 we have the equitetrabeam.
@@
 The pitch of the helix is an obvious choice, but is not defined when the
-torsion is $0$, an important special case. The radius or the axial
+curvature is $0$, an important special case. The radius or the axial
 distance between two nodes on the same rail are possible choices, but
@@
 
-Writing as robotocists, the ``colored'' approach of thinking of three rails seems natural to us,
-in part because our application
-is focused on the edges, rather than any sort of interpretaion of the tetrahedra as solids.
-\Cref{eq:general} is in terms of helices that are close
-to what you see when you look at a tetrahelix constructed from edges.
-Having proved \cref{generalformulaoptimal}, it becomes plain that one could also use
-a generalization of the orginal Coxeter/Gray formulation which uses a single helix
-to define all vertices, and a mathematician, chemist,
-or solid modeler might prefer that. This formulation is equivalent to \Cref{eq:general},
-but uses $\theta = \frac{\rho+ 2\pi}{3}$,
-the rotation between rails. The same constraint on $r_{opt}$ and $d_{opt}$ holds if the user seeks minimax optimality.
-
-\begin{align*}
-\numberthis  \label{eq:coxetergraygeneral}  
-V_{general}(\chi,k,\theta,d_{\theta},r_{\theta}) &= 
- \left [
-  \begin{tabular}{c}
-   $ r_{\theta} \cos(\chi k \theta) $\\
-   $ r_{\theta}  \sin(\chi k \theta) $\\
-   $ d_{\theta} k / 3 $
-  \end{tabular}
-  \right ] \\
-\text{where: } &
-\begin{tabular}{c}
-  $   1 = d_{\theta}^2 + 4 r_{\theta}^2 (\sin{ \frac{3\theta - 2\pi}{2}})^2 $ \\
-    $\chi \in \{-1,1\}$ \\  
-\end{tabular}
-\end{align*}
-
-Thus for any choice or $d$ and $r$ : $V_{general}(\chi,k,\theta,d,r) = H_{general}(\chi,n,c,\rho,d,r)$ when
-$\theta = \frac{\rho+ 2\pi}{3}$ and $k = 3n + c$,
-and both produce a minimax optimal tetrahelix for appropriate choices of $r$ and $d$ for
-$\frac{2\pi}{3} \leq \theta \leq \theta_{bc}$ or $0 \leq \rho \leq \rho_{bc}$.
-
 \section{The Inradius}
@@
 and $d = 1$ (the edgelength), where the cross sectional area is
-an equilateral triangle of unchanging orientation, as shown in \cref{equitetrabeam} and at the rear of \cref{fig:series}.
-We call this the \emph{equitetrabeam}.
+an equilateral triangle of unchanging orientation, as shown in \cref{fig:equitetrabeam} and at the rear of \cref{fig:series}.
+We call this the \emph{equitetrabeam}. It is not possible to generate an equitetrabeam from \cref{graycoxeter}
+without the split into three rails introduced by \cref{eq:colored} and completed in \cref{eq:general}.
 
@@
 In \cref{fig:series}, the furthest tetrahelix is the optimal equitetrabeam.
+\Cref{fig:equitetrabeam} is a closeup of an equitetrabeam.
 
 To the extent that we value tetrabeams (that is, tetrahelices with a rail angle of $0$,
-and therefore zero curvature and torsion) as mathematical or engineering objects,
+and therefore zero curvature and curvature) as mathematical or engineering objects,
 we have motivated the development of $H_{general}$ as a transformation of $V(n)$ defined by
@@
 
+The equitetrabeam may possibly be a novel construction.
+The fact that 6 members meet in a single point would have been a manufacturing disadvantage that
+may have dissuaded structural engineers from using this geometry.
+However, the advent of additive manufacturing, such a 3D printing, and the invention of two
+distinct concentric multimember joints\cite{song2003spherical,HamlinSandersonCMS} has improved that situation.
+
 Note that the equitetrabeam has chirality, which becomes important in our attempt to build a
@@
 \section{An Untwisted Continuum}
+\label{sec:continuum}
 
@@
 
+The curvature of a rail helix is given by:
+\begin{equation}
+  \frac{|r_{\rho}|}{r_{\rho}^2 + (d_{\rho}/\rho)^2}
+\end{equation}
+which goes to $0$ as $\rho$ approaches $0$ (the equitetrabeam.)
+As $\rho$ increase up to $\rho_{bc}$ the curvature increases smoothly until the BC Helix is reached.
+
 Perhaps surprisingly, the optimal untwisting is accomplished only by
@@
 The ``colored'' approach of \cref{eq:general} exposes these possibilities
-more than the approach of \cref{eq:coxtergraygeneral}.
+more than the approach of \cref{eq:coxetergraygeneral}.
 
@@
 Reread everything, especially the new parts.
-
-Introduct the torsion concept.

### 2017-04-14 js/bundle.js
adding MeshLine generation

@@ -83,7 +83,7 @@ module.exports.find_rrho_from_d_el = (rho,d,el) => {
     return r;
 }
 module.exports.find_drho_from_r = (rho,r) =>    {
-    return this.find_drho_from_r_el(rho,r,1)
+    return this.find_drho_from_r_el(rho,r,1);
 }
 
 module.exports.find_rrho_from_d = (rho,d) => {
@@ -92,7 +92,6 @@ module.exports.find_rrho_from_d = (rho,d) => {
 
 // Tha abs should not be needed here, as thise functions are even..
 module.exports.optimal_radius = (rho,el) =>
-// function optimal_radius(rho,el)
 {
     var rho_abs = Math.abs(rho);
     var numer = 2*el;
@@ -129,17 +128,6 @@ Math.distance3 = function(p0,p1) {
     z = p0[2] - p1[2];        
     return Math.sqrt(x*x + y*y + z*z);
 }
-// I have forgotten what this is supposed to test.
-function test_optimal_radius() {
-    var MAX_DEGREES = 45;
-    for(var i = 0; i < 100;i++) {
-	var rho = Math.PI*(i*MAX_DEGREES/100)/180;
-	var r = optimal_radius(rho,1.0);
-	var h1 = one_hop(r,rho,1.0);
-	var h2 = two_hop(r,rho,1.0);
-	console.log(180*rho/Math.PI,r,h1,h2-h1);
-    }
-}
 
 // Copute the optimal distance as a function of rho
 // (not using optimal_radius, because we want an independent check).
@@ -151,53 +139,11 @@ module.exports.optimal_distance = (rho,el) => {
     var den = t1+t2+t3;
     return el*Math.sqrt(1 - num/den);
 }
-function test_one_hop() {
-    var rho = BCrho;
-    rho = BCrho/2;
-    var len = 0.5;
-    var r_opt = optimal_radius(rho,len);
-    var d_opt = optimal_distance(rho,len);
-    console.log(rho,len,r_opt,d_opt);
-    var onehop = one_hop(r_opt,rho,len);
-    var p1 = H_general(0,0,BCrho,d_opt,r_opt);
-    var p2 = H_general(0,1,BCrho,d_opt,r_opt);
-    var distance = Math.distance3(p1,p2);
-    console.log(p1,p2);
[…]

### 2017-04-19 doc/TetrahelixUntwist.tex
lame-o attempt to add a wobble diagram

@@
 
-\title{Untwisting the Boerdijk--Coxeter}
+\title{Untwisting the Boerdijk--Coxeter Helix}
 \author{Robert L. Read \email{read.robert@gmail.com}
@@
 
-\Cref{fig:helixcomparison} illustrates this difference. Although the nodes conincide, \cref{graycoxeter} evaluated
-at real values generates the black helix, and \cref{eq:colored} defines the red, yellow, and blue helices. (In this figure
-these rail helices have been rendered at a slightly higher radius than the nodes; in actuality the helices are much close
-to the edges between the nodes that they nearly match.)
+\Cref{fig:helixcomparison} illustrates this difference with a 7-tetrahedra BC helix, which is
+in fact the same geometry as the robot illustrated in \cref{fig:glussbot}.
+Although the nodes conincide,
+\cref{graycoxeter} evaluated
+at real values generates the black helix which runs through every node, and \cref{eq:colored} defines
+the red, yellow, and blue helices. (In this figure
+these rail helices have been rendered at a slightly higher radius than the nodes for clarity;
+in actuality the maximum distance between the continuous, curved helix and the
+straight edges between nodes is much smaller than can be clearly rendered.)
 
@@
  (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) &= \text{\{definition of $\rho_{bc}$\}...} \\  
-  (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{algebra...} \\  
+  (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{\{algebra...\}} \\  
 c  ( \rho_{bc} +  2 \pi) /3  \\
@@
 
-The \emph{pitch} of any tetrahelix, defined as the length of a complete revolution
+The \emph{pitch} of any tetrahelix, defined as the axial length of a complete revolution
 where $\rho \neq 0$ is:
@@
 concept is to minimize the
-maximum difference between any two edges, because the Tetrobot uses
+maximum ratio between any two edge lengths, because the Tetrobot uses
 mechanical linear acutators with
@@
 A \emph{triple helix} is three congruent helices that share an axis. We show that
-optimal tetrahelices are triple helices.
+optimal tetrahelices are in fact triple helices with the same radius, so that all
+vertices are on a cylinder. In, stages, we demonstrate that optimal tetrahelices:
+\begin{enumerate}
+\item have the same pitch,
+\item have parallel axes,
+\item share the same axis,
+\item have the same radius.
+\end{enumerate}
 
-Suppose that all three rails do not have the same pitch. Starting at any shortest edge, as we move
-from node to node away from our start node edge lengths between rails must always lengthen without bound,
+Suppose that all three rails do not have the same pitch. Starting at any shortest edge between
+two rails, as we move
+from node to node away from our start edge the edge lengths
+between rails must always lengthen without bound,
 which cannot be optimal.
@@
 tetrahelix to be the radius of the largest
-cylinder parallel to this axis contained within the circumscribing cylinder
-which is penetrated by no edge.
+cylinder parallel to this axis that is surrounded by each tetrahelix and pentrated by no edge.
 Define a \emph{minimax edge-length optimal tetrahelix} or just an
@@
 no other tetrahelix of the same inradius and pitch with a lower maximum
-difference between its edge lengths.
+ratio between its edge lengths.
 
@@
 
-Since all three rails have the same rail length, no matter how we
+Since all three rails have the same rail edge length, no matter how we
 move the rails in the $xy$ plane if we shorten the $xy$ distance between
@@
 
+As a little lemma for the proof below, observe that a tetrahelix of zero radius, where
+all points lie on the same line,
+is not as optimal as a tetrahelix of a small radius. The edges between rails will be
+shorter than the rail edges, and moving them apart slightly lengthens the between-edge
+rails.
+
 \begin{theorem}
-  \label{thm:cylinder}
-  Any optimal tetrahelix with a rail angle less than $\pi$ has all vertices on a single cylinder.
+  Any optimal tetrahelix with a rail angle of magnitude less than $\pi$ has all three
+  axes conincident.
+  \label{thm:conincident}
 \end{theorem}
-
 \begin{proof}
-
-Case 1: Suppose that $\rho$ is zero. Then for any given inradius, an equilateral
-triangle is the minimax solution for all non-rail edges. Since there is only
-one rail-edge length, this is the minimax solution for the entire set. Since
-the vertices of an equilateral triangle lies on a circle, all points lie on
+  Case 1: Suppose that $\rho$ is zero. Then for any given inradius, the
+  figure in the $XY$-plane of an equilateral
+  triangle is the minimax solution for all non-rail edges. Since all
+  rail edges are of length 1, this is the minimax solution for the entire set. Since
+the vertices of an equilateral triangle lie on a circle, all points in three-space lie on
 a cylinder.
@@
 In this case each rail helix has
-curavature and places points on both sides of any line through the origin
-of the $xy$ plane (or both coincident on such a line.)
+curavature. The projection of points in the $XY$ plane creates a figure
+guaranteed to have point on either side of any line through the axis of such
+a helix, because the figure is either an $n$-gon or a circle.
+We show that the three helices share a common axis.
 
-We first show that the inradius is touched by one segment from each pair
-of rails.
+  Without loss of generality define the Red helix to have its axis on the $z$-axis.
+  Without loss of generatlity define the Blue helix to be a helix that
+  has an edge connection to the Red helix that is either a maximum or a minimum.
+  Let $B'$ be the blue helix translated in the $XY$-plane so that its axis is the $z$-axis and
+  condicent with the red helix $R$. Let $D$ be the distance between the axis of the Blue helix
+  $B$ and $B'$. We will show that if $D>0$ then $B$ ``wobbles'' in a way that cannot be optimal.
+  Define a wobble vector by:
+  \begin{equation*}
+    W(n) = B(n) - B'(n)
+  \end{equation*}
+  where $B(n)$ is the cartesian vector
+  $\begin{bmatrix}
+           x \\
+           y 
+  \end{bmatrix}$
+  for the projection of the $n$th blue vertex.
+  Note that $|| R(n) - B'(n+k)||$ is a constant for any $k$, because $R$ and $B'$ have the
+  same pitch and the same axis, even if they do not have the same radius
+  (which we are currently proving.)
 
@@
      \centering
-     \includegraphics[width=0.7\textwidth]{figures/UntouchingRail.png}
-     \caption{Untouching Rail}
-  \label{untouchingrailfig}
+     \includegraphics[width=0.7\textwidth]{figures/WobbleDiagram.png}
+     \caption{Wobble Vectors from Non-Coincident Axes}
+  \label{fig:wobble}
 \end{figure}
 
-\Cref{untouchingrailfig} depicts a projection of
-only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
-and the intermediary points $R$ and $Q$ on the other two rails.
+  Since $-\pi<\rho<\pi$, each rail helix rotates about its axis as a function of $n$ and
+  defines at least 3 unique points when projected onto the $XY$-plane around its axis.
+  If $2\pi/\rho$ is irrational, it defines a circle. If $2\pi/\rho$ is rational it defines
+  an n-gon in the $XY$-plane, where $n$ is at least 3 (when $\rho = 2\pi/3$).
+  The set of wobbles $\{W(n) | \text{for any n}\}$ thus contains at least three vectors,
+  pointing in different directions.
+  For any point not at the origin, at least one of these vectors moves closer to the
+  point and at least one moves further away.
 
-Supoose there is a rail $P$ which does not have a segment touching the incircle
-at all in the projection, as depicted in \cref{untouchingrailfig}.
-Then a segment connecting the other two $Q$ and $R$ is a longest
-rail, because any chord touching an incircle is longer than any which does not.
-These two rails ($Q$ and $R$) can be moved closer to each other, and further away from $P$, to form a better minimax solution
-by shortening the longest rail, until one of the segments from $P$ the previously
-untouching rail touches one of the incircle. By induction, then all rails have
-at least one segement touching each vertex on the rail that is tangent to the
-incircle in an optimal tetrahelix.
+    The set of all lengths in the tetrahelix is a superset of:
+    $L = \{|| R(n) - B(n)||\}$, which by our choice has at least one longest or shortest
+    length.
+    $L = \{|| R(n) - (B'(n) + W(n))||\}$ and so
+    $L = \{|| (R(n) - B'(n)) - W(n)||\}$.
+    But $R(n) - B'(n)$ is a constant, so the minimax value of $L$ is improved as $||W(n)||$
+    decreases.  
+    By our choice, this improves the minimax value of the total tetrahelix.
 
-Now suppose that you attempt to move the axis of one of the rails. Because
-$\rho > 0 $ and $\rho$ is not a multiple of $\pi$, there is some vertex on the two sides of any diameter
-halving our circle. Moving the axis of a tetrahelix lengthens a longest line while ``pinching'' the
-inradius on the other side, so it is not optimal. Since the axes of these helices are the
-same and they have the same curvature and pitch, the points defined by the helices all lie
-on a cylinder.
-
+    This process can be carried out on both the Blue and Yellow helices
+    (perhaps simultaneously) until $W(n)$ is
+    zero for both, finding a tetrahelix of improved overall minimax value at each step.
+    So a tetrahelix is optimal only when $W(n) = 0$, and therefore when $D=0$
+    $B(n) = B'(n)$, all three axes are conincident.
   \end{proof}
@@
 Note that \cref{thm:cylinder} is not true when $\rho$ is an odd integer multiple of $\pi$.
+
+Note: This is not a proof that they have the same radius, I will have to add that.
 
@@
   \label{eventhirds}
-  An optimal tetrahelix of any rail angle $\rho < \pi$ is a triple helix all nodes evenly spaced at $d/3$ intervals on the $z$ axis.
+  An optimal tetrahelix of any rail angle $\rho < \pi$ is a triple helix with all vertices evenly spaced at $d/3$ intervals on the $z$ axis.
   Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail and $2$ two-hop edges connected to the rail.
@@
   \label{generalformulaoptimal}
-  The tetrahelices generated by $H_{general}$ are optimal in terms of minimum maximum member length when $r_{\rho}$ is chosen so that
+  The tetrahelices generated by $H_{general}$ are optimal in terms of minimum maximum ratio of member length when $r_{\rho}$ is chosen so that
   the length of the one-hop edge is equal to the rail length.
@@
 projection, or the radius of a cylinder that would just fit inside the tetrahelix.
-A formula for the inradious of the tetrahelix is useful if you are designing it as a structure that bears something internally,
+A formula for the inradius of the tetrahelix is useful if you are designing it as a structure that bears something internally,
 such as a firehose, a pipe, or
@@
 \begin{corollary}
-  The equitetrabeam with minimal maximal edge difference is produced
+  The equitetrabeam with minimal maximal edge ratio is produced
   \newline by $H_{general}$ when $ r = \sqrt{\frac{8}{27}} $.
@@
 
-The curvature of a rail helix is given by:
+The curvature of a rail helix is foramlly given by:
 \begin{equation}
@@
 The ``colored'' approach of \cref{eq:general} exposes these possibilities
-more than the approach of \cref{eq:coxetergraygeneral}.
+more than the approach of \cref{graycoxeter}.
 
@@
 crossing the outside rails after hopping over the nearest
-vertex. Under the condition of miminum maximum length difference of
+vertex. Under the condition of miminum maximum length ratios of
 all members in the system, all such tetrahelices have vertices evenly
-spaced along the axis generated by a simple equation.  A mechanical
-machine, such as a robot or a variable-geometry truss, that can change
-the length of its members, can thus twist and untwist itself by
+spaced along the axis generated by a simple equation and are in fact triple helices.
+A machine, such as a robot or a variable-geometry truss, that can change
+the length of its members can thus twist and untwist itself by
 changing the length of the appropriate members to achieve any point in
-the continuum optimally. With a numeric solution, a design may choose
-a rotation angle and member lengths to obtain any desired pitch.
+the continuum. With a numeric solution, a design may choose
+a rotation angle and member lengths to obtain a desired pitch.
 
@@
 
+** Try to show that rotation must be symmetric over possible rotation.
+
+** Try to show 2-hop > rail for any optimal.
+
 http://epubs.siam.org/toc/sjaabq/1/1
 
-Improve the helix comparison by constructing by hand in the Inkscape.
+Reread everything, especially the new parts.
 
-Check the math on V_{general}.
+\begin{theorem}
+  \label{thm:cylinder}
+  Any optimal tetrahelix with a rail angle less than $\pi$ has all vertices on a single cylinder.
+\end{theorem}
 
-Reread everything, especially the new parts.
+\begin{proof}
+
+Case 1: Suppose that $\rho$ is zero. Then for any given inradius, an equilateral
+triangle is the minimax solution for all non-rail edges. Since there is only
+one rail-edge length, this is the minimax solution for the entire set. Since
+the vertices of an equilateral triangle lie on a circle, all points lie on
+a cylinder.
+
+Case 2: Suppose that $\rho$ is positive but less than $\pi$.
+In this case each rail helix has
+curavature and places points on both sides of any line through its axis.
+
+We first show that the inradius is touched by one segment from each pair
+of rails.
+
+\begin{figure}[H]
+     \centering
+     \includegraphics[width=0.7\textwidth]{figures/UntouchingRail.png}
+     \caption{Untouching Rail}
+  \label{untouchingrailfig}
+\end{figure}
+
+\Cref{untouchingrailfig} depicts a projection of
+only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
+and the intermediary points $R$ and $Q$ on the other two rails.
+
+Supoose there is a rail $P$ which does not have a segment touching the incircle
+at all in the projection, as depicted in \cref{untouchingrailfig}.
+Then a segment connecting the other two $Q$ and $R$ is a longest
+rail, because any chord touching an incircle is longer than any which does not.
+These two rails ($Q$ and $R$) can be moved closer to each other, and further away from $P$,
+to form a better minimax solution
+by shortening the longest rail, until one of the segments from $P$, the previously
+untouching rail, touches the incircle. By induction, then all rails have
+at least one segement touching each vertex on the rail that is tangent to the
+incircle in an optimal tetrahelix.
+
+Now suppose that you attempt to move the axis of one of the rails away from the center
+for our circle. Because
+$\rho > 0 $ and $\rho$ is not a multiple of $\pi$, there is some vertex on the two sides of any diameter
+halving our circle. Moving the axis of a tetrahelix lengthens a longest line while ``pinching'' the
+inradius on the other side, so it is not optimal. Since the axes of these helices are the
+same and they have the same curvature and pitch, the points defined by the helices all lie
+on a cylinder.
+\end{proof}

### 2017-04-24 doc/TetrahelixUntwist.tex
working on proofs

@@
 \item share the same axis,
-\item have the same radius.
+\item have the same radius,
+  \item have the same rail lengths,
+  \item have axialy equidistant nodes, and therefore
+  \item are in fact triple helices.
 \end{enumerate}
@@
 
-Since all three rails have the same rail edge length, no matter how we
-move the rails in the $xy$ plane if we shorten the $xy$ distance between
-vertices we shorten the total distance.
-Our tool for thinking about this is to collapse the $z$ dimension to form
-a two-dimensional figure of nodes and non-rail edges (see \cref{untouchingrailfig}.)
-Consider the projection along the $z$ axis of all vertices and non-rail edges into the $xy$ plane, which will be
-a figure of dots and connecting segments in the $xy$ plane. The convex
-hull for any one helix projection will be a circle (if its pitch is
-irrational) or a polygon if rational, or a point if the helix has
-zero curvature. Each of these figures by definition lies outside the
-circle of inradius $r_{in}$ in the $xy$ plane.
+%% Since all three rails have the same rail edge length, no matter how we
+%% move the rails in the $xy$ plane if we shorten the $xy$ distance between
+%% vertices we shorten the total distance.
+%% Our tool for thinking about this is to collapse the $z$ dimension to form
+%% a two-dimensional figure of nodes and non-rail edges (see \cref{fig:wobble}.)
+%% Consider the projection along the $z$ axis of all vertices and non-rail edges into the $xy$ plane, which will be
+%% a figure of dots and connecting segments in the $xy$ plane. The convex
+%% hull for any one helix projection will be a circle (if its pitch is
+%% irrational) or a polygon if rational, or a point if the helix has
+%% zero curvature. Each of these figures by definition lies outside the
+%% circle of inradius $r_{in}$ in the $xy$ plane.
 
@@
 
-Note that \cref{thm:cylinder} is not true when $\rho$ is an odd integer multiple of $\pi$.
-
-Note: This is not a proof that they have the same radius, I will have to add that.
-
-Now that we have shown that any optimal tetrahelix vertices
-are on helices of the same axes and pitch, we see that the vertices 
-of any optimal tetrahelix will lie on a cylinder, or a circle when axis dimension
-is projected out. Therefore it is reasonable to now speak of the \emph{radius} $r$
-of a tetrahelix as the radius of the cylinder, as distinct from the inradius $r_{in}$.
-
-Now that we have coincident axes, the same pitch, and the same radius, we can go on to
- the harder proof about where vertices occur along the $z$-axis.
-
- We show that in fact the nodes must be distributed in even thirds
- along the $z$-axis, as in fact they are in the regular BC helix.
-
- Note that from the point of view of a single edge, we are on a
- slanted cylinder, when $\rho \neq 0$.  This means from its point of
- view a cross section is an ellipse. So we have to be very careful in
- comparing lengths of edges relative to the tetrahedron, because a
- change in position along the edge changes the length of a line, but
- in a complicated way depending on where it is relative to the
- ellipse.
+Now we show that an optimal tetrahelix has the same radii for all three helices.
+To do this exhibit a symmetric tetrahelix (not yet shown to be optimal) which
+happens to be a tetrahelix, that has
+the property that all rail edges are equal to all one-hop edges and all two-hop
+edges are equal. Observe that although we have not get given the formula for the
+radii of such a triple helix, we observe there are some values for $r$ and $\alpha$
+for which this is true from this generic formula for a triple helix:
+\[
+\label{eq:triple}
+V_{triple}(n,c) =
+\left [
+  \begin{tabular}{c}
+   $ r \cos(n \alpha +  c 2 \pi /3)$\\
+   $ r \sin(n \alpha +  c 2 \pi /3) $\\
+   $ \frac{d(n +c / 3)}{3}   $
+  \end{tabular}
+  \right ],
+\text{where:}
+\begin{tabular}{c}
+  $c \in \{0,1,2\}$
+  \end{tabular}      
+\]
+In \cref{sec:parameterizing} we show how to find $r$ and $\alpha$.
 
@@
 the one-hop length.
+However, if we generate the three helices symmetrically with \cref{eq:triple},
+many of these lengths will be the same.
+
+Now consider a tetrahelix in which the radius of one of the helices is different.
+By the connections made in a tetrahelix, any increase to a radius increases both
+a one-hop and two-hop distance, and any decrease likewise decreases two.
+Since there exists a tetrahelix which has only two distinct classes of edge lengths,
+(the smaller being one-hop = rail, the larger being the two-hop distance), the helix
+with a larger radius increases a longest edge without increasing a shortest edges.
+Likewise, a helix with a smaller radius decreases a one-hop edge without decreasing
+a two-hop edge.  Therefore, a tetrahelix with different radii is not as some
+tetrahelix generated by \cref{eq:triple}, and so it not optimal. (Note however,
+that we have not yet exhibited a truly optimal tetrahelix, nor proven that such
+a tetrahelix occurs when the one-hop edge, length is equal to the rail edge length,
+which we do in \cref{sec:parameterizing}.)
+
+Because an optimal tetrhelix has equivalent radii for all three helices,
+it has equivalent rail edge lengths.
+
+%% \begin{theorem}
+%%   \label{thm:cylinder}
+%%   Any optimal tetrahelix with a rail angle less than $\pi$ has all vertices on a single cylinder.
+%% \end{theorem}
+
+%% \begin{proof}
+
+%% Case 1: Suppose that $\rho$ is zero. Then for any given inradius, an equilateral
+%% triangle is the minimax solution for all non-rail edges. Since there is only
+%% one rail-edge length, this is the minimax solution for the entire set. Since
+%% the vertices of an equilateral triangle lie on a circle, all points lie on
+%% a cylinder.
+
+%% Case 2: Suppose that $\rho$ is positive but less than $\pi$.
+%% In this case each rail helix has
+%% curavature and places points on both sides of any line through its axis.
+
+%% We first show that the inradius is touched by one segment from each pair
+%% of rails.
+
+%% \begin{figure}[H]
+%%      \centering
+%%      \includegraphics[width=0.7\textwidth]{figures/UntouchingRail.png}
+%%      \caption{Untouching Rail}
+%%   \label{untouchingrailfig}
+%% \end{figure}
+
+%% \Cref{untouchingrailfig} depicts a projection of
+%% only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
+%% and the intermediary points $R$ and $Q$ on the other two rails.
+
+%% Supoose there is a rail $P$ which does not have a segment touching the incircle
+%% at all in the projection, as depicted in \cref{untouchingrailfig}.
+%% Then a segment connecting the other two $Q$ and $R$ is a longest
+%% rail, because any chord touching an incircle is longer than any which does not.
+%% These two rails ($Q$ and $R$) can be moved closer to each other, and further away from $P$,
+%% to form a better minimax solution
+%% by shortening the longest rail, until one of the segments from $P$, the previously
+%% untouching rail, touches the incircle. By induction, then all rails have
+%% at least one segement touching each vertex on the rail that is tangent to the
+%% incircle in an optimal tetrahelix.
+
+%% Now suppose that you attempt to move the axis of one of the rails away from the center
+%% for our circle. Because
+%% $\rho > 0 $ and $\rho$ is not a multiple of $\pi$, there is some vertex on the two sides of any diameter
+%% halving our circle. Moving the axis of a tetrahelix lengthens a longest line while ``pinching'' the
+%% inradius on the other side, so it is not optimal. Since the axes of these helices are the
+%% same and they have the same curvature and pitch, the points defined by the helices all lie
+%% on a cylinder.
+%% \end{proof}
+
+%% Note: This is not a proof that they have the same radius, I will have to add that.
+
+Now that we have shown that any optimal tetrahelix vertices
+are on helices of the same axes and pitch, we see that the vertices 
+of any optimal tetrahelix will lie on a cylinder, or a circle when axis dimension
+is projected out. Therefore it is reasonable to now speak of the \emph{radius} $r$
+of a tetrahelix as the radius of the cylinder, as distinct from the inradius $r_{in}$.
+
+Now that we have coincident axes, the same pitch, and the same radius, we can go on to
+ the harder proof about where vertices occur along the $z$-axis.
+
+ We show that in fact the nodes must be distributed in even thirds
+ along the $z$-axis, as in fact they are in the regular BC helix.
+
+ Note that from the point of view of a single edge, we are on a
+ slanted cylinder, when $\rho \neq 0$.  This means from its point of
+ view a cross section is an ellipse. So we have to be very careful in
+ comparing lengths of edges relative to the tetrahedron, because a
+ change in position along the edge changes the length of a line, but
+ in a complicated way depending on where it is relative to the
+ ellipse.
+
  However, we have already shown the rail
@@
 
-By \cref{eventhirds} every optimal tetrahelix has vertices lying on helices expressible in the form:
+By \cref{eventhirds} we are justified renaming \cref{eq:triple} ``optimal'':
 \[
@@
 \]
-where we have not yet investigated in the general case the relationships beteween $\alpha$, $r$, and $d$ in this formulation.
+where we have not yet investigated in the general case the relationships beteween
+$\alpha$, $r$, and $d$ in this formulation.
 However, we understand that when $\alpha = 0$, the helices are degenerate, having curvature of $0$, and
@@
 \section{Parameterizing Tetrahelices via Rail Angle}
+\label{sec:parameterizing}
 
@@
 
-\begin{theorem}
-  \label{thm:cylinder}
-  Any optimal tetrahelix with a rail angle less than $\pi$ has all vertices on a single cylinder.
-\end{theorem}
-
-\begin{proof}
-
-Case 1: Suppose that $\rho$ is zero. Then for any given inradius, an equilateral
-triangle is the minimax solution for all non-rail edges. Since there is only
-one rail-edge length, this is the minimax solution for the entire set. Since
-the vertices of an equilateral triangle lie on a circle, all points lie on
-a cylinder.
-
-Case 2: Suppose that $\rho$ is positive but less than $\pi$.
-In this case each rail helix has
-curavature and places points on both sides of any line through its axis.
-
-We first show that the inradius is touched by one segment from each pair
-of rails.
-
-\begin{figure}[H]
-     \centering
-     \includegraphics[width=0.7\textwidth]{figures/UntouchingRail.png}
-     \caption{Untouching Rail}
-  \label{untouchingrailfig}
-\end{figure}
-
-\Cref{untouchingrailfig} depicts a projection of
-only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
-and the intermediary points $R$ and $Q$ on the other two rails.
-
-Supoose there is a rail $P$ which does not have a segment touching the incircle
-at all in the projection, as depicted in \cref{untouchingrailfig}.
-Then a segment connecting the other two $Q$ and $R$ is a longest
-rail, because any chord touching an incircle is longer than any which does not.
-These two rails ($Q$ and $R$) can be moved closer to each other, and further away from $P$,
-to form a better minimax solution
-by shortening the longest rail, until one of the segments from $P$, the previously
-untouching rail, touches the incircle. By induction, then all rails have
-at least one segement touching each vertex on the rail that is tangent to the
-incircle in an optimal tetrahelix.
-
-Now suppose that you attempt to move the axis of one of the rails away from the center
-for our circle. Because
-$\rho > 0 $ and $\rho$ is not a multiple of $\pi$, there is some vertex on the two sides of any diameter
-halving our circle. Moving the axis of a tetrahelix lengthens a longest line while ``pinching'' the
-inradius on the other side, so it is not optimal. Since the axes of these helices are the
-same and they have the same curvature and pitch, the points defined by the helices all lie
-on a cylinder.
-\end{proof}
+Proof Ideas:
+
+Now that we have shown parallel and conincident, we can definie ``one-hop'' and ``two-hop''
+clearly.
+
+Can we show that one-hop < two-hop in an optimal tetrahelix?
+
+This is true by definition, but we potentially have 6 such differences.
+If all are less than the maximum rail edge, we are not optimal, as a lower rail edge
+is better.
+If all are > than the minimum rail edge, we are not opitimal, as we can raise that
+rail edge.
+
+So MAX(non-rail) >= MIN(rail-edge).
+also: MIN(non-rail) <= MAX(rail).
+
+Conjecture: Increasing Radius increases length of all attached nodes.
+Lemma: If a line is drawn between a point P on one circule and a point Q on a nother circle,
+and the circles are parallel in space,
+increasing the radius of eitehr circle increases the length, no matter where the circles are,
+and no matter where the points are on the circle.
+
+Therefore if there is a single maximum radius and it has a longest edge coming to it,
+the minimax is made better by decreasing that radius until equal with the next radius.
+
+If a single radius is a shortest radius, the minimax is made better by
+increasing it.
+
+Can we proe this rigourously?
+
+Does a single large radius necessarily have a longest edge?
+A Rail edge would be longest if we allow any rotation, but we can severely
+limit rail angle to \rho_{bc}.
+
+New Idea:
+
+Suppose Red is a largest radius.  Blue and Yellow must be symmetrically distributed
+ccw and cw from Red.
+
+Proof sketch: if Red is a largest radius, the two-hop edges to Yellow and Blue
+are the longest two in the system.  Is one is longer than that other, rotating it
+is more optimum.
+
+Proof Idea:
+
+If two-hop edges are always longest and one-hop always shortest, then they
+should be equalized.
+
+* * *
+
+Proof idea.
+
+Thm: An optimal tetrahelix has a longest edge which is a two-hop edge.
+
+Proof:
+
+Case 1: If the longest edge is a rail edge, construct a better minimax optimal
+tetrahelix by increasing the radius of every helix, which does not change the
+rail length, until a non-rail edge is equal to the rail edge.  This increases
+the length of every non-rail edge, therefore it is a better helix.
+
+Case 2: The longest edge is a non-rail edge.
+
+WOLOG, this is an edge from Red to Blue. By assumption, at least one
+of three things must be true:
+1) The RED-BLUE 2-hop axial distance is longer than the other two 2-hop axial distances.
+2) One rail (call it Red) has a larger radius.
+3) The Red-Blue rails can be rotated closer together to decrease the
+RED-BLUE distance. (If the angle between RED and BLUE is zero, then one
+of the other must be true.)
+
+In case 1), construct a better tetrahelix axially shifting the BLUE rails to decrease
+the RED-BLUE 2-hop axial distance (and increase the 2-hop axial distance.) The effects
+our classes by:
+RR not affected
+BB not affected
+YY not affected
+RB- increased
+RB+ decreased
+BY- decreased
+BY+ increased
+RY- not affected
+RY+ not affected
+
+So if the set of shortest edges does not include BY-, this tetrahelix is better.
+If it does include BY-, we must show that RB+/BY- decreases as we move the rail.
+We could show the actual derivative of this.  Informally, the angle is more direct,
+so the change in RB+ should be greater. This may require comparison to the cylindrical
+solution.  If we assume this is true for the cylindrical solution, then we have shown
+a better solution exists. So case one is not optimal.
+
+So we must show that if a shortest edge is in RY-, RY+, RB-, we have to
+RB+ of these edges decreases. RY+ cannot be a shortest edge.
+Idea: if RY-, RB- are shortest, increase Y, B radius.
+So what does the derivative of RB+/RY- and RB+/RB- tell us? The further away it is,
+the straighter the push, so it is likely that the RB+ edge changes faster than the RY- edge
+decreases. If R has a bigger radius, can RY- be smaller than BY-? Seems like we will
+have to use the algebraic formula to do this---but I have no proof yet that it is an triple helix.
+
+Note, that if we could prove just this case, our equidistance proof would complete everything we need!
+So I need to show that RB+/RY- decreases as we shrink the radius---in other words, the RB+ line
+is more central than the RY- line.
+
+In case 3), if we rotate blue towards red:
+
+RR not affected
+BB not affected
+YY not affected
+RB- decreases
+RB+ decreases
+BY- increases
+BY+ increases
+RY- not affected
+RY+ not affected
+
+Attempt to create Proof of Equal Radius:
+
+Suppose that Red Radius is largest.
+
+Case RB+ is longest:
+We can understand the change of decreasing the Red Radius:
+
+RR decreases
+BB not affected
+YY not affected
+RB- decreases
+RB+ decreases
+BY- not affected
+BY+ not affected
+RY- decreases
+RY+ decreases
+
+Sub Case split:
+Case RB- is smallest:
+Increase B radius.
+Case RY- is smallest:
+Increase Y radius.
+Case RR is smallest:
+This is not possible if Red is has the largest Readius!
+Case: RB- = RY-  are smallest.  In increase both B and Y.
+
+Done case RB+ is longest.
+
+Case YB+ is longest:
+
+This can occur only if YB is not even 1/3rds.
+
+Case:
+YB- is the worst. Then we need to move the bar.
+
+Case:
+Rail BB is smallest.  Then  we are making better.
+
+Case:
+RB- is smallest (need to move blue.)
+RY- is smallest (need to move yellow.)
+
+(I think this is a combined proof.)
+
+Case RB+ amd YB+ are both longest.
+
+RR decreases
+BB not affected
+YY not affected
+RB- decreases
+RB+ decreases
+BY- not affected
+BY+ not affected
+RY- decreases
+RY+ decreases
+
+Decrease R and simultaneously rotate Y towards B
+to decrease YB+.
+
+Done with case YB+ is longest.
+
+Case RR is longest:
+
+Decrease radius improves.
+
+Now suppose the Red and Blue Radiii are equual and larger than yellow.
+
+Case split RB+ is longest.
+
+Increase Y does:
+RR not affected
+BB not affected
+YY increases
+RB- not affected
+RB+ not affected
+BY- increases
+BY+ increases
+RY- increases
+RY+ increases
+
+Sub case split: Shortest not RR,BB, or RB- or RB+, then we improve.
+If it is a rail, decrease all radii until this is not true.
+
+RB-, then we need to move Red relative to Blue. If we are already
+at even thirds and proper rotation is this possible? This might require
+going down the algebra level to prove.
+
+Case split YB+ or YR+ is longest.
+
+New Proof Idea:
+
+Prove optimality of equal one-hop edges from simple diagram.
+From that, show optimality of equidistance and radius.
+
+New Proof Idea:
+
+Proof that all radii are the same.
+
+Lemma: There is a solution with all one-hop edges equal to all rail edges
+and all two-hop edges longer.
+
+Assume that the solution with all one-hop and rail distances the same
+is optimal.  Assume that all two-hop edges are the same.
+
+Any change to a radii either increases both or decreases both for
+one set, thereby harming the optimum.  Y cannot be rotated
+toward both Red and Blue. Y cannot be shifted toward both Red and Blue.
+(We need a lemma here that Red and Blue are on the opposite side or the
+line through the circle of Red.)
+Therefore any different radius has a longer two-hop edge, and is not optimal.
+
+If we have all radii the same, then our existing proof works for
+equidistance.

### 2017-04-24 doc/TetrahelixUntwist.tex
some progress on proof

@@
 
-Since the axes are parallel, we may define the \emph{inradius}, represented by the letter $i$, of a
-tetrahelix to be the radius of the largest
-cylinder parallel to this axis that is surrounded by each tetrahelix and pentrated by no edge.
 Define a \emph{minimax edge-length optimal tetrahelix} or just an
 \emph{optimal tetrahelix} to be a tetrahelix for which there exists
-no other tetrahelix of the same inradius and pitch with a lower maximum
-ratio between its edge lengths.
+no other tetrahelix with lower ratio of longest edge length to shortest edge length.
 
@@
 
+  \Cref{fig:wobble} demonstrates illustrates this situation. Like most diagrams, it is
+  over specific, in that the two circles are drawn of the same radius but we do not
+  depend upon that in this proof.  The diagram represents the projection along the
+  $z$ axis of points into the $XY$-plane.
+
   \begin{figure}[H]
@@
 
-Now we show that an optimal tetrahelix has the same radii for all three helices.
-To do this exhibit a symmetric tetrahelix (not yet shown to be optimal) which
-happens to be a tetrahelix, that has
-the property that all rail edges are equal to all one-hop edges and all two-hop
-edges are equal. Observe that although we have not get given the formula for the
-radii of such a triple helix, we observe there are some values for $r$ and $\alpha$
-for which this is true from this generic formula for a triple helix:
-\[
+Now that we have show that axes are conincident and parallel and that the pitches
+are the same for all helices, we can assert that any optimum tetrahelix can
+be generated with an equation for helices:
+\begin{equation}
 \label{eq:triple}
@@
   \begin{tabular}{c}
-   $ r \cos(n \alpha +  c 2 \pi /3)$\\
-   $ r \sin(n \alpha +  c 2 \pi /3) $\\
+   $ r_c \cos(n \alpha +  c 2 \pi /3 + \phi_c)$\\
+   $ r_c \sin(n \alpha +  c 2 \pi /3 + \phi_c) $\\
    $ \frac{d(n +c / 3)}{3}   $
@@
   \end{tabular}      
-\]
-In \cref{sec:parameterizing} we show how to find $r$ and $\alpha$.
-
-In principle in any 3 helices with the same axis of the same radius
-having any relative
-displacement along the $z$ axis there are 9 distinct edge classes.
+\end{equation}
+Note that we have not yet show that the relationships of the radius $r$ or
+the phase $\phi$ for the three helies, so we denoted them with a $c$ subscript to show
+they are dependent on the color.
+In \cref{sec:parameterizing} we give a more specific version of this formula which
+is optimal.
+
+In principle in any three helices generated with $\cref{eq:triple}
+has at most nine distinct edge length classes. Each edge that connects
+two rails potentially has a longer length and shorter length we donote with
+a $+$ or $-$. So the classes are $\{$ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
 If when projecting all vertices on the the $z$-axis, the interval
@@
 Then there are 
-3 rail edges, 3 one-hop lengths between each pair of 3 rails, and 3 two hop
-lengths between each pair of 3 rails, where the two-hop length is at least
-the one-hop length.
+3 rail edges $\{$ RR, BB, YY\}$,
+3 one-hop lengths $\{$ RB_-, BY_-, RY_- \}$ between each pair of 3 rails,
+and 3 two-hop
+lengths $\{$ RB_+, BY_+, RY_+, \}$ between each pair of 3 rails,
+where the two-hop length is at least the one-hop length.
 However, if we generate the three helices symmetrically with \cref{eq:triple},
 many of these lengths will be the same.
+In fact, it is possible that there
+will be only two distinct such classes.
+
+Now we show that an optimal tetrahelix has the same radii for all three helices.
+To do this exhibit a symmetric tetrahelix (not yet shown to be optimal) which
+happens to be a triple helix, that has
+the property that all rail edges are equal to all one-hop edges and all two-hop
+edges are equal. 
+Observe that although we have not get given the formula for the
+radii of such a triple helix, we observe there are some values for $r$ and $\alpha$, and $\phi$
+for which all the three helices are symmetrically and evenly spaced. Furthermore,
+we can choose these values such that the three rail edges are of length unity and
+so that the one-hop lengths are also all of length unity, and the two-hop lengths
+are slightly longer. We call such a tetrahelix a two-class tetrahelix.
 
@@
 Likewise, a helix with a smaller radius decreases a one-hop edge without decreasing
-a two-hop edge.  Therefore, a tetrahelix with different radii is not as some
-tetrahelix generated by \cref{eq:triple}, and so it not optimal. (Note however,
-that we have not yet exhibited a truly optimal tetrahelix, nor proven that such
-a tetrahelix occurs when the one-hop edge, length is equal to the rail edge length,
-which we do in \cref{sec:parameterizing}.)
-
-Because an optimal tetrhelix has equivalent radii for all three helices,
-it has equivalent rail edge lengths.
+a two-hop edge.  Therefore, a tetrahelix with different radii is not optimal as some two-class 
+tetrahelix generated by \cref{eq:triple}, and so it not optimal. We have not yet
+proved that a two-class tetrahelix is optimal, but it suffices to show that there
+exist such a better tetrahelix to show that different radii imply a suboptimal
+tetrahelix.
+
+Because an optimal tetrhelix has equivalent radii and equivalent pitch for all three helices,
+it has equivalent rail edge lengths. Likewise, there is a single rail angle $\rho$ that
+represents the rotation of two nodes connected by a single rail edge, and it is the same
+for all three rails.
 
@@
 of any optimal tetrahelix will lie on a cylinder, or a circle when axis dimension
-is projected out. Therefore it is reasonable to now speak of the \emph{radius} $r$
-of a tetrahelix as the radius of the cylinder, as distinct from the inradius $r_{in}$.
-
-Now that we have coincident axes, the same pitch, and the same radius, we can go on to
+is projected out. Therefore it is reasonable to now speak of the singular \emph{radius} $r$
+of a tetrahelix as the radius of the cylinder.
+We can now go on to
 the harder proof about where vertices occur along the $z$-axis.
@@
 
-    As each helix is congruent to the others and shares an axis and are evenly spaced,
-    an optimal tetrahelix is a \emph{triple helix}.
 \end{proof}
@@
 
-By \cref{eventhirds} we are justified renaming \cref{eq:triple} ``optimal'':
-\[
-V_{optimal}(n,c) =
-\left [
-  \begin{tabular}{c}
-   $ r \cos(n \alpha +  c 2 \pi /3)$\\
-   $ r \sin(n \alpha +  c 2 \pi /3) $\\
-   $ \frac{d(n +c / 3)}{3}   $
-  \end{tabular}
-  \right ],
-\text{where:}
-\begin{tabular}{c}
-  $c \in \{0,1,2\}$
-  \end{tabular}      
-\]
-where we have not yet investigated in the general case the relationships beteween
-$\alpha$, $r$, and $d$ in this formulation.
-However, we understand that when $\alpha = 0$, the helices are degenerate, having curvature of $0$, and
+In \cref{sec:parameterizing} have not yet investigated in the general case the relationships beteween
+$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple}.
+However, we observe that when $\alpha = 0$, the helices are degenerate, having curvature of $0$, and
 we have the equitetrabeam.
+
+Taking all of these results together, 
+each helix in an optimal tetrahelix is congruent to the others, shares an axis, is the same radius, and are evenly spaced
+axially.
+An optimal tetrahelix is therefore a \emph{triple helix}.
 
@@
 
+Since the axes are parallel, we may define the \emph{inradius}, represented by the letter $i$, of a
+tetrahelix to be the radius of the largest
+cylinder parallel to this axis that is surrounded by each tetrahelix and pentrated by no edge.
+
 If we look down the axis of an optimal tetrahelix as shown in \cref{axialview}, it happens that only one of the one-hop edges

### 2017-04-25 doc/TetrahelixUntwist.tex
puttting aside till gait working

@@
 In this paper we assume the length of a rail
-is always $1$ as a simplification. (We make the rail length a parameter in our JavaScript code in
+is always $1$ as a simplification, except in proofs concenring rail length.
+(We make the rail length a parameter in our JavaScript code in
 \url{https://github.com/PubInv/tetrahelix/blob/master/js/tetrahelix_math.js} \cite{readtetrahelix}.)
@@
 \end{equation}
+which would not be much more complicated if the axes where not coincident.
 Note that we have not yet show that the relationships of the radius $r$ or

### 2017-04-25 doc/TetrahelixUntwist.tex
improved photographs

@@
 
-In principle in any three helices generated with $\cref{eq:triple}
+In principle in any three helices generated with \cref{eq:triple}
 has at most nine distinct edge length classes. Each edge that connects
 two rails potentially has a longer length and shorter length we donote with
-a $+$ or $-$. So the classes are $\{$ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
+a $+$ or $-$. So the classes are $\{ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
 If when projecting all vertices on the the $z$-axis, the interval
@@
 Then there are 
-3 rail edges $\{$ RR, BB, YY\}$,
-3 one-hop lengths $\{$ RB_-, BY_-, RY_- \}$ between each pair of 3 rails,
+3 rail edges $\{ RR, BB, YY\}$,
+3 one-hop lengths $\{ RB_-, BY_-, RY_- \}$ between each pair of 3 rails,
 and 3 two-hop
-lengths $\{$ RB_+, BY_+, RY_+, \}$ between each pair of 3 rails,
+lengths $\{ RB_{+}, BY_+, RY_+, \}$ between each pair of 3 rails,
 where the two-hop length is at least the one-hop length.
@@
   \centering
-     \includegraphics[width=0.9\textwidth]{figures/GlussBotBC.jpg}
+     \includegraphics[width=0.9\textwidth]{figures/MedCantedCropped.png}
      \caption{Glussbot in relaxed, or BC helix configuration}
-     \includegraphics[width=0.9\textwidth]{figures/GlussBotEquitetrabeamCropped.jpg}
+     \includegraphics[width=0.9\textwidth]{figures/EquitetrabeamCropped.png}
      \caption{The Equitetrabream: Fully Untwisted Glussbot in Hexapod Configuration}

### 2017-05-08 proofmath.m
adding proofmath.m

@@ -1,0 +1,1 @@
+function retval = square(x)
retval = x .* x;
endfunction



fplot (@square, [1, 10]);

function retval = funky(g,r,rho)
a = ((1 .+ g) ./ 2).^2 .+ r.^2 .* (1 .- cos(rho .* (1 .+ g)));
disp(a);
b = g.^2 .+ r.^2 .* (1 .- cos(2 .* g .* rho));
disp(b);
retval = sqrt(a) .- sqrt(b);
endfunction

function retval = funky0(g,r) 
retval = funky(g,[0:0.2:10],1.3);
endfunction

fplot (@funky0, [0,2/3])

### 2017-05-09 doc/TetrahelixUntwist.tex
improved proof by switching to radius

@@
 three helices about the central axis.
-The glussbot\cite{readglussbot} (or Tetrobot)\cite{TetrobotBook} uses the regularity of
+The \\
+Glussbot\cite{readglussbot} (or Tetrobot)\cite{TetrobotBook} uses the regularity of
 this geometry to make a tentacle-like robot that can crawl like a slug
-or mollusc.  The Tetrobot uses mechanical actuators which can change their length, connected by special joints,
-such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint, or the CMS joint\cite{HamlinSandersonCMS}
+or mollusc.  These modular robot systems uses mechanical actuators which can change their length, connected by special joints,
+such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint in the case of the Glussbot, or the CMS joint\cite{HamlinSandersonCMS}, in the case of the Tetrobot,
 which allow many members to meet in a single point.
@@
 a $+$ or $-$. So the classes are $\{ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
-If when projecting all vertices on the the $z$-axis, the interval
+If when projecting all vertices onto (dropping the $x$ and $y$ coordinates) the $z$-axis, the interval
 defined by the $z$ axis value of its endpoints contains no other vertices,
@@
 and $\chi = -1$ for clockwise.
+%% I have to add here whether I am using a left-handed or right-handed coordinate
+%% system.
 
@@
 
-We would really like to know the partial derivative of the two-hop - one-hop with respect
-to the radius to be able to understand how to choose the radius to form the minimimax optimum.
+By definition of minimax edge length optimality, we are trying to minimize:
+\[
+\frac{\max{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}{\min{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}
+\]
+But since $\text{two-hop}(r) >= \text{one-hop}(r)$, this is equivalent to:
+\[
+ \frac{   \max \{1,\text{two-hop}(r)\}}
+      {   \min \{1,\text{one-hop}(r)\}}
+\]
+This quantity will be equal to one of:
+\[ \frac{\text{two-hop}(r)}{1},
+\frac{1}{\text{one-hop}(r)},
+\frac{\text{two-hop}(r)}{\text{one-hop}(r)}
+\]
+
+We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
+By inspection it seems likely that we will minize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
+to 1, but to be absolutely sure we must examine the partial derivative of the ratio
+ $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ in this range.
+
+Although complicated, we can use Mathematica to investigate
+the partial derivative of the $\text{two-hop}(r) - \text{one-hop}(r)$ with respect
+to the radius to be able to understand how to choose the radius to form the minimax optimum.
 
@@
 \begin{align*}
-  \text{two-hop} - \text{one-hop}  &= \sqrt{\frac{4}{9}  + r_{\rho}^2(g_{\rho}+ j_{\rho})}
-  - \sqrt{\frac{1}{9} +r_{\rho}^2(f_{\rho}+k_{\rho}) }
+  \frac{\text{two-hop}}{ \text{one-hop}}  &=
+  \frac{\sqrt{\frac{4}{9}  + r_{\rho}^2(g_{\rho}+ j_{\rho})}}
+       {\sqrt{\frac{1}{9} +r_{\rho}^2(f_{\rho}+k_{\rho}) }}
 \end{align*}
@@
 radius $r_{\rho}$ is always negative.
-Since the partial derivative of $\text{two-hop} - \text{one-hop}$ with respect to the
-radius $r_{\rho}$ is negative up until $\rho_{bc}$ where it is $0$, 
-we opitmize the overall minimax distance by choosing the largest radius
+Since the partial derivative of $\text{two-hop} / \text{one-hop}$ with respect to the
+radius $r_{\rho}$ is negative up until $\rho_{bc}$, this ratio goes down
+as the radius goes up, and 
+we optimize the overall minimax distance by choosing the largest radius
 up until one-hop $= 1$, the rail-edge length.
@@
 of the whole system as we increase the radius
-up to the point that the shorter, one-hop distance is equal to the rail-length ($1$).
+up to the point that the shorter, one-hop distance is equal to the rail-length, $1$.
 Therefore, to optimize the whole system so long as $\rho \leq \rho_{bc}$,
@@
 Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $0 \leq \rho \leq \rho_{bc}$.
+%% Add here references to these equations.
 \end{proof}
@@
 
-If we look down the axis of an optimal tetrahelix as shown in \cref{axialview}, it happens that only one of the one-hop edges
+If we look down the axis of an optimal tetrahelix as shown in \cref{axialview}, it happens that only
+the one-hop edges
 (rendered in purple in our software)
@@
 changing the length of the two-hop member, leaving the one-hop member
-and rail length equivalent within this continuum.\footnote{Before deriving Equation \eqref{eqrhoopt}, we created a continuum by
+and rail length equivalent within this continuum.\footnote{Before
+deriving Equation \eqref{eqrhoopt}, we created a continuum by
 using a linear interpolation between the optimal radius for the

### 2017-05-09 doc/TetrahelixUntwist.tex
diagram improvements

@@
 
-\title{Untwisting the Boerdijk--Coxeter Helix}
+\title{Untwisting the Boerdijk-Coxeter Helix}
 \author{Robert L. Read \email{read.robert@gmail.com}
@@
 \begin{abstract}
-  The Boerdijk--Coxeter helix (BC helix, or tetrahelix) is a
+  The Boerdijk-Coxeter helix (BC helix, or tetrahelix) is a
   face-to-face stack of regular tetrahedra forming a helical column.  Considering the edges of
@@
 \begin{keywords}
-  Boedijk--Coxeter helix, tetrahelix, robotics, tetrobot, unconventional robots,
+  Boedijk-Coxeter helix, tetrahelix, robotics, tetrobot, unconventional robots,
   structural engineering, mechanical engineering, tensegrity, variable-geometry truss
@@
 
-The Boerdijk--Coxeter helix\cite{coxeter1985simplicial} (BC helix), is
+The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix), is
 a face-to-face stack of tetrahedra that winds about a straight axis.
@@
          \end{bmatrix}$
-for a counter-clockwise BC Helix:
+for a counter-clockwise BC Helix in a right-handed coordinate system:
 \begin{equation}
@@
 
-The pitch of the Boerdijk--Coxeter helix of edge length $1$ is the length of three tetrahedra times this number:
+The pitch of the Boerdijk-Coxeter helix of edge length $1$ is the length of three tetrahedra times this number:
 \begin{align*}
@@
   \item have the same rail lengths,
-  \item have axialy equidistant nodes, and therefore
+  \item have axially equidistant nodes, and therefore
   \item are in fact triple helices.
@@
     So a tetrahelix is optimal only when $W(n) = 0$, and therefore when $D=0$
-    $B(n) = B'(n)$, all three axes are conincident.
+    $B(n) = B'(n)$, and all three axes are conincident.
 \end{proof}
@@
 they are dependent on the color.
+We have not yet investigated in the general case the relationships beteween
+$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple}.
 In \cref{sec:parameterizing} we give a more specific version of this formula which
-is optimal.
+generates optimal tetrahelices.
+However, we observe that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
+but because of the $\phi_c$ term, they are not collinear.
+
+\begin{figure}[H]
+  \centering
+     \includegraphics[width=0.95\textwidth]{figures/edge-diagram.png}
+     \caption{Edge Naming}
+  \label{fig:naming}
+\end{figure}
 
@@
 we call it a \emph{one-hop} edge, and if it does contain another vertex we
-call it a \emph{two-hop} edge.
+call it a \emph{two-hop} edge, as illustrated in \cref{fig:naming}.
 Then there are 
@@
 Now we show that an optimal tetrahelix has the same radii for all three helices.
-To do this exhibit a symmetric tetrahelix (not yet shown to be optimal) which
+To do this we exhibit a symmetric tetrahelix (not yet shown to be optimal) which
 happens to be a triple helix, that has
@@
 radii of such a triple helix, we observe there are some values for $r$ and $\alpha$, and $\phi$
+in \cref{eq:triple}
 for which all the three helices are symmetrically and evenly spaced. Furthermore,
@@
 Likewise, a helix with a smaller radius decreases a one-hop edge without decreasing
-a two-hop edge.  Therefore, a tetrahelix with different radii is not optimal as some two-class 
+a two-hop edge.  Therefore, a tetrahelix with different radii is not as good as some two-class 
 tetrahelix generated by \cref{eq:triple}, and so it not optimal. We have not yet
@@
     $d/3$ from each other.
-
 \end{proof}
@@
 \emph{two-hop}. The one-hop edges are the edges between rails that are closest on the $z$-axis, and the two-hop edges are those that skip over a vertex.
-
-In \cref{sec:parameterizing} have not yet investigated in the general case the relationships beteween
-$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple}.
-However, we observe that when $\alpha = 0$, the helices are degenerate, having curvature of $0$, and
-we have the equitetrabeam.
 
@@
 the parameter $\chi = 1$ to indicate a chirality of counter-clockwise,
-and $\chi = -1$ for clockwise.
-%% I have to add here whether I am using a left-handed or right-handed coordinate
+and $\chi = -1$ for clockwise. We take our coordinate system to be right-handed,
+following the convention of Three.js, our rendering software.
+%% TODO: I have to add here whether I am using a left-handed or right-handed coordinate
 %% system.
@@
   \label{generalformulaoptimal}
-  The tetrahelices generated by $H_{general}$ are optimal in terms of minimum maximum ratio of member length when $r_{\rho}$ is chosen so that
+  For rail angles of magnitude at most $\rho_{bc}$, tetrahelices generated by $H_{general}$ are optimal in terms of minimum maximum ratio of member length when radius is chosen so that
   the length of the one-hop edge is equal to the rail length.
@@
 \begin{align*}
-  \text{rail} &= dist(H_{general}(n,c,\rho,d_{\rho},r_{\rho}),H_{general}(n+1,c,\rho,d_{\rho}),r_{\rho})) = 1 \\
-  \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho},r_{\rho}),H_{general}(n,c+1,\rho,d_{\rho},r_{\rho}))  \\
-  \text{two-hop} &= dist(H_{general}(n,c,\rho,d_{\rho},r_{\rho}),H_{general}(n,c+2,\rho,d_{\rho},r_{\rho}))  \\  
+  \text{rail} &= dist(H_{general}(n,c,\rho,d_{\rho},r),H_{general}(n+1,c,\rho,d_{\rho}),r)) = 1 \\
+  \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho},r),H_{general}(n,c+1,\rho,d_{\rho},r))  \\
+  \text{two-hop} &= dist(H_{general}(n,c,\rho,d_{\rho},r),H_{general}(n,c+2,\rho,d_{\rho},r))  \\  
 \end{align*}
@@
 \begin{align*}
-  \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}),r_{\rho})  \\
-%%  \text{one-hop} &= dist(H_{general}(0,0,\rho,d_{\rho}),H_{general}(0,1,\rho,d_{\rho},r_{\rho}))  \\  
-%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r_{\rho}\sin(0) - r_{\rho}\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
-%%    (r_{\rho}\cos(0) - r_{\rho}\cos(\rho/3 + 1\cdot\frac{2\pi}{3}))^2} \\
-%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r_{\rho}\sin(\rho/3 + \frac{2\pi}{3}))^2  +
-%%    (r_{\rho} - r_{\rho}\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
-%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
-%%    r_{\rho}^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
+  \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}),r)  \\
+%%  \text{one-hop} &= dist(H_{general}(0,0,\rho,d_{\rho}),H_{general}(0,1,\rho,d_{\rho},r))  \\  
+%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r\sin(0) - r\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
+%%    (r\cos(0) - r\cos(\rho/3 + 1\cdot\frac{2\pi}{3}))^2} \\
+%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (0  - r\sin(\rho/3 + \frac{2\pi}{3}))^2  +
+%%    (r - r\cos(\rho/3 + \frac{2\pi}{3}))^2} \\
+%%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r^2\sin^2(\rho/3 + \frac{2\pi}{3})  +
+%%    r^2(1 - \cos(\rho/3 + \frac{2\pi}{3}))^2} \\
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r_{\rho}^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
-  \text{but: }  d_{\rho}^2 &= 1 - 4 r_{\rho}^2 (\sin( \rho / 2)^2 \text{ ...so we substitute:}\\
+  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
+  \text{but: }  d_{\rho}^2 &= 1 - 4 r^2 (\sin( \rho / 2)^2 \text{ ...so we substitute:}\\
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.  
-  \text{one-hop}  &= \sqrt{\frac{1}{9}  + r_{\rho}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
+  \text{one-hop}  &= \sqrt{\frac{1}{9}  + r^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.    
@@
 \begin{align*}
-  \text{two-hop}  &= \sqrt{\frac{4}{9} + r_{\rho}^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
+  \text{two-hop}  &= \sqrt{\frac{4}{9} + r^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
 \end{align*}
@@
 \]
-But since $\text{two-hop}(r) >= \text{one-hop}(r)$, this is equivalent to:
+But since $\text{two-hop}(r) \geq \text{one-hop}(r)$, this is equivalent to:
 \[
@@
 This quantity will be equal to one of:
-\[ \frac{\text{two-hop}(r)}{1},
+\begin{equation}
+  \frac{\text{two-hop}(r)}{1},
 \frac{1}{\text{one-hop}(r)},
 \frac{\text{two-hop}(r)}{\text{one-hop}(r)}
-\]
+\label{eq:ratioset}
+\end{equation}
 
 We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
-By inspection it seems likely that we will minize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
-to 1, but to be absolutely sure we must examine the partial derivative of the ratio
+By inspection it seems likely that we will minimize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
+to 1, but to be absolutely sure and to decide which one, we must examine the partial derivative of the ratio
  $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ in this range.
@@
 \begin{align*}
-  \frac{\text{two-hop}}{ \text{one-hop}}  &=
-  \frac{\sqrt{\frac{4}{9}  + r_{\rho}^2(g_{\rho}+ j_{\rho})}}
-       {\sqrt{\frac{1}{9} +r_{\rho}^2(f_{\rho}+k_{\rho}) }}
+  \frac{\text{two-hop}(r_{\rho})}{ \text{one-hop}(r_{\rho})}  &=
+  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ j_{\rho})}}
+       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+k_{\rho}) }}
 \end{align*}
@@
 By graph inspection using Mathematica, we see the partial derivative of this with respect to
-radius $r_{\rho}$ is always negative.
-Since the partial derivative of $\text{two-hop} / \text{one-hop}$ with respect to the
-radius $r_{\rho}$ is negative up until $\rho_{bc}$, this ratio goes down
+radius $r$ is always negative, for any $\rho \leq \rho_{bc}$. (When the rail angle approaches
+$\pi$, corresponding to going almost to the other side of the tetrahelix, this is not necessarily true, hence the
+limitation in our statement of the theorem is meaningful.)
+Since the partial derivative of $\text{two-hop}(r) / \text{one-hop}(r)$ with respect to the
+radius $r$ is negative for all $\rho$ up until $\rho_{bc}$, this ratio goes down
 as the radius goes up, and 
-we optimize the overall minimax distance by choosing the largest radius
-up until one-hop $= 1$, the rail-edge length.
+we minimize the maximum edge-length ratio by choosing the largest radius
+up until one-hop $= 1$, the rail-edge length. If we attempted to increase the radius further
+we would not be optimal, because the ratio $\frac{\text{two-hop}(r)}{1}$ would because the
+largest ratio in our set of ratios \cref{eq:ratioset}.
 
@@
 In a plane, the octet truss\cite{richard1961synergetic} is such a geometry, but in a line, the
-Boerdijk--Coxeter helix is a regular structure.
+Boerdijk-Coxeter helix is a regular structure.
 
@@
 
-** Try to show that rotation must be symmetric over possible rotation.
-
-** Try to show 2-hop > rail for any optimal.
+** Add a better diagram that explains the ``two-hop'', ``one-hop'' process.  - done
+
+** TODO: should I use vector notation for my formulae?  (yes!)
+
+** Improve rail geometry diagram by making bolder.
+
+** Add the Mathematica notebook to the github repo (after cleaning up) and reference.
 

### 2017-05-09 doc/TetrahelixUntwist.tex
some improvements

@@
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
+
+\renewcommand{\vec}[1]{\mathbf{#1}}
 
@@
   \label{graycoxeter}
-V(n) =
+\vec{V}(n) =
 \left [
@@
 
-The apparent rotation of a vertex an outer-edge, $V(n)$ relative from $V(n+3)$ for any integer $n$
+The apparent rotation of a vertex an outer-edge, $\vec{V}(n)$ relative from $\vec{V}(n+3)$ for any integer $n$
 in \eqref{graycoxeter}, is $3 \theta_{bc} - 2\pi$).
@@
 \[
-(\forall n \in \mathbb{Z}, \forall c \in \{0,1,2\} : H_{BCcolored}(n,c) = V(3n +c))
+(\forall n \in \mathbb{Z}, \forall c \in \{0,1,2\} : \vec{H}_{BCcolored}(n,c) = \vec{V}(3n +c))
 \]
@@
   \label{eq:colored}
-H_{BCcolored}(n,c) =
+ \vec{H}_{BCcolored}(n,c) =
 \left [
@@
 
-The quantity $ (3 \theta_{bc} - 2 \pi) \approx 35.43 \degree $  is the angular shift between $V(3n + c)=H_{BCcolored}(n,c)$ and
-$V(3(n+1)+c)=H_{BCcolored}(n+1,c)$.
+The quantity $ (3 \theta_{bc} - 2 \pi) \approx 35.43 \degree $  is the angular shift between
+$ \vec{V}(3n + c)= \vec{H}_{BCcolored}(n,c)$ and
+$ \vec{V}(3(n+1)+c)= \vec{H}_{BCcolored}(n+1,c)$.
 This quantity appears so often that we call it the ``rail angle $\rho$''. For the BC helix, $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$.
@@
 
-The $H_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho_{bc}$ rather than $\theta_{bc}$.
+The $\vec{H}_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho_{bc}$ rather than $\theta_{bc}$.
 Intuitively we seek an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
@@
 \begin{equation}
-H_{BCcolored}(n,c) =
+\vec{H}_{BCcolored}(n,c) =
 \left [
@@
 From this formulation it is easy to see that moving one vertex on a rail
-($H_{BCcolored}(n,c)$ to $H_{BCcolored}(n+1,c)$ for any $n$ and $c$)
+($\vec{H}_{BCcolored}(n,c)$ to $\vec{H}_{BCcolored}(n+1,c)$ for any $n$ and $c$)
 moves us $\rho_{bc}$ radians around a circle. Since:
@@
   has an edge connection to the Red helix that is either a maximum or a minimum.
-  Let $B'$ be the blue helix translated in the $XY$-plane so that its axis is the $z$-axis and
+  Let $\vec{B'}$ be the blue helix $\vec{B}$ translated in the $XY$-plane so that its axis is the $z$-axis and
   condicent with the red helix $R$. Let $D$ be the distance between the axis of the Blue helix
-  $B$ and $B'$. We will show that if $D>0$ then $B$ ``wobbles'' in a way that cannot be optimal.
+  $\vec{B}$ and $\vec{B'}$. We will show that if $D>0$ then $\vec{B}$ ``wobbles'' in a way that cannot be optimal.
   Define a wobble vector by:
   \begin{equation*}
-    W(n) = B(n) - B'(n)
+    \vec{W}(n) = \vec{B}(n) - \vec{B}'(n)
   \end{equation*}
-  where $B(n)$ is the cartesian vector
+  where $\vec{B}(n)$ is the cartesian vector
   $\begin{bmatrix}
@@
   for the projection of the $n$th blue vertex.
-  Note that $|| R(n) - B'(n+k)||$ is a constant for any $k$, because $R$ and $B'$ have the
+  Note that $|| \vec{R}(n) - \vec{B'}(n+k)||$ is a constant for any $k$, because $R$ and $B'$ have the
   same pitch and the same axis, even if they do not have the same radius
@@
   an n-gon in the $XY$-plane, where $n$ is at least 3 (when $\rho = 2\pi/3$).
-  The set of wobbles $\{W(n) | \text{for any n}\}$ thus contains at least three vectors,
+  The set of wobbles $\{\vec{W}(n) | \text{for any n}\}$ thus contains at least three vectors,
   pointing in different directions.
@@
     The set of all lengths in the tetrahelix is a superset of:
-    $L = \{|| R(n) - B(n)||\}$, which by our choice has at least one longest or shortest
+    $L = \{|| \vec{R}(n) - \vec{B}(n)||\}$, which by our choice has at least one longest or shortest
     length.
-    $L = \{|| R(n) - (B'(n) + W(n))||\}$ and so
-    $L = \{|| (R(n) - B'(n)) - W(n)||\}$.
-    But $R(n) - B'(n)$ is a constant, so the minimax value of $L$ is improved as $||W(n)||$
+    $L = \{|| \vec{R}(n) - (\vec{B'}(n) + \vec{W}(n))||\}$ and so
+    $L = \{|| (\vec{R}(n) - \vec{B'}(n)) - \vec{W}(n)||\}$.
+    But $\vec{R}(n) - \vec{B'}(n)$ is a constant, so the minimax value of $L$ is improved as $||\vec{W}(n)||$
     decreases.  
@@
     This process can be carried out on both the Blue and Yellow helices
-    (perhaps simultaneously) until $W(n)$ is
+    (perhaps simultaneously) until $\vec{W}(n)$ is
     zero for both, finding a tetrahelix of improved overall minimax value at each step.
-    So a tetrahelix is optimal only when $W(n) = 0$, and therefore when $D=0$
-    $B(n) = B'(n)$, and all three axes are conincident.
+    So a tetrahelix is optimal only when $\vec{W}(n) = 0$, and therefore when $D=0$
+    $\vec{B}(n) = \vec{B'}(n)$, and all three axes are conincident.
 \end{proof}
@@
 \label{eq:triple}
-V_{triple}(n,c) =
+\vec{V}_{triple}(n,c) =
 \left [
@@
 The green edges are the two-hop edges and the purple edges are the one-hop edges. Note that the green
-edges are slightly longer than the purple edges.
+edges are slightly longer than the purple edges. In \ref{fig:naming}, which depicts the BC helix,
+the two-hop and one-hop edges are of equal length (but the projection onto the $z$-axis, the
+axial length, of the two-hop edge is longer than the axial one-hop length.)
 
@@
 input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
-formed in the X,Y plane $\angle H(0,0) O H(0,1)$ projecting out the $z$
+formed in the X,Y plane $\angle \vec{H}(0,0) O \vec{H}(0,1)$ projecting out the $z$
 axis and sighting along the positive $z$ axis. In other words, $\rho$
@@
 \numberthis  \label{eq:general}  
-H_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) &= 
+\vec{H}_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) &= 
  \left [
@@
 
-$H_{general}$ forces the user to select three values: $\rho$, $r_{\rho}$, and $d_{\rho}$ satisfying \eqref{railangle}.
+$\vec{H}_{general}$ forces the user to select three values: $\rho$, $r_{\rho}$, and $d_{\rho}$ satisfying \eqref{railangle}.
 
@@
   \label{generalformulaoptimal}
-  For rail angles of magnitude at most $\rho_{bc}$, tetrahelices generated by $H_{general}$ are optimal in terms of minimum maximum ratio of member length when radius is chosen so that
+  For rail angles of magnitude at most $\rho_{bc}$, tetrahelices generated by $\vec{H}_{general}$ are optimal in terms of minimum maximum ratio of member length when radius is chosen so that
   the length of the one-hop edge is equal to the rail length.
@@
 \begin{align*}
-  \text{rail} &= dist(H_{general}(n,c,\rho,d_{\rho},r),H_{general}(n+1,c,\rho,d_{\rho}),r)) = 1 \\
-  \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho},r),H_{general}(n,c+1,\rho,d_{\rho},r))  \\
-  \text{two-hop} &= dist(H_{general}(n,c,\rho,d_{\rho},r),H_{general}(n,c+2,\rho,d_{\rho},r))  \\  
+  \text{rail} &= dist(\vec{H}_{general}(n,c,\rho,d_{\rho},r),\vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) = 1 \\
+  \text{one-hop} &= dist(\vec{H}_{general}(n,c,\rho,d_{\rho},r),\vec{H}_{general}(n,c+1,\rho,d_{\rho},r))  \\
+  \text{two-hop} &= dist(\vec{H}_{general}(n,c,\rho,d_{\rho},r),\vec{H}_{general}(n,c+2,\rho,d_{\rho},r))  \\  
 \end{align*}
@@
 \begin{align*}
-  \text{one-hop} &= dist(H_{general}(n,c,\rho,d_{\rho}),H_{general}(n,c+1,\rho,d_{\rho}),r)  \\
-%%  \text{one-hop} &= dist(H_{general}(0,0,\rho,d_{\rho}),H_{general}(0,1,\rho,d_{\rho},r))  \\  
+  \text{one-hop} &= dist(\vec{H}_{general}(n,c,\rho,d_{\rho}),\vec{H}_{general}(n,c+1,\rho,d_{\rho}),r)  \\
+%%  \text{one-hop} &= dist(\vec{H}_{general}(0,0,\rho,d_{\rho}),\vec{H}_{general}(0,1,\rho,d_{\rho},r))  \\  
 %%  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + (r\sin(0) - r\sin(\rho/3+1\cdot\frac{2\pi}{3}))^2  +
@@
 
-By graph inspection using Mathematica, we see the partial derivative of this with respect to
+By graph inspection using Mathematica (\url{https://github.com/PubInv/tetrahelix/blob/master/tetrahelix.nb}), we see the partial derivative of this with respect to
 radius $r$ is always negative, for any $\rho \leq \rho_{bc}$. (When the rail angle approaches
@@
 
-Just as $H_{general}$ constructs the BC helix (with careful and non-obvious choices of parameters)
+Just as $\vec{H}_{general}$ constructs the BC helix (with careful and non-obvious choices of parameters)
 which is an important
@@
   The equitetrabeam with minimal maximal edge ratio is produced
-  \newline by $H_{general}$ when $ r = \sqrt{\frac{8}{27}} $.
+  \newline by $\vec{H}_{general}$ when $ r = \sqrt{\frac{8}{27}} $.
 \end{corollary}
@@
 and therefore zero curvature and curvature) as mathematical or engineering objects,
-we have motivated the development of $H_{general}$ as a transformation of $V(n)$ defined by
+we have motivated the development of $\vec{H}_{general}$ as a transformation of $\vec{V}(n)$ defined by
 Equation \eqref{graycoxeter} from Gray and Coxeter. It is difficult to see how
-the $V(n)$ 
+the $\vec{V}(n)$ 
 formulation could ever give rise to a continuum producing the tetrabeam,
@@
  a smooth continuum where $\rho$ transitions from positive to negative
- which remains optimal. One can use a negative $\rho$ in $H_{general}$
+ which remains optimal. One can use a negative $\rho$ in $\vec{H}_{general}$
  but it does not produce minimax optimal tetrahelices. In other words,
@@
  becomes shorter than one-hop.) Likewise, $\rho > \rho_{bc}$ generates
- a tetrahelix, but minimax optimality is not guaranteed by $H_{general}$.
+ a tetrahelix, but minimax optimality is not guaranteed by $\vec{H}_{general}$.
 
@@
  However, it should
-be noted that an engineer or architect may also use $H_{general}$
+be noted that an engineer or architect may also use $\vec{H}_{general}$
 directly and interactively, and that minimax length optimality is a
@@
 including deployable and moving trusses\cite{claypool2012readily}.
+
+\begin{figure}[H] %float with two figures
+  \centering
+     \includegraphics[width=0.9\textwidth]{figures/MedCantedCropped.png}
+     \caption{Glussbot in relaxed, or BC helix configuration}
+     \includegraphics[width=0.9\textwidth]{figures/EquitetrabeamCropped.png}
+     \caption{The Equitetrabream: Fully Untwisted Glussbot in Hexapod Configuration}
+     \label{fig:glussbot}
+\end{figure}
 
@@
   7-tet Tetrobot/Glussbot.
-
-\begin{figure}[H] %float with two figures
-  \centering
-     \includegraphics[width=0.9\textwidth]{figures/MedCantedCropped.png}
-     \caption{Glussbot in relaxed, or BC helix configuration}
-     \includegraphics[width=0.9\textwidth]{figures/EquitetrabeamCropped.png}
-     \caption{The Equitetrabream: Fully Untwisted Glussbot in Hexapod Configuration}
-     \label{fig:glussbot}
-\end{figure}
 
@@
 
-** Add a better diagram that explains the ``two-hop'', ``one-hop'' process.  - done
-
-** TODO: should I use vector notation for my formulae?  (yes!)
-
-** Improve rail geometry diagram by making bolder.
-
 ** Add the Mathematica notebook to the github repo (after cleaning up) and reference.

### 2017-05-11 doc/TetrahelixUntwist.tex
spelling and other improvements

@@
   inherently rigid, and therefore interesting to architects,
-  mechanical engineers, and robotocists.  A formula is developed that matches the
+  mechanical engineers, and roboticists.  A formula is developed that matches the
   visually apparent helices forming the outer rails of the BC helix.
@@
 \begin{keywords}
-  Boedijk-Coxeter helix, tetrahelix, robotics, tetrobot, unconventional robots,
+  Boerdijk-Coxeter helix, tetrahelix, robotics, tetrobot, unconventional robots,
   structural engineering, mechanical engineering, tensegrity, variable-geometry truss
@@
 a face-to-face stack of tetrahedra that winds about a straight axis.
-Because architects, structural engineers, and robotocists are inspired
+Because architects, structural engineers, and roboticists are inspired
 by and follow such regular mathematical models but can also build structures and
@@
 Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
-a term now commonly used. In this paper we reserve \emph{BC helix} to mean the purely regular structre and use \emph{tetrahelix} to refer
+a term now commonly used. In this paper we reserve \emph{BC helix} to mean the purely regular structure and use \emph{tetrahelix} to refer
 to any structure isomorphic to the BC helix.
@@
 we observe that it is useful to the mechanical engineer or
-robotocist because the structure remains an inherently rigid,
+roboticist because the structure remains an inherently rigid,
 omni-triangulated space frame, which is
@@
 
-In this formula, integral values of $n$ may be taken as a node number for one rail and used to compute its Cartesian
+In this formula, integral values of $n$ may be taken as a node number for one rail and used to compute
+its Cartesian
 coordinates. Allowing $n$ to take non-integer values defines a continuous
-helix in space which is close to the segmented polyline of the outer tetrahedra edges, and equals them at integer
+helix in space which is close to the segmented polyline of the outer
+tetrahedra edges, and equals them at integer
 values.
@@
 in fact the same geometry as the robot illustrated in \cref{fig:glussbot}.
-Although the nodes conincide,
+Although the nodes coincide,
 \cref{graycoxeter} evaluated
@@
 We expand 
-the expressions $\theta_{bc}$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c2\pi/3 $.
+the expressions $\theta_{bc}$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c 2\pi/3 $.
 \begin{align*}
@@
 
-We use the term \emph{tetrahelix} to mean any structure made of
-vertices and edges which is isomorphic to the BC helix and in which the
-vertices lie on three helices. We further demand that all edge lengths
-be finite, as we are only interested in physically constructable tetrahelices.
+We use the term \emph{tetrahelix} to mean any structure physically constructible of
+vertices and finite edges which is isomorphic to the BC helix and in which the
+vertices lie on three helices.
 By isomporphic we mean there is a one-to-one mapping between both
@@
 One could consider various definitions of optimality for a
-tetrahelix, but the most useful to us as robotocists working with the Tetrobot
+tetrahelix, but the most useful to us as roboticists working with the Tetrobot
 concept is to minimize the
@@
 
-%% Since all three rails have the same rail edge length, no matter how we
-%% move the rails in the $xy$ plane if we shorten the $xy$ distance between
-%% vertices we shorten the total distance.
-%% Our tool for thinking about this is to collapse the $z$ dimension to form
-%% a two-dimensional figure of nodes and non-rail edges (see \cref{fig:wobble}.)
-%% Consider the projection along the $z$ axis of all vertices and non-rail edges into the $xy$ plane, which will be
-%% a figure of dots and connecting segments in the $xy$ plane. The convex
-%% hull for any one helix projection will be a circle (if its pitch is
-%% irrational) or a polygon if rational, or a point if the helix has
-%% zero curvature. Each of these figures by definition lies outside the
-%% circle of inradius $r_{in}$ in the $xy$ plane.
-
 As a little lemma for the proof below, observe that a tetrahelix of zero radius, where
@@
 rails.
+
+In the proof below we find useful to consider projection diagrams that are the axial projection
+of a tetrahelix onto the $XY$-plane. \Cref{fig:projectionDiagram.png} is an example of such a diagram.
+\begin{lemma}
+  If the rail angle $0 < \rho < \pi$ is a rational multiple of $\pi$, then the projection of
+  edges long a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
+  regular polygon of 3 or more sides, else they form a circle.
+  \label{lemma:ngon}
+\end{lemma}
+\begin{proof}
+  All points lying on a helix projected along the axis lie on a circle in the $XY$-plane.
+  Helices are periodic in the $z$ dimension modulo $2\pi$.
+  If $2\pi/\rho$ is irrational, the projection onto the $XY$-plane will contain
+  an unbounded number of points on a circle.
+  Because $\pi$ is transcendental and irrational,
+  $2\pi/\rho$ is rational if and only $\rho = a\pi/b$, where $a$ and $b$ are integers.
+  Since $\rho < \pi$, $a < b$, and since $\rho > 0$, $a > 0$.
+  If and only if $2\pi/\rho$ is rational, the projection onto
+  the $XY$-plane will contain a finite number of points.
+  The number of points in the projection is $2b$ if $a$ is odd, and $b$ if $a$ is even.
+  This polygon has at least 3 sides, since either either $\rho$ is irrational or $b > a$, and therefore
+  $b >= 2$. If $a/b = 1/2$, the projection is a square, which has four sides. 
+\end{proof}
 
@@
 \begin{proof}
-  Case 1: Suppose that $\rho$ is zero. Then for any given inradius, the
-  figure in the $XY$-plane of an equilateral
-  triangle is the minimax solution for all non-rail edges. Since all
-  rail edges are of length 1, this is the minimax solution for the entire set. Since
-  the vertices of an equilateral triangle lie on a circle, all points in three-space lie on
-  a cylinder.
+  Case 1: Suppose that $\rho$ is zero.
+  Each helix has zero curvature, that is, is a straight line. These lines are eqivalent
+  to some three helices, possibly with different radii, so long as there is a phase
+  term in the defintion of the helix, as in \eqref{eq:colored}. We later show the
+  radii must be eqivalent.
 
@@
   Without loss of generality define the Red helix to have its axis on the $z$-axis.
-  Without loss of generatlity define the Blue helix to be a helix that
+  Since either a Red-to-Yellow or a Red-to-Blue edge is either a minimum or a maximum,
+  without loss of generatlity define the Blue helix to be a helix that
   has an edge connection to the Red helix that is either a maximum or a minimum.
-  Let $\vec{B'}$ be the blue helix $\vec{B}$ translated in the $XY$-plane so that its axis is the $z$-axis and
-  condicent with the red helix $R$. Let $D$ be the distance between the axis of the Blue helix
-  $\vec{B}$ and $\vec{B'}$. We will show that if $D>0$ then $\vec{B}$ ``wobbles'' in a way that cannot be optimal.
+  Let $B'$ be a translation in the $XY$-plane of the blue helix $B$  so that its axis is the $z$-axis and
+  conincident with the red helix $R$. Let $D$ be the distance between the axis of the Blue helix
+  $B$ and $B'$. We will show that if $D>0$ then $B$ ``wobbles'' in a way that cannot be optimal.
   Define a wobble vector by:
@@
   \end{equation*}
-  where $\vec{B}(n)$ is the cartesian vector
+  where $\vec{B}(n)$ and $\vec{B'}$ is the cartesian vector
   $\begin{bmatrix}
@@
   \end{bmatrix}$
-  for the projection of the $n$th blue vertex.
-  Note that $|| \vec{R}(n) - \vec{B'}(n+k)||$ is a constant for any $k$, because $R$ and $B'$ have the
-  same pitch and the same axis, even if they do not have the same radius
-  (which we are currently proving.)
+  for the projection of the $n$th vertex of $B$ and $B'$. 
+  Note that $|| \vec{R}(n) - \vec{B'}(n+k)||$ (the Euclidean distance of the vertices)
+  is a constant for any $k$, because $R$ and $B'$ have the
+  same pitch and the same axis, even if they do not have the same radius.
 
@@
 
-  Since $-\pi<\rho<\pi$, each rail helix rotates about its axis as a function of $n$ and
-  defines at least 3 unique points when projected onto the $XY$-plane around its axis.
-  If $2\pi/\rho$ is irrational, it defines a circle. If $2\pi/\rho$ is rational it defines
-  an n-gon in the $XY$-plane, where $n$ is at least 3 (when $\rho = 2\pi/3$).
-  The set of wobbles $\{\vec{W}(n) | \text{for any n}\}$ thus contains at least three vectors,
+  Since $\rho < \pi$ by assumption, by $\cref{lemma:ngon}$,
+  the set of wobbles $\{\vec{W}(n) | \text{for any n}\}$
+  contains at least three vectors,
   pointing in different directions.
@@
     $L = \{|| \vec{R}(n) - \vec{B}(n)||\}$, which by our choice has at least one longest or shortest
-    length.
+    length. (Note this is just the Euclidean distance formula written as a Euclidean norm.)
     $L = \{|| \vec{R}(n) - (\vec{B'}(n) + \vec{W}(n))||\}$ and so
@@
     decreases.  
-    By our choice, this improves the minimax value of the total tetrahelix.
+    By our choice that their is a Blue-to-Red edge that is either a maximum or a minimum,
+    this improves the minimax value of the total tetrahelix.
 
@@
 a $+$ or $-$. So the classes are $\{ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
-If when projecting all vertices onto (dropping the $x$ and $y$ coordinates) the $z$-axis, the interval
+If when projecting all vertices onto the $z$-axis (dropping the $x$ and $y$ coordinates), the interval
 defined by the $z$ axis value of its endpoints contains no other vertices,
@@
 
-Now we show that an optimal tetrahelix has the same radii for all three helices.
-To do this we exhibit a symmetric tetrahelix (not yet shown to be optimal) which
+\begin{theorem}
+  Optimal tetrahelices have the same radii for all three helices.
+\end{theorem}
+\begin{proof}
+To prove this we exhibit a symmetric tetrahelix (not yet shown to be optimal) which
 happens to be a triple helix, that has
@@
 tetrahelix.
+\end{proof}
 
@@
 
-%% \begin{theorem}
-%%   \label{thm:cylinder}
-%%   Any optimal tetrahelix with a rail angle less than $\pi$ has all vertices on a single cylinder.
-%% \end{theorem}
-
-%% \begin{proof}
-
-%% Case 1: Suppose that $\rho$ is zero. Then for any given inradius, an equilateral
-%% triangle is the minimax solution for all non-rail edges. Since there is only
-%% one rail-edge length, this is the minimax solution for the entire set. Since
-%% the vertices of an equilateral triangle lie on a circle, all points lie on
-%% a cylinder.
-
-%% Case 2: Suppose that $\rho$ is positive but less than $\pi$.
-%% In this case each rail helix has
-%% curavature and places points on both sides of any line through its axis.
-
-%% We first show that the inradius is touched by one segment from each pair
-%% of rails.
-
-%% \begin{figure}[H]
-%%      \centering
-%%      \includegraphics[width=0.7\textwidth]{figures/UntouchingRail.png}
-%%      \caption{Untouching Rail}
-%%   \label{untouchingrailfig}
-%% \end{figure}
-
-%% \Cref{untouchingrailfig} depicts a projection of
-%% only the point $P$, the point $P'$ which is an adjacent vertex on the same rail,
-%% and the intermediary points $R$ and $Q$ on the other two rails.
-
-%% Supoose there is a rail $P$ which does not have a segment touching the incircle
-%% at all in the projection, as depicted in \cref{untouchingrailfig}.
-%% Then a segment connecting the other two $Q$ and $R$ is a longest
-%% rail, because any chord touching an incircle is longer than any which does not.
-%% These two rails ($Q$ and $R$) can be moved closer to each other, and further away from $P$,
-%% to form a better minimax solution
-%% by shortening the longest rail, until one of the segments from $P$, the previously
-%% untouching rail, touches the incircle. By induction, then all rails have
-%% at least one segement touching each vertex on the rail that is tangent to the
-%% incircle in an optimal tetrahelix.
-
-%% Now suppose that you attempt to move the axis of one of the rails away from the center
-%% for our circle. Because
-%% $\rho > 0 $ and $\rho$ is not a multiple of $\pi$, there is some vertex on the two sides of any diameter
-%% halving our circle. Moving the axis of a tetrahelix lengthens a longest line while ``pinching'' the
-%% inradius on the other side, so it is not optimal. Since the axes of these helices are the
-%% same and they have the same curvature and pitch, the points defined by the helices all lie
-%% on a cylinder.
-%% \end{proof}
-
-%% Note: This is not a proof that they have the same radius, I will have to add that.
-
 Now that we have shown that any optimal tetrahelix vertices
 are on helices of the same axes and pitch, we see that the vertices 
-of any optimal tetrahelix will lie on a cylinder, or a circle when axis dimension
+of any optimal tetrahelix will lie on a cylinder, or a circle when the axis dimension
 is projected out. Therefore it is reasonable to now speak of the singular \emph{radius} $r$
@@
  along the $z$-axis, as in fact they are in the regular BC helix.
-
- Note that from the point of view of a single edge, we are on a
- slanted cylinder, when $\rho \neq 0$.  This means from its point of
- view a cross section is an ellipse. So we have to be very careful in
- comparing lengths of edges relative to the tetrahedron, because a
- change in position along the edge changes the length of a line, but
- in a complicated way depending on where it is relative to the
- ellipse.
 
@@
 \begin{proof}
-    Consider the tetrahelix in which the vertices are evenly spaced at
+    Consider a tetrahelix in which the vertices are evenly spaced at
     $d/3$ intervals on the $z$ axis. Every edge is either a rail edge,
@@
 
-    Any attempt to move any rail in either $z$ direction lengthens one two-hop edge to $t'$, where $t' > t$
-    and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be new edges.
+    Any attempt to perturb any rail in either $z$ direction lengthens one two-hop edge to $t'$, where $t' > t$
+    and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be the edge lengths of such a
+    perturbed tetrahelix.
     The minimax of $B$ is greater than the minimax of $A$ since there is a single rail length which cannot be both greater
@@
 axially.
-An optimal tetrahelix is therefore a \emph{triple helix}.
+An optimal tetrahelix is therefore a \emph{triple helix}, (of a radius we have not yet demonstrated.)
 
@@
 the parameter $\chi = 1$ to indicate a chirality of counter-clockwise,
-and $\chi = -1$ for clockwise. We take our coordinate system to be right-handed,
-following the convention of Three.js, our rendering software.
-%% TODO: I have to add here whether I am using a left-handed or right-handed coordinate
-%% system.
+and $\chi = -1$ for clockwise. We take our coordinate system to be right-handed.
 
@@
   \label{generalformulaoptimal}
-  For rail angles of magnitude at most $\rho_{bc}$, tetrahelices generated by $\vec{H}_{general}$ are optimal in terms of minimum maximum ratio of member length when radius is chosen so that
+  For rail angles of magnitude at most $\rho_{bc}$, tetrahelices generated by
+  $\vec{H}_{general}$ are optimal in terms of minimum maximum ratio of member
+  length when radius is chosen so that
   the length of the one-hop edge is equal to the rail length.
@@
 \begin{proof}
-This is proved by a minimax argument.
-
 By \cref{eventhirds}, we can compute the (at most) three edge-lengths of an optimal
@@
 \begin{align*}
-  \text{rail} &= dist(\vec{H}_{general}(n,c,\rho,d_{\rho},r),\vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) = 1 \\
-  \text{one-hop} &= dist(\vec{H}_{general}(n,c,\rho,d_{\rho},r),\vec{H}_{general}(n,c+1,\rho,d_{\rho},r))  \\
-  \text{two-hop} &= dist(\vec{H}_{general}(n,c,\rho,d_{\rho},r),\vec{H}_{general}(n,c+2,\rho,d_{\rho},r))  \\  
-\end{align*}
-where $dist$ is the Cartesian distance function.
-
-\begin{align*}
-  \text{one-hop} &= dist(\vec{H}_{general}(n,c,\rho,d_{\rho}),\vec{H}_{general}(n,c+1,\rho,d_{\rho}),r)  \\
+  \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || = 1 \\
+  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \\
+  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \\  
+\end{align*}
+This syntax just represents the Euclidean distance formula.
+
+\begin{align*}
+  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho}) - \vec{H}_{general}(n,c+1,\rho,d_{\rho}),r) || \\
 %%  \text{one-hop} &= dist(\vec{H}_{general}(0,0,\rho,d_{\rho}),\vec{H}_{general}(0,1,\rho,d_{\rho},r))  \\  
@@
 Although complicated, we can use Mathematica to investigate
-the partial derivative of the $\text{two-hop}(r) - \text{one-hop}(r)$ with respect
+the partial derivative of the $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ with respect
 to the radius to be able to understand how to choose the radius to form the minimax optimum.
@@
 \begin{align*}
-  \frac{\text{two-hop}(r_{\rho})}{ \text{one-hop}(r_{\rho})}  &=
+  \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
   \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ j_{\rho})}}
@@
 
-The curvature of a rail helix is foramlly given by:
+The curvature of a rail helix is formally given by:
 \begin{equation}
@@
      \includegraphics[width=0.9\textwidth]{figures/EquitetrabeamCropped.png}
-     \caption{The Equitetrabream: Fully Untwisted Glussbot in Hexapod Configuration}
+     \caption{The Equitetrabeam: Fully Untwisted Glussbot in Hexapod Configuration}
      \label{fig:glussbot}
@@
 transmutations of these geometries, which was in fact the motivation
-for creating the equitetrabream.
+for creating the equitetrabeam.
 
@@
 crossing the outside rails after hopping over the nearest
-vertex. Under the condition of miminum maximum length ratios of
+vertex. Under the condition of minimum maximum length ratios of
 all members in the system, all such tetrahelices have vertices evenly
@@
 changing the length of the appropriate members to achieve any point in
-the continuum. With a numeric solution, a design may choose
+the continuum. With a numeric solution, a designer may choose
 a rotation angle and member lengths to obtain a desired pitch.
@@
 
-** Add the Mathematica notebook to the github repo (after cleaning up) and reference.
+** Add the Mathematica notebook to the github repo (after cleaning up) and reference. -- done
+** Redo the proof
+** make sure our diagrams are right-handed.
 
@@
 Reread everything, especially the new parts.
-
-Proof Ideas:
-
-Now that we have shown parallel and conincident, we can definie ``one-hop'' and ``two-hop''
-clearly.
-
-Can we show that one-hop < two-hop in an optimal tetrahelix?
-
-This is true by definition, but we potentially have 6 such differences.
-If all are less than the maximum rail edge, we are not optimal, as a lower rail edge
-is better.
-If all are > than the minimum rail edge, we are not opitimal, as we can raise that
-rail edge.
-
-So MAX(non-rail) >= MIN(rail-edge).
-also: MIN(non-rail) <= MAX(rail).
-
-Conjecture: Increasing Radius increases length of all attached nodes.
-Lemma: If a line is drawn between a point P on one circule and a point Q on a nother circle,
-and the circles are parallel in space,
-increasing the radius of eitehr circle increases the length, no matter where the circles are,
-and no matter where the points are on the circle.
-
-Therefore if there is a single maximum radius and it has a longest edge coming to it,
-the minimax is made better by decreasing that radius until equal with the next radius.
-
-If a single radius is a shortest radius, the minimax is made better by
-increasing it.
-
-Can we proe this rigourously?
-
-Does a single large radius necessarily have a longest edge?
-A Rail edge would be longest if we allow any rotation, but we can severely
-limit rail angle to \rho_{bc}.
-
-New Idea:
-
-Suppose Red is a largest radius.  Blue and Yellow must be symmetrically distributed
-ccw and cw from Red.
-
-Proof sketch: if Red is a largest radius, the two-hop edges to Yellow and Blue
-are the longest two in the system.  Is one is longer than that other, rotating it
-is more optimum.
-
-Proof Idea:
-
-If two-hop edges are always longest and one-hop always shortest, then they
-should be equalized.
-
-* * *
-
-Proof idea.
-
-Thm: An optimal tetrahelix has a longest edge which is a two-hop edge.
-
-Proof:
-
-Case 1: If the longest edge is a rail edge, construct a better minimax optimal
-tetrahelix by increasing the radius of every helix, which does not change the
-rail length, until a non-rail edge is equal to the rail edge.  This increases
-the length of every non-rail edge, therefore it is a better helix.
-
-Case 2: The longest edge is a non-rail edge.
-
-WOLOG, this is an edge from Red to Blue. By assumption, at least one
-of three things must be true:
-1) The RED-BLUE 2-hop axial distance is longer than the other two 2-hop axial distances.
-2) One rail (call it Red) has a larger radius.
-3) The Red-Blue rails can be rotated closer together to decrease the
-RED-BLUE distance. (If the angle between RED and BLUE is zero, then one
-of the other must be true.)
-
-In case 1), construct a better tetrahelix axially shifting the BLUE rails to decrease
-the RED-BLUE 2-hop axial distance (and increase the 2-hop axial distance.) The effects
-our classes by:
-RR not affected
-BB not affected
-YY not affected
-RB- increased
-RB+ decreased
-BY- decreased
-BY+ increased
-RY- not affected
-RY+ not affected
-
-So if the set of shortest edges does not include BY-, this tetrahelix is better.
-If it does include BY-, we must show that RB+/BY- decreases as we move the rail.
-We could show the actual derivative of this.  Informally, the angle is more direct,
-so the change in RB+ should be greater. This may require comparison to the cylindrical
-solution.  If we assume this is true for the cylindrical solution, then we have shown
-a better solution exists. So case one is not optimal.
-
-So we must show that if a shortest edge is in RY-, RY+, RB-, we have to
-RB+ of these edges decreases. RY+ cannot be a shortest edge.
-Idea: if RY-, RB- are shortest, increase Y, B radius.
-So what does the derivative of RB+/RY- and RB+/RB- tell us? The further away it is,
-the straighter the push, so it is likely that the RB+ edge changes faster than the RY- edge
-decreases. If R has a bigger radius, can RY- be smaller than BY-? Seems like we will
-have to use the algebraic formula to do this---but I have no proof yet that it is an triple helix.
-
-Note, that if we could prove just this case, our equidistance proof would complete everything we need!
-So I need to show that RB+/RY- decreases as we shrink the radius---in other words, the RB+ line
-is more central than the RY- line.
-
-In case 3), if we rotate blue towards red:
-
-RR not affected
-BB not affected
-YY not affected
-RB- decreases
-RB+ decreases
-BY- increases
-BY+ increases
-RY- not affected
-RY+ not affected
-
-Attempt to create Proof of Equal Radius:
-
-Suppose that Red Radius is largest.
-
-Case RB+ is longest:
-We can understand the change of decreasing the Red Radius:
-
-RR decreases
-BB not affected
-YY not affected
-RB- decreases
-RB+ decreases
-BY- not affected
-BY+ not affected
-RY- decreases
-RY+ decreases
-
-Sub Case split:
-Case RB- is smallest:
-Increase B radius.
-Case RY- is smallest:
-Increase Y radius.
-Case RR is smallest:
-This is not possible if Red is has the largest Readius!
-Case: RB- = RY-  are smallest.  In increase both B and Y.
-
-Done case RB+ is longest.
-
-Case YB+ is longest:
-
-This can occur only if YB is not even 1/3rds.
-
-Case:
-YB- is the worst. Then we need to move the bar.
-
-Case:
-Rail BB is smallest.  Then  we are making better.
-
-Case:
-RB- is smallest (need to move blue.)
-RY- is smallest (need to move yellow.)
-
-(I think this is a combined proof.)
-
-Case RB+ amd YB+ are both longest.
-
-RR decreases
-BB not affected
-YY not affected
-RB- decreases
-RB+ decreases
-BY- not affected
-BY+ not affected
-RY- decreases
-RY+ decreases
-
-Decrease R and simultaneously rotate Y towards B
-to decrease YB+.
-
-Done with case YB+ is longest.
-
-Case RR is longest:
-
-Decrease radius improves.
-
-Now suppose the Red and Blue Radiii are equual and larger than yellow.
-
-Case split RB+ is longest.
-
-Increase Y does:
-RR not affected
-BB not affected
-YY increases
-RB- not affected
-RB+ not affected
-BY- increases
-BY+ increases
-RY- increases
-RY+ increases
-
-Sub case split: Shortest not RR,BB, or RB- or RB+, then we improve.
-If it is a rail, decrease all radii until this is not true.
-
-RB-, then we need to move Red relative to Blue. If we are already
-at even thirds and proper rotation is this possible? This might require
-going down the algebra level to prove.
-
-Case split YB+ or YR+ is longest.
-
-New Proof Idea:
-
-Prove optimality of equal one-hop edges from simple diagram.
-From that, show optimality of equidistance and radius.
-
-New Proof Idea:
-
-Proof that all radii are the same.
-
-Lemma: There is a solution with all one-hop edges equal to all rail edges
-and all two-hop edges longer.
-
-Assume that the solution with all one-hop and rail distances the same
-is optimal.  Assume that all two-hop edges are the same.
-
-Any change to a radii either increases both or decreases both for
-one set, thereby harming the optimum.  Y cannot be rotated
-toward both Red and Blue. Y cannot be shifted toward both Red and Blue.
-(We need a lemma here that Red and Blue are on the opposite side or the
-line through the circle of Red.)
-Therefore any different radius has a longer two-hop edge, and is not optimal.
-
-If we have all radii the same, then our existing proof works for
-equidistance.

### 2017-05-11 doc/TetrahelixUntwist.tex
nearly final

@@
 
-The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix), is
+The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix) (see \cref{fig:closeup,fig:closuporthog}, is
 a face-to-face stack of tetrahedra that winds about a straight axis.
@@
 this geometry to make a tentacle-like robot that can crawl like a slug
-or mollusc.  These modular robot systems uses mechanical actuators which can change their length, connected by special joints,
+or mollusc.  These modular robotic systems use mechanical actuators which can change their length, connected by special joints,
 such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint in the case of the Glussbot, or the CMS joint\cite{HamlinSandersonCMS}, in the case of the Tetrobot,
@@
      \caption{BC Helix Close-up (partly along axis)}
+  \label{fig:closeup}     
+\end{figure}
+\begin{figure}[H]
   \centering
@@
      \caption{BC Helix Close-up (orthogonal)}
-  \label{fig:closeup}
+  \label{fig:closeuporthog}
 \end{figure}
 
-Imagining \cref{fig:closeup} as a static mechanical structure,
+Imagining \cref{fig:closeup,fig:closeuporthog} as a static mechanical structure,
 we observe that it is useful to the mechanical engineer or
@@
 mechanically strong.
-Imagine further in \cref{fig:closeup}, that each static edge was replaced with an
-actuator that could dynamically become shorter or longer in response to electronic control,
-and the vertices were a joint that supported sufficient angular displacement
+Then we can imagine that each static edge is replaced with an
+actuator that can dynamically become shorter or longer in response to electronic control,
+and the vertices are a joint that supported sufficient angular displacement
 for this to be possible. An example of such a machine is a glussbot, shown in \cref{fig:glussbot}.
@@
 design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix},
-from which \cref{fig:closeup} and
-the figures below are taken.
+from which \cref{fig:closeup,fig:closeuporthog,fig:series}
+are taken.
 
@@
 
-\Cref{fig:series} displays a continuum of tetrahelices optimal in a certain sense, which is the result of this
+\Cref{fig:series} displays a continuum of tetrahelices optimal in a certain sense,
+which is the main result of this
 paper. The closest helix is the BC helix, and the furthest
-is the equitetrabeam, defined in \cref{sec:equitetrabeam}.
+is the equitetrabeam, defined in \cref{sec:equitetrabeam} and \cref{fig:naming,fig:equitestrabeam}.
 
@@
 We would like to design nearly regular tetrahelices with a formula that
-gives the vertices in space. Eventually we would like to design nearly regular
-tetrahelices by choosing the lengths of a small set of members.
+gives the vertices in space. Eventually we would like to design them
+by choosing the lengths of a small set of members.
 In a space frame, this is a static design choice; in a tetrobot, it is a
@@
 any curvature or pitch we choose. It is a goal of
-this paper to relate these two approaches to generating a tetrahelix
-continuum.
+this paper to relate the Cartesian coordinate approach and the member-length approachx to
+generating a tetrahelix continuum.
 
@@
 
-R.W. Gray's site\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in more accessible form, gives the Cartesian coordinates $\begin{bmatrix}
+R.W. Gray's website\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in more accessible form, gives the Cartesian coordinates $\begin{bmatrix}
            x \\
@@
 
-The apparent rotation of a vertex an outer-edge, $\vec{V}(n)$ relative from $\vec{V}(n+3)$ for any integer $n$
+The apparent rotation of a vertex on an outer-edge, that is $\vec{V}(n)$ relative from $\vec{V}(n+3)$
+for any integer $n$
 in \eqref{graycoxeter}, is $3 \theta_{bc} - 2\pi$).
@@
 \]
-we can see that there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a single revolution.
+we can see that there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a
+complete revolution of the tetrahelix.
 
@@
 The pitch is less than the number of tetrahedra because the tetrahedra
-are not lined up perfectly.  It is a famous and interesting result
+edges are not parallel to the axis of the tetrahelix.  It is a famous and interesting result
 that the pitch is irrational. A BC helix never has two tetrahedra at
@@
 optimal tetrahelices are in fact triple helices with the same radius, so that all
-vertices are on a cylinder. In, stages, we demonstrate that optimal tetrahelices:
+vertices are on a cylinder. In stages, we demonstrate that optimal tetrahelices:
 \begin{enumerate}
@@
 shorter than the rail edges, and moving them apart slightly lengthens the between-edge
-rails.
+rails, improving the ratios.
 
 In the proof below we find useful to consider projection diagrams that are the axial projection
-of a tetrahelix onto the $XY$-plane. \Cref{fig:projectionDiagram.png} is an example of such a diagram.
+of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram} is an example of such a diagram.
 \begin{lemma}
@@
   edges long a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
-  regular polygon of 3 or more sides, else they form a circle.
+  regular polygon of 3 or more sides, else they fill in a complete circle.
   \label{lemma:ngon}
@@
   an unbounded number of points on a circle.
+  If and only if $2\pi/\rho$ is rational, the projection onto
+  the $XY$-plane will contain a finite number of points.
   Because $\pi$ is transcendental and irrational,
@@
   Since $\rho < \pi$, $a < b$, and since $\rho > 0$, $a > 0$.
-  If and only if $2\pi/\rho$ is rational, the projection onto
-  the $XY$-plane will contain a finite number of points.
   The number of points in the projection is $2b$ if $a$ is odd, and $b$ if $a$ is even.
@@
   Each helix has zero curvature, that is, is a straight line. These lines are eqivalent
-  to some three helices, possibly with different radii, so long as there is a phase
+  to some three degenerate helices, possibly with different radii, so long as there is a phase
   term in the defintion of the helix, as in \eqref{eq:colored}. We later show the
@@
   curavature. The projection of points in the $XY$ plane creates a figure
-  guaranteed to have point on either side of any line through the axis of such
-  a helix, because the figure is either an $n$-gon or a circle.
+  guaranteed to have points on either side of any line through the axis of such
+  a helix, because the figure is either an $n$-gon or a circle \cref{lemma:ngon}.
   We show that the three helices share a common axis.
@@
   \end{equation*}
-  where $\vec{B}(n)$ and $\vec{B'}$ is the cartesian vector
+  where $\vec{B}(n)$ and $\vec{B'}(n)$ is the cartesian vector
   $\begin{bmatrix}
@@
 
-  \Cref{fig:wobble} demonstrates illustrates this situation. Like most diagrams, it is
+  \Cref{fig:wobble} illustrates this situation. Like most diagrams, it is
   over specific, in that the two circles are drawn of the same radius but we do not
   depend upon that in this proof.  The diagram represents the projection along the
-  $z$ axis of points into the $XY$-plane.
+  $z$ axis of a few points into the $XY$-plane.
 
@@
   contains at least three vectors,
-  pointing in different directions.
+  at least two of which pointing in different directions.
   For any point not at the origin, at least one of these vectors moves closer to the
@@
 \end{equation}
-which would not be much more complicated if the axes where not coincident.
-Note that we have not yet show that the relationships of the radius $r$ or
-the phase $\phi$ for the three helies, so we denoted them with a $c$ subscript to show
+which would be much more complicated if the axes where not coincident.
+Note that we have not yet show that the relationships of the radius $r_c$ or
+the phase $\phi_c$ for the three helies, so we denoted them with a $c$ subscript to show
 they are dependent on the color.
@@
 generates optimal tetrahelices.
-However, we observe that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
+We observe that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
 but because of the $\phi_c$ term, they are not collinear.
@@
 In fact, it is possible that there
-will be only two distinct such classes.
+will be only two distinct such classes (or even one, in the purely regular BC helix.)
 
@@
 the property that all rail edges are equal to all one-hop edges and all two-hop
-edges are equal. 
+edges are equal to each other. 
 Observe that although we have not get given the formula for the
@@
 The green edges are the two-hop edges and the purple edges are the one-hop edges. Note that the green
-edges are slightly longer than the purple edges. In \ref{fig:naming}, which depicts the BC helix,
+edges are slightly longer than the purple edges. In \cref{fig:naming}, which depicts the BC helix,
 the two-hop and one-hop edges are of equal length (but the projection onto the $z$-axis, the
@@
   Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail and $2$ two-hop edges connected to the rail.
-  The edge opposite of the rail edge is a one-hop edge.
+  The sixth edge is opposite of the rail edge and is a one-hop edge.
 \end{theorem}
@@
 
-The quantities $\rho,r,d$ are related by the expression:
+The quantities $\rho,r,d$ (see \cref{railanglefig}) are related by the expression:
 
@@
 In choosing $\rho$, one greatly constrains $r$ and $d$, but does not completely
-determine both of them together, so we treat both as parameters.
+determine both of them together, so we treat both as additional parameters.
 
@@
      \caption{General One-hop Projection Diagram}
-  \label{projectiondiagram}
-
+  \label{fig:projectiondiagram}
 \end{figure}
@@
 To the extent that we value tetrabeams (that is, tetrahelices with a rail angle of $0$,
-and therefore zero curvature and curvature) as mathematical or engineering objects,
+and therefore zero curvature) as mathematical or engineering objects,
 we have motivated the development of $\vec{H}_{general}$ as a transformation of $\vec{V}(n)$ defined by
@@
 For a pitch at least $ p \geq \frac{3  \sqrt{2}  \pi}{\sqrt{5}\rho_{bc}} \approx 9.64 $,
-using \eqref{dopt} produces minimax optimal tetrahelices.
+using \cref{dopt} produces minimax optimal tetrahelices.
 
@@
 be noted that an engineer or architect may also use $\vec{H}_{general}$ 
-directly and interactively, and that minimax length optimality is a
+directly and interactively  \url{https://pubinv.github.io/tetrahelix/},
+and that minimax length optimality is a
 mathematical starting point rather than the final word on the beauty and utility of
@@
 experimented with tensegrities\cite{NTRT}, a different point in the
-same design spectrum. These fields create a need to explore the notion
-of geometries changing over time, not generally considered directly by
-pure geometry.
+same design spectrum.
 
@@
 \begin{theorem}
-  By changing only the length of the longer members that connect two distinct rails (the two-hop members), we can dynamically untwist a tetrobot
+  By changing only the length of the longer members that connect two distinct rails (the two-hop members), we can dynamically untwist a glussbot
   forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane.

### 2017-05-11 doc/TetrahelixUntwist.tex
adding in my notes some justification of the b or 2b result in ngon lemma

@@
   Because $\pi$ is transcendental and irrational,
-  $2\pi/\rho$ is rational if and only $\rho = a\pi/b$, where $a$ and $b$ are integers.
+  $2\pi/\rho$ is rational if and only $\rho = a\pi/b$, where $a$ and $b$ are integers
+  and without loss of generality $a$ and $b$ are comprime.
   Since $\rho < \pi$, $a < b$, and since $\rho > 0$, $a > 0$.
@@
 Reread everything, especially the new parts.
+
+Note:
+
+I do not believe it is worth providing a proof of (b or 2b) result of lemma ngon.
+However, here are my notes if it becomes important:
+
+Basically by using the distributive nature of mod and the definiton of a helix,
+the cardinality of the set can remove the PI factor in the sin(x) = sin(x mod 2PI).
+Then we know that a, b, and 2 are integers.  We can provide the cardinality is
+the residue of [n*a mod 2b], which becomes an integer modulus operation.
+if a = k2, you can factor out 2, which has no bearing on cardinality. the
+cardinality is the | { nk mod b } | = b.
+
+If a is odd, it is | { n(2k+1) mod 2b) | = 2b.  How do we know we can
+  reach each integer < 2b?  By Bezout's Identity there exists x,y, nax + yc = gcd(a,c).
+  Take c = 2b.
+  But gcd(a,c) = 1, because they are relatively prime. Take but
+  So we have ax + y2b = 1.  But (ax + y2b) mod 2b = ax mod 2b. Now  (nax) mod 2b = n,
+  up until y = 2b -1.

### 2017-05-13 doc/TetrahelixUntwist.tex
removing glussbot name

@@
 
-The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix) (see \cref{fig:closeup,fig:closuporthog}, is
+The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix) (see \cref{fig:closeup,fig:closeuporthog}, is
 a face-to-face stack of tetrahedra that winds about a straight axis.
@@
 three helices about the central axis.
-The \\
-Glussbot\cite{readglussbot} (or Tetrobot)\cite{TetrobotBook} uses the regularity of
+The Tetrobot\cite{readglussbot,TetrobotBook} uses the regularity of
 this geometry to make a tentacle-like robot that can crawl like a slug
 or mollusc.  These modular robotic systems use mechanical actuators which can change their length, connected by special joints,
-such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint in the case of the Glussbot, or the CMS joint\cite{HamlinSandersonCMS}, in the case of the Tetrobot,
+such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint or the CMS joint\cite{HamlinSandersonCMS} used in the original Tetrobot,
 which allow many members to meet in a single point.
@@
 and the vertices are a joint that supported sufficient angular displacement
-for this to be possible. An example of such a machine is a glussbot, shown in \cref{fig:glussbot}.
+for this to be possible. An example of such a machine is a Tetrobot,
+shown in \cref{fig:tetrobot}.
 
@@
 \Cref{fig:helixcomparison} illustrates this difference with a 7-tetrahedra BC helix, which is
-in fact the same geometry as the robot illustrated in \cref{fig:glussbot}.
+in fact the same geometry as the robot illustrated in \cref{fig:tetrobot}.
 Although the nodes coincide,
@@
      \includegraphics[width=0.9\textwidth]{figures/MedCantedCropped.png}
-     \caption{Glussbot in relaxed, or BC helix configuration}
+     \caption{7-Tet Tetrobot in relaxed, or BC helix configuration}
      \includegraphics[width=0.9\textwidth]{figures/EquitetrabeamCropped.png}
-     \caption{The Equitetrabeam: Fully Untwisted Glussbot in Hexapod Configuration}
-     \label{fig:glussbot}
+     \caption{The Equitetrabeam: Fully Untwisted 7-Tet Tetrobot in Hexapod Configuration}
+     \label{fig:tetrobot}
 \end{figure}
@@
 \begin{theorem}
-  By changing only the length of the longer members that connect two distinct rails (the two-hop members), we can dynamically untwist a glussbot
+  By changing only the length of the longer members that connect two distinct rails (the two-hop members), we can dynamically untwist a tetrobot
   forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane.
@@
   Proof by our computer program that does this using Equation \eqref{eq:general} applied to the
-  7-tet Tetrobot/Glussbot.
+  7-tet Tetrobot.
 
@@
 
-The Gluss Project \url{http://pubinv.github.io/gluss/} is part of Public Invention \url{https://pubinv.github.io/PubInv/},
+The Tetrobot Project \url{http://pubinv.github.io/gluss/} is part of Public Invention \url{https://pubinv.github.io/PubInv/},
 a free-libre, open-source research, hardware, and software project that welcomes volunteers.

### 2017-05-15 doc/TetrahelixUntwist.tex
removing glussbot name
final tweaks

@@
 three helices about the central axis.
-The Tetrobot\cite{readglussbot,TetrobotBook} uses the regularity of
+The \\
+Tetrobot\cite{readglussbot,TetrobotBook} uses the regularity of
 this geometry to make a tentacle-like robot that can crawl like a slug
@@
 Such machines can
-follow purely regular mathematical models such as the Boerdijk–-Coxeter
+follow purely regular mathematical models such as the Boerdijk-Coxeter
 helix or the Octet Truss\cite{richard1961synergetic}.
@@
 paper. The closest helix is the BC helix, and the furthest
-is the equitetrabeam, defined in \cref{sec:equitetrabeam} and \cref{fig:naming,fig:equitestrabeam}.
+is the equitetrabeam, defined in \cref{sec:equitetrabeam} and \cref{fig:naming,fig:equitetrabeam}.
 

### 2017-05-26 doc/TetrahelixUntwist.tex
made changes from Mary

@@
 
-The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix) (see \cref{fig:closeup,fig:closeuporthog}, is
+The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix) (see \cref{fig:closeup,fig:closeuporthog}), is
 a face-to-face stack of tetrahedra that winds about a straight axis.
@@
 actuator that can dynamically become shorter or longer in response to electronic control,
-and the vertices are a joint that supported sufficient angular displacement
+and the vertices are joints that support sufficient angular displacement
 for this to be possible. An example of such a machine is a Tetrobot,
@@
 any curvature or pitch we choose. It is a goal of
-this paper to relate the Cartesian coordinate approach and the member-length approachx to
+this paper to relate the Cartesian coordinate approach and the member-length approach to
 generating a tetrahelix continuum.
 
-H.S.M Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and translation of the tetrahedra, showing the
+H.S.M Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and translation of the tetrahedra by showing the
 rotation is:
@@
 \[
-h_{bc} = 1/\sqrt{10}
+h_{bc} = 1/\sqrt{10}.
 \]
@@
 
-R.W. Gray's website\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in more accessible form, gives the Cartesian coordinates $\begin{bmatrix}
+R.W. Gray's website\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in a more accessible form, gives the Cartesian coordinates $\begin{bmatrix}
            x \\
@@
 \[
-(\forall n \in \mathbb{Z}, \forall c \in \{0,1,2\} : \vec{H}_{BCcolored}(n,c) = \vec{V}(3n +c))
+(\forall n \in \mathbb{Z}, \forall c \in \{0,1,2\} : \vec{H}_{BCcolored}(n,c) = \vec{V}(3n +c)) .
 \]
@@
     $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$ \\
-    $ h_{bc} = 1/\sqrt{10} $ \\    
+    $ h_{bc} = 1/\sqrt{10} $. \\    
   \end{tabular}      
@@
   \label{pitcheqn}
-p(\rho) = \frac{2 \pi  \cdot d}{\rho}
+p(\rho) = \frac{2 \pi  \cdot d}{\rho} \text{ .}
 \end{equation}
@@
   &= \frac{6 \pi}{\sqrt{10}\rho_{bc}} 
-  &\approx 9.64 
+  &\approx 9.64 \text{ .}
 \end{align*}
@@
 We develop below slightly irregular edge lengths that support, for example, a pitch of precisely 12
-tetrahedra in one revolution which would allow an architect to design a
-column having a basis and a capital in the same relation to the
-tetrahedra they touch at the bottom and top of the column.
+tetrahedra in one revolution which would allow an architect to
+design a column having the top and bottom tetrahedra in the same relationship to the capital and the basis to the
+viewer.
 
@@
 
-Suppose that all three rails do not have the same pitch. Starting at any shortest edge between
+Suppose that all three rails do not have the same pitch. If we start at any shortest edge between
 two rails, as we move
@@
   $2\pi/\rho$ is rational if and only $\rho = a\pi/b$, where $a$ and $b$ are integers
-  and without loss of generality $a$ and $b$ are comprime.
-  Since $\rho < \pi$, $a < b$, and since $\rho > 0$, $a > 0$.
+  and without loss of generality $a$ and $b$ are coprime.
+  $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
   The number of points in the projection is $2b$ if $a$ is odd, and $b$ if $a$ is even.
-  This polygon has at least 3 sides, since either either $\rho$ is irrational or $b > a$, and therefore
+  This polygon has at least 3 sides, since either $\rho$ is irrational or $b > a$, and therefore
   $b >= 2$. If $a/b = 1/2$, the projection is a square, which has four sides. 
@@
   \begin{equation*}
-    \vec{W}(n) = \vec{B}(n) - \vec{B}'(n)
+    \vec{W}(n) = \vec{B}(n) - \vec{B}'(n) \text{ .}
   \end{equation*}
@@
 
-Now that we have show that axes are conincident and parallel and that the pitches
+Now that we have shown that axes are conincident and parallel and that the pitches
 are the same for all helices, we can assert that any optimum tetrahelix can
@@
 which would be much more complicated if the axes where not coincident.
-Note that we have not yet show that the relationships of the radius $r_c$ or
+Note that we have not yet shown that the relationships of the radius $r_c$ or
 the phase $\phi_c$ for the three helies, so we denoted them with a $c$ subscript to show
@@
 and 3 two-hop
-lengths $\{ RB_{+}, BY_+, RY_+, \}$ between each pair of 3 rails,
+lengths $\{ RB_{+}, BY_+, RY_+ \}$ between each pair of 3 rails,
 where the two-hop length is at least the one-hop length.
@@
 In fact, it is possible that there
-will be only two distinct such classes (or even one, in the purely regular BC helix.)
+will be only two distinct such classes, or even one, in the purely regular BC helix.
 
@@
 Likewise, a helix with a smaller radius decreases a one-hop edge without decreasing
-a two-hop edge.  Therefore, a tetrahelix with different radii is not as good as some two-class 
+a two-hop edge.  Therefore, a tetrahelix with different radii is not as optimal as some two-class 
 tetrahelix generated by \cref{eq:triple}, and so it not optimal. We have not yet
@@
     $d/3$ intervals on the $z$ axis. Every edge is either a rail edge,
-    or it makes one hop, or it makes two hops. All of the one-hop
+    or it makes one hop, or two hops. All of the one-hop
     edges are equal length.  All of the two-hop edges are equal
@@
     than $t'$ and $o'$ and less than $t'$ and $o'$.
-    Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other, and
-    all two-hop edges equal to each other, and the $z$ distances between rails equal, and therefore
+    Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other,
+    all two-hop edges equal to each other, the $z$ distances between rails equal, and therefore
     $d/3$ from each other.
@@
 axially.
-An optimal tetrahelix is therefore a \emph{triple helix}, (of a radius we have not yet demonstrated.)
+An optimal tetrahelix is therefore a \emph{triple helix}, of a radius we have not yet demonstrated.
 
@@
 Checking the important special case of the BC helix, we find that this equation
-indeed holds true (treating $d$ in this equation as $3 h_{bc}$ as defined by
+indeed holds true, treating $d$ in this equation as $3 h_{bc}$ as defined by
 Gray and Coxeter, that is, $d_{bc} = 3h_{bc}$, where they are using
@@
 up until one-hop $= 1$, the rail-edge length. If we attempted to increase the radius further
-we would not be optimal, because the ratio $\frac{\text{two-hop}(r)}{1}$ would because the
+we would not be optimal, because the ratio $\frac{\text{two-hop}(r)}{1}$ would become the
 largest ratio in our set of ratios \cref{eq:ratioset}.
@@
 up to the point that the shorter, one-hop distance is equal to the rail-length, $1$.
-Therefore, to optimize the whole system so long as $\rho \leq \rho_{bc}$,
+In order to optimize the whole system so long as $\rho \leq \rho_{bc}$,
 we equate one-hop to $1$ to find the optimum radius:
@@
   \label{eq:inradius}
-  r_{in}(\rho) = r \sin{\frac{\pi - \rho}{6}}
+  r_{in}(\rho) = r \sin{\frac{\pi - \rho}{6}} \text{ ,}
 \end{equation}
-Which can be seen from the trigonometry of a diagram of the projected one-hop edges
+which can be seen from the trigonometry of a diagram of the projected one-hop edges
 connecting four sequentially numbered vertices:
@@
 even further does produce a clockwise tetrahelix, but one in which the
- one-hop and two-hop lengths in the wrong places (that is, two-hop
- becomes shorter than one-hop.) Likewise, $\rho > \rho_{bc}$ generates
+ one-hop and two-hop lengths in the wrong places, that is, two-hop
+ becomes shorter than one-hop.
+ Likewise, $\rho > \rho_{bc}$ generates
  a tetrahelix, but minimax optimality is not guaranteed by $\vec{H}_{general}$.
 
- The pitch of a helix (see \cref{pitcheqn}, for a fixed $z$-axis travel $d$,
- is trivial.
+ The pitch of a helix for a fixed $z$-axis travel $d$
+ is trivial (see \cref{pitcheqn}).
 However, if one is computing 
-$z$-axis travel from \eqref{dopt} the pitch is not simple.
+$z$-axis travel from \cref{dopt} the pitch is not simple.
 It increases monotonically and smoothly with decreasing $\rho$, so
-Equation \eqref{pitcheqn} can be easily solved numerically with a Newton-Raphson
+\cref{pitcheqn} can be easily solved numerically with a Newton-Raphson
 solver, as we do on our website.
@@
 
-In this way a rail angle can be chosen for any desired (sufficiently large) pitch, yield
-the optimum radius, one-hop, and two-hop lengths an engineer needs to
+In this way a rail angle can be chosen for any desired (sufficiently large) pitch, yielding
+the optimum radius, the one-hop length, and the two-hop length an engineer needs to
 construct a physical structure.
@@
 \begin{equation}
-  \frac{|r_{\rho}|}{r_{\rho}^2 + (d_{\rho}/\rho)^2}
+  \frac{|r_{\rho}|}{r_{\rho}^2 + (d_{\rho}/\rho)^2} \text{ .}
 \end{equation}

### 2017-05-26 doc/TetrahelixUntwist.tex
teaks

@@
 
-$\theta_{bc}$ is approximately $0.37 \cdot 2 \pi$ radians or  $131.81$ degrees.
+Note that $\theta_{bc}$ is approximately $0.37 \cdot 2 \pi$ radians or  $131.81$ degrees.
 The angle $\theta_{bc}$ is the rotation of \emph{each} tetrahedron, not the tetraheda along a rail.  In \cref{fig:closeup},
@@
 \end{equation}
-where $n$ represents each integer numbered node in succession on every colored rail.
+and where $n$ represents each integer numbered node in succession on every colored rail.
 
@@
     (c/3)  (3 \theta_{bc})  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
- (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) &= \text{\{definition of $\rho_{bc}$\}...} \\  
+ (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) &= \text{\{definition of $\rho_{bc}$\ ...\}} \\  
   (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{\{algebra...\}} \\  
@@
   and without loss of generality $a$ and $b$ are coprime.
-  $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
+  Since $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
   The number of points in the projection is $2b$ if $a$ is odd, and $b$ if $a$ is even.

### 2017-05-26 doc/TetrahelixUntwist.tex
getting closer to final

@@
   parameters that give edge-length minimax-optimal tetrahelices
-  are given, defining a continuum of tetrahelices of varying curvature.
-  The endpoints of the optimality of this continuum are the BC helix and
+  are given, defining a continuum of optimum tetrahelices of varying curvature.
+  The endpoints of this continuum are the BC helix and
   a structure of zero curvature, the \emph{equitetrabeam}.
@@
 we observe that it is useful to the mechanical engineer or
-roboticist because the structure remains an inherently rigid,
+roboticist because the structure is an inherently rigid,
 omni-triangulated space frame, which is
@@
 design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix},
-from which \cref{fig:closeup,fig:closeuporthog,fig:series}
+from which \cref{fig:closeup,fig:closeuporthog,fig:series,fig:naming,fig:equitetrabeam}
 are taken.
@@
 for any integer $n$
-in \eqref{graycoxeter}, is $3 \theta_{bc} - 2\pi$).
+in \eqref{graycoxeter}, is $3 \theta_{bc} - 2\pi$.
 
 This formula defines a helix, but it is not any of the apparent helices, or \emph{rail} helices, of the
-BC helix, but rather one that winds three times as rapidly through all
+BC helix, but rather one that winds much more rapidly through all
 nodes. To a designer of tetrahelices, it is more natural to think of
@@
  $ h_{bc} = 1/\sqrt{10} $ \\
- $ \theta_{bc} = \arccos(-2/3) $ \\
+ $ \theta_{bc} = \arccos(-2/3) $ \text{ .}\\
   \end{tabular}      
@@
 We expand 
-the expressions $\theta_{bc}$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c 2\pi/3 $.
+the expressions $\theta_{bc}$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c 2\pi/3 $. Thus:
 \begin{align*}
@@
   (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{\{algebra...\}} \\  
-c  ( \rho_{bc} +  2 \pi) /3  \\
+c  ( \rho_{bc} +  2 \pi) /3 \text{ .} \\
 \end{align*}
@@
 tetrahedra in one revolution which would allow an architect to
-design a column having the top and bottom tetrahedra in the same relationship to the capital and the basis to the
+design a pleasing column having the top and bottom tetrahedra in the same relationship to the capital and the basis to the
 viewer.
@@
   If the rail angle $0 < \rho < \pi$ is a rational multiple of $\pi$, then the projection of
-  edges long a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
-  regular polygon of 3 or more sides, else they fill in a complete circle.
+  edges in a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
+  regular polygon of 3 or more sides, or else they fill in a complete circle.
   \label{lemma:ngon}
@@
   Case 1: Suppose that $\rho$ is zero.
-  Each helix has zero curvature, that is, is a straight line. These lines are eqivalent
-  to some three degenerate helices, possibly with different radii, so long as there is a phase
+  Each helix has zero curvature, that is, it is a straight line. These lines are eqivalent
+  to some three degenerate helices with conincident axes, possibly with different radii, so long as there is a phase
   term in the defintion of the helix, as in \eqref{eq:colored}. We later show the
@@
   In this case each rail helix has
-  curavature. The projection of points in the $XY$ plane creates a figure
+  curvature. The projection of points in the $XY$ plane creates a figure
   guaranteed to have points on either side of any line through the axis of such
-  a helix, because the figure is either an $n$-gon or a circle \cref{lemma:ngon}.
+  a helix, because the figure is either an $n$-gon or a circle by \cref{lemma:ngon}.
   We show that the three helices share a common axis.
@@
   Without loss of generality define the Red helix to have its axis on the $z$-axis.
-  Since either a Red-to-Yellow or a Red-to-Blue edge is either a minimum or a maximum,
+  Since there must be at least one Red-to-Yellow or a Red-to-Blue edge that is either a minimum or a maximum,
   without loss of generatlity define the Blue helix to be a helix that
@@
   \end{equation*}
-  where $\vec{B}(n)$ and $\vec{B'}(n)$ is the cartesian vector
+  where $\vec{B}(n)$ and $\vec{B'}(n)$ is the vector
   $\begin{bmatrix}
@@
     zero for both, finding a tetrahelix of improved overall minimax value at each step.
-    So a tetrahelix is optimal only when $\vec{W}(n) = 0$, and therefore when $D=0$
-    $\vec{B}(n) = \vec{B'}(n)$, and all three axes are conincident.
+    So a tetrahelix is optimal only when $\vec{W}(n) = 0$, and therefore when $D=0$ and
+    $\vec{B}(n) = \vec{B'}(n)$, and all three axes are coincident.
 \end{proof}
@@
 
-In principle in any three helices generated with \cref{eq:triple}
+In principle any three helices generated with \cref{eq:triple}
 has at most nine distinct edge length classes. Each edge that connects
-two rails potentially has a longer length and shorter length we donote with
+two rails potentially has a longer length and shorter length we denote with
 a $+$ or $-$. So the classes are $\{ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
@@
 for which all the three helices are symmetrically and evenly spaced. Furthermore,
-we can choose these values such that the three rail edges are of length unity and
-so that the one-hop lengths are also all of length unity, and the two-hop lengths
-are slightly longer. We call such a tetrahelix a two-class tetrahelix.
+we can choose these values such that the three rail edges are of length $1$ and
+so that the one-hop lengths are also all of length $1$, and the two-hop lengths
+are slightly longer.
 
@@
 
-Now that we have shown that any optimal tetrahelix vertices
+Now that we have shown that on any optimal tetrahelix the vertices
 are on helices of the same axes and pitch, we see that the vertices 
@@
     than $t'$ and $o'$ and less than $t'$ and $o'$.
-    Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other,
-    all two-hop edges equal to each other, the $z$ distances between rails equal, and therefore
-    $d/3$ from each other.
+    Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other, and
+    all two-hop edges equal to each other, the $z$ distances between rails equal. Therefore vertices are
+    $d/3$ from each other on the $z$-axis.
 \end{proof}
@@
 \begin{align*}
-  1^2 &= d^2 + (2 r \sin{ \rho / 2})^2 \\
+  1^2 &= d^2 + (2 r \sin{ \rho / 2})^2 , \text{ or }\\
 %%  1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 \\
@@
   $   1 = d_{\rho}^2 + 4 r_{\rho}^2 (\sin{ \rho / 2})^2 $ \\
-    $\chi \in \{-1,1\}$ \\  
+    $\chi \in \{-1,1\}$ \text{ .} \\  
 \end{tabular}
@@
 \begin{equation*}
-  j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)
+  j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2
 \end{equation*}
 \begin{equation*}
-  k_{\rho} = (\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)
+  k_{\rho} = \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2
 \end{equation*}
@@
 limitation in our statement of the theorem is meaningful.)
-Since the partial derivative of $\text{two-hop}(r) / \text{one-hop}(r)$ with respect to the
+Since the partial derivative of  $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ with respect to the
 radius $r$ is negative for all $\rho$ up until $\rho_{bc}$, this ratio goes down
@@
   1 &=  \sqrt{\frac{1}{9}  + r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
-  r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }} \numberthis  \label{eqrhoopt} \\
+  r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }} \text{ .} \numberthis  \label{eqrhoopt} \\
 \end{align*}
@@
 %%  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
-    d_{opt} &= \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
+    d_{opt} &= \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}  \text{ .}  \numberthis  \label{dopt}  \\      
 \end{align*}
@@
 tetrahelix to be the radius of the largest
-cylinder parallel to this axis that is surrounded by each tetrahelix and pentrated by no edge.
+cylinder parallel to this axis that is surrounded by each tetrahelix and penetrated by no edge.
 
@@
 In this way a rail angle can be chosen for any desired (sufficiently large) pitch, yielding
-the optimum radius, the one-hop length, and the two-hop length an engineer needs to
+the optimum radius, the one-hop length, and the two-hop length that an engineer needs to
 construct a physical structure.
@@
 be noted that an engineer or architect may also use $\vec{H}_{general}$ 
-directly and interactively  \url{https://pubinv.github.io/tetrahelix/},
+directly and interactively via \url{https://pubinv.github.io/tetrahelix/},
 and that minimax length optimality is a
@@
 used as a beam, an engineer might start with the optimal tetrabeam and
-dilate it in one dimension to ``deepen'' the beam. Similarly, simple
-length changes curve the equitetrabeam into an ``arch''.
+dilate it in one dimension to stiffen the beam by deepening it. Similarly, simple
+length changes curve the equitetrabeam into an arch.
 The ``colored'' approach of \cref{eq:general} exposes these possibilities
@@
 \begin{proof}
-  Proof by our computer program that does this using Equation \eqref{eq:general} applied to the
+  Proof by our computer program that does this using Equation \eqref{eq:general} applied to the physical
   7-tet Tetrobot.
@@
 a free-libre, open-source research, hardware, and software project that welcomes volunteers.
-It is our goal to organize projects for the benefit of all humanity without seeking profit or intellectual property.
 To assist, contact \email{read.robert@gmail.com}.

### 2017-05-26 doc/TetrahelixUntwist.tex
improving grammar of equations

@@
  $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $ \\
- $ \theta_{bc} = \arccos(-2/3) $ \\
+ $ \theta_{bc} = \arccos(-2/3) $  \text{ ,}\\
   \end{tabular}      
@@
 We expand 
-the expressions $\theta_{bc}$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c 2\pi/3 $. Thus:
-\begin{align*}
- c \theta_{bc}  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
-    (c/3)  (3 \theta_{bc})  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
- (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) &= \text{\{definition of $\rho_{bc}$\ ...\}} \\  
-  (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{\{algebra...\}} \\  
-c  ( \rho_{bc} +  2 \pi) /3 \text{ .} \\
+the expressions $\theta_{bc}$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c 2\pi/3 $.
+
+%% Thus:
+%% \begin{align*}
+%%  c \theta_{bc}  &=   \text{\{we aim for 3 in denominator, so we split...\}} \\
+%%     (c/3)  (3 \theta_{bc})  &=   \text{\{we want $2\pi$ in numerator, so add canceling terms...\}} \\
+%%  (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) &= \text{\{definition of $\rho_{bc}$\ ...\}} \\  
+%%   (c / 3) \rho_{bc}  + c 2 \pi /3 &=  \text{\{algebra...\}} \\  
+%% c  ( \rho_{bc} +  2 \pi) /3 \text{ .} \\
+%% \end{align*}
+
+Thus, starting with the expression:
+\begin{align*}
+  c \theta_{bc} 
+\end{align*}
+we introduce 3 into the denominator...
+\begin{align*}
+  (c/3)  (3 \theta_{bc}) 
+\end{align*}
+we want $2\pi$ in numerator, so add canceling terms...
+\begin{align*}
+  (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) 
+\end{align*}
+...and then use the definition of $\rho_{bc}$
+\begin{align*}
+  (c / 3) \rho_{bc}  + c 2 \pi /3 
+\end{align*}
+finally using algebra, we obtain
+\begin{align*}
+  c  ( \rho_{bc} +  2 \pi) /3  \text{.}
 \end{align*}
@@
   &= \frac{6 \pi}{\sqrt{10}\rho_{bc}} 
-  &\approx 9.64 \text{ .}
-\end{align*}
+ \text{ ,}
+\end{align*}
+which is approximately $9.64$.
 
@@
 %%  1 &= d^2 + 4 r^2 (\sin{ \rho / 2})^2 \\
-  d^2 &= 1 - 4 r^2 (\sin{ \rho / 2})^2    \numberthis  \label{railangle} \\
+  d^2 &= 1 - 4 r^2 (\sin{ \rho / 2})^2  \text{ .}  \numberthis  \label{railangle} \\
 \end{align*}
@@
   \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || = 1 \\
-  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \\
-  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \\  
-\end{align*}
-This syntax just represents the Euclidean distance formula.
+  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{ and,} \\
+  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \text{ .}\\  
+\end{align*}
+This syntax just represents the Euclidean distance formula. Thus:
 
@@
   \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho}) - \vec{H}_{general}(n,c+1,\rho,d_{\rho}),r) || \\
+\end{align*}
+so:
+\begin{align*}
 %%  \text{one-hop} &= dist(\vec{H}_{general}(0,0,\rho,d_{\rho}),\vec{H}_{general}(0,1,\rho,d_{\rho},r))  \\  
@@
   \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
-  \text{but: }  d_{\rho}^2 &= 1 - 4 r^2 (\sin( \rho / 2)^2 \text{ ...so we substitute:}\\
+\end{align*}
+but: $  d_{\rho}^2 = 1 - 4 r^2 (\sin( \rho / 2)^2$, so we substitute:
+\begin{align*}
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.  
-  \text{one-hop}  &= \sqrt{\frac{1}{9}  + r^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
+  \text{one-hop}  &= \sqrt{\frac{1}{9}  + r^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{.}\\
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.    
@@
 \begin{align*}
-  \text{two-hop}  &= \sqrt{\frac{4}{9} + r^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \\
+  \text{two-hop}  &= \sqrt{\frac{4}{9} + r^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \text{.}\\
 \end{align*}
@@
 \[
-\frac{\max{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}{\min{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}
+\frac{\max{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}{\min{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}} \text{.}
 \]
@@
  \frac{   \max \{1,\text{two-hop}(r)\}}
-      {   \min \{1,\text{one-hop}(r)\}}
+      {   \min \{1,\text{one-hop}(r)\}} \text{.}
 \]
@@
 \frac{1}{\text{one-hop}(r)},
-\frac{\text{two-hop}(r)}{\text{one-hop}(r)}
+\frac{\text{two-hop}(r)}{\text{one-hop}(r)} \text{.}
 \label{eq:ratioset}
@@
 \begin{equation*}
-  f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9}
+  f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9} \text{,}
   \end{equation*}
 \begin{equation*}
-  g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} 
-\end{equation*}
-
-\begin{equation*}
-  j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2
+  g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} \text{,}
 \end{equation*}
 \begin{equation*}
-  k_{\rho} = \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2
+  j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2 \text{,}
+\end{equation*}
+and:
+\begin{equation*}
+  k_{\rho} = \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2 \text{.}
 \end{equation*}
@@
   \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ j_{\rho})}}
-       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+k_{\rho}) }}
+       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+k_{\rho}) }} \text{.}
 \end{align*}
@@
 \begin{align*}
-  1 &=  \sqrt{\frac{1}{9}  + r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
+  1 &=  \sqrt{\frac{1}{9}  + r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{, so...} \\
   r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }} \text{ .} \numberthis  \label{eqrhoopt} \\
@@
 a free-libre, open-source research, hardware, and software project that welcomes volunteers.
-To assist, contact \email{read.robert@gmail.com}.
+To assist, contact\\
+\email{read.robert@gmail.com}.
 

### 2017-05-27 doc/TetrahelixUntwist.tex
formatting

@@
 this geometry to make a tentacle-like robot that can crawl like a slug
-or mollusc.  These modular robotic systems use mechanical actuators which can change their length, connected by special joints,
-such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint or the CMS joint\cite{HamlinSandersonCMS} used in the original Tetrobot,
+or mollusk.  These modular robotic systems use mechanical actuators which can
+change their length, connected by special joints,
+such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint or the CMS joint\cite{HamlinSandersonCMS}
+used in the original Tetrobot,
 which allow many members to meet in a single point.
@@
 
-Ideally we would have a simple formula for defining the nodes based on
+Ideally we would have a simple formula for defining the vertices based on
 any curvature or pitch we choose. It is a goal of
@@
   \begin{tabular}{c}
- $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $\\
- $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $ \\
- $ \theta_{bc} = \arccos(-2/3) $  \text{ ,}\\
+ $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $,\\
+ $ h_{bc} = 1/\sqrt{10} \approx 0.3162 $, and \\
+ $ \theta_{bc} = \arccos(-2/3) $  \text{,}\\
   \end{tabular}      
 \end{equation}
-and where $n$ represents each integer numbered node in succession on every colored rail.
+and where $n$ represents each integer numbered vertex in succession on every colored rail.
 
@@
 for any integer $n$
-in \eqref{graycoxeter}, is $3 \theta_{bc} - 2\pi$.
+in \cref{graycoxeter}, is $3 \theta_{bc} - 2\pi$.
 
@@
 BC helix, but rather one that winds much more rapidly through all
-nodes. To a designer of tetrahelices, it is more natural to think of
+vertices. To a designer of tetrahelices, it is more natural to think of
 the three helices which are visually apparent, that is, those three
@@
 This situation is illustrated in \cref{fig:helixcomparison}, wherein the black helix represents that
-generated by \cref{graycoxeter},
+generated by Equaiton \cref{graycoxeter},
 and the colored helices are generated by \cref{eq:colored}.
@@
 In order to develop the continuum of slightly irregular tetrahelices described in \cref{sec:continuum},
-we need a formula that gives us the nodes of just
-one rail helix, denoted by color $c$ and integer node number $n$:
+we need a formula that gives us the vertices of just
+one rail helix, denoted by color $c$ and integer vertex number $n$:
 \[
@@
   \begin{tabular}{c}
- $ r_{bc} = \frac{3\sqrt{3}}{10} $\\
- $ h_{bc} = 1/\sqrt{10} $ \\
- $ \theta_{bc} = \arccos(-2/3) $ \text{ .}\\
+ $ r_{bc} = \frac{3\sqrt{3}}{10} $,\\
+ $ h_{bc} = 1/\sqrt{10} $, and \\
+ $ \theta_{bc} = \arccos(-2/3) $ \text{.}\\
   \end{tabular}      
@@
 
-In this formula, integral values of $n$ may be taken as a node number for one rail and used to compute
+In this formula, integral values of $n$ may be taken as a vertex number for one rail and used to compute
 its Cartesian
@@
 in fact the same geometry as the robot illustrated in \cref{fig:tetrobot}.
-Although the nodes coincide,
+Although the vertices coincide,
  \cref{graycoxeter} evaluated
-at real values generates the black helix which runs through every node, and \cref{eq:colored} defines
+at real values generates the black helix which runs through every vertex, and \cref{eq:colored} defines
 the red, yellow, and blue helices. (In this figure
-these rail helices have been rendered at a slightly higher radius than the nodes for clarity;
+these rail helices have been rendered at a slightly higher radius than the vertices for clarity;
 in actuality the maximum distance between the continuous, curved helix and the
-straight edges between nodes is much smaller than can be clearly rendered.)
+straight edges between vertices is much smaller than can be clearly rendered.)
 
 The quantity $ (3 \theta_{bc} - 2 \pi) \approx 35.43 \degree $  is the angular shift between
+adjacent vertices on the same rail:
 $ \vec{V}(3n + c)= \vec{H}_{BCcolored}(n,c)$ and
@@
 
-Note in \cref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In \eqref{graycoxeter} and \eqref{eq:colored}, the variable
+Note in \cref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In Equaiton \cref{graycoxeter} and  \cref{eq:colored}, the variable
 $h$ is used for one third of the distance we name $d$. We will later justify that $d = 3h$.
@@
 We expand 
-the expressions $\theta_{bc}$ and $\rho_{bc}$ in \eqref{eq:colored} and seek to isolate the term $c 2\pi/3 $.
+the expressions $\theta_{bc}$ and $\rho_{bc}$ in \cref{eq:colored} and seek to isolate the term $c 2\pi/3 $.
 
@@
 \end{align*}
-finally using algebra, we obtain
+finally we obtain:
 \begin{align*}
@@
 %%  $\kappa = n + c/3$ \\
-    $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$ \\
+    $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$, and \\
     $ h_{bc} = 1/\sqrt{10} $. \\    
@@
   \label{pitcheqn}
-p(\rho) = \frac{2 \pi  \cdot d}{\rho} \text{ .}
+p(\rho) = \frac{2 \pi  d}{\rho} \text{.}
 \end{equation}
 
-The pitch of the Boerdijk-Coxeter helix of edge length $1$ is the length of three tetrahedra times this number:
-\begin{align*}
-   \frac{3 h_{bc}\cdot  2 \pi }{\rho_{bc}} 
-  &= \frac{6 \pi}{\sqrt{10}\rho_{bc}} 
- \text{ ,}
-\end{align*}
-which is approximately $9.64$.
+The pitch of the Boerdijk-Coxeter helix of edge length $1$ is the length of three tetrahedra times
+$p(\rho_{bc})$:
+\begin{align*}
+   \frac{3 h_{bc}  2 \pi }{\rho_{bc}} 
+   = \frac{6 \pi}{\sqrt{10}\rho_{bc}}
+   \approx 9.64
+ \text{.}
+\end{align*}
 
@@
   \item have the same rail lengths,
-  \item have axially equidistant nodes, and therefore
+  \item have axially equidistant vertices, and therefore
   \item are in fact triple helices.
@@
 two rails, as we move
-from node to node away from our start edge the edge lengths
+from vertex to vertex away from our start edge the edge lengths
 between rails must always lengthen without bound,
@@
   to some three degenerate helices with conincident axes, possibly with different radii, so long as there is a phase
-  term in the defintion of the helix, as in \eqref{eq:colored}. We later show the
+  term in the defintion of the helix, as in \cref{eq:colored}. We later show the
   radii must be eqivalent.
@@
     $L = \{|| \vec{R}(n) - \vec{B}(n)||\}$, which by our choice has at least one longest or shortest
-    length. (Note this is just the Euclidean distance formula written as a Euclidean norm.)
+    length.
     $L = \{|| \vec{R}(n) - (\vec{B'}(n) + \vec{W}(n))||\}$ and so
@@
 In fact, it is possible that there
-will be only two distinct such classes, or even one, in the purely regular BC helix.
+will be only two distinct such classes. In the purely regular BC helix there is only one length.
 
@@
 it has equivalent rail edge lengths. Likewise, there is a single rail angle $\rho$ that
-represents the rotation of two nodes connected by a single rail edge, and it is the same
+represents the rotation of two vertices connected by a single rail edge, and it is the same
 for all three rails.
@@
 
- We show that in fact the nodes must be distributed in even thirds
+ We show that in fact the vertices must be distributed in even thirds
  along the $z$-axis, as in fact they are in the regular BC helix.
@@
 curvature is $0$, an important special case. The radius or the axial
-distance between two nodes on the same rail are possible choices, but
+distance between two vertices on the same rail are possible choices, but
 perhaps the clearest choice is to build formulae that takes as their
 input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
-formed in the X,Y plane $\angle \vec{H}(0,0) O \vec{H}(0,1)$ projecting out the $z$
+formed in the X,Y plane with origin $O$: $\angle \vec{H}(0,0) O \vec{H}(0,1)$ projecting out the $z$
 axis and sighting along the positive $z$ axis. In other words, $\rho$
@@
 Gray and Coxeter, that is, $d_{bc} = 3h_{bc}$, where they are using
-$h$ for the axial height from one node to
-the next of a different color, but we use $d$ to mean distance between nodes of
+$h$ for the axial height from one vertex to
+the next of a different color, but we use $d$ to mean distance between vertices of
 the  same color.
@@
 \begin{tabular}{c}
-  $   1 = d_{\rho}^2 + 4 r_{\rho}^2 (\sin{ \rho / 2})^2 $ \\
-    $\chi \in \{-1,1\}$ \text{ .} \\  
+  $   1 = d_{\rho}^2 + 4 r_{\rho}^2 (\sin{ \rho / 2})^2 $, and \\
+    $\chi \in \{-1,1\}$ \text{.} \\  
 \end{tabular}
@@
 
-$\vec{H}_{general}$ forces the user to select three values: $\rho$, $r_{\rho}$, and $d_{\rho}$ satisfying \eqref{railangle}.
+$\vec{H}_{general}$ forces the user to select three values: $\rho$, $r_{\rho}$, and $d_{\rho}$ satisfying \cref{railangle}.
 
@@
 \begin{align*}
-  \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || = 1 \\
+  \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || = 1 \text{ ,} \\
   \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{ and,} \\
@@
 \end{align*}
-This syntax just represents the Euclidean distance formula. Thus:
+This syntax just represents the Euclidean distance between vertices. Thus:
 
@@
 
-We can now give a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \eqref{railangle}:
+We can now give a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \cref{railangle}:
 
@@
 an equilateral triangle of unchanging orientation, as shown in \cref{fig:equitetrabeam} and at the rear of \cref{fig:series}.
-We call this the \emph{equitetrabeam}. It is not possible to generate an equitetrabeam from \cref{graycoxeter}
+We call this the \emph{equitetrabeam}. It is not possible to generate an equitetrabeam from 
+\cref{graycoxeter}
 without the split into three rails introduced by \cref{eq:colored} and completed in  \cref{eq:general}.
@@
   The equitetrabeam with minimal maximal edge ratio is produced
-  \newline by $\vec{H}_{general}$ when $ r = \sqrt{\frac{8}{27}} $.
+  \newline by $\vec{H}_{general}$ when $ r = \sqrt{\frac{8}{27}} $ and the longest member is $\frac{2}{\sqrt{3}}$,
+  which is less than $16\%$ longer
+  than the shortest member.
 \end{corollary}
@@
 \begin{proof}
-Choosing $d = 1$ and $\rho = 0$ we use Equation \eqref{eqrhoopt} to find the radius of 
+Choosing $d = 1$ and $\rho = 0$ we use  \cref{eqrhoopt} to find the radius of 
 optimal minimax difference.
-
-Substituting into \eqref{eq:general}:
-
-\begin{align*}
-  \text{one-hop} &= \sqrt{\frac{1}{9} + 3r^2}\\
-\end{align*}
-Then:
-\begin{align*}
-   1  &=  \sqrt{\frac{1}{9} + 3r^2} & \text{ solved by... }\\
-   r  &= \sqrt{\frac{8}{27}} &\approx 0.54 \\
-\end{align*}
+Substituting into  \cref{eq:general} and setting one-hop\footnote{Before developing the optimal solution  \cref{eqrhoopt} we found another interesting but non-optimal tetrabeam of zero curvature
+by setting
+the mean of one-hop and two-hop to 1 ($(\text{one-hop} + \text{two-hop})/2 = 1$),
+  which gives $r = \sqrt{35}/4$ and
+  three length classes of $\frac{11}{12}, \frac{12}{12}, \frac{13}{12}$.}
+ to $1$
+gives:
+%% \begin{align*}
+%%   1  &=  \sqrt{\frac{1}{9} + 3r^2} \\
+%% \end{align*}  
+%% and solving for $r$, gives
+%% \begin{align*}
+%%    r  &= \sqrt{\frac{8}{27}} \approx 0.54 \text{.}\\
+%% \end{align*}
+$ 1  =  \sqrt{\frac{1}{9} + 3r^2} $, or $ r  = \sqrt{\frac{8}{27}}$. This radius
+produces a two-hop edge length of $\frac{2}{\sqrt{3}} \approx 1.1547$.
 \end{proof}
 
-This radius\footnote{Another interesting but non-optimal solution is derived by setting
-  (one-hop + two-hop)/2 = 1,
-  occurs at $r = \sqrt{35}/4$ which produces
-  three length classes of $11/12, 12/12, 13/12$.}
-produces a two-hop rail length of $\frac{2}{\sqrt{3}}$.
-The difference between this and $1$ is $\approx 15.47\% $. The inradius of the equitetrabeam of unit
-rail length from both Equation \eqref{eq:inradius} and the fact that the inradius of
+The inradius of the equitetrabeam of unit
+rail length from both  \cref{eq:inradius} and the fact that the inradius of
 an equilateral triangle is half the circumradius is $\sqrt{\frac{8}{27}}/2$, or $\frac{\sqrt{6}}{9}$.
@@
 we have motivated the development of $\vec{H}_{general}$ as a transformation of $\vec{V}(n)$ defined by
-Equation \eqref{graycoxeter} from Gray and Coxeter. It is difficult to see how
+ \cref{graycoxeter} from Gray and Coxeter. It is difficult to see how
 the $\vec{V}(n)$ 
@@
 
-We observe that Equations \eqref{eqrhoopt} and \eqref{dopt} compute $r_{opt}$ and $d_{opt}$ which
+We observe that  \cref{eqrhoopt,dopt} compute $r_{opt}$ and $d_{opt}$ which
 create an optimal tetrahelix for any rail angle $\rho$ between $0$, which
@@
  chirality, that is, one still must decide to connect the one-hop edge to
- the clockwise or the counter-clockwise node, it is not possible to build
+ the clockwise or the counter-clockwise vertex, it is not possible to build
  a smooth continuum where $\rho$ transitions from positive to negative
@@
 and rail length equivalent within this continuum.\footnote{Before
-deriving Equation \eqref{eqrhoopt}, we created a continuum by
+deriving  \cref{eqrhoopt}, we created a continuum by
 using a linear interpolation between the optimal radius for the
@@
 approach was at most 1\% worse than the optimum computed by
-\eqref{eqrhoopt}.}
+\cref{eqrhoopt}.}
  However, it should
@@
 experimented with tensegrities\cite{NTRT}, a different point in the
-same design spectrum.
+same design spectrum. In particular the tetrahelix is related to the
+tetraspline\cite{mirletz2014} concept used as a physical concept of a tensegrity robot.
+Although tensegrities are not member-for-member isomorphic to the tetrahelix
+as the tetrobot is, they often used repeated tetrahedral cells, so this
+work of pure geometry has some relevance to them.
 
@@
 However, a robot must move, and so it is interesting to consider the
-transmutations of these geometries, which was in fact the motivation
-for creating the equitetrabeam.
-
-\begin{theorem}
-  By changing only the length of the longer members that connect two distinct rails (the two-hop members), we can dynamically untwist a tetrobot
+transmutations of these regular geometries. Developing a functional
+gait for our physical Tetrobot was in fact the motivation
+for this work.
+By changing only the length of the longer members that connect two
+distinct rails (the two-hop members), we can dynamically untwist a tetrobot
 forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane.
-\end{theorem}
-
-\begin{proof}
-  Proof by our computer program that does this using Equation \eqref{eq:general} applied to the physical
+
+  Proof by our computer program that does this using  \cref{eq:general} applied to the physical
   7-tet Tetrobot.
@@
 hexapod gaits may be applied to make the robot walk or crawl.
-
-\end{proof}
 
@@
 
-The Tetrobot Project \url{http://pubinv.github.io/gluss/} is part of Public Invention \url{https://pubinv.github.io/PubInv/},
+The Tetrobot Project:\\  
+\url{http://pubinv.github.io/tetrobot/} is part of Public Invention,
 a free-libre, open-source research, hardware, and software project that welcomes volunteers.
-To assist, contact\\
+To assist, contact:\\
 \email{read.robert@gmail.com}.
@@
 
+May want to read this article:
+
+http://ieeexplore.ieee.org/abstract/document/7759811/?reload=true
+
 http://epubs.siam.org/toc/sjaabq/1/1
@@
 
-Basically by using the distributive nature of mod and the definiton of a helix,
+Basically by using the distributive nature of mod and the definition of a helix,
 the cardinality of the set can remove the PI factor in the sin(x) = sin(x mod 2PI).

### 2017-05-28 doc/TetrahelixUntwist.tex
abstract changed
final

@@
 
+%% TODO: Add something about Tetrobots into abstract.
 \begin{abstract}
@@
   A formula for the inradius of optimal tetrahelices is given.
-  Utility for static and variable geometry
-  truss/space frame design and robotics is discussed.
+  The continuum allows a regular Tetrobot in the BC configuration to untwist into a hexapodal or $n$-podal robot
+  to use standard gaits.
 \end{abstract}
@@
 Imagining \cref{fig:closeup,fig:closeuporthog} as a static mechanical structure,
-we observe that it is useful to the mechanical engineer or
-roboticist because the structure is an inherently rigid,
-omni-triangulated space frame, which is
-mechanically strong.
+we observe that it is useful to the mechanical engineer
+because the structure is a mechanically strong, inherently rigid,
+omni-triangulated space frame.
 Then we can imagine that each static edge is replaced with an
@@
 each tetrahedron has either a yellow, blue, or red outer edge or rail.
-That is, a blue-rail tetrahedron is rotated slightly more than a $1/3$ of a revolution to match the face of the yellow tetrahedra.
+That is, a blue-rail tetrahedron is rotated slightly more than a $1/3$ of a revolution to match the face of the yellow tetrahedron.
 
@@
 \end{equation}
-and where $n$ represents each integer numbered vertex in succession on every colored rail.
+and where $n$ represents each integer numbered vertex in succession on the $z$-axis.
 
@@
 This situation is illustrated in \cref{fig:helixcomparison}, wherein the black helix represents that
-generated by Equaiton \cref{graycoxeter},
+generated by \cref{graycoxeter},
 and the colored helices are generated by \cref{eq:colored}.
@@
 
-Note in \cref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In Equaiton \cref{graycoxeter} and  \cref{eq:colored}, the variable
+Note in \cref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In \cref{graycoxeter} and  \cref{eq:colored}, the variable
 $h$ is used for one third of the distance we name $d$. We will later justify that $d = 3h$.
@@
 
-In the proof below we find useful to consider projection diagrams that are the axial projection
+In the proof below we find it useful to consider projection diagrams that are the axial projection
 of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram} is an example of such a diagram.
@@
 Observe that although we have not get given the formula for the
-radii of such a triple helix, we observe there are some values for $r$ and $\alpha$, and $\phi$
+radii of such a triple helix, there are some values for $r$ and $\alpha$, and $\phi$
 in \cref{eq:triple}
@@
   \label{eventhirds}
-  An optimal tetrahelix of any rail angle $\rho < \pi$ is a triple helix with all vertices evenly spaced at $d/3$ intervals on the $z$ axis.
+  An optimal tetrahelix of any rail angle $0 \leq \rho < \pi$ is a triple helix with all vertices evenly spaced at $d/3$ intervals on the $z$ axis.
   Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail and $2$ two-hop edges connected to the rail.
@@
 This syntax just represents the Euclidean distance between vertices. Thus:
-
-\begin{align*}
-  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho}) - \vec{H}_{general}(n,c+1,\rho,d_{\rho}),r) || \\
-\end{align*}
-so:
 \begin{align*}
@@
 Although complicated, we can use Mathematica to investigate
-the partial derivative of the $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ with respect
+the partial derivative of $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ with respect
 to the radius to be able to understand how to choose the radius to form the minimax optimum.
@@
 (degenerate) case when the rail angle $\rho = 0$
-and $d = 1$ (the edgelength), where the cross sectional area is
+and $d = 1$ (the edge-length), where the cross sectional area is
 an equilateral triangle of unchanging orientation, as shown in \cref{fig:equitetrabeam} and at the rear of \cref{fig:series}.
@@
  Likewise, $\rho > \rho_{bc}$ generates
- a tetrahelix, but minimax optimality is not guaranteed by $\vec{H}_{general}$.
-
- The pitch of a helix for a fixed $z$-axis travel $d$
+ a tetrahelix, but we have not proved or investigated optimality in that range.
+
+ The pitch of a helix for a known $z$-axis travel $d$
  is trivial (see \cref{pitcheqn}).
-However, if one is computing 
-$z$-axis travel from \cref{dopt} the pitch is not simple.
-It increases monotonically and smoothly with decreasing $\rho$, so
+If one is varying $\rho$ to obtain a desired pitch
+from \cref{dopt} and \cref{pitcheqn} it is not so simple.
+However, the pitch increases monotonically and smoothly with decreasing $\rho$, so
 \cref{pitcheqn} can be easily solved numerically with a Newton-Raphson
@@
 as the tetrobot is, they often used repeated tetrahedral cells, so this
-work of pure geometry has some relevance to them.
+work of pure geometry has some applied relevance to them.
 
@@
 By changing only the length of the longer members that connect two
-distinct rails (the two-hop members), we can dynamically untwist a tetrobot
-forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane.
-
-  Proof by our computer program that does this using  \cref{eq:general} applied to the physical
-  7-tet Tetrobot.
+distinct rails (the two-hop members), we can dynamically untwist a physical Tetrobot
+forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane,
+as shown in \cref{fig:tetrobot}.
 
@@
 we may consider each vertex touching the ground a foot or pseudopod. A robot can thus
-become a hexapod or $n$-pod robot, and the already well-developed approaches to
+become a hexapod or $n$-pod tetrobot, and the already well-developed approaches to
 hexapod gaits may be applied to make the robot walk or crawl.

### 2017-06-15 doc/TetrahelixUntwist.tex
Edits from Daryl

@@
-\documentclass[review]{siamonline1116}
+% \documentclass[review]{siamonline1116}
+\documentclass[twocolumn,10pt]{asme2ej}
 % \usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
 % \usepackage{hyperref}
-% \usepackage{graphicx}
+\usepackage{graphicx}
 \usepackage{gensymb}
@@
 \usepackage{amsfonts}
-% \usepackage{hyperref}
+\usepackage{hyperref}
+\usepackage{cleveref}
 
@@
 
-% \newtheorem{theorem}{Theorem}
-% \newtheorem{corollary}{Corollary}
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
+\newtheorem{lemma}{Lemma}
 
@@
 \title{Untwisting the Boerdijk-Coxeter Helix}
-\author{Robert L. Read \email{read.robert@gmail.com}
+\author{Robert L. Read
+  \affiliation{
+    Founder, Public Invention \\
+    Austin, TX, 78704 \\
+    Email: \href{mailto:read.robert@gmail.com}{read.robert@gmail.com} 
+    }
 }
@@
 
-\begin{keywords}
-  Boerdijk-Coxeter helix, tetrahelix, robotics, tetrobot, unconventional robots,
-  structural engineering, mechanical engineering, tensegrity, variable-geometry truss
-\end{keywords}
-\begin{AMS}
-  51M15
-\end{AMS}
+%% \begin{keywords}
+%%   Boerdijk-Coxeter helix, tetrahelix, robotics, tetrobot, unconventional robots,
+%%   structural engineering, mechanical engineering, tensegrity, variable-geometry truss
+%% \end{keywords}
+%% \begin{AMS}
+%%   51M15
+%% \end{AMS}
 
@@
 a face-to-face stack of tetrahedra that winds about a straight axis.
-Because architects, structural engineers, and roboticists are inspired
-by and follow such regular mathematical models but can also build structures and
+Architects, structural engineers, and roboticists are inspired
+by and follow such regular mathematical models.
+However, since they can also build structures and
 machines of differing or even dynamically changing length, it is
@@
 such as the 3D printable Song-Kwon-Kim\cite{song2003spherical} joint or the CMS joint\cite{HamlinSandersonCMS}
-used in the original Tetrobot,
-which allow many members to meet in a single point.
+used in the original Tetrobot.
+This allows many members to meet in a single point.
 Such machines can
@@
 Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
-a term now commonly used. In this paper we reserve \emph{BC helix} to mean the purely regular structure and use \emph{tetrahelix} to refer
+a term now commonly used. In this paper, we reserve \emph{BC helix} to mean the purely regular structure and use \emph{tetrahelix} to refer
 to any structure isomorphic to the BC helix.
 
-\begin{figure}[H]
+\begin{figure}
   \centering
-     \includegraphics[width=0.95\textwidth]{figures/BCHelixCloseUp.png}
+     \includegraphics[width=0.45\textwidth]{figures/BCHelixCloseUp.png}
      \caption{BC Helix Close-up (partly along axis)}
@@
 \end{figure}
-\begin{figure}[H]
+\begin{figure}
   \centering
-     \includegraphics[width=0.95\textwidth]{figures/VerticalCloseUp.png}
+     \includegraphics[width=0.45\textwidth]{figures/VerticalCloseUp.png}
      \caption{BC Helix Close-up (orthogonal)}
@@
 
-Imagining \cref{fig:closeup,fig:closeuporthog} as a static mechanical structure,
+Imagining \cref{fig:closeup} or \cref{fig:closeuporthog} as a static mechanical structure,
 we observe that it is useful to the mechanical engineer
@@
 design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix},
-from which \cref{fig:closeup,fig:closeuporthog,fig:series,fig:naming,fig:equitetrabeam}
+from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
 are taken.
@@
   \centering
-     \includegraphics[width=1.0\textwidth]{figures/TetrahelixSeries2.png}
+     \includegraphics[width=0.45\textwidth]{figures/TetrahelixSeries2.png}
      \caption{A Continuum of Tetrahelices}
@@
 We would like to design nearly regular tetrahelices with a formula that
-gives the vertices in space. Eventually we would like to design them
+gives the vertices in space. Eventually, we would like to design them
 by choosing the lengths of a small set of members.
@@
 
-Ideally we would have a simple formula for defining the vertices based on
+Ideally, we would have a simple formula for defining the vertices based on
 any curvature or pitch we choose. It is a goal of
@@
 Note that $\theta_{bc}$ is approximately $0.37 \cdot 2 \pi$ radians or  $131.81$ degrees.
-The angle $\theta_{bc}$ is the rotation of \emph{each} tetrahedron, not the tetraheda along a rail.  In \cref{fig:closeup},
+The angle $\theta_{bc}$ is the rotation of \emph{each} tetrahedron, not the tetrahedra along a rail.  In \cref{fig:closeup},
 each tetrahedron has either a yellow, blue, or red outer edge or rail.
@@
 generated by \cref{graycoxeter},
-and the colored helices are generated by \cref{eq:colored}.
-
-In order to develop the continuum of slightly irregular tetrahelices described in \cref{sec:continuum},
+and the colored helices are generated by \cref{eq:colored}, below.
+
+In order to develop the continuum of slightly irregular tetrahelices,
 we need a formula that gives us the vertices of just
@@
   \centering
-     \includegraphics[width=0.7\textwidth]{figures/Unified.png}
+     \includegraphics[width=0.45\textwidth]{figures/Unified.png}
      \caption{Rail helices (H) vs. Coxeter/Gray helix (V) }
@@
 at real values generates the black helix which runs through every vertex, and \cref{eq:colored} defines
-the red, yellow, and blue helices. (In this figure
+the red, yellow, and blue helices. In this figure,
 these rail helices have been rendered at a slightly higher radius than the vertices for clarity;
-in actuality the maximum distance between the continuous, curved helix and the
-straight edges between vertices is much smaller than can be clearly rendered.)
+in actuality, the maximum distance between the continuous, curved helix and the
+straight edges between vertices is much smaller than can be clearly rendered.
 
@@
 $ \vec{V}(3(n+1)+c)= \vec{H}_{BCcolored}(n+1,c)$.
-This quantity appears so often that we call it the ``rail angle $\rho$''. For the BC helix, $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$.
-
-\begin{figure}[H]
+This quantity appears so often that we call it the ``rail angle, $\rho$''. For the BC helix, $\rho_{bc} = (3 \theta_{bc} - 2 \pi)$.
+
+\begin{figure}
      \centering
-     \includegraphics[width=0.7\textwidth]{figures/RailAngleGeometry.png}
+     \includegraphics[width=0.45\textwidth]{figures/RailAngleGeometry.png}
      \caption{Rail Angle Geometry}
@@
 
-Note in \cref{railanglefig} the $z$-axis travel for one rail edge is denoted by $d$. In \cref{graycoxeter} and  \cref{eq:colored}, the variable
-$h$ is used for one third of the distance we name $d$. We will later justify that $d = 3h$.
-In this paper we assume the length of a rail
-is always $1$ as a simplification, except in proofs concenring rail length.
-(We make the rail length a parameter in our JavaScript code in
-\url{https://github.com/PubInv/tetrahelix/blob/master/js/tetrahelix_math.js} \cite{readtetrahelix}.)
+Note, in \cref{railanglefig}, the $z$-axis travel for one rail edge is denoted by $d$. In \cref{graycoxeter} and  \cref{eq:colored}, the variable
+$h$ is used for one third of the distance, we name $d$. We will later justify that $d = 3h$.
+In this paper, we assume the length of a rail
+is always $1$ as a simplification, except in proofs concerning rail length.
+We make the rail length a parameter in our JavaScript code in
+\url{https://github.com/PubInv/tetrahelix/blob/master/js/tetrahelix_math.js} \cite{readtetrahelix}.
 
 The $\vec{H}_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho_{bc}$ rather than $\theta_{bc}$.
-Intuitively we seek an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
+Intuitively, we seek an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
 We expand 
@@
 
-Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued.)
+Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued).
 We can now assert that in \cref{fig:helixcomparison} the black helix winds at
@@
 $p(\rho_{bc})$:
-\begin{align*}
+\begin{equation}
    \frac{3 h_{bc}  2 \pi }{\rho_{bc}} 
@@
  \text{.}
-\end{align*}
+\end{equation}
 
@@
 has been explored\cite{sadler2013periodic}. 
-We develop below slightly irregular edge lengths that support, for example, a pitch of precisely 12
+We develop, below, slightly irregular edge lengths that support, for example, a pitch of precisely 12
 tetrahedra in one revolution which would allow an architect to
@@
 optimal tetrahelices are in fact triple helices with the same radius, so that all
-vertices are on a cylinder. In stages, we demonstrate that optimal tetrahelices:
+vertices are on a cylinder. In stages, we demonstrate that the helices in optimal tetrahelices:
 \begin{enumerate}
@@
 \item have the same radius,
-  \item have the same rail lengths,
+  \item have the same rail length,
   \item have axially equidistant vertices, and therefore
@@
 two rails, as we move
-from vertex to vertex away from our start edge the edge lengths
+from vertex to vertex away from our start edge, the edge lengths
 between rails must always lengthen without bound,
@@
 
-In the proof below we find it useful to consider projection diagrams that are the axial projection
+In the proof, below, we find it useful to consider projection diagrams that are the axial projection
 of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram} is an example of such a diagram.
@@
   Because $\pi$ is transcendental and irrational,
-  $2\pi/\rho$ is rational if and only $\rho = a\pi/b$, where $a$ and $b$ are integers
-  and without loss of generality $a$ and $b$ are coprime.
+  $2\pi/\rho$ is rational if and only if $\rho = a\pi/b$, where $a$ and $b$ are integers
+  and, without loss of generality, $a$ and $b$ are coprime.
   Since $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
@@
   This polygon has at least 3 sides, since either $\rho$ is irrational or $b > a$, and therefore
-  $b >= 2$. If $a/b = 1/2$, the projection is a square, which has four sides. 
+  $b \geq 2$. If $a/b = 1/2$, the projection is a square, which has four sides. 
 \end{proof}
@@
   Case 2: Suppose that $\rho$ is positive but less than $\pi$.
-  In this case each rail helix has
+  In this case, each rail helix has
   curvature. The projection of points in the $XY$ plane creates a figure
@@
 
-  Without loss of generality define the Red helix to have its axis on the $z$-axis.
+  Without loss of generality, define the Red helix to have its axis on the $z$-axis.
   Since there must be at least one Red-to-Yellow or a Red-to-Blue edge that is either a minimum or a maximum,
-  without loss of generatlity define the Blue helix to be a helix that
+  without loss of generality, define the Blue helix to be a helix that
   has an edge connection to the Red helix that is either a maximum or a minimum.
@@
 
-  \begin{figure}[H]
+  \begin{figure}
      \centering
-     \includegraphics[width=0.7\textwidth]{figures/WobbleDiagram.png}
+     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram.png}
      \caption{Wobble Vectors from Non-Coincident Axes}
@@
   contains at least three vectors,
-  at least two of which pointing in different directions.
+  at least two of which point in different directions.
   For any point not at the origin, at least one of these vectors moves closer to the
@@
     The set of all lengths in the tetrahelix is a superset of:
-    $L = \{|| \vec{R}(n) - \vec{B}(n)||\}$, which by our choice has at least one longest or shortest
+    $L = \{|| \vec{R}(n) - \vec{B}(n)||\}$, which, by our choice,
+    has at least one longest or shortest
     length.
@@
     decreases.  
-    By our choice that their is a Blue-to-Red edge that is either a maximum or a minimum,
+    By our choice that there is a Blue-to-Red edge that is either a maximum or a minimum,
     this improves the minimax value of the total tetrahelix.
@@
 Note that we have not yet shown that the relationships of the radius $r_c$ or
-the phase $\phi_c$ for the three helies, so we denoted them with a $c$ subscript to show
+the phase $\phi_c$ for the three helices, so we denoted them with a $c$ subscript to show
 they are dependent on the color.
@@
 $\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple}.
-In \cref{sec:parameterizing} we give a more specific version of this formula which
+In \cref{sec:parameterizing}, we give a more specific version of this formula which
 generates optimal tetrahelices.
@@
 
-\begin{figure}[H]
+\begin{figure}
   \centering
-     \includegraphics[width=0.95\textwidth]{figures/edge-diagram.png}
+     \includegraphics[width=0.45\textwidth]{figures/edge-diagram.png}
      \caption{Edge Naming}
@@
 
-In principle any three helices generated with \cref{eq:triple}
+In principle, any three helices generated with \cref{eq:triple}
 has at most nine distinct edge length classes. Each edge that connects
@@
 where the two-hop length is at least the one-hop length.
-However, if we generate the three helices symmetrically with \cref{eq:triple},
+However, if we symmetrically generate the three helices  with \cref{eq:triple},
 many of these lengths will be the same.
@@
 \begin{theorem}
-  Optimal tetrahelices have the same radii for all three helices.
+  Optimal tetrahelices have the same radius for all three helices.
 \end{theorem}
 \begin{proof}
-To prove this we exhibit a symmetric tetrahelix (not yet shown to be optimal) which
+To prove this theorem, we exhibit a symmetric tetrahelix (not yet shown to be optimal) which
 happens to be a triple helix, that has
@@
 Since there exists a tetrahelix which has only two distinct classes of edge lengths,
-(the smaller being one-hop = rail, the larger being the two-hop distance), the helix
+(he smaller being one-hop = rail, the larger being the two-hop distance, the helix
 with a larger radius increases a longest edge without increasing a shortest edges.
@@
 proved that a two-class tetrahelix is optimal, but it suffices to show that there
-exist such a better tetrahelix to show that different radii imply a suboptimal
+exists such a better tetrahelix to show that different radii imply a suboptimal
 tetrahelix.
@@
 of any optimal tetrahelix will lie on a cylinder, or a circle when the axis dimension
-is projected out. Therefore it is reasonable to now speak of the singular \emph{radius} $r$
+is projected out. Therefore, it is reasonable to now speak of the singular radius $r$
 of a tetrahelix as the radius of the cylinder.
@@
 
- We show that in fact the vertices must be distributed in even thirds
- along the $z$-axis, as in fact they are in the regular BC helix.
+ We show that, in fact, the vertices must be distributed in even thirds
+ along the $z$-axis as they are in the regular BC helix.
 
@@
 
-\begin{figure}[H]
+\begin{figure}
      \centering
-     \includegraphics[width=0.8\textwidth]{figures/EquitetrabeamCloseUp.png}
+     \includegraphics[width=0.45\textwidth]{figures/EquitetrabeamCloseUp.png}
      \caption{Equitetrabeam}
@@
   An optimal tetrahelix of any rail angle $0 \leq \rho < \pi$ is a triple helix with all vertices evenly spaced at $d/3$ intervals on the $z$ axis.
-  Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail and $2$ two-hop edges connected to the rail.
+  Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail, and $2$ two-hop edges connected to the rail.
   The sixth edge is opposite of the rail edge and is a one-hop edge.
@@
     Every vertex is connected to 4 non-rail edges. There is a one-hop edge
-    in both the positive and negative $z$ direction. Likewise there is a two-hop
+    in both the positive and negative $z$ direction. Likewise, there is a two-hop
     edge in both the positive and negative $z$ direction. Let $A$ be the set
@@
     The minimax of $B$ is greater than the minimax of $A$ since there is a single rail length which cannot be both greater
-    than $t'$ and $o'$ and less than $t'$ and $o'$.
+    than $o'$ and $t'$ and less than $o'$ and $t'$.
     Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other, and
-    all two-hop edges equal to each other, the $z$ distances between rails equal. Therefore vertices are
+    all two-hop edges equal to each other, and the $z$ distances between rails equal. Therefore, vertices are
     $d/3$ from each other on the $z$-axis.
@@
 Taking all of these results together, 
-each helix in an optimal tetrahelix is congruent to the others, shares an axis, is the same radius, and are evenly spaced
-axially.
+each helix in an optimal tetrahelix is congruent to the others, shares an axis, is the same radius, and is evenly spaced
+axially with the others.
 An optimal tetrahelix is therefore a \emph{triple helix}, of a radius we have not yet demonstrated.
@@
 input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
-formed in the X,Y plane with origin $O$: $\angle \vec{H}(0,0) O \vec{H}(0,1)$ projecting out the $z$
-axis and sighting along the positive $z$ axis. In other words, $\rho$
+formed in the X,Y plane with origin $O$: $\angle \vec{H}(0,0) O \vec{H}(0,1)$ projecting out the
+$z$-axis and sighting along the positive $z$a-xis. In other words, $\rho$
 controls how far a rail edge of a tetrahelix deviates from being
@@
 
-$\vec{H}_{general}$ forces the user to select three values: $\rho$, $r_{\rho}$, and $d_{\rho}$ satisfying \cref{railangle}.
+$\vec{H}_{general}$ forces the user to select three values satisfying \cref{railangle}: $\rho$, $r_{\rho}$, and $d_{\rho}$.
 
@@
   For rail angles of magnitude at most $\rho_{bc}$, tetrahelices generated by
-  $\vec{H}_{general}$ are optimal in terms of minimum maximum ratio of member
+  $\vec{H}_{general}$ are optimal in terms of minimum maximum (minimax) ratio of member
   length when radius is chosen so that
@@
 We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
-By inspection it seems likely that we will minimize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
+By inspection, it seems likely that we will minimize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
 to 1, but to be absolutely sure and to decide which one, we must examine the partial derivative of the ratio
@@
 By graph inspection using Mathematica (\url{https://github.com/PubInv/tetrahelix/blob/master/tetrahelix.nb}), we see the partial derivative of this with respect to
-radius $r$ is always negative, for any $\rho \leq \rho_{bc}$. (When the rail angle approaches
+radius $r$ is always negative, for any $\rho \leq \rho_{bc}$. When the rail angle approaches
 $\pi$, corresponding to going almost to the other side of the tetrahelix, this is not necessarily true, hence the
-limitation in our statement of the theorem is meaningful.)
+limitation in our statement of the theorem is meaningful.
 Since the partial derivative of  $\frac{\text{two-hop}(r)}{\text{one-hop}(r)}$ with respect to the
@@
 we minimize the maximum edge-length ratio by choosing the largest radius
-up until one-hop $= 1$, the rail-edge length. If we attempted to increase the radius further
+up until one-hop $= 1$, the rail-edge length. If we attempted to further increase the radius
 we would not be optimal, because the ratio $\frac{\text{two-hop}(r)}{1}$ would become the
@@
 
-Therefore we decrease the minimax length
+Therefore, we decrease the minimax length
 of the whole system as we increase the radius
@@
 
-Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix for an $0 \leq \rho \leq \rho_{bc}$.
+Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix where $0 \leq \rho \leq \rho_{bc}$.
 %% Add here references to these equations.
@@
 
-\begin{figure}[H]
+\begin{figure}
      \centering
-     \includegraphics[width=0.4\textwidth]{figures/AxialView.png}
+     \includegraphics[width=0.45\textwidth]{figures/AxialView.png}
      \caption{Axial view of a BC-Helix}
@@
 
-\begin{figure}[H]
+\begin{figure}
      \centering
-     \includegraphics[width=0.8\textwidth]{figures/ProjectionDiagram.png}
+     \includegraphics[width=0.45\textwidth]{figures/ProjectionDiagram.png}
      \caption{General One-hop Projection Diagram}
@@
 
-From this equation with the help of symbolic computation we observe that inradius of the BC helix of unit rail length is $r_{in(\rho_{bc})} = \frac{3}{10\sqrt{2}} \approx 0.21$.
+From this equation, with the help of symbolic computation, we observe that inradius of the BC helix of unit rail length is $r_{in(\rho_{bc})} = \frac{3}{10\sqrt{2}} \approx 0.21$.
 
@@
 may have dissuaded structural engineers from using this geometry.
-However, the advent of additive manufacturing, such a 3D printing, and the invention of two
+However, the advent of additive manufacturing, such as 3D printing, and the invention of two
 distinct concentric multimember joints\cite{song2003spherical,HamlinSandersonCMS} has improved that situation.
@@
 
-In this way a rail angle can be chosen for any desired (sufficiently large) pitch, yielding
+In this way, a rail angle can be chosen for any desired (sufficiently large) pitch, yielding
 the optimum radius, the one-hop length, and the two-hop length that an engineer needs to
@@
 using a linear interpolation between the optimal radius for the
-Equitetrabeam and the BC Helix. This minimax optimum of this simpler
+equitetrabeam and the BC Helix. This minimax optimum of this simpler
 approach was at most 1\% worse than the optimum computed by
@@
 mathematical starting point rather than the final word on the beauty and utility of
-physical structures. For example, a structural engineer might increase
+physical structures. For example, a structural engineer might increase a
 radius past optimality in order to resist buckling.
@@
 
-\begin{figure}[H] %float with two figures
+\begin{figure}
   \centering
-     \includegraphics[width=0.9\textwidth]{figures/MedCantedCropped.png}
+     \includegraphics[width=0.5\textwidth]{figures/MedCantedCropped.png}
      \caption{7-Tet Tetrobot in relaxed, or BC helix configuration}
-     \includegraphics[width=0.9\textwidth]{figures/EquitetrabeamCropped.png}
+     \includegraphics[width=0.5\textwidth]{figures/EquitetrabeamCropped.png}
      \caption{The Equitetrabeam: Fully Untwisted 7-Tet Tetrobot in Hexapod Configuration}
@@
 the lengths of members joined at the center of a joint, thereby
-creating a connection to pure geometry. More recently NASA has
-experimented with tensegrities\cite{NTRT}, a different point in the
-same design spectrum. In particular the tetrahelix is related to the
+creating a connection to pure geometry. More recently, NASA has
+experimented with tensegrities\cite{NTRT,chen2017soft}, a different point in the
+same design spectrum. In particular, the tetrahelix is related to the
 tetraspline\cite{mirletz2014} concept used as a physical concept of a tensegrity robot.
 Although tensegrities are not member-for-member isomorphic to the tetrahelix
-as the tetrobot is, they often used repeated tetrahedral cells, so this
+as the tetrobot is, they often use repeated tetrahedral cells, so this
 work of pure geometry has some applied relevance to them.
@@
 To assist, contact:\\
-\email{read.robert@gmail.com}.
+\href{mailto:read.robert@gmail.com}{read.robert@gmail.com}.
 

### 2017-06-16 doc/TetrahelixUntwist.tex
formatted for Mechanisms and Robotic

@@
 rotation is:
-\[
+\begin{equation}
 \theta_{bc} = \arccos(-2/3) 
-\]
+\end{equation}
 and the translation:
-\[
+\begin{equation}
 h_{bc} = 1/\sqrt{10}.
-\]
+\end{equation}
 
@@
   \right ],
-\text{where:}
-  \begin{tabular}{c}
+\end{equation}
+\text{where: \qquad}
+  \begin{tabular}{l}
  $ r_{bc} = \frac{3\sqrt{3}}{10} \approx 0.5196 $,\\
@@
   \end{tabular}
-\end{equation}
-and where $n$ represents each integer numbered vertex in succession on the $z$-axis.
+
+and $n$ represents each integer numbered vertex in succession on the $z$-axis.
 
@@
   \right ],
-\text{where}
-  \begin{tabular}{c}
+\end{equation}
+\text{where:  \qquad}
+  \begin{tabular}{l}
  $ r_{bc} = \frac{3\sqrt{3}}{10} $,\\
@@
   \end{tabular}
-\end{equation}
 
@@
 finally we obtain:
-\begin{align*}
+\begin{equation}
   c  ( \rho_{bc} +  2 \pi) /3  \text{.}
-\end{align*}
+\end{equation}
 
@@
   \right ],
-\text{where}
-  \begin{tabular}{c}
+\end{equation}
+\text{where: \qquad}
+  \begin{tabular}{l}
 %%  $\kappa = n + c/3$ \\
@@
 moves us $\rho_{bc}$ radians around a circle. Since:
-\[ \frac{2 \pi}{\rho_{bc}} \approx 10.16
-\]
+$ \frac{2 \pi}{\rho_{bc}} \approx 10.16 $
 we can see that there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a
@@
   Define a wobble vector by:
-  \begin{equation*}
+  \begin{equation}
     \vec{W}(n) = \vec{B}(n) - \vec{B}'(n) \text{ .}
-  \end{equation*}
+  \end{equation}
   where $\vec{B}(n)$ and $\vec{B'}(n)$ is the vector
@@
   \right ],
-\text{where:}
-\begin{tabular}{c}
-  $c \in \{0,1,2\}$
+\end{equation}
+\text{where: \qquad}
+\begin{tabular}{l}
+  $c \in \{0,1,2\}$,
   \end{tabular}
-\end{equation}
+
 which would be much more complicated if the axes where not coincident.
@@
 Rewriting our formulation in terms of $\rho$:
-\begin{align*}
-\numberthis  \label{eq:general}  
-\vec{H}_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) &= 
+\begin{equation}
+  \begin{split}
+  \label{eq:general}  
+\vec{H}_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) = \\ 
  \left [
@@
   \right ] \\
-\text{where: } &
-\begin{tabular}{c}
+   \end{split}
+\end{equation}  
+\text{where: \qquad} 
+\begin{tabular}{l}
   $   1 = d_{\rho}^2 + 4 r_{\rho}^2 (\sin{ \rho / 2})^2 $, and \\
@@
 \end{tabular}
-\end{align*}
 
@@
 tetrahelix by formula universally quantified by $n$ and $c$:
-\begin{align*}
-  \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || = 1 \text{ ,} \\
-  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{ and,} \\
-  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r) - \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \text{ .}\\  
-\end{align*}
+\begin{equation}
+  \begin{split}
+  1 = \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
+  &  \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r))  \text{ ,} \\
+  \end{split}
+\end{equation}
+\begin{equation}
+  \begin{split}  
+  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
+  &  \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{ and,} \\
+  \end{split}  
+\end{equation}  
+  \begin{equation}
+  \begin{split}    
+  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
+  &  \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \text{ .}\\
+  \end{split}  
+\end{equation}
+
 This syntax just represents the Euclidean distance between vertices. Thus:
-\begin{align*}
+\begin{equation}
 %%  \text{one-hop} &= dist(\vec{H}_{general}(0,0,\rho,d_{\rho}),\vec{H}_{general}(0,1,\rho,d_{\rho},r))  \\  
@@
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.
-  \text{one-hop}  &= \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
-\end{align*}
-but: $  d_{\rho}^2 = 1 - 4 r^2 (\sin( \rho / 2)^2$, so we substitute:
-\begin{align*}
-  %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.  
-  \text{one-hop}  &= \sqrt{\frac{1}{9}  + r^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{.}\\
-  %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.    
-\end{align*}
+  \text{one-hop}  = \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} 
+\end{equation}
+
+where: $  d_{\rho}^2 = 1 - 4 r^2 (\sin( \rho / 2)^2$.
+
+%% so we substitute:
+%% \begin{align*}
+%%   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.  
+%%   \text{one-hop}  &= \sqrt{\frac{1}{9}  + r^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{.}\\
+%%   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.    
+%% \end{align*}
 
 By similar algebra and trigonometry:
-\begin{align*}
-  \text{two-hop}  &= \sqrt{\frac{4}{9} + r^2 (-\frac{16 (\sin^2( \rho / 2))}{9} + \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \text{.}\\
-\end{align*}
+\begin{equation}
+  \text{two-hop}  = \sqrt{\frac{4 d_{\rho}^2}{9} +  \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \text{.}\\
+\end{equation}
 
@@
 Let:
-\begin{equation*}
+\begin{equation}
   f_{\rho} = -\frac{4 (\sin^2( \rho / 2))}{9} \text{,}
-  \end{equation*}
-\begin{equation*}
+  \end{equation}
+\begin{equation}
   g_{\rho} = -\frac{16 (\sin^2( \rho / 2))}{9} \text{,}
-\end{equation*}
-\begin{equation*}
+\end{equation}
+\begin{equation}
   j_{\rho} = \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2 \text{,}
-\end{equation*}
+\end{equation}
 and:
-\begin{equation*}
+\begin{equation}
   k_{\rho} = \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2 \text{.}
-\end{equation*}
+\end{equation}
 
 Then:
-\begin{align*}
+\begin{equation}
+  \begin{split}
   \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
@@
        {\sqrt{\frac{1}{9} +r^2(f_{\rho}+k_{\rho}) }} \text{.}
-\end{align*}
+  \end{split}       
+\end{equation}
 
@@
 
-\begin{align*}
-  1 &=  \sqrt{\frac{1}{9}  + r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{, so...} \\
-  r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }} \text{ .} \numberthis  \label{eqrhoopt} \\
-\end{align*}
+\begin{equation}
+  1 =  \sqrt{
+    \begin{tabular}{ccc}
+    $  \frac{1}{9} $ & + & $ r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} \; \;+ $\\
+$      \sin^2(\rho/3+ \frac{2\pi}{3}) $ & + & $ (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2) $
+    \end{tabular}
+    }
+\end{equation}    
+from which it follows that:
+
+\begin{equation}
+  r_{opt} = \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }} \text{ .} \numberthis  \label{eqrhoopt}
+\end{equation}
 
@@
 
-\begin{align*}
-  d_{opt}^2 &= 1 - 4 (\frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }})^2 (\sin{ \rho / 2})^2   \\
+\begin{equation}
+  %%  d_{opt}^2 &= 1 - 4 (\frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }})^2 (\sin{ \rho / 2})^2   \\
+  d_{opt}^2 = 1 - 4 (r_{opt})^2 (\sin{ \rho / 2})^2,
+\end{equation}
+which we can expand,
+\begin{equation}
 %%  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
-  d_{opt}^2 &= 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
+  d_{opt}^2 = 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
+\end{equation}
+and then rewrite:
+\begin{equation}
 %%  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
-    d_{opt} &= \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}  \text{ .}  \numberthis  \label{dopt}  \\      
-\end{align*}
+    d_{opt} = \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}  \text{ .}  \numberthis  \label{dopt}  \\      
+\end{equation}
 

### 2017-06-16 doc/TetrahelixUntwist.tex
read-through with new formatting

@@
 three helices about the central axis.
-The \\
+The 
 Tetrobot\cite{readglussbot,TetrobotBook} uses the regularity of
@@
 Imagining \cref{fig:closeup} or \cref{fig:closeuporthog} as a static mechanical structure,
-we observe that it is useful to the mechanical engineer
+we can observe that it is useful to the mechanical engineer
 because the structure is a mechanically strong, inherently rigid,
@@
   \end{tabular}      
-
 which would be much more complicated if the axes where not coincident.
@@
 Since there exists a tetrahelix which has only two distinct classes of edge lengths,
-(he smaller being one-hop = rail, the larger being the two-hop distance, the helix
+the smaller being one-hop = rail, the larger being the two-hop distance, the helix
 with a larger radius increases a longest edge without increasing a shortest edges.
@@
 By \cref{eventhirds}, we can compute the (at most) three edge-lengths of an optimal
-tetrahelix by formula universally quantified by $n$ and $c$:
+tetrahelix by formulae universally quantified by $n$ and $c$:
 \begin{equation}
@@
 which can be seen from the trigonometry of a diagram of the projected one-hop edges
-connecting four sequentially numbered vertices:
+connecting four sequentially numbered vertices, shown in \cref{fig:projectiondiagram}.
 
@@
 \begin{corollary}
-  The equitetrabeam with minimal maximal edge ratio is produced
+  The equitetrabeam with minimum maximum edge ratio is produced
   \newline by $\vec{H}_{general}$ when $ r = \sqrt{\frac{8}{27}} $ and the longest member is $\frac{2}{\sqrt{3}}$,

### 2017-06-17 doc/TetrahelixUntwist.tex
update

@@
   computing the
-  parameters that give edge-length minimax-optimal tetrahelices
+  parameters that give proven edge-length minimax-optimal tetrahelices
   are given, defining a continuum of optimum tetrahelices of varying curvature.
+  Only $1/3$rd of the members in the system change their length to reach
+  any point in the continuu.
   The endpoints of this continuum are the BC helix and
@@
   A formula for the inradius of optimal tetrahelices is given.
-  The continuum allows a regular Tetrobot in the BC configuration to untwist into a hexapodal or $n$-podal robot
+  The continuum allows a regular Tetrobot supporting a length change of less than $16\%$ in the
+  BC configuration to untwist into a hexapodal or $n$-podal robot
   to use standard gaits.
@@
 
-The BC Helix is the end point of a continuum of tetrahelices, the
-other end point being an untwisted tetrahelix with equilateral cross
-section, constructed by changing the length of only those members
-crossing the outside rails after hopping over the nearest
-vertex. Under the condition of minimum maximum length ratios of
-all members in the system, all such tetrahelices have vertices evenly
+There exists a continuum of minimax edge-length optimal tetrahelices
+having as one end-poing the Boerdijk-Coxeter Helix and at  the
+other end point a completely untwisted tetrahelix with equilateral cross
+section and planar faces, the equitetrabeam.
+By changing the length of only $1/3$ of
+the members by less than $16\%$, all configurations in the continuum may be reached.
+All such optimal tetrahelices have vertices evenly
 spaced along the axis generated by a simple equation and are in fact triple helices.
 A machine, such as a robot or a variable-geometry truss, that can change
-the length of its members can thus twist and untwist itself by
-changing the length of the appropriate members to achieve any point in
-the continuum. With a numeric solution, a designer may choose
-a rotation angle and member lengths to obtain a desired pitch.
+the length of its members by $16\%$ can thus twist and untwist itself.
+A completely regular Tetrobot can thus untwist itself to create a planar
+face on the ground for locomotion.
+With a numeric solution, a designer may choose
+a rotation angle and member lengths to obtain an optimal tetrahelix design
+of any pitch.
 
@@
 
-\bibliographystyle{siamplain}
+\bibliographystyle{asmems4}
 \bibliography{IEEEabrv,gluss}

### 2017-06-17 doc/TetrahelixUntwist.tex
changing abstract

@@
   are given, defining a continuum of optimum tetrahelices of varying curvature.
-  Only $1/3$rd of the members in the system change their length to reach
-  any point in the continuu.
   The endpoints of this continuum are the BC helix and
   a structure of zero curvature, the \emph{equitetrabeam}.
+  Only one out of three members in the system change their length to reach
+  any point in the continuum.
   Numerically finding the rail angle from the equation for
@@
 There exists a continuum of minimax edge-length optimal tetrahelices
-having as one end-poing the Boerdijk-Coxeter Helix and at  the
-other end point a completely untwisted tetrahelix with equilateral cross
+having as one end the Boerdijk-Coxeter Helix and at  the
+other end a completely untwisted tetrahelix with equilateral cross
 section and planar faces, the equitetrabeam.
-By changing the length of only $1/3$ of
-the members by less than $16\%$, all configurations in the continuum may be reached.
-All such optimal tetrahelices have vertices evenly
-spaced along the axis generated by a simple equation and are in fact triple helices.
+By changing the length of only one out of three members by less than $16\%$,
+all configurations in the continuum may be reached.
+All such optimal may be generated by a simple equation giving coordinates or by
+selecting approprate edge-lengths.
+All such optimal tetrahelices are proven to be triple helices.
 A machine, such as a robot or a variable-geometry truss, that can change
-the length of its members by $16\%$ can thus twist and untwist itself.
-A completely regular Tetrobot can thus untwist itself to create a planar
+the length of some of its members by $16\%$ can thus twist and untwist itself.
+A completely regular Tetrobot can untwist itself to create a planar
 face on the ground for locomotion.
 With a numeric solution, a designer may choose
-a rotation angle and member lengths to obtain an optimal tetrahelix design
-of any pitch.
+a rotation angle to obtain an optimal tetrahelix design
+of any pitch, including rational ones.
 

### 2017-06-19 doc/TetrahelixUntwist.tex
retitling and re-arrangement

@@
 
-\title{Untwisting the Boerdijk-Coxeter Helix}
+\title{A Continuum of Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix}
 \author{Robert L. Read
@@
 
+Trusses and space frames remain an important design field in
+mechanical and structural engineering\cite{mikulas1985sequentially},
+including deployable and moving trusses\cite{claypool2012readily,gezgin2017new}.
+
+\subsection{Utility for Robotics}
+
+\begin{figure}
+  \centering
+     \includegraphics[width=0.5\textwidth]{figures/MedCantedCropped.png}
+     \caption{7-Tet Tetrobot in relaxed, or BC helix configuration}
+     \includegraphics[width=0.5\textwidth]{figures/EquitetrabeamCropped.png}
+     \caption{The Equitetrabeam: Fully Untwisted 7-Tet Tetrobot in Hexapod Configuration}
+     \label{fig:tetrobot}
+\end{figure}
+
+Starting twenty years ago, Sanderson\cite{sanderson1996modular},
+Hamlin,\cite{TetrobotBook}, Lee\cite{lee2002dynamic}, and others
+ created a style of robotics based on changing
+the lengths of members joined at the center of a joint, thereby
+creating a connection to pure geometry. More recently, NASA has
+experimented with tensegrities\cite{NTRT,chen2017soft}, a different point in the
+same design spectrum. In particular, the tetrahelix is related to the
+tetraspline\cite{mirletz2014} concept used as a physical concept of a tensegrity robot.
+Although tensegrities are not member-for-member isomorphic to the tetrahelix
+as the tetrobot is, they often use repeated tetrahedral cells, so this
+work of pure geometry has some applied relevance to them.
+
+As suggested by Buckminster Fuller, the most convenient geometries to
+consider are those that have regular member lengths, in order to
+facilitate the inexpensive manufacture and construction of the robot.
+In a plane, the octet truss\cite{richard1961synergetic} is such a geometry, but in a line, the
+Boerdijk-Coxeter helix is a regular structure.
+
+However, a robot must move, and so it is interesting to consider the
+transmutations of these regular geometries. Developing a functional
+gait for our physical Tetrobot was in fact the motivation
+for this work.
+By changing only the length of the longer members that connect two
+distinct rails (the two-hop members), we can dynamically untwist a physical Tetrobot
+forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane,
+as shown in \cref{fig:tetrobot}.
+
+By untwisting the tetrahelix so that is has a planar surface resting on the ground,
+we may consider each vertex touching the ground a foot or pseudopod. A robot can thus
+become a hexapod or $n$-pod tetrobot, and the already well-developed approaches to
+hexapod gaits may be applied to make the robot walk or crawl.
+
 \section{A Designer's Formulation of the BC Helix}
@@
 
-Trusses and space frames remain an important design field in
-mechanical and structural engineering\cite{mikulas1985sequentially},
-including deployable and moving trusses\cite{claypool2012readily}.
-
-\begin{figure}
-  \centering
-     \includegraphics[width=0.5\textwidth]{figures/MedCantedCropped.png}
-     \caption{7-Tet Tetrobot in relaxed, or BC helix configuration}
-     \includegraphics[width=0.5\textwidth]{figures/EquitetrabeamCropped.png}
-     \caption{The Equitetrabeam: Fully Untwisted 7-Tet Tetrobot in Hexapod Configuration}
-     \label{fig:tetrobot}
-\end{figure}
-
-\section{Utility for Robotics}
-
-Starting twenty years ago, Sanderson\cite{sanderson1996modular},
-Hamlin,\cite{TetrobotBook}, Lee\cite{lee2002dynamic}, and others
- created a style of robotics based on changing
-the lengths of members joined at the center of a joint, thereby
-creating a connection to pure geometry. More recently, NASA has
-experimented with tensegrities\cite{NTRT,chen2017soft}, a different point in the
-same design spectrum. In particular, the tetrahelix is related to the
-tetraspline\cite{mirletz2014} concept used as a physical concept of a tensegrity robot.
-Although tensegrities are not member-for-member isomorphic to the tetrahelix
-as the tetrobot is, they often use repeated tetrahedral cells, so this
-work of pure geometry has some applied relevance to them.
-
-As suggested by Buckminster Fuller, the most convenient geometries to
-consider are those that have regular member lengths, in order to
-facilitate the inexpensive manufacture and construction of the robot.
-In a plane, the octet truss\cite{richard1961synergetic} is such a geometry, but in a line, the
-Boerdijk-Coxeter helix is a regular structure.
-
-However, a robot must move, and so it is interesting to consider the
-transmutations of these regular geometries. Developing a functional
-gait for our physical Tetrobot was in fact the motivation
-for this work.
-By changing only the length of the longer members that connect two
-distinct rails (the two-hop members), we can dynamically untwist a physical Tetrobot
-forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane,
-as shown in \cref{fig:tetrobot}.
-
-By untwisting the tetrahelix so that is has a planar surface resting on the ground,
-we may consider each vertex touching the ground a foot or pseudopod. A robot can thus
-become a hexapod or $n$-pod tetrobot, and the already well-developed approaches to
-hexapod gaits may be applied to make the robot walk or crawl.
-
 \section{Conclusion}
@@
 all configurations in the continuum may be reached.
-All such optimal may be generated by a simple equation giving coordinates or by
-selecting approprate edge-lengths.
-All such optimal tetrahelices are proven to be triple helices.
+All such optimal tetrahelices may be generated by a simple equation giving coordinates or by
+selecting approprate edge-lengths and are in fact triple helices.
 A machine, such as a robot or a variable-geometry truss, that can change
@@
 a free-libre, open-source research, hardware, and software project that welcomes volunteers.
-To assist, contact:\\
+To assist, contact:
 \href{mailto:read.robert@gmail.com}{read.robert@gmail.com}.

### 2017-06-19 doc/TetrahelixUntwist.tex
final yet again

@@
   The Boerdijk-Coxeter helix (BC helix, or tetrahelix) is a
-  face-to-face stack of regular tetrahedra forming a helical column.  Considering the edges of
-  these tetrahedra as structural members, the resulting structure is attractive and
-  inherently rigid, and therefore interesting to architects,
+  face-to-face stack of regular tetrahedra forming a helical column.  Treating the edges of
+  these tetrahedra as structural members creates an attractive and
+  inherently rigid space frame, and therefore interesting to architects,
   mechanical engineers, and roboticists.  A formula is developed that matches the
@@
 However, since they can also build structures and
-machines of differing or even dynamically changing length, it is
+machines from members of differing or even dynamically changing length, it is
 useful to develop the mathematics of structures formed from tetrahedra
@@
 Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
-a term now commonly used. In this paper, we reserve \emph{BC helix} to mean the purely regular structure and use \emph{tetrahelix} to refer
+a term now commonly used. In this paper, we reserve \emph{BC helix} to mean the purely
+regular structure and use \emph{tetrahelix} to refer
 to any structure isomorphic to the BC helix.
@@
 same design spectrum. In particular, the tetrahelix is related to the
-tetraspline\cite{mirletz2014} concept used as a physical concept of a tensegrity robot.
+tetraspline\cite{mirletz2014} concept used as a model of a tensegrity robot.
 Although tensegrities are not member-for-member isomorphic to the tetrahelix
@@
 In a plane, the octet truss\cite{richard1961synergetic} is such a geometry, but in a line, the
-Boerdijk-Coxeter helix is a regular structure.
+Boerdijk-Coxeter helix is such a regular structure.
 
@@
 transmutations of these regular geometries. Developing a functional
-gait for our physical Tetrobot was in fact the motivation
+gait for our physical Tetrobot (the 7-Tet Glussbot) was in fact the motivation
 for this work.
-By changing only the length of the longer members that connect two
-distinct rails (the two-hop members), we can dynamically untwist a physical Tetrobot
+By changing only the length of only one third of the members,
+we can dynamically untwist a physical Tetrobot
 forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane,
@@
 we may consider each vertex touching the ground a foot or pseudopod. A robot can thus
-become a hexapod or $n$-pod tetrobot, and the already well-developed approaches to
+become a hexapod or $n$-pod Tetrobot, and the already well-developed approaches to
 hexapod gaits may be applied to make the robot walk or crawl.
@@
 by choosing the lengths of a small set of members.
-In a space frame, this is a static design choice; in a tetrobot, it is a
+In a space frame, this is a static design choice; in a Tetrobot, it is a
 dynamic choice that can be used to twist the robot and/or exert linear or
@@
 
-H.S.M Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and translation of the tetrahedra by showing the
+H.S.M Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and
+translation of the tetrahedra by showing the
 rotation is:
@@
 inconvenient to designers, who might prefer a rational pitch.
-The idea of developing a rational period by arranging solid tetrahedra by relaxing the face-to-face matching
+The idea of developing a rational period by arranging solid tetrahedra by relaxing
+the face-to-face matching
 has been explored\cite{sadler2013periodic}. 
-We develop, below, slightly irregular edge lengths that support, for example, a pitch of precisely 12
+We develop, below, slightly irregular edge lengths that support, for example,
+a pitch of precisely 12
 tetrahedra in one revolution which would allow an architect to
-design a pleasing column having the top and bottom tetrahedra in the same relationship to the capital and the basis to the
-viewer.
+design a pleasing column having the top and bottom tetrahedra in the same relationship to the
+viewer on both the capital and the basis.
 
@@
 In the proof, below, we find it useful to consider projection diagrams that are the axial projection
-of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram} is an example of such a diagram.
+of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram,fig:wobble} are examples
+of such a diagram.
 \begin{lemma}
@@
   \Cref{fig:wobble} illustrates this situation. Like most diagrams, it is
-  over specific, in that the two circles are drawn of the same radius but we do not
+  overspecific, in that the two circles are drawn of the same radius but we do not
   depend upon that in this proof.  The diagram represents the projection along the
-  $z$ axis of a few points into the $XY$-plane.
+  $z$-axis of a few points into the $XY$-plane.
 
@@
 a $+$ or $-$. So the classes are $\{ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
-If when projecting all vertices onto the $z$-axis (dropping the $x$ and $y$ coordinates), the interval
-defined by the $z$ axis value of its endpoints contains no other vertices,
+If when projecting all vertices onto the $z$-axis (dropping the $x$ and $y$ coordinates),
+the interval
+defined by the $z$-axis value of its endpoints contains no other vertices,
 we call it a \emph{one-hop} edge, and if it does contain another vertex we
@@
 In fact, it is possible that there
-will be only two distinct such classes. In the purely regular BC helix there is only one length.
+will be only two distinct such classes, and in fact in  the purely regular BC helix there is only one length.
 
@@
   \label{eventhirds}
-  An optimal tetrahelix of any rail angle $0 \leq \rho < \pi$ is a triple helix with all vertices evenly spaced at $d/3$ intervals on the $z$ axis.
+  An optimal tetrahelix of any rail angle $0 \leq \rho < \pi$ is a triple helix with all vertices evenly spaced at $d/3$ intervals on the $z$-axis.
   Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail, and $2$ two-hop edges connected to the rail.
@@
     Consider a tetrahelix in which the vertices are evenly spaced at
-    $d/3$ intervals on the $z$ axis. Every edge is either a rail edge,
+    $d/3$ intervals on the $z$-axis. Every edge is either a rail edge,
     or it makes one hop, or two hops. All of the one-hop
@@
 formed in the X,Y plane with origin $O$: $\angle \vec{H}(0,0) O \vec{H}(0,1)$ projecting out the
-$z$-axis and sighting along the positive $z$a-xis. In other words, $\rho$
+$z$-axis and sighting along the positive $z$-axis. In other words, $\rho$
 controls how far a rail edge of a tetrahelix deviates from being
@@
 $h$ for the axial height from one vertex to
-the next of a different color, but we use $d$ to mean distance between vertices of
+the next of a different color, but we use $d$ to mean the axial distance between vertices of
 the  same color.
@@
 \begin{equation}
-  \text{two-hop}  = \sqrt{\frac{4 d_{\rho}^2}{9} +  \sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \text{.}\\
+  \text{two-hop}  = \sqrt{\frac{4 d_{\rho}^2}{9} +  r^2(\sin^2(2\rho/3 + \frac{4\pi}{3})  + (1 - \cos(2\rho/3 + \frac{4\pi}{3}))^2)} \text{.}\\
 \end{equation}
@@
 
-Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, we can construct minimax optimal tetrahelix where $0 \leq \rho \leq \rho_{bc}$.
+Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, we can
+construct a minimax optimal tetrahelix where $0 \leq \rho \leq \rho_{bc}$.
 %% Add here references to these equations.
@@
 we have motivated the development of $\vec{H}_{general}$ as a transformation of $\vec{V}(n)$ defined by
- \cref{graycoxeter} from Gray and Coxeter. It is difficult to see how
-the $\vec{V}(n)$ 
-formulation could ever give rise to a continuum producing the tetrabeam,
-since setting the angle in that equation to zero can produce only collinear points.
+\cref{graycoxeter} from Gray and Coxeter.
 
@@
 However, the advent of additive manufacturing, such as 3D printing, and the invention of two
-distinct concentric multimember joints\cite{song2003spherical,HamlinSandersonCMS} has improved that situation.
+distinct concentric multi-member joints\cite{song2003spherical,HamlinSandersonCMS} has improved that situation.
 
@@
 
-There exists a continuum of minimax edge-length optimal tetrahelices
-having as one end the Boerdijk-Coxeter Helix and at  the
+It is proven there exists a continuum of minimax edge-length optimal tetrahelices
+having as one end the completely regular Boerdijk-Coxeter Helix and at the
 other end a completely untwisted tetrahelix with equilateral cross
@@
 all configurations in the continuum may be reached.
-All such optimal tetrahelices may be generated by a simple equation giving coordinates or by
-selecting approprate edge-lengths and are in fact triple helices.
+All such optimal tetrahelices may provably be generated by a
+simple equation giving coordinates or by
+selecting appropriate edge lengths generated from the same equation. 
 A machine, such as a robot or a variable-geometry truss, that can change

### 2018-03-06 r1doc/RebuttalTetrahelixUntwistV2.tex
response to reviewers (initial)

\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{color}
\usepackage{cleveref}

\newcommand{\highlighttext}[1] {\textcolor{red}{#1}}

\title{Rebuttal: JMR-17-1184 (Research Paper), A Continuum of Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix}
\author{Robert L. Read \\
  Public Invention \\
    Email: \href{mailto:read.robert@gmail.com}{read.robert@gmail.com}   
	}

\date{\today}
% Hint: \title{what ever}, \author{who care} and \date{when ever} could stand 
% before or after the \begin{document} command 
% BUT the \maketitle command MUST come AFTER the \begin{document} command! 
\begin{document}

\maketitle

\section{Thanks}

The author wishes to thank the reviewers for their careful and attentive work. Each comment is responded
to below, on a point-by-point basis.

\section{Response to Reviewer \#1}

\subsection{Overview}

Slightly irregular edge lengths consisting the tetrahelix are introduced to develop one exact
revolution of the tetrahelix structure using the integer number of the tetrahedron in this paper.
Therefore, the efficient modeling of the tetrahelix using tetrahedral is proposed, and this research
can be applied to the robot or architecture field.

\subsection{Remarks}

In this paper, the optimality criterion is proposed to minimize the minimax which means the
difference between longest and shortest edge. For optimization, 7 conditions were considered.
However, these 7 conditions are just based on the author’s experience, but is not fully supported
by academic background such as kinematic measure to make any comparison between optimal
design and non-optimal design.

To parameterize the tetrahelix with respect to the rail angle, the relationship between one-hop edge,
two-hop edge, and rail edge is proposed.

The inradius of the tetrahelix was also calculated to consider the insertion of material inside the
tetrahelix.

The equitetrabeam is introduced as a special case that the rail angle is zero. It is proposed that
transformation from tetrahelix to equitetrabeam is possible by changing the minimax ratio about
16\%.

Overall, this paper is acceptable, but requires some revision. The following includes some comments.

\subsection{Modification}
\begin{itemize}
\item
The sentences of this paper need to be compact. Please read several times and then clean
the sentences.
``without loss of generality'' $\rightarrow$ ``generally''
\highlighttext{The term ``without loss of generality'' is being used as specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowwed in proof because of symmetry or an ability to make
  a choice that does not change the validity of the proof.
  However, because this was in order to clarify this, I have added the word ``assume'' to the first use of the phrase ``without loss of generality'' and the phrase ``By symmetry'' to the second use.
  }

\highlighttext{TODO: reread looking for additional ways to make sentences more compact.}
\item
  The explantaion for figure 8 can be erased by drawing the general case for figure 8.
  \item
    Instead of sentence starting to ‘we……’ , the passive sentence is recommended.
    \item 
 The following sentence is obscure. You’d better suggest a way to measure optimality using
 some kinematic indices :
\begin{quote}
 We have not yet proved that a two-class tetrahelix is optimal, but it suffices to show
that there exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
\end{quote}

\highlighttext{This sentence has been clarified to show that ``not yet proved'' means
  ``not yet reached the proof in this paper of that fact that'' by changing the sentence to refer
  to the next theorem:
  \begin{quote}
  We have not yet {\em
proved theorem 3 which asserts} that a two-class tetrahelix is optimal, but it suffices to show that there
exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
  \end{quote}
  I unfortunately am not sure how to relate this notion of optimality to kinematic indexes, but
  have attempted elsewhere to clarify why this definition of optimality is valuable for
  Tetrobot-style robots.
  }
\item 
 It is recommended to change:
 ``conincident'' $\rightarrow$ ``coincident''
 \highlighttext{Corrected--an embarassing mistake in my spelling correction software.}
 \item
\item In page 3, after the eq. (4)
  In this formula, ``integral values of n'' $\rightarrow$ In this formula, ``integer values of n''
  \highlighttext{Corrected.}
  \item 
In eq. (23), need to be changed as

\begin{equation}
  \begin{split}
  \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ j_{\rho})}}
       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+k_{\rho}) }} \text{.}
  \end{split}       
\end{equation}
$\rightarrow$ 
\begin{equation}
  \begin{split}
  \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ k_{\rho})}}
       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+j_{\rho}) }} \text{.}
  \end{split}       
\end{equation}
\highlighttext{This has been corrected, thanks for the careful catch of an embarassing mistake.}

\item 
- In page 8, the graph could not be observed through this following address,
https://github.com/PubInv/tetrahelix/blob/master/tetrahelix.nb . For user not using the
Mathematica, it is recommended to show the tendency of the graph of eq. (23) by setting
rail angle as 0, 15, and 30(deg).

\highlighttext{
  In order to make this clearer and avoid forcing the user to follow a link, I have included the graphic
  inline in the document with the following change to the relevant sentence:}

\begin{quote}

By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram} we see the partial derivative of this with respect to
radius $r$ is always negative, for any $\rho \leq \rho_{bc}$.

\begin{figure}
     \centering
     \includegraphics[width=0.45\textwidth]{figures/PartialDerivativeDiagram.png}
     \caption{Partial Derivative against $\rho$ and $r$: $ \frac{\partial \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}}{\partial \rho, r} $ }
  \label{fig:partialderivativediagram}
\end{figure}
\end{quote}

\item
  - In eq. (27) and (28), it needs to be changed as 9/2 instead of 9.
  \highlighttext{Corrected--thank you!}  
  \item
- Figure 12 interferes to understanding the related contents. It is recommended to change
figure 12 referring the following figure,
\item
- It would be great to add the snapshot and explanation showing the application of this
conclusion

\highlighttext{In order to more clearly tie this to the actual research robot for which it was developed,
  I have re-referenced the photograph which occurs early in the paper and modified the text:}

\begin{quote}
  \begin{figure}
  \centering
     \includegraphics[width=0.5\textwidth]{figures/MedCantedCropped.png}
     \caption{7-Tet Tetrobot in relaxed, or BC helix configuration}
     \includegraphics[width=0.5\textwidth]{figures/EquitetrabeamCropped.png}
     \caption{The Equitetrabeam: Fully Untwisted 7-Tet Tetrobot in Hexapod Configuration}
     \label{fig:tetrobot}
\end{figure}

A machine, such as \highlighttext{the} Tetrobot or a variable-geometry truss \highlighttext{ depicted in \cref{fig:tetrobot}}, that can change
the length of some of its members by $16\%$ can thus twist and untwist itself.
A completely regular Tetrobot can untwist itself to create a planar
face on the ground for locomotion \highlighttext{via standard gaits}.
\end{quote}

\end{itemize}

\section{Response to Reviewer \#2}

Title: A Continuum of Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix

This paper proposed a method to transform the BC helix to Planar-faced tetrahelix by minimizing the difference between the longest and shortest edges, under some constraints. The author tried to explain his finding logically, and the background of the research is explained well. Also, the author shared the materials for this research at github. I have some comments for this paper as follows:

\begin{enumerate}

  \item
 I can see the organization of this paper is as follows: 
 Intro (2pages) – A designer’s formulation for the BC helix(2 pages) – Optimal tetrahelices are triple helix(3 pages) – Parameterizing tetrahelices via rail angle(2 pages) – The inradius(0.5 pages) – The Equitetrabeam (0.5 pages) – An Untwisted continuum (0.5 pages) – Conclusion
 \item 
I think the author tried to explain all the findings but I think the organization of the paper should be revised to be emphasized carefully. Even for the researchers in this field, I am not convinced the paper is clearly written to emphasize the contribution well. Some sections can be combined, and the organization should be changed to emphasize the major contribution of this paper. I think this is the most significant point to improve the readability of the paper.

  \item
    I think the explaining optimization part should be revised. For a certain optimization problem, I think mathematics definition or algorithmic explanation can be helpful to understand the problem quickly. I think the author should refer problem definition standards from other optimization papers to revise this.

  \item    
    In my opinion, the problem definition and proof of theorems looks being done based on personal experiences. I recommend using mathematical derivation or expression if possible.

  \item    
 I think the demonstration by experiment can be helpful to understand the idea. Video attachment is recommended.

\end{enumerate}

Minors)

\begin{itemize}
  \item
    I am very confusing to the term “An untwisted continuum” and “equitetrabeam.”
    \highlighttext{I have attempted to clarify this by adding the phrase:
      We call this the \emph{equitetrabeam}\textbf{, a portmanteau of ``equilateral tetrahedral beam''}.}
    Some other terminologies should be checked for 
“Conincident” should be “coincident”
\item
Title is little bit not easy to be understood. “A continuum of optimal tetrahelices” can be changed to some other expression.
\end{itemize}

\section{Conclusions}\label{conclusions}

\bibliographystyle{asmems4}
\bibliography{IEEEabrv,gluss}

\end{document}

### 2018-03-06 r1doc/TetrahelixUntwistV2.tex
response to reviewers (initial)

--- 2017-06-19 doc/TetrahelixUntwist.tex
@@
 
+\usepackage{color}
+
 % \usepackage{float}
@@
 \renewcommand{\vec}[1]{\mathbf{#1}}
+
+\newcommand{\highlighttext}[1] {\textcolor{red}{#1}}
 
@@
 
-In this formula, integral values of $n$ may be taken as a vertex number for one rail and used to compute
+In this formula, \highlighttext{integer} values of $n$ may be taken as a vertex number for one rail and used to compute
 its Cartesian
@@
   $2\pi/\rho$ is rational if and only if $\rho = a\pi/b$, where $a$ and $b$ are integers
-  and, without loss of generality, $a$ and $b$ are coprime.
+  and, \highlighttext{assume} without loss of generality, $a$ and $b$ are coprime.
   Since $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
@@
   Any optimal tetrahelix with a rail angle of magnitude less than $\pi$ has all three
-  axes conincident.
-  \label{thm:conincident}
+  axes coincident.
+  \label{thm:coincident}
 \end{theorem}
@@
   Each helix has zero curvature, that is, it is a straight line. These lines are eqivalent
-  to some three degenerate helices with conincident axes, possibly with different radii, so long as there is a phase
+  to some three degenerate helices with coincident axes, possibly with different radii, so long as there is a phase
   term in the defintion of the helix, as in \cref{eq:colored}. We later show the
@@
 
-  Without loss of generality, define the Red helix to have its axis on the $z$-axis.
+  \highlighttext{By symmetry} without loss of generality, define the Red helix to have its axis on the $z$-axis.
   Since there must be at least one Red-to-Yellow or a Red-to-Blue edge that is either a minimum or a maximum,
@@
   Let $B'$ be a translation in the $XY$-plane of the blue helix $B$  so that its axis is the $z$-axis and
-  conincident with the red helix $R$. Let $D$ be the distance between the axis of the Blue helix
+  coincident with the red helix $R$. Let $D$ be the distance between the axis of the Blue helix
   $B$ and $B'$. We will show that if $D>0$ then $B$ ``wobbles'' in a way that cannot be optimal.
@@
 
-Now that we have shown that axes are conincident and parallel and that the pitches
+Now that we have shown that axes are coincident and parallel and that the pitches
 are the same for all helices, we can assert that any optimum tetrahelix can
@@
 tetrahelix generated by \cref{eq:triple}, and so it not optimal. We have not yet
-proved that a two-class tetrahelix is optimal, but it suffices to show that there
+\highlighttext{proved \cref{thm:eventhirds} which asserts} that a two-class tetrahelix is optimal, but it suffices to show that there
 exists such a better tetrahelix to show that different radii imply a suboptimal
@@
 \begin{theorem}
-  \label{eventhirds}
+  \label{thm:eventhirds}
   An optimal tetrahelix of any rail angle $0 \leq \rho < \pi$ is a triple helix with all vertices evenly spaced at $d/3$ intervals on the $z$-axis.
@@
 
- Note that based on \cref{eventhirds}, there are only 3 possible lengths in an optimal tethrahelix,
+ Note that based on \cref{thm:eventhirds}, there are only 3 possible lengths in an optimal tethrahelix,
  and we are justified in classifying edge lengths as \emph{rail}, \emph{one-hop}, or
@@
 \begin{proof}
-By \cref{eventhirds}, we can compute the (at most) three edge-lengths of an optimal
+By \cref{thm:eventhirds}, we can compute the (at most) three edge-lengths of an optimal
 tetrahelix by formulae universally quantified by $n$ and $c$:
@@
 
-We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
+Wek now that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
 By inspection, it seems likely that we will minimize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
@@
   \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
-  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ j_{\rho})}}
-       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+k_{\rho}) }} \text{.}
+  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ \highlighttext{k_{\rho}})}}
+       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+\highlighttext{j_{\rho}}) }} \text{.}
   \end{split}       
@@
 
-By graph inspection using Mathematica (\url{https://github.com/PubInv/tetrahelix/blob/master/tetrahelix.nb}), we see the partial derivative of this with respect to
-radius $r$ is always negative, for any $\rho \leq \rho_{bc}$. When the rail angle approaches
+\highlighttext{
+By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram} we see the partial derivative of this with respect to
+radius $r$ is always negative, for any $\rho \leq \rho_{bc}$.
+}
+When the rail angle approaches
 $\pi$, corresponding to going almost to the other side of the tetrahelix, this is not necessarily true, hence the
@@
 
+\begin{figure}
+     \centering
+     \includegraphics[width=0.45\textwidth]{figures/PartialDerivativeDiagram.png}
+     \caption{Partial Derivative against $\rho$ and $r$: $ \frac{\partial \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}}{\partial \rho, r} $ }
+  \label{fig:partialderivativediagram}
+\end{figure}
+
 Therefore, we decrease the minimax length
@@
 %%  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
-  d_{opt}^2 = 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
+  d_{opt}^2 = 1 - \frac{16(\sin{ \rho / 2})^2}{\highlighttext{\frac{9}{2}} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
 \end{equation}
@@
 %%  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
-    d_{opt} = \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}  \text{ .}  \numberthis  \label{dopt}  \\      
+    d_{opt} = \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + \highlighttext{\frac{9}{2}} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}  \text{ .}  \numberthis  \label{dopt}  \\      
 \end{equation}
@@
 an equilateral triangle of unchanging orientation, as shown in \cref{fig:equitetrabeam} and at the rear of \cref{fig:series}.
-We call this the \emph{equitetrabeam}. It is not possible to generate an equitetrabeam from 
+We call this the \emph{equitetrabeam}\highlighttext{, a portmanteau of ``equilateral tetrahedral beam''}.
+It is not possible to generate an equitetrabeam from 
 \cref{graycoxeter}
@@
 selecting appropriate edge lengths generated from the same equation. 
-A machine, such as a robot or a variable-geometry truss, that can change
+A machine, such as \highlighttext{the} Tetrobot or a variable-geometry truss \highlighttext{ depicted in \cref{fig:tetrobot}}, that can change
 the length of some of its members by $16\%$ can thus twist and untwist itself.
 A completely regular Tetrobot can untwist itself to create a planar
-face on the ground for locomotion.
+face on the ground for locomotion \highlighttext{via standard gaits}.
 With a numeric solution, a designer may choose

### 2018-03-07 r1doc/RebuttalTetrahelixUntwistV2.tex
some improvements
latest updates

@@
 figure 12 referring the following figure,
+
+\highlighttext{The reviewer has provided an excellent simplifying diagram. I have created a diagram similar
+  (see \cref{fig:projectiondiagram})
+  to theirs but retaining the numbering features, which are useful in the first place the
+  figure is referenced. I thank the reviewer for this improvedment.}
+
+\begin{figure}
+     \centering
+     \includegraphics[width=0.45\textwidth]{figures/GeneralProjectionDiagramV2.png}
+     \caption{General One-hop Projection Diagram}
+  \label{fig:projectiondiagram}
+\end{figure}
+
 \item
@@
 
+   \highlighttext {
+     In order to attempt to clarify the results of the paper I have added as the final subsection of the introduction the following summary of the contributions.
+\subsection{Summary of Results}
+The remainder of this  paper:
+\begin{itemize}
+\item Provides a new formulation for the BC helix that is more natural for engineers,
+\item Defines a concept of minimum maximum edge-length optimality and proves that all
+    optimal tetrahelices are in fact triple helices,
+\item Provides formulae for construct optimal tetrahelices of different twists or for optimally
+    transforming a
+    robot from a twisted to a planar configuration,
+\item Gives a formula for the inradius of an optimal tetrahelix,
+\item Describes a completely planar tetrahlix (the \emph{equitetrabeam} useful as a structural beam or for apply standard robot gaits to a tetrahedral robot, and
+\item Discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
+\end{itemize}
+}
+
   \item
@@
 I think the author should refer problem definition standards from other optimization papers to revise this.
+    \highlighttext{
+      In order to clarify the ``Optimal Tetrahelices are Triple Helices'' section as requested,
+      I have provided a mathematical description of the optimization, and a more mathematical
+      description of the definition of the tetrahelix.
+      }
 
@@
     In my opinion, the problem definition and proof of theorems looks being done based on personal experiences. I recommend using mathematical derivation or expression if possible.
+    \highlighttext{
+      I believe the theorems are all true (and verified by computer experimentation) and that the proofs
+      are rigorous. However, in deference to the reviewer I have attempted to express parts of them
+      more formally in several places. Unfortunately, it is beyond my ability to make them more formal
+      in the space allowed in this paper. I hope readers will find them convincing at the available length.
+      }
 
@@
   Title is little bit not easy to be understood. “A continuum of optimal tetrahelices” can be changed to some other expression.
+  \highlighttext{
+    I have changed the title to:
+ ``Optimal Tetrahelices Transforming between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix''
+}
 \end{itemize}

### 2018-03-07 r1doc/TetrahelixUntwistV2.tex
some improvements
latest updates

@@
 
-\title{A Continuum of Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix}
+\title{Optimal Tetrahelices Transforming between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix}
 \author{Robert L. Read
@@
   a structure of zero curvature, the \emph{equitetrabeam}.
-  Only one out of three members in the system change their length to reach
+ Only one out of three members in the system change their length \highlighttext{ to transform
+  the structure into }
   any point in the continuum.
@@
 hexapod gaits may be applied to make the robot walk or crawl.
+
+\subsection{Summary of Results}
+
+\highlighttext{
+The remainder of this  paper:
+\begin{enumerate}
+\item Provides a new formulation for the BC helix that is more natural for engineers,
+\item Defines a concept of minimum maximum edge-length optimality and proves that all
+    optimal tetrahelices are in fact triple helices,
+\item Provides formulae for construct optimal tetrahelices of different twists or for optimally
+    transforming a
+    robot from a twisted to a planar configuration,
+\item Gives a formula for the inradius of an optimal tetrahelix,
+\item Describes a completely planar tetrahlix (the \emph{equitetrabeam} useful as a structural beam or for apply standard robot gaits to a tetrahedral robot, and
+\item Discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
+\end{enumerate}
+}
 
@@
 
+\section{Optimal Tetrahelices are Triple Helices - redux}
+
+\highlighttext{
+As engineers and roboticists it is desirable to design tetrahelices that
+are slightly irregular that ``untwist'' the BC Helix in an optimal way.
+For machines
+made out linear actuators with limited range of extension,
+the best definition of optimality is to minimize the difference in
+lengths between the shortest and longest members in the robot of a given radius.
+}
+
+\highlighttext{
+We use the term \emph{tetrahelix} to mean any structure physically constructible of
+vertices and finite edges which is isomorphic to the BC helix, but with possibly different edge lengths,
+and in which the
+vertices lie on three helices (red, blue, and yellow, or ($R,B,Y$)). 
+Mathematically, this structure extends
+without bound, although physical robots or variable geometry trusses will
+be truncations of such a structure.
+This idea is captured by a function $T$ that gives the length between any
+two nodes that are connected, and undefined ($\perp$) when not connected :
+$T(n_1,n_2) : \mathbb{Z} \times \mathbb{Z} \mapsto \mathbb{R} \cup \{\perp\} $.
+To describe a physically reailizable machine, the function $T$ representing a tetrahelix
+is constrained:
+$(\forall n_1,n_2 : T(n_1,n_2) > 0)$.
+For a BC Helix, $(\forall x,y : T(x,y) \neq \perp \wedge T(x,z) \neq \perp \Rightarrow T(x,y) = 1)$.
+}
+
+\highlighttext{
+The ratio of the longest member in a testrahelix to the shortest is:
+\[
+R(T) = \frac{\max \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}{\min \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}
+\]
+}
+
+\highlighttext{
+  The ratio of the BC Helix is 1 :$ R(H_{BC}) = 1$.
+  }
+\highlighttext{
+A \emph{triple helix} is three congruent helices that share an axis. The remainder of this
+section proves that
+optimal tetrahelices are in fact triple helices.
+In stages, we prove that the helices in optimal tetrahelices:
+\begin{enumerate}
+\item have the same pitch,
+\item have parallel axes,
+\item share the same axis,
+\item have the same radius,
+  \item have the same rail length,
+  \item have axially equidistant vertices, and therefore
+  \item are in fact triple helices.
+\end{enumerate}
+The formula for radius that optimizes the tetrahelix for a given rail angle
+is the result of the \cref{sec:parameterizing}.
+}
+
+\highlighttext{
+\begin{theorem}
+  All three helices in any physically realizable tetrahelix have the same pitch and parallel axes.
+  \label{thm:pitchandparallel}
+\end{theorem}
+}
+
+\begin{proof}
+\highlighttext{  
+Suppose that all three rails do not have the same pitch.
+If we start at any shortest edge ($n_1,n_2$) between
+two rails, choosing a node $k$ 
+further away from $n_1$, such that  $k >> n1$, increases edge lengths $T(n_1,k)$
+between rails must always lengthen without bound,
+which is not physically realizable.
+So we are justified in talking about the
+\emph{pitch} of 
+the optimal tetrahelix as the pitch of its three rail helices $(R,B,Y)$, even though there are
+three such helices of equivalent pitch.
+}
+
+\highlighttext{  
+Similarly, if the axes are not parallel, there is an edge of $T(x,y)$
+unbounded length in the structure, which is not physical.
+}
+\end{proof}
+
+\highlighttext{  
+Since the axes of helices of any physical tetrahelix are parallel, take
+them to be parallel to the $z$ axis. Define the radius of the tetrahelix:
+\begin{multline*}
+rad(T) = \text{the radius of the smallest cylinder} \\
+\text{which contains all of nodes of the tetrahelix } T
+\end{multline*}
+Define a \emph{minimax edge-length optimal tetrahelix} or just an
+\emph{optimal tetrahelix} to be a tetrahelix for which there exists
+no other tetrahelix with lower ratio of longest edge length to
+shortest edge length of the same radius
+\begin{equation}
+  OPT(T) \equiv \neg (\exists S : R(S) < R(T) \wedge rad(S) = rad(T))
+  \label{eq:optdef}
+\end{equation}
+}
+
+As a little lemma for the proof below, observe that a tetrahelix of zero radius, where
+all points lie on the same line,
+is not as optimal as a tetrahelix of a small radius. The edges between rails $(R,B,Y)$ will be
+shorter than the rail edges, and moving them apart slightly lengthens the between-edge
+rails, improving the ratios.
+
+In the proof, below, we find it useful to consider projection diagrams that are the axial projection
+of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram,fig:wobble} are examples
+of such a diagram.
+\begin{lemma}
+  If the rail angle $0 < \rho < \pi$ is a rational multiple of $\pi$, then the projection of
+  edges in a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
+  regular polygon of 3 or more sides, or else they fill in a complete circle.
+  \label{lemma:ngon}
+\end{lemma}
+\begin{proof}
+  All points lying on a helix projected along the axis lie on a circle in the $XY$-plane.
+  Helices are periodic in the $z$ dimension modulo $2\pi$.
+  If $2\pi/\rho$ is irrational, the projection onto the $XY$-plane will contain
+  an unbounded number of points on a circle.
+  If and only if $2\pi/\rho$ is rational, the projection onto
+  the $XY$-plane will contain a finite number of points.
+  Because $\pi$ is transcendental and irrational,
+  $2\pi/\rho$ is rational if and only if $\rho = a\pi/b$, where $a$ and $b$ are integers
+  and, \highlighttext{assume} without loss of generality, $a$ and $b$ are coprime.
+  Since $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
+  The number of points in the projection is $2b$ if $a$ is odd, and $b$ if $a$ is even.
+  This polygon has at least 3 sides, since either $\rho$ is irrational or $b > a$, and therefore
+  $b \geq 2$. If $a/b = 1/2$, the projection is a square, which has four sides. 
+\end{proof}
+
+\begin{theorem}
+  Any optimal tetrahelix with a rail angle of magnitude less than $\pi$ has all three
+  axes coincident.
+  \label{thm:coincident}
+\end{theorem}
+\begin{proof}
+  Case 1: Suppose that $\rho$ is zero.
+  Each helix has zero curvature, that is, it is a straight line. These lines are eqivalent
+  to some three degenerate helices with coincident axes, possibly with different radii,
+  so long as there is a phase
+  term in the defintion of the helix, as in \cref{eq:colored}. We later show the
+  radii must be eqivalent.
+
+  Case 2: Suppose that $\rho$ is positive but less than $\pi$.
+  In this case, each rail helix has
+  curvature. The projection of points in the $XY$ plane creates a figure
+  guaranteed to have points on either side of any line through the axis of such
+  a helix, because the figure is either an $n$-gon or a circle by \cref{lemma:ngon}.
+  We show that the three helices share a common axis.
+
+  \highlighttext{By symmetry} without loss of generality, define the Red helix to have its axis on the $z$-axis.
+  Since there must be at least one Red-to-Yellow or a Red-to-Blue edge that is either a minimum or a maximum,
+  without loss of generality, define the Blue helix to be a helix that
+  has an edge connection to the Red helix that is either a maximum or a minimum.
+  Let $B'$ be a translation in the $XY$-plane of the blue helix $B$  so that its axis is the $z$-axis and
+  coincident with the red helix $R$. Let $D$ be the distance between the axis of the Blue helix
+  $B$ and $B'$. We will show that if $D>0$ then $B$ ``wobbles'' in a way that cannot be optimal.
+  Define a wobble vector by:
+  \begin{equation}
+    \vec{W}(n) = \vec{B}(n) - \vec{B}'(n) \text{ .}
+  \end{equation}
+  where $\vec{B}(n)$ and $\vec{B'}(n)$ is the vector
+  $\begin{bmatrix}
+    x \\
+    y 
+  \end{bmatrix}$
+  for the projection of the $n$th vertex of $B$ and $B'$. 
+  Note that $|| \vec{R}(n) - \vec{B'}(n+k)||$ (the Euclidean distance of the vertices)
+  is a constant for any $k$, because $R$ and $B'$ have the
+  same pitch and the same axis, even if they do not have the same radius.
+
+  \Cref{fig:wobble} illustrates this situation. Like most diagrams, it is
+  overspecific, in that the two circles are drawn of the same radius but we do not
+  depend upon that in this proof.  The diagram represents the projection along the
+  $z$-axis of a few points into the $XY$-plane.
+
+  \begin{figure}
+     \centering
+     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram.png}
+     \caption{Wobble Vectors from Non-Coincident Axes}
+  \label{fig:wobble}
+\end{figure}
+
+  Since $\rho < \pi$ by assumption, by $\cref{lemma:ngon}$,
+  the set of wobbles $\{\vec{W}(n) | \text{for any n}\}$
+  contains at least three vectors,
+  at least two of which point in different directions.
+  For any point not at the origin, at least one of these vectors moves closer to the
+  point and at least one moves further away.
+
+    The set of all lengths in the tetrahelix is a superset of:
+    $L = \{|| \vec{R}(n) - \vec{B}(n)||\}$, which, by our choice,
+    has at least one longest or shortest
+    length.
+    $L = \{|| \vec{R}(n) - (\vec{B'}(n) + \vec{W}(n))||\}$ and so
+    $L = \{|| (\vec{R}(n) - \vec{B'}(n)) - \vec{W}(n)||\}$.
+    But $\vec{R}(n) - \vec{B'}(n)$ is a constant, so the minimax value of $L$ is improved as $||\vec{W}(n)||$
+    decreases.  
+    By our choice that there is a Blue-to-Red edge that is either a maximum or a minimum,
+    this improves the minimax value of the total tetrahelix.
+
+    This process can be carried out on both the Blue and Yellow helices
+    (perhaps simultaneously) until $\vec{W}(n)$ is
+    zero for both, finding a tetrahelix of improved overall minimax value at each step.
+    So a tetrahelix is optimal only when $\vec{W}(n) = 0$, and therefore when $D=0$ and
+    $\vec{B}(n) = \vec{B'}(n)$, and all three axes are coincident.
+\end{proof}
+
+Now that we have shown that axes are coincident and parallel and that the pitches
+are the same for all helices, we can assert that any optimum tetrahelix can
+be generated with an equation for helices:
+\begin{equation}
+\label{eq:triple}
+\vec{V}_{triple}(n,c) =
+\left [
+  \begin{tabular}{c}
+   $ r_c \cos(n \alpha +  c 2 \pi /3 + \phi_c)$\\
+   $ r_c \sin(n \alpha +  c 2 \pi /3 + \phi_c) $\\
+   $ \frac{d(n +c / 3)}{3}   $
+  \end{tabular}
+  \right ],
+\end{equation}
+\text{where: \qquad}
+\begin{tabular}{l}
+  $c \in \{0,1,2\}$,
+  \end{tabular}      
+which would be much more complicated if the axes where not coincident.
+\highlighttext{
+Note that we have not yet shown that the relationships of the radius $r_c$ or
+the phase $\phi_c$ for the three helices, so we denoted them with a $c$ subscript to show
+they are dependent on the color ($R,B,Y$). 
+\[
+rad(\vec{V}_{triple}(n,c)) = max \{r_R, r_B, r_Y\}
+\]
+}
+
+We have not yet investigated in the general case the relationships beteween
+$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple}.
+In \cref{sec:parameterizing}, we give a more specific version of this formula which
+generates optimal tetrahelices.
+We observe that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
+but because of the $\phi_c$ term, they are not collinear.
+
+\begin{figure}
+  \centering
+     \includegraphics[width=0.45\textwidth]{figures/edge-diagram.png}
+     \caption{Edge Naming}
+  \label{fig:naming}
+\end{figure}
+
+In principle, any three helices generated with \cref{eq:triple}
+has at most nine distinct edge length classes. Each edge that connects
+two rails potentially has a longer length and shorter length we denote with
+a $+$ or $-$. So the classes are $\{ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
+If when projecting all vertices onto the $z$-axis (dropping the $x$ and $y$ coordinates),
+the interval
+defined by the $z$-axis value of its endpoints contains no other vertices,
+we call it a \emph{one-hop} edge, and if it does contain another vertex we
+call it a \emph{two-hop} edge, as illustrated in \cref{fig:naming}.
+Then there are 
+3 rail edges $\{ RR, BB, YY\}$,
+3 one-hop lengths $\{ RB_-, BY_-, RY_- \}$ between each pair of 3 rails,
+and 3 two-hop
+lengths $\{ RB_{+}, BY_+, RY_+ \}$ between each pair of 3 rails,
+where the two-hop length is at least the one-hop length.
+However, if we symmetrically generate the three helices  with \cref{eq:triple},
+many of these lengths will be the same.
+In fact, it is possible that there
+will be only two distinct such classes, and in fact in  the purely regular BC helix there is only one length.
+
+\begin{theorem}
+  Optimal tetrahelices have the same radius for all three helices.
+\end{theorem}
+\begin{proof}
+To prove this theorem, we exhibit a symmetric tetrahelix (not yet shown to be optimal) which
+happens to be a triple helix, that has
+the property that all rail edges are equal to all one-hop edges and all two-hop
+edges are equal to each other. 
+Observe that although we have not get given the formula for the
+radii of such a triple helix, there are some values for $r$ and $\alpha$, and $\phi$
+in \cref{eq:triple}
+for which all the three helices are symmetrically and evenly spaced. Furthermore,
+we can choose these values such that the three rail edges are of length $1$ and
+so that the one-hop lengths are also all of length $1$, and the two-hop lengths
+are slightly longer.
+
+Now consider a tetrahelix in which the radius of one of the helices is different.
+By the connections made in a tetrahelix, any increase to a radius increases both
+a one-hop and two-hop distance, and any decrease likewise decreases two.
+Since there exists a tetrahelix which has only two distinct classes of edge lengths,
+the smaller being one-hop = rail, the larger being the two-hop distance, the helix
+with a larger radius increases a longest edge without increasing a shortest edges.
+Likewise, a helix with a smaller radius decreases a one-hop edge without decreasing
+a two-hop edge.
+
+Therefore, a tetrahelix with different radii is not as optimal as some two-class 
+tetrahelix generated by \cref{eq:triple}, \highlighttext{ and so by \cref{eq:optdef}} it not optimal.
+
+We have not yet
+\highlighttext{proved \cref{thm:eventhirds} which asserts} that a two-class tetrahelix is optimal, but it suffices to show that there
+exists such a better tetrahelix to show that different radii imply a suboptimal
+tetrahelix.
+\end{proof}
+
+Because an optimal tetrhelix has equivalent radii and equivalent pitch for all three helices,
+it has equivalent rail edge lengths. Likewise, there is a single rail angle $\rho$ that
+represents the rotation of two vertices connected by a single rail edge, and it is the same
+for all three rails.
+
+Now that we have shown that on any optimal tetrahelix the vertices
+are on helices of the same axes and pitch, we see that the vertices 
+of any optimal tetrahelix will lie on a cylinder, or a circle when the axis dimension
+is projected out. Therefore, it is reasonable to now speak of the singular radius $r$
+of a tetrahelix as the radius of the cylinder.
+We can now go on to
+the harder proof about where vertices occur along the $z$-axis.
+
+ We show that, in fact, the vertices must be distributed in even thirds
+ along the $z$-axis as they are in the regular BC helix.
+
+ However, we have already shown the rail
+ lengths are equal in any optimal tetrahelix.
+
+\begin{figure}
+     \centering
+     \includegraphics[width=0.45\textwidth]{figures/EquitetrabeamCloseUp.png}
+     \caption{Equitetrabeam}
+  \label{fig:equitetrabeam}
+\end{figure}
+
+\Cref{fig:equitetrabeam} shows the equitetrabeam, which is defined in \cref{sec:equitetrabeam},
+but also conveniently illustrates the one-hop and two-hop edge defintions.
+The green edges are the two-hop edges and the purple edges are the one-hop edges. Note that the green
+edges are slightly longer than the purple edges. In \cref{fig:naming}, which depicts the BC helix,
+the two-hop and one-hop edges are of equal length (but the projection onto the $z$-axis, the
+axial length, of the two-hop edge is longer than the axial one-hop length.)
+
+\begin{theorem}
+  \label{thm:eventhirds}
+  An optimal tetrahelix of any rail angle $0 \leq \rho < \pi$ is a triple helix with all vertices evenly spaced at $d/3$ intervals on the $z$-axis.
+  Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail, and $2$ two-hop edges connected to the rail.
+  The sixth edge is opposite of the rail edge and is a one-hop edge.
+\end{theorem}
+
+\begin{proof}
+    Consider a tetrahelix in which the vertices are evenly spaced at
+    $d/3$ intervals on the $z$-axis. Every edge is either a rail edge,
+    or it makes one hop, or two hops. All of the one-hop
+    edges are equal length.  All of the two-hop edges are equal
+    length.
+
+    Every vertex is connected to 4 non-rail edges. There is a one-hop edge
+    in both the positive and negative $z$ direction. Likewise, there is a two-hop
+    edge in both the positive and negative $z$ direction. Let $A$ be the set
+    of edge lengths, which has only 3 members, represented by $A = \{o,t,r\}$ for
+    the one-hop, two-hop, and rail edge lengths.
+
+    Any attempt to perturb any rail in either $z$ direction lengthens one two-hop edge to $t'$, where $t' > t$
+    and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be the edge lengths of such a
+    perturbed tetrahelix.
+    The minimax of $B$ is greater than the minimax of $A$ since there is a single rail length which cannot be both greater
+    than $o'$ and $t'$ and less than $o'$ and $t'$.
+    Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other, and
+    all two-hop edges equal to each other, and the $z$ distances between rails equal. Therefore, vertices are
+    $d/3$ from each other on the $z$-axis.
+\end{proof}
+
+ Note that based on \cref{thm:eventhirds}, there are only 3 possible lengths in an optimal tethrahelix,
+ and we are justified in classifying edge lengths as \emph{rail}, \emph{one-hop}, or
+\emph{two-hop}. The one-hop edges are the edges between rails that are closest on the $z$-axis, and the two-hop edges are those that skip over a vertex.
+
+Taking all of these results together, 
+each helix in an optimal tetrahelix is congruent to the others, shares an axis, is the same radius, and is evenly spaced
+axially with the others.
+An optimal tetrahelix is therefore a \emph{triple helix}, of a radius we have not yet demonstrated.
+
 \section{Parameterizing Tetrahelices via Rail Angle}
@@
      \centering
-     \includegraphics[width=0.45\textwidth]{figures/ProjectionDiagram.png}
+     \includegraphics[width=0.45\textwidth]{figures/GeneralProjectionDiagramV2.png}
      \caption{General One-hop Projection Diagram}

### 2018-03-07 r1doc/TetrahelixUntwistV2.tex
added video and others

@@
 developed here is available in JavaScript and demonstrated by an interactive
-design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix},
+design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
+\highlighttext{and a video\cite{readvideo}},
 from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
@@
 \highlighttext{
-Note that we have not yet shown that the relationships of the radius $r_c$ or
-the phase $\phi_c$ for the three helices, so we denoted them with a $c$ subscript to show
-they are dependent on the color ($R,B,Y$). 
+Having not yet investigated in the general case the relationships beteween
+$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple} for the three helices
+which is developed in \cref{eqrhoopt} these are denoted with a $c$ subscript to show
+they are dependent on the color ($c \in \{R,B,Y\}$). 
 \[

### 2018-03-08 r1doc/RebuttalTetrahelixUntwistV2.tex
added video and others
more updates

@@
 ``without loss of generality'' $\rightarrow$ ``generally''
-\highlighttext{The term ``without loss of generality'' is being used as specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowwed in proof because of symmetry or an ability to make
+\highlighttext{The term ``without loss of generality'' is being used specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowed in proof because of symmetry or an ability to make
   a choice that does not change the validity of the proof.
-  However, because this was in order to clarify this, I have added the word ``assume'' to the first use of the phrase ``without loss of generality'' and the phrase ``By symmetry'' to the second use.
+  However, because this was unclear to the reviewer, in order to clarify this, I have added the word ``assume'' to the first use of the phrase ``without loss of generality'' and the phrase ``By symmetry'' to the second use.
   }
@@
     Instead of sentence starting to ‘we……’ , the passive sentence is recommended.
+    \highlighttext{
+      I believe editorial opinon is somewhat divided on the use of the word ``we'' when it is used to mean ``the author and the reader togheter'' as I have used it.
+Most editors do not prefer passive sentences in general.
+      Nonetheless, in deference to the reviewer, I have searched the paper for each use of the ``we'' and
+      removed it in most, but not all cases.
+      }
     \item 
@@
 
-\highlighttext{This sentence has been clarified to show that ``not yet proved'' means
+\highlighttext{
+  The reviewer has generally noted that I may not have motivated my definition of ``optimality''
+  strongly enough. To improve this, I have made some changes:
+... displays a continuum of tetrahelices optimal in a \bf{
+  in the sense of being
+as regular as possible},
+which is the main result of this
+paper.
+}
+
+\highlighttext{
+  Additionally, in the section on Optimal Tetrahelices, I have inserted the following sentence which helps to
+  explain the definition of optimality:
+  \bf{By maintaining all lengths as close to the same ``regular'' length as possible,
+such as the mean length of the actuator,
+one retains the greatest possible freedom of motion for the robot.}
+  }
+
+\highlighttext{This specific sentence has been clarified to show that ``not yet proved'' means
   ``not yet reached the proof in this paper of that fact that'' by changing the sentence to refer
@@
 
-By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram} we see the partial derivative of this with respect to
+  By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram}
+  observe that the partial derivative of this with respect to
 radius $r$ is always negative, for any $\rho \leq \rho_{bc}$.
@@
   to theirs but retaining the numbering features, which are useful in the first place the
-  figure is referenced. I thank the reviewer for this improvedment.}
+  figure is referenced, and in explaining the derivation of the inradius.
+  I thank the reviewer for this improvement.}
 
@@
     I think the demonstration by experiment can be helpful to understand the idea. Video attachment is recommended.
+    \highlighttext{
+All math
+developed here is available in JavaScript and demonstrated by an interactive
+design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
+\bf{and a video[9]},
+from which figs. 1 and 2 and later figures in this paper 
+are taken.      
+      }
 

### 2018-03-08 r1doc/TetrahelixUntwistV2.tex
more updates

@@
 useful to develop the mathematics of structures formed from tetrahedra
-where we relax regularity.
+where \highlighttext{one relaxes} regularity.
 
@@
 Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
-a term now commonly used. In this paper, we reserve \emph{BC helix} to mean the purely
+a term now commonly used. \highlighttext{This paper} reserves \emph{BC helix} to mean the purely
 regular structure and use \emph{tetrahelix} to refer
@@
 Imagining \cref{fig:closeup} or \cref{fig:closeuporthog} as a static mechanical structure,
-we can observe that it is useful to the mechanical engineer
+observe that it is useful to the mechanical engineer
 because the structure is a mechanically strong, inherently rigid,
 omni-triangulated space frame.
-Then we can imagine that each static edge is replaced with an
+Then imagine that each static edge is replaced with an
 actuator that can dynamically become shorter or longer in response to electronic control,
@@
 be able to ``untwist'' it and to form a tetrahelix space frame that has a
-flat planar surface. By making length changes in a certain way, we can
-untwist a tetrahelix to form a \emph{tetrabeam} which has planar faces
+flat planar surface. By making length changes in a certain way, a \highlighttext{tetrahelix untwists} to form a \emph{tetrabeam} which has planar faces
 and has, for example, an equilateral triangular profile. This paper
@@
 
-\Cref{fig:series} displays a continuum of tetrahelices optimal in a certain sense,
+\Cref{fig:series} displays a continuum of tetrahelices optimal in a \highlighttext{in the sense of being
+as regular as possible},
 which is the main result of this
@@
 By changing only the length of only one third of the members,
-we can dynamically untwist a physical Tetrobot
+\highlighttext{one} can dynamically untwist a physical Tetrobot
 forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane,
-as shown in \cref{fig:tetrobot}.
+as shown in figs. \highlighttext{4 and} 5.
 
 By untwisting the tetrahelix so that is has a planar surface resting on the ground,
-we may consider each vertex touching the ground a foot or pseudopod. A robot can thus
+each vertex touching the ground \highlighttext{becomes} a foot or pseudopod. A robot can thus
 become a hexapod or $n$-pod Tetrobot, and the already well-developed approaches to
@@
     optimal tetrahelices are in fact triple helices,
-\item Provides formulae for construct optimal tetrahelices of different twists or for optimally
+\item Provides formulae for constructing optimal tetrahelices of different twists or for optimally
     transforming a
@@
 \item Gives a formula for the inradius of an optimal tetrahelix,
-\item Describes a completely planar tetrahlix (the \emph{equitetrabeam} useful as a structural beam or for apply standard robot gaits to a tetrahedral robot, and
+\item Describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
+  a structural beam or for applying standard robot gaits to a tetrahedral robot, and
 \item Discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
@@
 
-We would like to design nearly regular tetrahelices with a formula that
-gives the vertices in space. Eventually, we would like to design them
+\highlighttext{Engineers} would like to design nearly regular tetrahelices with a formula that
+gives the vertices in space. Eventually, \highlighttext{this would be done}
 by choosing the lengths of a small set of members.
@@
 
-Ideally, we would have a simple formula for defining the vertices based on
+Ideally, \highlighttext{a simple formula would define} the vertices based on
 any curvature or pitch we choose. It is a goal of
@@
 
-H.S.M Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and
+H.S.M. Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and
 translation of the tetrahedra by showing the
@@
 which are closely approximated by the outer edges or rails of
-the BC helix. We think of each of these three rails as being a different color: red, blue, or yellow.
+the BC helix. Think of each of these three rails as being a different color: red, blue, or yellow.
 This situation is illustrated in \cref{fig:helixcomparison}, wherein the black helix represents that
@@
 In order to develop the continuum of slightly irregular tetrahelices,
-we need a formula that gives us the vertices of just
+\highlighttext{a formula is needed}
+ that gives us the vertices of just
 one rail helix, denoted by color $c$ and integer vertex number $n$:
@@
 Note, in \cref{railanglefig}, the $z$-axis travel for one rail edge is denoted by $d$. In \cref{graycoxeter} and  \cref{eq:colored}, the variable
-$h$ is used for one third of the distance, we name $d$. We will later justify that $d = 3h$.
+$h$ is used for one third of the distance we name $d$. \highlighttext{The fact that $d = 3h$ is justified later}.
 In this paper, we assume the length of a rail
 is always $1$ as a simplification, except in proofs concerning rail length.
-We make the rail length a parameter in our JavaScript code in
+The rail length is a parameter in the JavaScript code in
 \url{https://github.com/PubInv/tetrahelix/blob/master/js/tetrahelix_math.js} \cite{readtetrahelix}.
@@
 The $\vec{H}_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho_{bc}$ rather than $\theta_{bc}$.
-Intuitively, we seek an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
+Intuitively, an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$ \highlighttext{is sought}.
 We expand 
@@
 \end{align*}
-we introduce 3 into the denominator...
+introduce 3 into the denominator...
 \begin{align*}
@@
 \end{align*}
-we want $2\pi$ in numerator, so add canceling terms...
+\highlighttext{seeking} $2\pi$ in the numerator, add canceling terms...
 \begin{align*}
@@
 \end{align*}
-finally we obtain:
+\highlighttext{to} finally obtain:
 \begin{equation}
@@
 Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued).
-We can now assert that in \cref{fig:helixcomparison} the black helix winds at
+\highlighttext{It can now be asserted that} in \cref{fig:helixcomparison} the black helix winds at
 $\frac{3 \theta_{bc}}{\rho_{bc}} \approx 11.16 $ times the rate of a rail helix.
@@
 $ \frac{2 \pi}{\rho_{bc}} \approx 10.16 $
-we can see that there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a
+there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a
 complete revolution of the tetrahelix.
@@
 has been explored\cite{sadler2013periodic}. 
-We develop, below, slightly irregular edge lengths that support, for example,
+\highlighttext{The next sections develop} slightly irregular edge lengths that support, for example,
 a pitch of precisely 12
@@
 
-We use the term \emph{tetrahelix} to mean any structure physically constructible of
-vertices and finite edges which is isomorphic to the BC helix and in which the
-vertices lie on three helices.
-By isomporphic we mean there is a one-to-one mapping between both
-vertices and edges in the two tetrahelices.
-One could consider various definitions of optimality for a
-tetrahelix, but the most useful to us as roboticists working with the Tetrobot
-concept is to minimize the
-maximum ratio between any two edge lengths, because the Tetrobot uses
-mechanical linear acutators with
-limited range of extension.
-
-A \emph{triple helix} is three congruent helices that share an axis. We show that
-optimal tetrahelices are in fact triple helices with the same radius, so that all
-vertices are on a cylinder. In stages, we demonstrate that the helices in optimal tetrahelices:
+\highlighttext{
+As engineers and roboticists it is desirable to design tetrahelices that
+are slightly irregular that ``untwist'' the BC Helix in an optimal way.
+For machines
+made out of linear actuators with limited range of extension,
+the best definition of optimality is to minimize the difference in
+lengths between the shortest and longest members in the robot of a given radius.
+By maintaining all lengths as close to the same ``regular'' length as possible,
+such as the mean length of the actuator,
+one retains the greatest possible freedom of motion for the robot.
+}
+
+\highlighttext{
+This paper use the term \emph{tetrahelix} to mean any structure physically constructible of
+vertices and finite edges which is isomorphic to the BC helix, but with possibly different edge lengths,
+and in which the
+vertices lie on three helices (red, blue, and yellow, or ($R,B,Y$)). 
+Mathematically, this structure extends
+without bound, although physical robots or variable geometry trusses will
+be truncations of such a structure.
+This idea is captured by a function $T$ that gives the length between any
+two nodes that are connected, and undefined ($\perp$) when not connected :
+$T(n_1,n_2) : \mathbb{Z} \times \mathbb{Z} \mapsto \mathbb{R} \cup \{\perp\} $.
+To describe a physically realizable machine, the function $T$ representing a tetrahelix
+is constrained:
+$(\forall n_1,n_2 : T(n_1,n_2) > 0)$.
+For a BC Helix, $(\forall x,y : T(x,y) \neq \perp \Rightarrow T(x,y) = 1)$.
+}
+
+\highlighttext{
+The ratio of the longest member in a testrahelix to the shortest is:
+\begin{equation}
+R(T) = \frac{\max \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}{\min \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}
+\label{eq:optdef}
+\end{equation}
+}
+
+\highlighttext{
+  The ratio of the BC Helix is 1: $ R(H_{BC}) = 1$.
+  }
+\highlighttext{
+A \emph{triple helix} is three congruent helices that share an axis. The remainder of this
+section proves that
+optimal tetrahelices are in fact triple helices.
+In stages, this section proves that the helices in optimal tetrahelices:
 \begin{enumerate}
@@
 \end{enumerate}
-
-Suppose that all three rails do not have the same pitch. If we start at any shortest edge between
-two rails, as we move
-from vertex to vertex away from our start edge, the edge lengths
-between rails must always lengthen without bound,
-which cannot be optimal.
-So we are justified in talking about the
+The formula for radius that optimizes the tetrahelix for a given rail angle
+is the result of the \cref{sec:parameterizing}.
+}
+
+\highlighttext{
+\begin{theorem}
+  All three helices in any physically realizable tetrahelix have the same pitch and parallel axes.
+  \label{thm:pitchandparallel}
+\end{theorem}
+}
+
+\begin{proof}
+\highlighttext{  
+Suppose that all three rails do not have the same pitch.
+Let $n1$ be a node on a  shortest edge between
+two rails. Let $n2$ be a node on a different rail.
+Increasing the difference $\|n2-n1\|$, increasing edge lengths $T(n_1,n_2)$
+without bound,
+which is not physically realizable.
+}
+
+\highlighttext{  
+  Similarly, if the axes are not parallel, for any length $\lambda$ there is an edge of $T(x,y)$
+  such that $T(x,y) > \lambda$, which is not physical.
+}
+\end{proof}
+
+\highlighttext{
+\Cref{thm:pitchandparallel} justifies talking about the singular
 \emph{pitch} of 
-the optimal tetrahelix as the pitch of its three rail helices, even though there are
+the optimal tetrahelix as the pitch of its three rail helices $(R,B,Y)$, even though there are
 three such helices of equivalent pitch.
-
-Similarly, if the axes are not parallel, there is an edge of
-unbounded length in the structure, so we do not consider such cases.
-
+Since the axes of helices of any physical tetrahelix are parallel, take
+them to be parallel to the $z$ axis. Define the radius of the tetrahelix:
+\begin{multline*}
+rad(T) = \text{the radius of the smallest cylinder} \\
+\text{which contains all of nodes of the tetrahelix } T
+\end{multline*}
 Define a \emph{minimax edge-length optimal tetrahelix} or just an
 \emph{optimal tetrahelix} to be a tetrahelix for which there exists
-no other tetrahelix with lower ratio of longest edge length to shortest edge length.
-
-We wish to show that in an optimal tetrahelix, all vertices lie on the cylinder
-of radius $r$, regardless of where they lie on the $z$-axis.
-
-As a little lemma for the proof below, observe that a tetrahelix of zero radius, where
+no other tetrahelix  of the same radius with lower ratio of longest edge length to
+shortest edge length
+\begin{equation}
+  OPT(T) \equiv \neg (\exists S : R(S) < R(T) \wedge rad(S) = rad(T))
+  \label{eq:optdef}
+\end{equation}
+}
+
+\highlighttext{
+\begin{lemma}
+  A tetrahelix where all points lie on the same line is not optimal.
+    \label{lemma:notpoint}
+\end{lemma}
+\begin{proof}
+As a little lemma for the proof below, observe that a tetrahelix $T$ of zero radius, where
 all points lie on the same line,
-is not as optimal as a tetrahelix of a small radius. The edges between rails will be
-shorter than the rail edges, and moving them apart slightly lengthens the between-edge
-rails, improving the ratios.
-
-In the proof, below, we find it useful to consider projection diagrams that are the axial projection
+is not as optimal as a tetrahelix of a small radius. The edges between rails $(R,B,Y)$ will be
+shorter than the rail edges, and moving them apart slightly to form $T'$ lengthens the between-edge
+rails, improving the ratios, so $R(T') < R(T)$.
+\end{proof}
+}
+
+In the proof, below, \highlighttext{it is} useful to consider projection diagrams that are the axial projection
 of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram,fig:wobble} are examples
@@
   edges in a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
-  regular polygon of 3 or more sides, or else they fill in a complete circle.
+  regular polygon of 3 or more sides, \highlighttext{otherwise} they fill in a complete circle.
   \label{lemma:ngon}
@@
   All points lying on a helix projected along the axis lie on a circle in the $XY$-plane.
+\highlighttext{(By \cref{lemma:notpoint}, the circle is not a simple point.)}
   Helices are periodic in the $z$ dimension modulo $2\pi$.
@@
   Each helix has zero curvature, that is, it is a straight line. These lines are eqivalent
-  to some three degenerate helices with coincident axes, possibly with different radii, so long as there is a phase
-  term in the defintion of the helix, as in \cref{eq:colored}. We later show the
-  radii must be eqivalent.
+  to some three degenerate helices with coincident axes, possibly with different radii,
+  so long as there is a phase
+  term in the defintion of the helix, as in \cref{eq:colored}. \highlighttext{That the
+  radii must be eqivalent is shown later}.
 
@@
   a helix, because the figure is either an $n$-gon or a circle by \cref{lemma:ngon}.
-  We show that the three helices share a common axis.
 
@@
   \Cref{fig:wobble} illustrates this situation. Like most diagrams, it is
-  overspecific, in that the two circles are drawn of the same radius but we do not
-  depend upon that in this proof.  The diagram represents the projection along the
+  overspecific, in that the two circles are drawn of the same radius but \highlighttext{
+    this proof does not depend on that.
+  }
+  The diagram represents the projection along the
   $z$-axis of a few points into the $XY$-plane.
@@
 
-Now that we have shown that axes are coincident and parallel and that the pitches
-are the same for all helices, we can assert that any optimum tetrahelix can
-be generated with an equation for helices:
+Now that \highlighttext{it is provent that the} axes are coincident and parallel and that the pitches
+are the same for all helices, any optimum tetrahelix can
+be generated with a \highlighttext{simple} equation for helices:
 \begin{equation}
@@
 which would be much more complicated if the axes where not coincident.
-Note that we have not yet shown that the relationships of the radius $r_c$ or
-the phase $\phi_c$ for the three helices, so we denoted them with a $c$ subscript to show
-they are dependent on the color.
-We have not yet investigated in the general case the relationships beteween
+\highlighttext{
+Having not yet investigated in the general case the relationships beteween
+$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple} for the three helices
+(the relationships are developed in \cref{eqrhoopt}) these are denoted with a $c$ subscript to show
+they are dependent on the color ($c \in \{R,B,Y\}$).
+Since any optimal tetrahelix is described by \cref{eq:triple},
+\[
+rad(\vec{V}_{triple}(n,c)) = max \{r_R, r_B, r_Y\}
+\]
+}
+
+\highlighttext{This equation does not completely explain} the  relationships beteween
 $\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple}.
@@
 generates optimal tetrahelices.
-We observe that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
+\highlighttext{Observe} that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
 but because of the $\phi_c$ term, they are not collinear.
@@
 where the two-hop length is at least the one-hop length.
-However, if we symmetrically generate the three helices  with \cref{eq:triple},
+However, \highlighttext{generating} the three helices with \cref{eq:triple}
+\highlighttext{ will cause }
 many of these lengths will be the same.
@@
 \begin{proof}
-To prove this theorem, we exhibit a symmetric tetrahelix (not yet shown to be optimal) which
+To prove this theorem, \highlighttext{one may} exhibit a symmetric tetrahelix (not yet shown to be optimal) which
 happens to be a triple helix, that has
@@
 edges are equal to each other. 
-Observe that although we have not get given the formula for the
-radii of such a triple helix, there are some values for $r$ and $\alpha$, and $\phi$
+Observe that although the formula for the
+radii of such a triple helix \highlighttext{has not yet been developed},
+there are some values for $r$ and $\alpha$, and $\phi$
 in \cref{eq:triple}
 for which all the three helices are symmetrically and evenly spaced. Furthermore,
-we can choose these values such that the three rail edges are of length $1$ and
-so that the one-hop lengths are also all of length $1$, and the two-hop lengths
-are slightly longer.
-
-Now consider a tetrahelix in which the radius of one of the helices is different.
-By the connections made in a tetrahelix, any increase to a radius increases both
-a one-hop and two-hop distance, and any decrease likewise decreases two.
-Since there exists a tetrahelix which has only two distinct classes of edge lengths,
-the smaller being one-hop = rail, the larger being the two-hop distance, the helix
-with a larger radius increases a longest edge without increasing a shortest edges.
-Likewise, a helix with a smaller radius decreases a one-hop edge without decreasing
-a two-hop edge.  Therefore, a tetrahelix with different radii is not as optimal as some two-class 
-tetrahelix generated by \cref{eq:triple}, and so it not optimal. We have not yet
-\highlighttext{proved \cref{thm:eventhirds} which asserts} that a two-class tetrahelix is optimal, but it suffices to show that there
-exists such a better tetrahelix to show that different radii imply a suboptimal
-tetrahelix.
-\end{proof}
-
-Because an optimal tetrhelix has equivalent radii and equivalent pitch for all three helices,
-it has equivalent rail edge lengths. Likewise, there is a single rail angle $\rho$ that
-represents the rotation of two vertices connected by a single rail edge, and it is the same
-for all three rails.
-
-Now that we have shown that on any optimal tetrahelix the vertices
-are on helices of the same axes and pitch, we see that the vertices 
-of any optimal tetrahelix will lie on a cylinder, or a circle when the axis dimension
-is projected out. Therefore, it is reasonable to now speak of the singular radius $r$
-of a tetrahelix as the radius of the cylinder.
-We can now go on to
-the harder proof about where vertices occur along the $z$-axis.
-
- We show that, in fact, the vertices must be distributed in even thirds
- along the $z$-axis as they are in the regular BC helix.
-
- However, we have already shown the rail
- lengths are equal in any optimal tetrahelix.
-
-\begin{figure}
-     \centering
-     \includegraphics[width=0.45\textwidth]{figures/EquitetrabeamCloseUp.png}
-     \caption{Equitetrabeam}
-  \label{fig:equitetrabeam}
-\end{figure}
-
-\Cref{fig:equitetrabeam} shows the equitetrabeam, which is defined in \cref{sec:equitetrabeam},
-but also conveniently illustrates the one-hop and two-hop edge defintions.
-The green edges are the two-hop edges and the purple edges are the one-hop edges. Note that the green
-edges are slightly longer than the purple edges. In \cref{fig:naming}, which depicts the BC helix,
-the two-hop and one-hop edges are of equal length (but the projection onto the $z$-axis, the
-axial length, of the two-hop edge is longer than the axial one-hop length.)
-
-\begin{theorem}
-  \label{thm:eventhirds}
-  An optimal tetrahelix of any rail angle $0 \leq \rho < \pi$ is a triple helix with all vertices evenly spaced at $d/3$ intervals on the $z$-axis.
-  Any one tetrahedron in a tetrahelix has $1$ rail edge, $2$ one-hop edges connected to the rail, and $2$ two-hop edges connected to the rail.
-  The sixth edge is opposite of the rail edge and is a one-hop edge.
-\end{theorem}
-
-\begin{proof}
-    Consider a tetrahelix in which the vertices are evenly spaced at
-    $d/3$ intervals on the $z$-axis. Every edge is either a rail edge,
-    or it makes one hop, or two hops. All of the one-hop
-    edges are equal length.  All of the two-hop edges are equal
-    length.
-
-    Every vertex is connected to 4 non-rail edges. There is a one-hop edge
-    in both the positive and negative $z$ direction. Likewise, there is a two-hop
-    edge in both the positive and negative $z$ direction. Let $A$ be the set
-    of edge lengths, which has only 3 members, represented by $A = \{o,t,r\}$ for
-    the one-hop, two-hop, and rail edge lengths.
-
-    Any attempt to perturb any rail in either $z$ direction lengthens one two-hop edge to $t'$, where $t' > t$
-    and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be the edge lengths of such a
-    perturbed tetrahelix.
-    The minimax of $B$ is greater than the minimax of $A$ since there is a single rail length which cannot be both greater
-    than $o'$ and $t'$ and less than $o'$ and $t'$.
-    Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other, and
-    all two-hop edges equal to each other, and the $z$ distances between rails equal. Therefore, vertices are
-    $d/3$ from each other on the $z$-axis.
-\end{proof}
-
- Note that based on \cref{thm:eventhirds}, there are only 3 possible lengths in an optimal tethrahelix,
- and we are justified in classifying edge lengths as \emph{rail}, \emph{one-hop}, or
-\emph{two-hop}. The one-hop edges are the edges between rails that are closest on the $z$-axis, and the two-hop edges are those that skip over a vertex.
-
-Taking all of these results together, 
-each helix in an optimal tetrahelix is congruent to the others, shares an axis, is the same radius, and is evenly spaced
-axially with the others.
-An optimal tetrahelix is therefore a \emph{triple helix}, of a radius we have not yet demonstrated.
-
-\section{Optimal Tetrahelices are Triple Helices - redux}
-
-\highlighttext{
-As engineers and roboticists it is desirable to design tetrahelices that
-are slightly irregular that ``untwist'' the BC Helix in an optimal way.
-For machines
-made out linear actuators with limited range of extension,
-the best definition of optimality is to minimize the difference in
-lengths between the shortest and longest members in the robot of a given radius.
-}
-
-\highlighttext{
-We use the term \emph{tetrahelix} to mean any structure physically constructible of
-vertices and finite edges which is isomorphic to the BC helix, but with possibly different edge lengths,
-and in which the
-vertices lie on three helices (red, blue, and yellow, or ($R,B,Y$)). 
-Mathematically, this structure extends
-without bound, although physical robots or variable geometry trusses will
-be truncations of such a structure.
-This idea is captured by a function $T$ that gives the length between any
-two nodes that are connected, and undefined ($\perp$) when not connected :
-$T(n_1,n_2) : \mathbb{Z} \times \mathbb{Z} \mapsto \mathbb{R} \cup \{\perp\} $.
-To describe a physically reailizable machine, the function $T$ representing a tetrahelix
-is constrained:
-$(\forall n_1,n_2 : T(n_1,n_2) > 0)$.
-For a BC Helix, $(\forall x,y : T(x,y) \neq \perp \wedge T(x,z) \neq \perp \Rightarrow T(x,y) = 1)$.
-}
-
-\highlighttext{
-The ratio of the longest member in a testrahelix to the shortest is:
-\[
-R(T) = \frac{\max \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}{\min \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}
-\]
-}
-
-\highlighttext{
-  The ratio of the BC Helix is 1 :$ R(H_{BC}) = 1$.
-  }
-\highlighttext{
-A \emph{triple helix} is three congruent helices that share an axis. The remainder of this
-section proves that
-optimal tetrahelices are in fact triple helices.
-In stages, we prove that the helices in optimal tetrahelices:
-\begin{enumerate}
-\item have the same pitch,
-\item have parallel axes,
-\item share the same axis,
-\item have the same radius,
-  \item have the same rail length,
-  \item have axially equidistant vertices, and therefore
-  \item are in fact triple helices.
-\end{enumerate}
-The formula for radius that optimizes the tetrahelix for a given rail angle
-is the result of the \cref{sec:parameterizing}.
-}
-
-\highlighttext{
-\begin{theorem}
-  All three helices in any physically realizable tetrahelix have the same pitch and parallel axes.
-  \label{thm:pitchandparallel}
-\end{theorem}
-}
-
-\begin{proof}
-\highlighttext{  
-Suppose that all three rails do not have the same pitch.
-If we start at any shortest edge ($n_1,n_2$) between
-two rails, choosing a node $k$ 
-further away from $n_1$, such that  $k >> n1$, increases edge lengths $T(n_1,k)$
-between rails must always lengthen without bound,
-which is not physically realizable.
-So we are justified in talking about the
-\emph{pitch} of 
-the optimal tetrahelix as the pitch of its three rail helices $(R,B,Y)$, even though there are
-three such helices of equivalent pitch.
-}
-
-\highlighttext{  
-Similarly, if the axes are not parallel, there is an edge of $T(x,y)$
-unbounded length in the structure, which is not physical.
-}
-\end{proof}
-
-\highlighttext{  
-Since the axes of helices of any physical tetrahelix are parallel, take
-them to be parallel to the $z$ axis. Define the radius of the tetrahelix:
-\begin{multline*}
-rad(T) = \text{the radius of the smallest cylinder} \\
-\text{which contains all of nodes of the tetrahelix } T
-\end{multline*}
-Define a \emph{minimax edge-length optimal tetrahelix} or just an
-\emph{optimal tetrahelix} to be a tetrahelix for which there exists
-no other tetrahelix with lower ratio of longest edge length to
-shortest edge length of the same radius
-\begin{equation}
-  OPT(T) \equiv \neg (\exists S : R(S) < R(T) \wedge rad(S) = rad(T))
-  \label{eq:optdef}
-\end{equation}
-}
-
-As a little lemma for the proof below, observe that a tetrahelix of zero radius, where
-all points lie on the same line,
-is not as optimal as a tetrahelix of a small radius. The edges between rails $(R,B,Y)$ will be
-shorter than the rail edges, and moving them apart slightly lengthens the between-edge
-rails, improving the ratios.
-
-In the proof, below, we find it useful to consider projection diagrams that are the axial projection
-of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram,fig:wobble} are examples
-of such a diagram.
-\begin{lemma}
-  If the rail angle $0 < \rho < \pi$ is a rational multiple of $\pi$, then the projection of
-  edges in a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
-  regular polygon of 3 or more sides, or else they fill in a complete circle.
-  \label{lemma:ngon}
-\end{lemma}
-\begin{proof}
-  All points lying on a helix projected along the axis lie on a circle in the $XY$-plane.
-  Helices are periodic in the $z$ dimension modulo $2\pi$.
-  If $2\pi/\rho$ is irrational, the projection onto the $XY$-plane will contain
-  an unbounded number of points on a circle.
-  If and only if $2\pi/\rho$ is rational, the projection onto
-  the $XY$-plane will contain a finite number of points.
-  Because $\pi$ is transcendental and irrational,
-  $2\pi/\rho$ is rational if and only if $\rho = a\pi/b$, where $a$ and $b$ are integers
-  and, \highlighttext{assume} without loss of generality, $a$ and $b$ are coprime.
-  Since $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
-  The number of points in the projection is $2b$ if $a$ is odd, and $b$ if $a$ is even.
-  This polygon has at least 3 sides, since either $\rho$ is irrational or $b > a$, and therefore
-  $b \geq 2$. If $a/b = 1/2$, the projection is a square, which has four sides. 
-\end{proof}
-
-\begin{theorem}
-  Any optimal tetrahelix with a rail angle of magnitude less than $\pi$ has all three
-  axes coincident.
-  \label{thm:coincident}
-\end{theorem}
-\begin{proof}
-  Case 1: Suppose that $\rho$ is zero.
-  Each helix has zero curvature, that is, it is a straight line. These lines are eqivalent
-  to some three degenerate helices with coincident axes, possibly with different radii,
-  so long as there is a phase
-  term in the defintion of the helix, as in \cref{eq:colored}. We later show the
-  radii must be eqivalent.
-
-  Case 2: Suppose that $\rho$ is positive but less than $\pi$.
-  In this case, each rail helix has
-  curvature. The projection of points in the $XY$ plane creates a figure
-  guaranteed to have points on either side of any line through the axis of such
-  a helix, because the figure is either an $n$-gon or a circle by \cref{lemma:ngon}.
-  We show that the three helices share a common axis.
-
-  \highlighttext{By symmetry} without loss of generality, define the Red helix to have its axis on the $z$-axis.
-  Since there must be at least one Red-to-Yellow or a Red-to-Blue edge that is either a minimum or a maximum,
-  without loss of generality, define the Blue helix to be a helix that
-  has an edge connection to the Red helix that is either a maximum or a minimum.
-  Let $B'$ be a translation in the $XY$-plane of the blue helix $B$  so that its axis is the $z$-axis and
-  coincident with the red helix $R$. Let $D$ be the distance between the axis of the Blue helix
-  $B$ and $B'$. We will show that if $D>0$ then $B$ ``wobbles'' in a way that cannot be optimal.
-  Define a wobble vector by:
-  \begin{equation}
-    \vec{W}(n) = \vec{B}(n) - \vec{B}'(n) \text{ .}
-  \end{equation}
-  where $\vec{B}(n)$ and $\vec{B'}(n)$ is the vector
-  $\begin{bmatrix}
-    x \\
-    y 
-  \end{bmatrix}$
-  for the projection of the $n$th vertex of $B$ and $B'$. 
-  Note that $|| \vec{R}(n) - \vec{B'}(n+k)||$ (the Euclidean distance of the vertices)
-  is a constant for any $k$, because $R$ and $B'$ have the
-  same pitch and the same axis, even if they do not have the same radius.
-
-  \Cref{fig:wobble} illustrates this situation. Like most diagrams, it is
-  overspecific, in that the two circles are drawn of the same radius but we do not
-  depend upon that in this proof.  The diagram represents the projection along the
-  $z$-axis of a few points into the $XY$-plane.
-
-  \begin{figure}
-     \centering
-     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram.png}
-     \caption{Wobble Vectors from Non-Coincident Axes}
-  \label{fig:wobble}
-\end{figure}
-
-  Since $\rho < \pi$ by assumption, by $\cref{lemma:ngon}$,
-  the set of wobbles $\{\vec{W}(n) | \text{for any n}\}$
-  contains at least three vectors,
-  at least two of which point in different directions.
-  For any point not at the origin, at least one of these vectors moves closer to the
-  point and at least one moves further away.
-
-    The set of all lengths in the tetrahelix is a superset of:
-    $L = \{|| \vec{R}(n) - \vec{B}(n)||\}$, which, by our choice,
-    has at least one longest or shortest
-    length.
-    $L = \{|| \vec{R}(n) - (\vec{B'}(n) + \vec{W}(n))||\}$ and so
-    $L = \{|| (\vec{R}(n) - \vec{B'}(n)) - \vec{W}(n)||\}$.
-    But $\vec{R}(n) - \vec{B'}(n)$ is a constant, so the minimax value of $L$ is improved as $||\vec{W}(n)||$
-    decreases.  
-    By our choice that there is a Blue-to-Red edge that is either a maximum or a minimum,
-    this improves the minimax value of the total tetrahelix.
-
-    This process can be carried out on both the Blue and Yellow helices
-    (perhaps simultaneously) until $\vec{W}(n)$ is
-    zero for both, finding a tetrahelix of improved overall minimax value at each step.
-    So a tetrahelix is optimal only when $\vec{W}(n) = 0$, and therefore when $D=0$ and
-    $\vec{B}(n) = \vec{B'}(n)$, and all three axes are coincident.
-\end{proof}
-
-Now that we have shown that axes are coincident and parallel and that the pitches
-are the same for all helices, we can assert that any optimum tetrahelix can
-be generated with an equation for helices:
-\begin{equation}
-\label{eq:triple}
-\vec{V}_{triple}(n,c) =
-\left [
-  \begin{tabular}{c}
-   $ r_c \cos(n \alpha +  c 2 \pi /3 + \phi_c)$\\
-   $ r_c \sin(n \alpha +  c 2 \pi /3 + \phi_c) $\\
-   $ \frac{d(n +c / 3)}{3}   $
-  \end{tabular}
-  \right ],
-\end{equation}
-\text{where: \qquad}
-\begin{tabular}{l}
-  $c \in \{0,1,2\}$,
-  \end{tabular}      
-which would be much more complicated if the axes where not coincident.
-\highlighttext{
-Having not yet investigated in the general case the relationships beteween
-$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple} for the three helices
-which is developed in \cref{eqrhoopt} these are denoted with a $c$ subscript to show
-they are dependent on the color ($c \in \{R,B,Y\}$). 
-\[
-rad(\vec{V}_{triple}(n,c)) = max \{r_R, r_B, r_Y\}
-\]
-}
-
-We have not yet investigated in the general case the relationships beteween
-$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple}.
-In \cref{sec:parameterizing}, we give a more specific version of this formula which
-generates optimal tetrahelices.
-We observe that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
-but because of the $\phi_c$ term, they are not collinear.
-
-\begin{figure}
-  \centering
-     \includegraphics[width=0.45\textwidth]{figures/edge-diagram.png}
-     \caption{Edge Naming}
-  \label{fig:naming}
-\end{figure}
-
-In principle, any three helices generated with \cref{eq:triple}
-has at most nine distinct edge length classes. Each edge that connects
-two rails potentially has a longer length and shorter length we denote with
-a $+$ or $-$. So the classes are $\{ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
-If when projecting all vertices onto the $z$-axis (dropping the $x$ and $y$ coordinates),
-the interval
-defined by the $z$-axis value of its endpoints contains no other vertices,
-we call it a \emph{one-hop} edge, and if it does contain another vertex we
-call it a \emph{two-hop} edge, as illustrated in \cref{fig:naming}.
-Then there are 
-3 rail edges $\{ RR, BB, YY\}$,
-3 one-hop lengths $\{ RB_-, BY_-, RY_- \}$ between each pair of 3 rails,
-and 3 two-hop
-lengths $\{ RB_{+}, BY_+, RY_+ \}$ between each pair of 3 rails,
-where the two-hop length is at least the one-hop length.
-However, if we symmetrically generate the three helices  with \cref{eq:triple},
-many of these lengths will be the same.
-In fact, it is possible that there
-will be only two distinct such classes, and in fact in  the purely regular BC helix there is only one length.
-
-\begin{theorem}
-  Optimal tetrahelices have the same radius for all three helices.
-\end{theorem}
-\begin{proof}
-To prove this theorem, we exhibit a symmetric tetrahelix (not yet shown to be optimal) which
-happens to be a triple helix, that has
-the property that all rail edges are equal to all one-hop edges and all two-hop
-edges are equal to each other. 
-Observe that although we have not get given the formula for the
-radii of such a triple helix, there are some values for $r$ and $\alpha$, and $\phi$
-in \cref{eq:triple}
-for which all the three helices are symmetrically and evenly spaced. Furthermore,
-we can choose these values such that the three rail edges are of length $1$ and
+\highlighttext{one} can choose these values such that the three rail edges are of length $1$ and
 so that the one-hop lengths are also all of length $1$, and the two-hop lengths
@@
 Therefore, a tetrahelix with different radii is not as optimal as some two-class 
-tetrahelix generated by \cref{eq:triple}, \highlighttext{ and so by \cref{eq:optdef}} it not optimal.
-
-We have not yet
-\highlighttext{proved \cref{thm:eventhirds} which asserts} that a two-class tetrahelix is optimal, but it suffices to show that there
+tetrahelix generated by \cref{eq:triple}, \highlighttext{ and so by \cref{eq:optdef}} is not optimal.
+
+\highlighttext{Although \cref{thm:eventhirds} which asserts} that a two-class tetrahelix is optimal
+\highlighttext{has not yet been proven}, it suffices to show that there
 exists such a better tetrahelix to show that different radii imply a suboptimal
@@
 
-Now that we have shown that on any optimal tetrahelix the vertices
-are on helices of the same axes and pitch, we see that the vertices 
+Now that \highlighttext{is proven} that on any optimal tetrahelix the vertices
+are on helices of the same axes and pitch, \highlighttext{observe} that the vertices 
 of any optimal tetrahelix will lie on a cylinder, or a circle when the axis dimension
@@
 of a tetrahelix as the radius of the cylinder.
-We can now go on to
+\highlighttext{This allows }
 the harder proof about where vertices occur along the $z$-axis.
 
- We show that, in fact, the vertices must be distributed in even thirds
+\highlighttext{In fact,} the vertices must be distributed in even thirds
  along the $z$-axis as they are in the regular BC helix.
-
- However, we have already shown the rail
+ \highlighttext{Note that it is already proven that} the rail
  lengths are equal in any optimal tetrahelix.
@@
     perturbed tetrahelix.
-    The minimax of $B$ is greater than the minimax of $A$ since there is a single rail length which cannot be both greater
+    \highlighttext{The minimax of $R(B)$ is greater than the minimax of $R(A)$} since there is a
+    single rail length which cannot be both greater
     than $o'$ and $t'$ and less than $o'$ and $t'$.
@@
 axially with the others.
-An optimal tetrahelix is therefore a \emph{triple helix}, of a radius we have not yet demonstrated.
+An optimal tetrahelix is therefore a \emph{triple helix}, of a radius formulated in \cref{eqrhoopt}.
 
@@
 perhaps the clearest choice is to build formulae that takes as their
-input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
+input the ``rail angle'' $\rho$. \highlighttext{Define} $\rho$ to be the angle
 formed in the X,Y plane with origin $O$: $\angle \vec{H}(0,0) O \vec{H}(0,1)$ projecting out the
@@
 controls how far a rail edge of a tetrahelix deviates from being
-parallel with the axis, or the ``twistiness'' of the tetrahelix. We use
+parallel with the axis, or the ``twistiness'' of the tetrahelix. \highlighttext{Use }
 the parameter $\chi = 1$ to indicate a chirality of counter-clockwise,
-and $\chi = -1$ for clockwise. We take our coordinate system to be right-handed.
+and $\chi = -1$ for clockwise. \highlighttext{Take} our coordinate system to be right-handed.
 
@@
 
-Checking the important special case of the BC helix, we find that this equation
+Checking the important special case of the BC helix, find that this equation
 indeed holds true, treating $d$ in this equation as $3 h_{bc}$ as defined by
@@
 In choosing $\rho$, one greatly constrains $r$ and $d$, but does not completely
-determine both of them together, so we treat both as additional parameters.
+determine both of them together, so \highlighttext{one must} treat both as additional parameters.
 
@@
 \begin{proof}
-By \cref{thm:eventhirds}, we can compute the (at most) three edge-lengths of an optimal
+By \cref{thm:eventhirds}, \highlighttext{one} can compute the (at most) three edge-lengths of an optimal
 tetrahelix by formulae universally quantified by $n$ and $c$:
@@
 
-By definition of minimax edge length optimality, we are trying to minimize:
+By definition of minimax edge length optimality \cref{eq:optdef}, we are trying to minimize:
 \[
-\frac{\max{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}{\min{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}} \text{.}
+R(T(r)) = \frac{\max{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}}{\min{\{1,\text{one-hop}(r),\text{two-hop}(r)}\}} \text{.}
 \]
@@
 \[
- \frac{   \max \{1,\text{two-hop}(r)\}}
+R(T(r)) =  \frac{   \max \{1,\text{two-hop}(r)\}}
       {   \min \{1,\text{one-hop}(r)\}} \text{.}
@@
 
-Wek now that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
+We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
 By inspection, it seems likely that we will minimize this set by equating $\text{one-hop}(r)$ or $\text{two-hop}(r)$
@@
 \highlighttext{
-By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram} we see the partial derivative of this with respect to
+  By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram}
+  observe that the partial derivative of this with respect to
 radius $r$ is always negative, for any $\rho \leq \rho_{bc}$.
@@
 as the radius goes up, and 
-we minimize the maximum edge-length ratio by choosing the largest radius
-up until one-hop $= 1$, the rail-edge length. If we attempted to further increase the radius
-we would not be optimal, because the ratio $\frac{\text{two-hop}(r)}{1}$ would become the
+\highlighttext{one minimizes} the maximum edge-length ratio by choosing the largest radius
+up until one-hop $= 1$, the rail-edge length. If \highlighttext{one} attempted to further increase the radius
+\highlighttext{the tetrahelix} would not be optimal,
+because the ratio $\frac{\text{two-hop}(r)}{1}$ would become the
 largest ratio in our set of ratios \cref{eq:ratioset}.
@@
 
-Therefore, we decrease the minimax length
-of the whole system as we increase the radius
+Therefore, \highlighttext{one decreases} the minimax length
+of the whole system as the radius \highlighttext{increases}
 up to the point that the shorter, one-hop distance is equal to the rail-length, $1$.
 In order to optimize the whole system so long as $\rho \leq \rho_{bc}$,
-we equate one-hop to $1$ to find the optimum radius:
+equate one-hop to $1$ to find the optimum radius:
 
@@
 
-We can now give a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \cref{railangle}:
+\highlighttext{This leads to} a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \cref{railangle}:
 
@@
 \end{equation}
-which we can expand,
+which \highlighttext{is expanded to:}
 \begin{equation}
@@
 
-Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, we can
+Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, \highlighttext{one} can
 construct a minimax optimal tetrahelix where $0 \leq \rho \leq \rho_{bc}$.
@@
 
-Since the axes are parallel, we may define the \emph{inradius}, represented by the letter $i$, of a
+Since the axes are parallel, may define the \emph{inradius}, represented by the letter $i$, of a
 tetrahelix to be the radius of the largest
@@
 
-If we look down the axis of an optimal tetrahelix as shown in \cref{axialview}, it happens that only
+If one looks down the axis of an optimal tetrahelix as shown in \cref{axialview}, it happens that only
 the one-hop edges
@@
 
-From this equation, with the help of symbolic computation, we observe that inradius of the BC helix of unit rail length is $r_{in(\rho_{bc})} = \frac{3}{10\sqrt{2}} \approx 0.21$.
+From this equation, with the help of symbolic computation, \highlighttext{one may} observe that the inradius of the BC helix of unit rail length is $r_{in(\rho_{bc})} = \frac{3}{10\sqrt{2}} \approx 0.21$.
 
@@
 \begin{proof}
-Choosing $d = 1$ and $\rho = 0$ we use  \cref{eqrhoopt} to find the radius of 
-optimal minimax difference.
-Substituting into  \cref{eq:general} and setting one-hop\footnote{Before developing the optimal solution  \cref{eqrhoopt} we found another interesting but non-optimal tetrabeam of zero curvature
+Choosing $d = 1$ and $\rho = 0$ \highlighttext{one can} use \cref{eqrhoopt} to find the radius of 
+optimal minimax difference. Substituting into  \cref{eq:general} and setting one-hop\footnote{Before developing
+  the optimal solution  \cref{eqrhoopt} we found another interesting but non-optimal tetrabeam of zero curvature
 by setting
@@
 
-To the extent that we value tetrabeams (that is, tetrahelices with a rail angle of $0$,
+To the extent that \highlighttext{one values} tetrabeams (that is, tetrahelices with a rail angle of $0$,
 and therefore zero curvature) as mathematical or engineering objects,
-we have motivated the development of $\vec{H}_{general}$ as a transformation of $\vec{V}(n)$ defined by
+\highlighttext{this paper} has motivated the development of $\vec{H}_{general}$ as a transformation of $\vec{V}(n)$ defined by
 \cref{graycoxeter} from Gray and Coxeter.
@@
 
-We observe that  \cref{eqrhoopt,dopt} compute $r_{opt}$ and $d_{opt}$ which
+\highlighttext{Observe} that  \cref{eqrhoopt,dopt} compute $r_{opt}$ and $d_{opt}$ which
 create an optimal tetrahelix for any rail angle $\rho$ between $0$, which
@@
  Likewise, $\rho > \rho_{bc}$ generates
- a tetrahelix, but we have not proved or investigated optimality in that range.
+ a tetrahelix, but \highlighttext{its optimality has not proved or investigated} in that range.
 
@@
 \cref{pitcheqn} can be easily solved numerically with a Newton-Raphson
-solver, as we do on our website.
+solver, as \highlighttext{is done} on our website.
 For a pitch at least $ p \geq \frac{3  \sqrt{2}  \pi}{\sqrt{5}\rho_{bc}} \approx 9.64 $,
@@
 and rail length equivalent within this continuum.\footnote{Before
-deriving  \cref{eqrhoopt}, we created a continuum by
+deriving  \cref{eqrhoopt}, \highlighttext{a continuum was created} by
 using a linear interpolation between the optimal radius for the

### 2018-03-09 r1doc/RebuttalTetrahelixUntwistV2.tex
getting close

@@
 ``without loss of generality'' $\rightarrow$ ``generally''
-\highlighttext{The term ``without loss of generality'' is being used specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowed in proof because of symmetry or an ability to make
+\highlighttext{The term ``without loss of generality'' is being used specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowed in a proof because of symmetry or an ability to make
   a choice that does not change the validity of the proof.
@@
 
-\highlighttext{TODO: reread looking for additional ways to make sentences more compact.}
 \item
   The explantaion for figure 8 can be erased by drawing the general case for figure 8.
+  \highlighttext{Yes, you are correct, thank you, I have made the diagram (see \cref{fig:wobble}) more general and removed the
+    disclaiming text.}
+    \begin{figure}
+     \centering
+     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram2.png}
+     \caption{Wobble Vectors from Non-Coincident Axes}
+  \label{fig:wobble}
+\end{figure}
   \item
@@
     \highlighttext{
-      I believe editorial opinon is somewhat divided on the use of the word ``we'' when it is used to mean ``the author and the reader togheter'' as I have used it.
+      I believe editorial opinon is somewhat divided\cite{firstperson} on the use of the word ``we'' when it is used to mean ``the author and the reader together'' as I have used it.
 Most editors do not prefer passive sentences in general.
@@
     \item 
- The following sentence is obscure. You’d better suggest a way to measure optimality using
+ The following sentence is obscure. You'd better suggest a way to measure optimality using
  some kinematic indices :
@@
       are rigorous. However, in deference to the reviewer I have attempted to express parts of them
-      more formally in several places. Unfortunately, it is beyond my ability to make them more formal
+      more formally in several places. Unfortunately, it is beyond my ability to make them more completely formal
       in the space allowed in this paper. I hope readers will find them convincing at the available length.
@@
     \highlighttext{
-All math
+I have included a public link to a video\cite{tetrahelixvideo} in the citations, and will upload the same video to the journal if appropriate.
+\begin{quote}All math
 developed here is available in JavaScript and demonstrated by an interactive
@@
 are taken.      
+\end{quote}
     }
@@
   \item
-    I am very confusing to the term “An untwisted continuum” and “equitetrabeam.”
+    I am very confusing to the term ``An untwisted continuum'' and ``equitetrabeam.''
     \highlighttext{I have attempted to clarify this by adding the phrase:
@@
     I have changed the title to:
- ``Optimal Tetrahelices Transforming between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix''
+ ``Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix''
 }

### 2018-03-09 r1doc/TetrahelixUntwistV2.tex
getting close

@@
 
-\title{Optimal Tetrahelices Transforming between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix}
+\title{Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix}
 \author{Robert L. Read
@@
 design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
-\highlighttext{and a video\cite{readvideo}},
+\highlighttext{and a video\cite{tetrahelixvideo}},
 from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
@@
 
-  \Cref{fig:wobble} illustrates this situation. Like most diagrams, it is
-  overspecific, in that the two circles are drawn of the same radius but \highlighttext{
-    this proof does not depend on that.
-  }
+  \Cref{fig:wobble} illustrates this situation.
   The diagram represents the projection along the
@@
      \centering
-     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram.png}
+     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram2.png}
      \caption{Wobble Vectors from Non-Coincident Axes}

### 2018-03-09 r1doc/RebuttalTetrahelixUntwistV2.tex
yet another update

@@
 \item
-  The explantaion for figure 8 can be erased by drawing the general case for figure 8.
+  The explanation for figure 8 can be erased by drawing the general case for figure 8.
   \highlighttext{Yes, you are correct, thank you, I have made the diagram (see \cref{fig:wobble}) more general and removed the
@@
     \highlighttext{
-      I believe editorial opinon is somewhat divided\cite{firstperson} on the use of the word ``we'' when it is used to mean ``the author and the reader together'' as I have used it.
+      I believe editorial opinion is somewhat divided\cite{firstperson} on the use of the word ``we'' when it is used to mean ``the author and the reader together'' as I have used it.
 Most editors do not prefer passive sentences in general.
@@
 \end{equation}
-\highlighttext{This has been corrected, thanks for the careful catch of an embarassing mistake.}
+\highlighttext{This has been corrected, thanks for the careful catch of an embarrassing mistake.}
 

### 2018-03-09 r1doc/RebuttalTetrahelixUntwistV2.tex
yet another update

@@
 
-The author wishes to thank the reviewers for their careful and attentive work. Each comment is responded
+The author wishes to thank the reviewers for their careful and attentive work, that has
+significantly improved the paper. Each comment is responded
 to below, on a point-by-point basis.
@@
   strongly enough. To improve this, I have made some changes:
-... displays a continuum of tetrahelices optimal in a \bf{
+... displays a continuum of tetrahelices optimal \bf{
   in the sense of being
@@
  ``conincident'' $\rightarrow$ ``coincident''
- \highlighttext{Corrected--an embarassing mistake in my spelling correction software.}
+ \highlighttext{Corrected--an embarrassing mistake in my spelling correction software.}
  \item
@@
    \highlighttext {
-     In order to attempt to clarify the results of the paper I have added as the final subsection of the introduction the following summary of the contributions.
-\subsection{Summary of Results}
 The remainder of this  paper:
-\begin{itemize}
-\item Provides a new formulation for the BC helix that is more natural for engineers,
-\item Defines a concept of minimum maximum edge-length optimality and proves that all
+\begin{enumerate}
+\item provides a new formulation for the BC helix that is more natural for engineers,
+\item defines a concept of minimum maximum edge-length optimality that maintains
+  the structure as close to regularity as possible,
+  \item proves that all
     optimal tetrahelices are in fact triple helices,
-\item Provides formulae for construct optimal tetrahelices of different twists or for optimally
+\item provides formulae for constructing optimal tetrahelices of different twists or for optimally
     transforming a
-    robot from a twisted to a planar configuration,
-\item Gives a formula for the inradius of an optimal tetrahelix,
-\item Describes a completely planar tetrahlix (the \emph{equitetrabeam} useful as a structural beam or for apply standard robot gaits to a tetrahedral robot, and
-\item Discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
-\end{itemize}
+    robot from a twisted to a planar configuration in a way that maintains optimum regularity,
+\item gives a formula for the inradius of an optimal tetrahelix,
+\item describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
+  a structural beam or for applying standard robot gaits to a tetrahedral robot, and
+\item discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
+  \end{enumearate}
 }
@@
       I believe the theorems are all true (and verified by computer experimentation) and that the proofs
-      are rigorous. However, in deference to the reviewer I have attempted to express parts of them
-      more formally in several places. Unfortunately, it is beyond my ability to make them more completely formal
+      are rigorous. However, in deference to the reviewer I have significantly rewritten parts of them
+      more formally in several places. Unfortunately, it is beyond my ability to make them completely formal
       in the space allowed in this paper. I hope readers will find them convincing at the available length.
@@
 design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
-\bf{and a video[9]},
+\bf{and a video\cite{tetrahelixvideo}},
 from which figs. 1 and 2 and later figures in this paper 
@@
     “Conincident” should be “coincident”
+    \highlighttext{This has been corrected, thank you.}
 \item

### 2018-03-09 r1doc/TetrahelixUntwistV2.tex
yet another update

@@
 
-\Cref{fig:series} displays a continuum of tetrahelices optimal in a \highlighttext{in the sense of being
+\Cref{fig:series} displays a continuum of tetrahelices optimal \highlighttext{in the sense of being
 as regular as possible},
@@
 \begin{enumerate}
-\item Provides a new formulation for the BC helix that is more natural for engineers,
-\item Defines a concept of minimum maximum edge-length optimality and proves that all
+\item provides a new formulation for the BC helix that is more natural for engineers,
+\item defines a concept of minimum maximum edge-length optimality that maintains
+  the structure as close to regularity as possible,
+  \item proves that all
     optimal tetrahelices are in fact triple helices,
-\item Provides formulae for constructing optimal tetrahelices of different twists or for optimally
+\item provides formulae for constructing optimal tetrahelices of different twists or for optimally
     transforming a
-    robot from a twisted to a planar configuration,
-\item Gives a formula for the inradius of an optimal tetrahelix,
-\item Describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
+    robot from a twisted to a planar configuration in a way that maintains optimum regularity,
+\item gives a formula for the inradius of an optimal tetrahelix,
+\item describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
   a structural beam or for applying standard robot gaits to a tetrahedral robot, and
-\item Discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
+\item discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
 \end{enumerate}
@@
 
-Now that \highlighttext{it is provent that the} axes are coincident and parallel and that the pitches
+Now that \highlighttext{it is proven that the} axes are coincident and parallel and that the pitches
 are the same for all helices, any optimum tetrahelix can
@@
 $\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple} for the three helices
-(the relationships are developed in \cref{eqrhoopt}) these are denoted with a $c$ subscript to show
+ these are denoted with a $c$ subscript to show
 they are dependent on the color ($c \in \{R,B,Y\}$).
+In \cref{sec:parameterizing}, we give a more specific version (\cref{eqrhoopt}) of this formula which
+generates optimal tetrahelices.
 Since any optimal tetrahelix is described by \cref{eq:triple},
@@
 
-\highlighttext{This equation does not completely explain} the  relationships beteween
-$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple}.
-In \cref{sec:parameterizing}, we give a more specific version of this formula which
-generates optimal tetrahelices.
 \highlighttext{Observe} that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,

### 2018-03-09 r1doc/TetrahelixUntwistV2.tex
yet another update

@@
   these tetrahedra as structural members creates an attractive and
-  inherently rigid space frame, and therefore interesting to architects,
+  inherently rigid space frame, and therefore is interesting to architects,
   mechanical engineers, and roboticists.  A formula is developed that matches the
@@
   parameters that give proven edge-length minimax-optimal tetrahelices
-  are given, defining a continuum of optimum tetrahelices of varying curvature.
+  are given,
+  \highlighttext{
+  allowing transformation through a continnum of 
+  of optimum tetrahelices of varying curvature while maximizing regularity.}
   The endpoints of this continuum are the BC helix and
@@
 for this to be possible. An example of such a machine is a Tetrobot,
-shown in \cref{fig:tetrobot}.
+shown in figs. [4] and \cref{fig:tetrobot}.
 
@@
 \highlighttext{Engineers} would like to design nearly regular tetrahelices with a formula that
-gives the vertices in space. Eventually, \highlighttext{this would be done}
+gives the vertices in space. Ideally, \highlighttext{this would be done}
 by choosing the lengths of a small set of members.
@@
 
-This allows us to redefine:
+This \highlighttext{allows \cref{eq:colored} to be rewritten}:
 
@@
 Suppose that all three rails do not have the same pitch.
-Let $n1$ be a node on a  shortest edge between
-two rails. Let $n2$ be a node on a different rail.
-Increasing the difference $\|n2-n1\|$, increasing edge lengths $T(n_1,n_2)$
+Let $n_1$ be a node on a  shortest edge between
+two rails. Let $n_2$ be a node on a different rail.
+Increasing the difference $\|n_2-n_1\|$ increases edge lengths $T(n_1,n_2)$
 without bound,
@@
 \highlighttext{ will cause }
-many of these lengths will be the same.
+many of these lengths to be the same.
 In fact, it is possible that there
@@
     perturbed tetrahelix.
-    \highlighttext{The minimax of $R(B)$ is greater than the minimax of $R(A)$} since there is a
+    \highlighttext{The minimax of $B$ is greater than the minimax of $A$: $R(B) > R(A) $} since there is a
     single rail length which cannot be both greater
@@
   1 = \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
-  &  \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r))  \text{ ,} \\
+  &  \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || \text{ ,} \\
   \end{split}
@@
 
-Since the axes are parallel, may define the \emph{inradius}, represented by the letter $i$, of a
+Since the axes are parallel, one may define the \emph{inradius}, represented by the letter $i$, of a
 tetrahelix to be the radius of the largest

### 2018-03-09 r1doc/TetrahelixUntwistV2.tex
yet another update

@@
   \highlighttext{
-  allowing transformation through a continnum of 
+  allowing transformation through a continuum of 
   of optimum tetrahelices of varying curvature while maximizing regularity.}
@@
 \item gives a formula for the inradius of an optimal tetrahelix,
-\item describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
-  a structural beam or for applying standard robot gaits to a tetrahedral robot, and
+\item describes a completely planar tetrahelix (the \emph{equitetrabeam}) useful as
+  a structural beam or for applying standarod robot gaits to a tetrahedral robot, and
 \item discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
@@
 Having not yet investigated in the general case the relationships beteween
-$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple} for the three helices
+$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple} for the three helices,
  these are denoted with a $c$ subscript to show
 they are dependent on the color ($c \in \{R,B,Y\}$).
-In \cref{sec:parameterizing}, we give a more specific version (\cref{eqrhoopt}) of this formula which
+In \cref{sec:parameterizing}, we give a more specific version (\cref{eq:general}) of this formula which
 generates optimal tetrahelices.
@@
 
-\section{Contact and Getting Involved}
+\subsection{Contact and Getting Involved}
 
@@
 \href{mailto:read.robert@gmail.com}{read.robert@gmail.com}.
+
+\subsection{Acknowledgment}
+
+\highlighttext{
+The author thanks the reviewers for their useful suggestions.
+}
 

### 2018-03-09 r1doc/RebuttalTetrahelixUntwistV2.tex
yet another update

@@
 Most editors do not prefer passive sentences in general.
-      Nonetheless, in deference to the reviewer, I have searched the paper for each use of the ``we'' and
+      Nonetheless, in deference to the reviewer, I have searched the paper for each use of the word ``we'' and
       removed it in most, but not all cases.
@@
  \highlighttext{Corrected--an embarrassing mistake in my spelling correction software.}
- \item
 \item In page 3, after the eq. (4)
@@
 
+   \highlighttext{
+     In order to address this, I have added the sentence below at the end of the introduction.
+     }
+
    \highlighttext {
@@
 \item discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
-  \end{enumearate}
+  \end{enumerate}
 }
@@
 
-Minors)
+Minors:
 
@@
 
-\section{Conclusions}\label{conclusions}
-
 \bibliographystyle{asmems4}

### 2018-03-09 r1doc/TetrahelixUntwistV2.tex
yet another update

@@
 Tetrobot\cite{readglussbot,TetrobotBook} uses the regularity of
-this geometry to make a tentacle-like robot that can crawl like a slug
-or mollusk.  These modular robotic systems use mechanical actuators which can
+this geometry to make a tentacle-like robot that can crawl like a mollusk.
+These modular robotic systems use mechanical actuators which can
 change their length, connected by special joints,
@@
 follow purely regular mathematical models such as the Boerdijk-Coxeter
-helix or the Octet Truss\cite{richard1961synergetic}.
+helix or the octet truss\cite{richard1961synergetic}.
 
@@
 for this to be possible. An example of such a machine is a Tetrobot,
-shown in figs. [4] and \cref{fig:tetrobot}.
+shown in fig. 4 and \cref{fig:tetrobot}.
 
@@
   a structural beam or for applying standarod robot gaits to a tetrahedral robot, and
-\item discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
+\item discusses the continuum of optimal tetrahelices between the BC helix and equitetrabeam.
 \end{enumerate}
@@
          \end{bmatrix}$
-for a counter-clockwise BC Helix in a right-handed coordinate system:
+for a counter-clockwise BC helix in a right-handed coordinate system:
 \begin{equation}
@@
 the red, yellow, and blue helices. In this figure,
-these rail helices have been rendered at a slightly higher radius than the vertices for clarity;
+these \highlighttext{continuous} rail helices have been rendered at a slightly higher radius than the vertices for clarity;
 in actuality, the maximum distance between the continuous, curved helix and the
@@
 As engineers and roboticists it is desirable to design tetrahelices that
-are slightly irregular that ``untwist'' the BC Helix in an optimal way.
+are slightly irregular that ``untwist'' the BC helix in an optimal way.
 For machines
@@
 $(\forall n_1,n_2 : T(n_1,n_2) > 0)$.
-For a BC Helix, $(\forall x,y : T(x,y) \neq \perp \Rightarrow T(x,y) = 1)$.
+For a BC helix, $(\forall x,y : T(x,y) \neq \perp \Rightarrow T(x,y) = 1)$.
 }
@@
 \highlighttext{
-  The ratio of the BC Helix is 1: $ R(H_{BC}) = 1$.
+  The ratio of the BC helix is 1: $ R(H_{BC}) = 1$.
   }
@@
 
-Since the axes are parallel, one may define the \emph{inradius}, represented by the letter $i$, of a
+Since the axes are parallel, one may define the \emph{inradius}, represented by \highlighttext{$r_{in}$}, of a
 tetrahelix to be the radius of the largest
@@
  Likewise, $\rho > \rho_{bc}$ generates
- a tetrahelix, but \highlighttext{its optimality has not proved or investigated} in that range.
+ a tetrahelix, but \highlighttext{its optimality has not been proved or investigated} in that range.
 
@@
 which goes to $0$ as $\rho$ approaches $0$ (the equitetrabeam.)
-As $\rho$ increase up to $\rho_{bc}$ the curvature increases smoothly until the BC Helix is reached.
+As $\rho$ increase up to $\rho_{bc}$ the curvature increases smoothly until the BC helix is reached.
 
@@
 using a linear interpolation between the optimal radius for the
-equitetrabeam and the BC Helix. This minimax optimum of this simpler
+equitetrabeam and the BC helix. This minimax optimum of this simpler
 approach was at most 1\% worse than the optimum computed by
@@
 It is proven there exists a continuum of minimax edge-length optimal tetrahelices
-having as one end the completely regular Boerdijk-Coxeter Helix and at the
+having as one end the completely regular Boerdijk-Coxeter helix and at the
 other end a completely untwisted tetrahelix with equilateral cross

### 2018-04-16 rfinaldoc/JMR-17-1184-paper.tex
removed highlights

--- 2018-03-09 r1doc/TetrahelixUntwistV2.tex
@@
 % \documentclass[review]{siamonline1116}
-\documentclass[twocolumn,10pt]{asme2ej}
+\documentclass[10pt,final]{journals-1.0/asme2ej}
 % \usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
@@
 
-\newcommand{\highlighttext}[1] {\textcolor{red}{#1}}
-
 % \usepackage{draftwatermark}
@@
 \title{Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix}
-\author{Robert L. Read
+\author{Robert L. Read, PhD
   \affiliation{
@@
   are given,
-  \highlighttext{
   allowing transformation through a continuum of 
-  of optimum tetrahelices of varying curvature while maximizing regularity.}
+  of optimum tetrahelices of varying curvature while maximizing regularity.
   The endpoints of this continuum are the BC helix and
   a structure of zero curvature, the \emph{equitetrabeam}.
- Only one out of three members in the system change their length \highlighttext{ to transform
-  the structure into }
+ Only one out of three members in the system change their length to transform
+  the structure into
   any point in the continuum.
@@
 useful to develop the mathematics of structures formed from tetrahedra
-where \highlighttext{one relaxes} regularity.
+where one relaxes regularity.
 
@@
 Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
-a term now commonly used. \highlighttext{This paper} reserves \emph{BC helix} to mean the purely
+a term now commonly used. This paper reserves \emph{BC helix} to mean the purely
 regular structure and use \emph{tetrahelix} to refer
@@
 be able to ``untwist'' it and to form a tetrahelix space frame that has a
-flat planar surface. By making length changes in a certain way, a \highlighttext{tetrahelix untwists} to form a \emph{tetrabeam} which has planar faces
+flat planar surface. By making length changes in a certain way, a tetrahelix untwists to form a \emph{tetrabeam} which has planar faces
 and has, for example, an equilateral triangular profile. This paper
@@
 design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
-\highlighttext{and a video\cite{tetrahelixvideo}},
+and a video\cite{tetrahelixvideo},
 from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
@@
 
-\Cref{fig:series} displays a continuum of tetrahelices optimal \highlighttext{in the sense of being
-as regular as possible},
+\Cref{fig:series} displays a continuum of tetrahelices optimal in the sense of being
+as regular as possible,
 which is the main result of this
@@
 By changing only the length of only one third of the members,
-\highlighttext{one} can dynamically untwist a physical Tetrobot
+one can dynamically untwist a physical Tetrobot
 forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane,
-as shown in figs. \highlighttext{4 and} 5.
+as shown in figs. 4 and 5.
 
 By untwisting the tetrahelix so that is has a planar surface resting on the ground,
-each vertex touching the ground \highlighttext{becomes} a foot or pseudopod. A robot can thus
+each vertex touching the ground becomes a foot or pseudopod. A robot can thus
 become a hexapod or $n$-pod Tetrobot, and the already well-developed approaches to
@@
 
-\highlighttext{
 The remainder of this  paper:
@@
 \end{enumerate}
-}
 
@@
 
-\highlighttext{Engineers} would like to design nearly regular tetrahelices with a formula that
-gives the vertices in space. Ideally, \highlighttext{this would be done}
+Engineers would like to design nearly regular tetrahelices with a formula that
+gives the vertices in space. Ideally, this would be done
 by choosing the lengths of a small set of members.
@@
 
-Ideally, \highlighttext{a simple formula would define} the vertices based on
+Ideally, a simple formula would define the vertices based on
 any curvature or pitch we choose. It is a goal of
@@
 In order to develop the continuum of slightly irregular tetrahelices,
-\highlighttext{a formula is needed}
+a formula is needed
 that gives us the vertices of just
@@
 
-In this formula, \highlighttext{integer} values of $n$ may be taken as a vertex number for one rail and used to compute
+In this formula, integer values of $n$ may be taken as a vertex number for one rail and used to compute
 its Cartesian
@@
 the red, yellow, and blue helices. In this figure,
-these \highlighttext{continuous} rail helices have been rendered at a slightly higher radius than the vertices for clarity;
+these continuous rail helices have been rendered at a slightly higher radius than the vertices for clarity;
 in actuality, the maximum distance between the continuous, curved helix and the
@@
 Note, in \cref{railanglefig}, the $z$-axis travel for one rail edge is denoted by $d$. In \cref{graycoxeter} and  \cref{eq:colored}, the variable
-$h$ is used for one third of the distance we name $d$. \highlighttext{The fact that $d = 3h$ is justified later}.
+$h$ is used for one third of the distance we name $d$. The fact that $d = 3h$ is justified later.
 In this paper, we assume the length of a rail
@@
 The $\vec{H}_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho_{bc}$ rather than $\theta_{bc}$.
-Intuitively, an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$ \highlighttext{is sought}.
+Intuitively, an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$ is sought.
 We expand 
@@
 \end{align*}
-\highlighttext{seeking} $2\pi$ in the numerator, add canceling terms...
+seeking $2\pi$ in the numerator, add canceling terms...
 \begin{align*}
@@
 \end{align*}
-\highlighttext{to} finally obtain:
+to finally obtain:
 \begin{equation}
@@
 
-This \highlighttext{allows \cref{eq:colored} to be rewritten}:
+This allows \cref{eq:colored} to be rewritten:
 
@@
 Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued).
-\highlighttext{It can now be asserted that} in \cref{fig:helixcomparison} the black helix winds at
+It can now be asserted that in \cref{fig:helixcomparison} the black helix winds at
 $\frac{3 \theta_{bc}}{\rho_{bc}} \approx 11.16 $ times the rate of a rail helix.
@@
 has been explored\cite{sadler2013periodic}. 
-\highlighttext{The next sections develop} slightly irregular edge lengths that support, for example,
+The next sections develop slightly irregular edge lengths that support, for example,
 a pitch of precisely 12
@@
 
-\highlighttext{
 As engineers and roboticists it is desirable to design tetrahelices that
@@
 one retains the greatest possible freedom of motion for the robot.
-}
-
-\highlighttext{
+
 This paper use the term \emph{tetrahelix} to mean any structure physically constructible of
@@
 For a BC helix, $(\forall x,y : T(x,y) \neq \perp \Rightarrow T(x,y) = 1)$.
-}
-
-\highlighttext{
+
 The ratio of the longest member in a testrahelix to the shortest is:
@@
 \end{equation}
-}
-
-\highlighttext{
+
  The ratio of the BC helix is 1: $ R(H_{BC}) = 1$.
-  }
-\highlighttext{
+
 A \emph{triple helix} is three congruent helices that share an axis. The remainder of this
@@
 is the result of the \cref{sec:parameterizing}.
-}
-
-\highlighttext{
+
 \begin{theorem}
@@
 \end{theorem}
-}
 
 \begin{proof}
-\highlighttext{  
 Suppose that all three rails do not have the same pitch.
@@
 which is not physically realizable.
-}
-
-\highlighttext{  
+
 Similarly, if the axes are not parallel, for any length $\lambda$ there is an edge of $T(x,y)$
 such that $T(x,y) > \lambda$, which is not physical.
-}
+
 \end{proof}
 
-\highlighttext{
 \Cref{thm:pitchandparallel} justifies talking about the singular
@@
 \end{equation}
-}
-
-\highlighttext{
+
 \begin{lemma}
@@
 \end{proof}
-}
-
-In the proof, below, \highlighttext{it is} useful to consider projection diagrams that are the axial projection
+
+In the proof, below, it is useful to consider projection diagrams that are the axial projection
 of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram,fig:wobble} are examples
@@
   edges in a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
-  regular polygon of 3 or more sides, \highlighttext{otherwise} they fill in a complete circle.
+  regular polygon of 3 or more sides, otherwise they fill in a complete circle.
   \label{lemma:ngon}
@@
   All points lying on a helix projected along the axis lie on a circle in the $XY$-plane.
-\highlighttext{(By \cref{lemma:notpoint}, the circle is not a simple point.)}
+(By \cref{lemma:notpoint}, the circle is not a simple point.)
   Helices are periodic in the $z$ dimension modulo $2\pi$.
@@
   $2\pi/\rho$ is rational if and only if $\rho = a\pi/b$, where $a$ and $b$ are integers
-  and, \highlighttext{assume} without loss of generality, $a$ and $b$ are coprime.
+  and, assume without loss of generality, $a$ and $b$ are coprime.
   Since $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
@@
   so long as there is a phase
-  term in the defintion of the helix, as in \cref{eq:colored}. \highlighttext{That the
-  radii must be eqivalent is shown later}.
+  term in the defintion of the helix, as in \cref{eq:colored}. That the
+  radii must be eqivalent is shown later.
 
@@
 
-  \highlighttext{By symmetry} without loss of generality, define the Red helix to have its axis on the $z$-axis.
+  By symmetry without loss of generality, define the Red helix to have its axis on the $z$-axis.
   Since there must be at least one Red-to-Yellow or a Red-to-Blue edge that is either a minimum or a maximum,
@@
 
-Now that \highlighttext{it is proven that the} axes are coincident and parallel and that the pitches
+Now that it is proven that the axes are coincident and parallel and that the pitches
 are the same for all helices, any optimum tetrahelix can
-be generated with a \highlighttext{simple} equation for helices:
+be generated with a simple equation for helices:
 \begin{equation}
@@
 which would be much more complicated if the axes where not coincident.
-\highlighttext{
 Having not yet investigated in the general case the relationships beteween
@@
 \]
-}
-
-\highlighttext{Observe} that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
+
+Observe that when $\alpha = 0$, the helices are degenerate, having curvature of $0$,
 but because of the $\phi_c$ term, they are not collinear.
@@
 where the two-hop length is at least the one-hop length.
-However, \highlighttext{generating} the three helices with \cref{eq:triple}
-\highlighttext{ will cause }
+However, generating the three helices with \cref{eq:triple}
+ will cause
 many of these lengths to be the same.
@@
 \begin{proof}
-To prove this theorem, \highlighttext{one may} exhibit a symmetric tetrahelix (not yet shown to be optimal) which
+To prove this theorem, one may exhibit a symmetric tetrahelix (not yet shown to be optimal) which
 happens to be a triple helix, that has
@@
 Observe that although the formula for the
-radii of such a triple helix \highlighttext{has not yet been developed},
+radii of such a triple helix has not yet been developed,
 there are some values for $r$ and $\alpha$, and $\phi$
@@
 for which all the three helices are symmetrically and evenly spaced. Furthermore,
-\highlighttext{one} can choose these values such that the three rail edges are of length $1$ and
+one can choose these values such that the three rail edges are of length $1$ and
 so that the one-hop lengths are also all of length $1$, and the two-hop lengths
@@
 Therefore, a tetrahelix with different radii is not as optimal as some two-class 
-tetrahelix generated by \cref{eq:triple}, \highlighttext{ and so by \cref{eq:optdef}} is not optimal.
-
-\highlighttext{Although \cref{thm:eventhirds} which asserts} that a two-class tetrahelix is optimal
-\highlighttext{has not yet been proven}, it suffices to show that there
+tetrahelix generated by \cref{eq:triple}, and so by \cref{eq:optdef} is not optimal.
+
+Although \cref{thm:eventhirds} which asserts that a two-class tetrahelix is optimal
+has not yet been proven, it suffices to show that there
 exists such a better tetrahelix to show that different radii imply a suboptimal
@@
 
-Now that \highlighttext{is proven} that on any optimal tetrahelix the vertices
-are on helices of the same axes and pitch, \highlighttext{observe} that the vertices 
+Now that is proven that on any optimal tetrahelix the vertices
+are on helices of the same axes and pitch, observe that the vertices 
 of any optimal tetrahelix will lie on a cylinder, or a circle when the axis dimension
@@
 of a tetrahelix as the radius of the cylinder.
-\highlighttext{This allows }
+This allows
 the harder proof about where vertices occur along the $z$-axis.
 
-\highlighttext{In fact,} the vertices must be distributed in even thirds
+In fact, the vertices must be distributed in even thirds
  along the $z$-axis as they are in the regular BC helix.
- \highlighttext{Note that it is already proven that} the rail
+ Note that it is already proven that the rail
  lengths are equal in any optimal tetrahelix.
@@
     perturbed tetrahelix.
-    \highlighttext{The minimax of $B$ is greater than the minimax of $A$: $R(B) > R(A) $} since there is a
+    The minimax of $B$ is greater than the minimax of $A$: $R(B) > R(A) $ since there is a
     single rail length which cannot be both greater
@@
 perhaps the clearest choice is to build formulae that takes as their
-input the ``rail angle'' $\rho$. \highlighttext{Define} $\rho$ to be the angle
+input the ``rail angle'' $\rho$. Define $\rho$ to be the angle
 formed in the X,Y plane with origin $O$: $\angle \vec{H}(0,0) O \vec{H}(0,1)$ projecting out the
@@
 controls how far a rail edge of a tetrahelix deviates from being
-parallel with the axis, or the ``twistiness'' of the tetrahelix. \highlighttext{Use }
+parallel with the axis, or the ``twistiness'' of the tetrahelix. Use
 the parameter $\chi = 1$ to indicate a chirality of counter-clockwise,
-and $\chi = -1$ for clockwise. \highlighttext{Take} our coordinate system to be right-handed.
+and $\chi = -1$ for clockwise. Take our coordinate system to be right-handed.
 
@@
 In choosing $\rho$, one greatly constrains $r$ and $d$, but does not completely
-determine both of them together, so \highlighttext{one must} treat both as additional parameters.
+determine both of them together, so one must treat both as additional parameters.
 
@@
 \begin{proof}
-By \cref{thm:eventhirds}, \highlighttext{one} can compute the (at most) three edge-lengths of an optimal
+By \cref{thm:eventhirds}, one can compute the (at most) three edge-lengths of an optimal
 tetrahelix by formulae universally quantified by $n$ and $c$:
@@
   \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}  &=
-  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ \highlighttext{k_{\rho}})}}
-       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+\highlighttext{j_{\rho}}) }} \text{.}
+  \frac{\sqrt{\frac{4}{9}  + r^2(g_{\rho}+ k_{\rho})}}
+       {\sqrt{\frac{1}{9} +r^2(f_{\rho}+j_{\rho}) }} \text{.}
   \end{split}       
@@
 
-\highlighttext{
   By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram}
@@
 radius $r$ is always negative, for any $\rho \leq \rho_{bc}$.
-}
+
 When the rail angle approaches
@@
 as the radius goes up, and 
-\highlighttext{one minimizes} the maximum edge-length ratio by choosing the largest radius
-up until one-hop $= 1$, the rail-edge length. If \highlighttext{one} attempted to further increase the radius
-\highlighttext{the tetrahelix} would not be optimal,
+one minimizes the maximum edge-length ratio by choosing the largest radius
+up until one-hop $= 1$, the rail-edge length. If one attempted to further increase the radius
+the tetrahelix would not be optimal,
 because the ratio $\frac{\text{two-hop}(r)}{1}$ would become the
@@
 
-Therefore, \highlighttext{one decreases} the minimax length
-of the whole system as the radius \highlighttext{increases}
+Therefore, one decreases the minimax length
+of the whole system as the radius increases
 up to the point that the shorter, one-hop distance is equal to the rail-length, $1$.
@@
 
-\highlighttext{This leads to} a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \cref{railangle}:
+This leads to a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \cref{railangle}:
 
@@
 \end{equation}
-which \highlighttext{is expanded to:}
+which is expanded to:
 \begin{equation}
 %%  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
-  d_{opt}^2 = 1 - \frac{16(\sin{ \rho / 2})^2}{\highlighttext{\frac{9}{2}} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
+  d_{opt}^2 = 1 - \frac{16(\sin{ \rho / 2})^2}{\frac{9}{2} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
 \end{equation}
@@
 %%  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
-    d_{opt} = \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + \highlighttext{\frac{9}{2}} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}  \text{ .}  \numberthis  \label{dopt}  \\      
-\end{equation}
-
-Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, \highlighttext{one} can
+    d_{opt} = \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + \frac{9}{2} ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}  \text{ .}  \numberthis  \label{dopt}  \\      
+\end{equation}
+
+Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, one can
 construct a minimax optimal tetrahelix where $0 \leq \rho \leq \rho_{bc}$.
@@
 
-Since the axes are parallel, one may define the \emph{inradius}, represented by \highlighttext{$r_{in}$}, of a
+Since the axes are parallel, one may define the \emph{inradius}, represented by $r_{in}$, of a
 tetrahelix to be the radius of the largest
@@
 
-From this equation, with the help of symbolic computation, \highlighttext{one may} observe that the inradius of the BC helix of unit rail length is $r_{in(\rho_{bc})} = \frac{3}{10\sqrt{2}} \approx 0.21$.
+From this equation, with the help of symbolic computation, one may observe that the inradius of the BC helix of unit rail length is $r_{in(\rho_{bc})} = \frac{3}{10\sqrt{2}} \approx 0.21$.
 
@@
 an equilateral triangle of unchanging orientation, as shown in \cref{fig:equitetrabeam} and at the rear of \cref{fig:series}.
-We call this the \emph{equitetrabeam}\highlighttext{, a portmanteau of ``equilateral tetrahedral beam''}.
+We call this the \emph{equitetrabeam}, a portmanteau of ``equilateral tetrahedral beam''.
 It is not possible to generate an equitetrabeam from 
@@
 \begin{proof}
-Choosing $d = 1$ and $\rho = 0$ \highlighttext{one can} use \cref{eqrhoopt} to find the radius of 
+Choosing $d = 1$ and $\rho = 0$ one can use \cref{eqrhoopt} to find the radius of 
 optimal minimax difference. Substituting into  \cref{eq:general} and setting one-hop\footnote{Before developing
@@
 
-To the extent that \highlighttext{one values} tetrabeams (that is, tetrahelices with a rail angle of $0$,
+To the extent that one values tetrabeams (that is, tetrahelices with a rail angle of $0$,
 and therefore zero curvature) as mathematical or engineering objects,
-\highlighttext{this paper} has motivated the development of $\vec{H}_{general}$ as a transformation of $\vec{V}(n)$ defined by
+this paper has motivated the development of $\vec{H}_{general}$ as a transformation of $\vec{V}(n)$ defined by
 \cref{graycoxeter} from Gray and Coxeter.
@@
 
-\highlighttext{Observe} that  \cref{eqrhoopt,dopt} compute $r_{opt}$ and $d_{opt}$ which
+Observe that  \cref{eqrhoopt,dopt} compute $r_{opt}$ and $d_{opt}$ which
 create an optimal tetrahelix for any rail angle $\rho$ between $0$, which
@@
  Likewise, $\rho > \rho_{bc}$ generates
- a tetrahelix, but \highlighttext{its optimality has not been proved or investigated} in that range.
+ a tetrahelix, but its optimality has not been proved or investigated in that range.
 
@@
 \cref{pitcheqn} can be easily solved numerically with a Newton-Raphson
-solver, as \highlighttext{is done} on our website.
+solver, as is done on our website.
 For a pitch at least $ p \geq \frac{3  \sqrt{2}  \pi}{\sqrt{5}\rho_{bc}} \approx 9.64 $,
@@
 and rail length equivalent within this continuum.\footnote{Before
-deriving  \cref{eqrhoopt}, \highlighttext{a continuum was created} by
+deriving  \cref{eqrhoopt}, a continuum was created by
 using a linear interpolation between the optimal radius for the
@@
 selecting appropriate edge lengths generated from the same equation. 
-A machine, such as \highlighttext{the} Tetrobot or a variable-geometry truss \highlighttext{ depicted in \cref{fig:tetrobot}}, that can change
+A machine, such as the Tetrobot or a variable-geometry truss  depicted in \cref{fig:tetrobot},
+that can change
 the length of some of its members by $16\%$ can thus twist and untwist itself.
 A completely regular Tetrobot can untwist itself to create a planar
-face on the ground for locomotion \highlighttext{via standard gaits}.
+face on the ground for locomotion via standard gaits.
 With a numeric solution, a designer may choose
@@
 
-\highlighttext{
 The author thanks the reviewers for their useful suggestions.
-}
 
@@
 \end{document}
-
-TODO:
-
-** Add the Mathematica notebook to the github repo (after cleaning up) and reference. -- done
-** Redo the proof
-** make sure our diagrams are right-handed.
-
-May want to read this article:
-
-http://ieeexplore.ieee.org/abstract/document/7759811/?reload=true
-
-http://epubs.siam.org/toc/sjaabq/1/1
-
-Reread everything, especially the new parts.
-
-Note:
-
-I do not believe it is worth providing a proof of (b or 2b) result of lemma ngon.
-However, here are my notes if it becomes important:
-
-Basically by using the distributive nature of mod and the definition of a helix,
-the cardinality of the set can remove the PI factor in the sin(x) = sin(x mod 2PI).
-Then we know that a, b, and 2 are integers.  We can provide the cardinality is
-the residue of [n*a mod 2b], which becomes an integer modulus operation.
-if a = k2, you can factor out 2, which has no bearing on cardinality. the
-cardinality is the | { nk mod b } | = b.
-
-If a is odd, it is | { n(2k+1) mod 2b) | = 2b.  How do we know we can
-  reach each integer < 2b?  By Bezout's Identity there exists x,y, nax + yc = gcd(a,c).
-  Take c = 2b.
-  But gcd(a,c) = 1, because they are relatively prime. Take but
-  So we have ax + y2b = 1.  But (ax + y2b) mod 2b = ax mod 2b. Now  (nax) mod 2b = n,
-  up until y = 2b -1.

### 2018-04-16 rfinaldoc/JMR-17-1184-text-only.tex
removed highlights

--- 2018-04-16 rfinaldoc/JMR-17-1184-paper.tex
@@
 has been explored\cite{sadler2013periodic}. 
-The next sections develop slightly irregular edge lengths that support, for example,
+The next sections develop} slightly irregular edge lengths that support, for example,
 a pitch of precisely 12
@@
 one minimizes the maximum edge-length ratio by choosing the largest radius
-up until one-hop $= 1$, the rail-edge length. If one attempted to further increase the radius
+up until one-hop $= 1$, the rail-edge length. If \highlighttext{one} attempted to further increase the radius
 the tetrahelix would not be optimal,

### 2018-04-19 rfinaldoc/JMR-17-1184-paper.tex
final

@@
   \right ],
-\end{equation}
-\text{where: \qquad}
+\text{ \qquad where: \qquad}
   \begin{tabular}{l}
@@
   \end{tabular}      
+\end{equation}
 
@@
   \right ],
-\end{equation}
-\text{where:  \qquad}
+\text{ \qquad where:  \qquad}
   \begin{tabular}{l}
@@
   \right ],
-\end{equation}
-\text{where: \qquad}
+\text{\qquad where: \qquad}
   \begin{tabular}{l}
@@
 them to be parallel to the $z$ axis. Define the radius of the tetrahelix:
-\begin{multline*}
-rad(T) = \text{the radius of the smallest cylinder} \\
-\text{which contains all of nodes of the tetrahelix } T
-\end{multline*}
+\begin{align*}
+rad(T) = \text{the radius of the smallest cylinder which contains all of nodes of the tetrahelix } T
+\end{align*}
 Define a \emph{minimax edge-length optimal tetrahelix} or just an
@@
   \right ],
-\end{equation}
-\text{where: \qquad}
+\text{\qquad where: \qquad}
 \begin{tabular}{l}
@@
 \end{tabular}
+\end{equation}
 which would be much more complicated if the axes where not coincident.
@@
   \label{eq:general}  
-\vec{H}_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) = \\ 
+\vec{H}_{general}(\chi,n,c,\rho,d_{\rho},r_{\rho}) =  
  \left [
@@
    \end{split}
-\end{equation}  
-\text{where: \qquad} 
+\text{\qquad where: } 
 \begin{tabular}{l}
@@
 \end{tabular}
+\end{equation}
 
@@
   \begin{split}
-  1 = \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
-  &  \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || \text{ ,} \\
+  1 = \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - 
+  \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || \text{ ,} \\
   \end{split}
@@
   \begin{split}  
-  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
-  &  \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{ and,} \\
+  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - 
+   \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{\qquad and,} \\
   \end{split}  
@@
   \begin{split}    
-  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
-  &  \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \text{ .}\\
+  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - 
+   \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \text{ .}\\
   \end{split}  
@@
   %% Formula above checks at sqrt(8/27), 1, 0, and rho_bc, h_bc, r_bc.
-  \text{one-hop}  = \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} 
-\end{equation}
-
-where: $  d_{\rho}^2 = 1 - 4 r^2 (\sin( \rho / 2)^2$.
+  \text{one-hop}  = \sqrt{\frac{d_{\rho}^2}{9} + r^2(\sin^2(\rho/3 + \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \text{\qquad where: \qquad}   d_{\rho}^2 = 1 - 4 r^2 (\sin( \rho / 2)^2.
+\end{equation}
 
@@
   1 =  \sqrt{
-    \begin{tabular}{ccc}
-    $  \frac{1}{9} $ & + & $ r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} \; \;+ $\\
-$      \sin^2(\rho/3+ \frac{2\pi}{3}) $ & + & $ (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2) $
-    \end{tabular}
+      \frac{1}{9}   +   r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} \; \;+ \sin^2(\rho/3+ \frac{2\pi}{3}) + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2) 
     }

### 2018-04-19 rfinaldoc/JMR-17-1184-paper.tex
text only

@@
 \usepackage{color}
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+
+\fancyhead{} % clear all header fields
+\renewcommand{\headrulewidth}{0pt} % no line in header area
+\fancyfoot{} % clear all footer fields
+\lfoot{JMR-17-1184}
+\cfoot{\thepage}           % page number in "outer" position of footer line
+\rfoot{Read}
 
@@
 
-R.W. Gray's website\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in a more accessible form, gives the Cartesian coordinates $\begin{bmatrix}
+R.W. Gray's website\cite{graytetrahelix}, repeating a formula by Coxeter\cite{coxeter1985simplicial} in a more accessible form, gives the Cartesian coordinates in the form: $\begin{bmatrix}
            x \\
@@
   \centering
-     \includegraphics[width=0.45\textwidth]{figures/edge-diagram.png}
+     \includegraphics[width=0.65\textwidth]{figures/edge-diagram.png}
      \caption{Edge Naming}
@@
      \centering
-     \includegraphics[width=0.45\textwidth]{figures/EquitetrabeamCloseUp.png}
+     \includegraphics[width=0.65\textwidth]{figures/EquitetrabeamCloseUp.png}
      \caption{Equitetrabeam}
@@
 
-The Tetrobot Project:\\  
+The Tetrobot Project:  
 \url{http://pubinv.github.io/tetrobot/} is part of Public Invention,

### 2018-04-19 rfinaldoc/JMR-17-1184-text-only.tex
text only

--- 2018-04-16 rfinaldoc/JMR-17-1184-paper.tex
@@
 
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+
+\fancyhead{} % clear all header fields
+\renewcommand{\headrulewidth}{0pt} % no line in header area
+\fancyfoot{} % clear all footer fields
+\cfoot{\thepage}           % page number in "outer" position of footer line
+
 % \usepackage{float}
@@
 % \usepackage{draftwatermark}
+
+\usepackage{setspace}
+\doublespacing
 
@@
   \centering
-     \includegraphics[width=0.45\textwidth]{figures/BCHelixCloseUp.png}
+     %% \includegraphics[width=0.45\textwidth]{figures/BCHelixCloseUp.png}
      \caption{BC Helix Close-up (partly along axis)}
@@
   \centering
-     \includegraphics[width=0.45\textwidth]{figures/VerticalCloseUp.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/VerticalCloseUp.png}
      \caption{BC Helix Close-up (orthogonal)}
@@
   \centering
-     \includegraphics[width=0.45\textwidth]{figures/TetrahelixSeries2.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/TetrahelixSeries2.png}
      \caption{A Continuum of Tetrahelices}
@@
   \centering
-     \includegraphics[width=0.5\textwidth]{figures/MedCantedCropped.png}
+%%     \includegraphics[width=0.5\textwidth]{figures/MedCantedCropped.png}
      \caption{7-Tet Tetrobot in relaxed, or BC helix configuration}
-     \includegraphics[width=0.5\textwidth]{figures/EquitetrabeamCropped.png}
+%%     \includegraphics[width=0.5\textwidth]{figures/EquitetrabeamCropped.png}
      \caption{The Equitetrabeam: Fully Untwisted 7-Tet Tetrobot in Hexapod Configuration}
@@
   \centering
-     \includegraphics[width=0.45\textwidth]{figures/Unified.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/Unified.png}
      \caption{Rail helices (H) vs. Coxeter/Gray helix (V) }
@@
      \centering
-     \includegraphics[width=0.45\textwidth]{figures/RailAngleGeometry.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/RailAngleGeometry.png}
      \caption{Rail Angle Geometry}
@@
      \centering
-     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram2.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram2.png}
      \caption{Wobble Vectors from Non-Coincident Axes}
@@
   \centering
-     \includegraphics[width=0.45\textwidth]{figures/edge-diagram.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/edge-diagram.png}
      \caption{Edge Naming}
@@
      \centering
-     \includegraphics[width=0.45\textwidth]{figures/EquitetrabeamCloseUp.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/EquitetrabeamCloseUp.png}
      \caption{Equitetrabeam}
@@
      \centering
-     \includegraphics[width=0.45\textwidth]{figures/PartialDerivativeDiagram.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/PartialDerivativeDiagram.png}
      \caption{Partial Derivative against $\rho$ and $r$: $ \frac{\partial \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}}{\partial \rho, r} $ }
@@
      \centering
-     \includegraphics[width=0.45\textwidth]{figures/AxialView.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/AxialView.png}
      \caption{Axial view of a BC-Helix}
@@
      \centering
-     \includegraphics[width=0.45\textwidth]{figures/GeneralProjectionDiagramV2.png}
+%%     \includegraphics[width=0.45\textwidth]{figures/GeneralProjectionDiagramV2.png}
      \caption{General One-hop Projection Diagram}
@@
 
+\section{Table Caption List}
+
+No tables are used in this paper.
+
+\section{Figure Caption List}
+
+\begin{enumerate}
+\item
+  BC Helix Close-up (partly along axis)
+\item
+  BC Helix Close-up (orthogonal)
+\item
+  A Continuum of Tetrahelices
+\item
+  7-Tet Tetrobot in relaxed, or BC helix configuration
+\item
+  The Equitetrabeam: Fully Untwisted 7-Tet Tetrobot in Hexapod Configuration
+\item
+  Rail helices (H) vs. Coxeter/Gray helix (V)
+\item
+  Rail Angle Geometry
+\item
+  Wobble Vectors from Non-Coincident Axes
+\item
+  Edge Naming
+\item
+  Equitetrabeam
+\item
+  Partial Derivative against $\rho$ and $r$: $ \frac{\partial \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}}{\partial \rho, r} $
+\item
+  Axial view of a BC-Helix
+\item
+  General One-hop Projection Diagram
+\end{enumerate}
+
 \end{document}

### 2018-04-19 rfinaldoc/JMR-17-1184-paper.tex
final2

@@
 \end{equation}
-
 Note that $\theta_{bc}$ is approximately $0.37 \cdot 2 \pi$ radians or  $131.81$ degrees.
@@
 \end{equation}
-
 and $n$ represents each integer numbered vertex in succession on the $z$-axis.
@@
 \end{equation}
-
 In this formula, integer values of $n$ may be taken as a vertex number for one rail and used to compute
@@
 \end{equation}  
-
 This allows \cref{eq:colored} to be rewritten:
-
 %% Actually, I am not sure if this is a clearer formulation...it might be, and need to put it in general!!!
@@
 \end{equation}
-
 Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued).
@@
 \end{equation}
-
 The pitch of the Boerdijk-Coxeter helix of edge length $1$ is the length of three tetrahedra times
@@
 \end{equation}
-
 The pitch is less than the number of tetrahedra because the tetrahedra
@@
 \end{equation}
-
  The ratio of the BC helix is 1: $ R(H_{BC}) = 1$.
@@
 \end{equation}
-
 \begin{lemma}
@@
 \end{equation}  
-
 $\vec{H}_{general}$ forces the user to select three values satisfying \cref{railangle}: $\rho$, $r_{\rho}$, and $d_{\rho}$.
@@
 \end{equation}
-
 %% so we substitute:
@@
 %% \end{align*}
-
 By similar algebra and trigonometry:
@@
 \end{equation}
-
 By definition of minimax edge length optimality \cref{eq:optdef}, we are trying to minimize:
@@
 \end{equation}
-
 We know that both one-hop($r$) and two-hop($r$) increase monotonically and continuously with increasing $r$.
@@
 \end{equation}
-
 Then:
@@
 \end{equation}
-
   By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram}
@@
 equate one-hop to $1$ to find the optimum radius:
-
 \begin{equation}
@@
 from which it follows that:
-
 \begin{equation}
@@
 \end{equation}
-
 This leads to a formula for $ d_{opt} $ computed from $\rho, r_{opt}$ via the rail angle equation \cref{railangle}:
-
 \begin{equation}
@@
 \end{equation}
-
 Thus, by computing $r_{opt}$  and $d_{opt}$ as a function of $\rho$ from this equation, one can
@@
 \begin{corollary}
-  The equitetrabeam with minimum maximum edge ratio is produced
-  \newline by $\vec{H}_{general}$ when $ r = \sqrt{\frac{8}{27}} $ and the longest member is $\frac{2}{\sqrt{3}}$,
+  The equitetrabeam with minimum maximum edge ratio is produced by $\vec{H}_{general}$ when $ r = \sqrt{\frac{8}{27}} $ and the longest member is $\frac{2}{\sqrt{3}}$,
   which is less than $16\%$ longer

### 2018-04-19 rfinaldoc/JMR-17-1184-text-only.tex
final2

@@
 \end{equation}
-
 The ratio of the BC helix is 1: $ R(H_{BC}) = 1$.
@@
 \end{equation}  
-
 This syntax just represents the Euclidean distance between vertices. Thus:
@@
 \end{equation}
-
 By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram}

### 2018-05-08 rfinaldoc/JMR-17-1184-paper.tex
hopefully final final

@@
     Founder, Public Invention \\
+    1709 Norris Dr. \\
     Austin, TX, 78704 \\
@@
   pitch allows optimal tetrahelices of any pitch to be designed. 
-  An interactive tool for such design and experimentation is provided: \url{https://pubinv.github.io/tetrahelix/}.
+  An interactive tool for such design and experimentation is provided.
   A formula for the inradius of optimal tetrahelices is given.
@@
 omni-triangulated space frame.
-Then imagine that each static edge is replaced with an
-actuator that can dynamically become shorter or longer in response to electronic control,
-and the vertices are joints that support sufficient angular displacement
-for this to be possible. An example of such a machine is a Tetrobot,
-shown in fig. 4 and \cref{fig:tetrobot}.
 
@@
 
+If each static edge is replaced with an
+actuator that can dynamically become shorter or longer in response to electronic control,
+and the vertices are joints that support sufficient angular displacement
+for this to be possible, a moving robot named the Tetrobot is created as 
+shown in fig. 4 and \cref{fig:tetrobot}.
 Trusses and space frames remain an important design field in
